### 2018-05-22 VV570/HW1/assignment.tex
add ex2,3

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Introduction to Numerical Analysis \\ HW1 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yu Cang \\ 018370210001} % Your name

\date{\normalsize\today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title

%----------------------------------------------------------------------------------------
%	PROBLEM 1
%----------------------------------------------------------------------------------------

\section{Metric Space}

%----------------------------------------------------------------------------------------
%	PROBLEM 2
%----------------------------------------------------------------------------------------

\section{Continuity}

\begin{enumerate}
\item $y=\frac{1}{x}$ is continuous over $(0, +\infty)$, but not uniform continuous.
      \begin{proof}
      	Let $x_1 = \frac{1}{n+1}$,  $x_2 = \frac{1}{n}$. 
      	Then $\lim\limits_{n \rightarrow +\infty} x_2-x_1 = \frac{1}{n(n+1)} = 0 $.
      	But $\lim\limits_{n \rightarrow +\infty} y_2- y_1 = -1 \neq 0 $.
      	Thus it is not uniform continuous.
      \end{proof}
\item $y=\sqrt{x}$ is uniform continuous over $(0, +\infty)$ but not Lipschitz continuous.
	  \begin{proof}
	  	As $y\prime = \frac{1}{2\sqrt{x}}$, 
	  	the slope tends towards infty when $x$ approaches 0, 
	  	thus it is not Lipschitz continuous.  
	  \end{proof}
\end{enumerate}

%----------------------------------------------------------------------------------------
%	PROBLEM 3
%----------------------------------------------------------------------------------------

\section{Cardinalty}
\begin{enumerate}
	\item 
		\begin{proof}
			The following function is a one-to-one mapping from N to Z, thus N and Z have the same number of elements.

			\begin{equation}
			f(n) = 
				\begin{cases}
					-\frac{n}{2} & \text{n is even}\\
					\frac{n+1}{2} & \text{n is odd}
				\end{cases}
			\end{equation}

			Arange the elements in N and Q in the pascal triangle style as below, and it is clear enough to see the one-to-one mapping from N to Q with rationals are grouped according to the sum of dividend and divisor. Thus N and Q have the same number of elements.

			\begin{tabular}{c|c}
				\begin{tabular}{rccccccccc}
					&&&&&1\\\noalign{\smallskip\smallskip}
					&&&&2&&3\\\noalign{\smallskip\smallskip}
					&&&4&&&&5\\\noalign{\smallskip\smallskip}
					&&6&&7&&8&&9\\\noalign{\smallskip\smallskip}
					&10&&&&&&&&11\\\noalign{\smallskip\smallskip}
					&&&&&...\\\noalign{\smallskip\smallskip}
				\end{tabular} &
				\begin{tabular}{rccccccccc}
					&&&&&$\frac{1}{1}$ \\\noalign{\smallskip\smallskip}
					&&&&$\frac{1}{2}$&&$\frac{2}{1}$\\\noalign{\smallskip\smallskip}
					&&&$\frac{1}{3}$&&&&$\frac{3}{1}$\\\noalign{\smallskip\smallskip}
					&&$\frac{1}{4}$&&$\frac{2}{3}$&&$\frac{3}{2}$&&$\frac{4}{1}$\\\noalign{\smallskip\smallskip}
					&$\frac{1}{5}$&&&&&&&&$\frac{5}{1}$\\\noalign{\smallskip\smallskip}
					&&&&&...\\\noalign{\smallskip\smallskip}
				\end{tabular}
			\end{tabular}

		\end{proof}	
	\item 
		\begin{proof}
			The following function is a one-to-one mapping from [0, 1] to R, thus they have the same number of elements.

			\begin{equation}
				f(x) = 
				\begin{cases}
				-\infty& \text{x=0}\\
				tan[\pi(x-0.5)] & \text{0 < x < 1}\\
				+\infty& \text{x=1}
				\end{cases}
			\end{equation}

		\end{proof}
	\item
		\begin{proof}
			Suppose all the real numbers can be listed, and each one is marked as $r_i$, where $i=1,2,3...$. Given a real number $r\prime$ such that its \textbf{i-th} digit is different from that in $r_i$, it's obvious that $r\prime$ is not included in the real numbers listed above, which is contradictory to the hypothesis. Thus real numbers can not be listed and it contains more elements than N.
		\end{proof}
\end{enumerate}

%----------------------------------------------------------------------------------------
%	PROBLEM 4
%----------------------------------------------------------------------------------------

\section{Slides}

\begin{enumerate}
	\item
		\begin{proof}

		\end{proof}

	\item
		\begin{proof}

		\end{proof}
\end{enumerate}

%----------------------------------------------------------------------------------------

\end{document}

### 2018-05-23 VV570/HW1/assignment.tex
add ex4

@@
 \usepackage[english]{babel} % English language/hyphenation
-\usepackage{amsmath,amsfonts,amsthm} % Math packages
+\usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages
 
@@
 		\begin{proof}
+			Let $E$ be an inner product space over $\mathbb{C}$, and $u, v\in E$.
+			Given $Y$ defined as below, where $\lambda \in \mathbb{R}$.
+
+			\begin{equation}
+				Y = {\vert u-\lambda v \vert}^2
+			\end{equation}
+
+			It's obvious that $Y\geq0$. Expand the squares according to the definition of inner products, the inequality can be written as below.
+
+			\begin{equation}
+				<v, v>\lambda^2 -(<u, v>+<v, u>)\lambda + <u, u> \ \ \geq \ 0
+			\end{equation}
+
+			The LHS of the inequality can be viewed as a quadratic function where $\lambda$ is the variable. Thus, the discriminant is semi-negative definite, which can be written as below.
+
+			\begin{equation}
+				\Delta = (<u, v>+<v, u>)^2 - 4<u,u><v,v> \ \ \leq \ 0
+			\end{equation}
+
+			As $<v, u> = \overline{<u, v>}$, the inequality above can be simplified as below.
+
+			\begin{equation}
+				<u, v>^2 + {\overline{<u, v>}}^2 + 2{\vert <u,v> \vert}^2 \ \ \leq \ 4 \lVert u \rVert^2 \lVert v \rVert^2 \label{cs}			
+			\end{equation}
+
+			For $x \in \mathbb{C}$, the following equality is justified.
+			\begin{equation}
+				x^2 + \bar{x}^2 = \frac{1}{2}[(x+\bar{x})^2+(x-\bar{x})^2] = \frac{1}{2}[(2Re(x))^2+(2Im(x))^2] = 2 {\vert x \vert}^2 \label{der}
+			\end{equation}
+
+			Since $<u, v>$ is an complex number, apply (\ref{der}) into (\ref{cs}) and eliminate the constant 4, the Cauchy-Schwarz inequality is obtained at last.
+
+			\begin{equation}
+				{\vert <u,v> \vert}^2 \leq \lVert u \rVert^2 \lVert v \rVert^2
+			\end{equation}
 
@@
 		\begin{proof}
+			$d(x, y)$ is non-negative follows from the definition of metric space.
+			\begin{equation}
+				\begin{aligned}
+					d(x, y) & = \frac{1}{2}(d(x, y) + d(x, y)) \\
+							& = \frac{1}{2}(d(x, y) + d(y, x))  &\text{By symmetry}\\
+							& \geq  \frac{1}{2} d(x, x)  &\text{By triangle inequality} \\
+							&  = 0  &\text{By identity of indiscernible}
+				\end{aligned}
+			\end{equation}
 

### 2018-05-23 VV570/HW1/assignment.tex
add ex5.1

@@
       	Let $x_1 = \frac{1}{n+1}$,  $x_2 = \frac{1}{n}$. 
-      	Then $\lim\limits_{n \rightarrow +\infty} x_2-x_1 = \frac{1}{n(n+1)} = 0 $.
-      	But $\lim\limits_{n \rightarrow +\infty} y_2- y_1 = -1 \neq 0 $.
+      	Then $\lim\limits_{n \rightarrow +\infty} \vert x_2-x_1 \vert = \frac{1}{n(n+1)} = 0 $.
+      	But $\lim\limits_{n \rightarrow +\infty} \vert y_2- y_1 \vert = 1 \neq 0 $.
       	Thus it is not uniform continuous.
@@
 %----------------------------------------------------------------------------------------
+%	PROBLEM 5
+%----------------------------------------------------------------------------------------
+
+\section{Linear Algebra}
+
+\begin{enumerate}
+	\item
+		\begin{proof}
+			Suppose $\{u_1, u_2, ...
+, u_m \}$ forms the basis of Ker($f$), and it can be extended to form the basis of $V_1$, which is denoted as $\{u_1, u_2, ...
+, u_m, v_1, v_2, ...
+, v_n \}$.
+It's clear that the dimension of Ker($f$) is $m$ and the dimension of $V_1$ is $m+n$.
+So, it is left to prove that the dimension of $V_2$ is $n$.
+
+			The dimension of $V_2$ is $n$ means $\{f(v_1), f(v_2), ...
+, f(v_n)\}$ forms a basis of $V_2$.
+To see that, let $w$ be an arbitary vector in $V_1$, thus, there exist unique scalars $a_i$, $b_j$ such that
+			\begin{equation}
+				w = a_1 u_1 + a_2 u_2 + ... + a_m u_m + b_1 v_1 + b_2 v_2 + ... + b_n v_n
+			\end{equation}
+
+			The image of $w$ under mapping $f$ is given as below.
+			\begin{equation}
+				\begin{aligned}
+					f(w) & = \sum_{i=1}^{m}a_i f(u_i) + \sum_{j=1}^{m}b_j f(v_j) \\
+						 & = \sum_{j=1}^{m}b_j f(v_j)  \ \ \ \  \text{As $f(u_i) = 0$}
+				\end{aligned}
+			\end{equation}
+
+			Thus $\{f(v_1), f(v_2), ... , f(v_n)\}$ spans $V_2$. It is left to show that they are linearly independent, which means there's no redundancy in the list.
+
+			Given coefficents $c_i$ such that
+			\begin{equation}
+				c_1 f(v_1) + c_2 f(v_2) + ... + c_n f(v_n) = 0 \label{cdis}
+			\end{equation}
+
+			Since $f$ is a linear mapping, (\ref{cdis}) can be grouped as below.
+			\begin{equation}
+				f(c_1 v_1 + c_2 v_2 + ... + c_n v_n) = 0
+			\end{equation}
+
+			Thus $c_1 v_1 + c_2 v_2 + ... + c_n v_n \in Ker(f)$. As $\{u_1, u_2, ... , u_m \}$ forms the basis of Ker($f$), there exists coefficients $d_i$ such that
+			\begin{equation}
+				c_1 v_1 + c_2 v_2 + ... + c_n v_n = d_1 u_1 + d_2 u_2 + ... + d_m u_m \label{diff}
+			\end{equation}
+
+			Since $\{u_1, u_2, ...
+, u_m, v_1, v_2, ...
+, v_n \}$ forms the basis of $V_1$, all the coefficients in (\ref{diff}) should be 0.
+Thus, (\ref{cdis}) is valid if and only if all the coefficents $c_i$ is 0, which implies that $\{f(v_1), f(v_2), ...
+, f(v_n)\}$ are linearly independent.
+
+			Thus, $\{f(v_1), f(v_2), ... , f(v_n)\}$ forms the basis of $V_2$, and the dimension of $V_2$ is therefore $n$. The rank-nullity theorem written as below is proved.
+			\begin{equation}
+				dim(V_1) = dim(ker(f)) + dim(V_2)
+			\end{equation}
+		\end{proof}
+	\item
+		\begin{proof}
+
+		\end{proof}
+	\item
+		\begin{proof}
+
+		\end{proof}
+\end{enumerate}
+
+%----------------------------------------------------------------------------------------
 

### 2018-05-23 VV570/HW1/assignment.tex
add ex1, 7

@@
 \usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages
+
+\usepackage{algorithm, algorithmic}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}} %Use Input in the format of Algorithm  
+\renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm
+
+\usepackage{listings}
+\lstset{language=Matlab}
 
@@
 \section{Metric Space}
+\begin{enumerate}
+	\item
+		\begin{proof}
+			Since there's no elements in $\emptyset$, so $\emptyset$ is open, as $X^\complement = \emptyset$, so $X$ is closed.\\
+			$X$ is open as it contains all the elemnets, since $\emptyset^\complement = X$, thus $\emptyset$ is closed. 
+		\end{proof}
+	\item
+		\begin{proof}
+			Since
+			\begin{equation}
+				T \triangleq (U_1 \cap U_2 \cap ... \cap U_m)^\complement = U_1^\complement \cup U_2^\complement \cup ... \cup U_m^\complement
+			\end{equation}
+			And ${U_i}^\complement$ is open, as $U_i$ is closed.\\
+			Thus, $T$ is open, and therefore the intersection is closed. 
+		\end{proof}
+	\item 
+		\begin{proof}
+			Since
+			\begin{equation}
+				T \triangleq (U_1 \cup U_2 \cup ... \cup U_m)^\complement = U_1^\complement \cap U_2^\complement \cap ... \cap U_m^\complement
+			\end{equation}
+			And ${U_i}^\complement$ is open, as $U_i$ is closed.\\
+			Thus, $T$ is open, and therefore the intersection is closed. 
+		\end{proof}
+
+\end{enumerate}
 
@@
 		\end{proof}
+
 	\item
 		\begin{proof}
+			Let $U, V, W$ be vector spaces over the same field $K$, function $f$ be a linear map from $U$ to $V$ and function $g$ be a linear map from $V$ to $W$.
+It's left to show that the composition of $f$ and $g$, denoted as $h$, which maps a vector in $U$ to $W$, is still a linear map.
 
+			Given $u_1, u_2 \in U$ and any scalar $c \in \mathbb{K}$, then
+			\begin{equation}
+				\begin{aligned}
+					h(u_1 + u_2) & = g(f(u_1 + u_2)) \\
+								 & = g(f(u_1) + f(u_2)) \\
+								 & = g(f(u_1)) + g(f(u_2)) \\
+								 & = h(u_1) + h(u_2)
+				\end{aligned}
+			\end{equation}
+
+			\begin{equation}
+				\begin{aligned}
+					h(c u_1) & = g(f(c u_1)) \\
+							 & = g(c f(u_1)) \\
+						     & = c g(f(u_1)) \\
+							 & = c h(u_1)
+				\end{aligned}
+			\end{equation}
+
+			Thus, the composition of two linear maps is still a linear map.
+		\end{proof}
+
+	\item
+		\begin{proof}
+			Let $U, V$ be vector spaces over the same field $K$, function $f$ be linear maps from $U$ to $V$.
+It's left to show that the inverse of $f$, denoted as $f^{-1}$, which maps a vector in $V$ to $U$ is still a linear map.
+
+			By inverse, it means that
+			\begin{equation}
+				f(f^{-1}(x)) = f^{-1}(f(x)) = x
+			\end{equation}
+
+			Given $u_1, u_2 \in U$ and any scalar $c \in \mathbb{K}$, denote the counterpart of $u_1, u_2$ in $V$ as $v_1, v_2$ under the linear mapping function $f$. Then
+
+			\begin{equation}
+				\begin{aligned}
+					f^{-1}(v_1 + v_2) & = f^{-1}(f(u_1) + f(u_2)) \\
+									  & = f^{-1}(f(u_1 + u_2)) \\
+									  & = u_1 + u_2 \\
+									  & = f^{-1}(v_1) + f^{-1}(v_2)
+				\end{aligned}
+			\end{equation}
+
+			\begin{equation}
+				\begin{aligned}
+					f^{-1}(c v_1) & = f^{-1}(c f(u_1)) \\
+							      & = f^{-1}(f(c u_1)) \\
+								  & = c u_1 \\
+								  & = c f^{-1}(v_1)
+				\end{aligned}
+			\end{equation}
+
+			Thus, the inverse of a linear map is still a linear map.
+		\end{proof}
+\end{enumerate}
+
+%----------------------------------------------------------------------------------------
+%	PROBLEM 6
+%----------------------------------------------------------------------------------------
+
+\section{Discontinuous linear maps}
+\begin{enumerate}
+	\item 
+		\begin{proof}
+			The $k$ times derivative of $f_n(x)$ can be written as below.
+			\begin{equation}
+				f_n^{(k)}(x) = n^{k-1} sin(nx+ \frac{k\pi}{2}) \ \ \ \ k = 0, 1, 2, 3, ...
+			\end{equation}
+			It's clear that $f_n^{(k)}(x)$ is continous for any $k$, thus $f_n(x) \in C^\infty(\mathbb{R})$.
 		\end{proof}
 	\item 
+		\begin{equation}
+			d f_n(x) = cos(nx) dx
+		\end{equation}
+	\item
 		\begin{proof}
+			Let $x_0 = 0, x_1 = \frac{\pi}{2n}$, then
+			\begin{equation}
+				\lim\limits_{n->+\infty} \vert x_1-x_0 \vert = 0
+			\end{equation}
+			\begin{equation}
+				\lim\limits_{n->+\infty} \vert df_n(x_1) - df_n(x_0) \vert = \vert 0-dx \vert = |dx| \neq 0
+			\end{equation}
+			Thus, the differential is not continous when n tends to infty.
+		\end{proof}
+	\item 
+		Sorry, haven't figured out yet...
 
-		\end{proof}
+\end{enumerate}
+
+%----------------------------------------------------------------------------------------
+%	PROBLEM 7
+%----------------------------------------------------------------------------------------
+
+\section{pi}
+\begin{enumerate}
+	\item 
+		The main program(see Algorithm\ref{machin}) adopts Machin's formula to calculate $\pi$.
+		\begin{equation}
+			\pi = 4[4atan(\frac{1}{5}) - atan(\frac{1}{239})]
+		\end{equation}
+
+		Subroutine(see Algorithm\ref{atan_inv}) calculating $atan(\frac{1}{x})$ is used by the main program. Since
+		\begin{equation}
+			atan(x) = \frac{1}{1}x - \frac{1}{3}x^3 + \frac{1}{5}x^5 - \frac{1}{7} x^7 + ...
+		\end{equation}
+
+		Therefore
+		\begin{equation}
+			atan(\frac{1}{x}) = \frac{1}{x} - \frac{1}{3x^3} + \frac{1}{5x^5} - \frac{1}{7x^7} + ...
+		\end{equation}
+
+		\begin{algorithm}
+			\caption{Calculation of $\pi$ using Machin's formula}  
+			\label{machin}
+			\begin{algorithmic}[1]
+				\REQUIRE
+				None.
+				\ENSURE
+				The value of $\pi$ with approximation.
+				\RETURN $4[4 atan(1/5) - atan(1/239)]$
+			\end{algorithmic}  
+		\end{algorithm}
+
+		\begin{algorithm}
+			\caption{Calculation of $atan(\frac{1}{x})$}
+			\label{atan_inv}
+			\begin{algorithmic}[1]
+				\REQUIRE x
+				\ENSURE $atan(\frac{1}{x})$
+				\STATE $ret \gets 0$
+				\STATE $e \gets 1/x$
+				\STATE $s \gets - x^2$
+				\STATE $c \gets 1$
+				\WHILE {$e \neq 0$}
+				\STATE $ret \gets ret + e/c$
+				\STATE $e \gets e/s$
+				\STATE $c \gets c + 2$
+				\ENDWHILE
+				\RETURN ret
+			\end{algorithmic}  
+		\end{algorithm}
+
+	\newpage
+
+	\item
+		The matlab code is given as below.
+		\begin{verbatim}
+			function [pi] = pi_machin()
+			pi = 4*(4*atan_inv(5) - atan_inv(239));
+
+			function [r] = atan_inv(x)
+			r = 0;
+			e = 1/x;
+			s = - x*x;
+			c = 1;
+			while (e ~= 0)
+			r = r + e/c;
+			e = e/s;
+			c = c+2;
+			end
+		\end{verbatim}	
 \end{enumerate}

### 2018-05-23 VV570/HW1/pi_machin.m
add code and pdf

@@ -1,0 +1,13 @@
+function [pi] = pi_machin()
+pi = 4*(4*atan_inv(5) - atan_inv(239));
+
+function [r] = atan_inv(x)
+r = 0;
+e = 1/x;
+s = - x*x;
+c = 1;
+while (e ~= 0)
+    r = r + e/c;
+    e = e/s;
+    c = c+2;
+end

### 2018-05-28 VV570/LAB1/LAB1_Task1.m
add class temp

@@ -1,0 +1,37 @@
+%(a)
+x=[1, 2, 3, 4, 5, 6];
+y=[66, 66, 65, 64, 63, 63];
+
+lagrinterpol(x, y, 4.5)
+
+%(b)
+poly([2,3,5,7,9])
+
+%(c)
+syms s;
+f = (s-2)*(s-7)*(s-1)*(s-8)*(s-2)*(s-8);
+expand(f)
+
+%(d)
+a=[2, 7, 1, 8, 2, 8];
+P=poly([a(1), a(2), a(3)]);
+Q = poly([a(4), a(5), a(6)]);
+conv(P, Q)
+
+%(e)
+coeff=[a(1), a(2), a(3)];
+polyval(coeff, [a(4), a(5), a(6)])
+
+%(f)
+[c0, c1] = lagrinterpolde(x, y)
+xs = linspace(1,6,100);
+yder = polyval(c1, xs);
+plot(xs, yder)
+
+
+
+
+
+
+
+

### 2018-05-28 VV570/LAB1/LAB1_Task2.m

@@ -1,0 +1,47 @@
+%(a)
+clear all;
+close all;
+N = 5;
+xdata = linspace(0,1000, N+1);
+ydata = randn([1, N+1]);
+Cnewton = newpoly(xdata, ydata)
+Clagrange = lagrinterpolde(xdata, ydata)
+
+%(b)
+N = 100;
+xdata = linspace(0, 1000, N+1);
+ydata = randn([1, N+1]);
+tic
+    Cnewton = newpoly(xdata, ydata);
+toc
+
+tic
+    Clagrange = lagrinterpolde(xdata, ydata);
+toc
+
+%(c)
+N = 10;
+xdata = linspace(0,1000, N+1);
+rng(0)
+ydata = randn([1,N+1]);
+Cnewton = newpoly(xdata,ydata);
+Clagrange = lagrinterpolde(xdata,ydata);
+x_plot_points = linspace(0,1000,500);
+plot(xdata, ydata,'.')
+figure(1)
+plot(x_plot_points, polyval(Cnewton, x_plot_points ),'b')
+plot(x_plot_points, polyval(Clagrange, x_plot_points), '-.r')
+
+N = 30;
+xdata = linspace(0,1000, N+1);
+rng(0)
+ydata = randn([1,N+1]);
+Cnewton = newpoly(xdata,ydata);
+Clagrange = lagrinterpolde(xdata,ydata);
+x_plot_points = linspace(0,1000,500);
+plot(xdata, ydata,'.')
+figure(2)
+plot( x_plot_points, polyval(Cnewton, x_plot_points ),'b')
+plot( x_plot_points, polyval(Clagrange, x_plot_points), '-.r')
+
+    

### 2018-05-28 VV570/LAB1/LAB1_Task3.m

@@ -1,0 +1,18 @@
+%(a)
+clear all;
+close all;
+
+syms x
+f = symfun(1/(1+25*x^2),x);
+N = 10;
+xdata = linspace(-1, 1, N+1);
+ydata = double(f(xdata));
+polyfit(xdata, ydata, N)
+
+%(b)
+syms x
+f = symfun(1/(1+25*x^2),x);
+N = 20;
+xdata = linspace(-1, 1, N+1);
+ydata = double(f(xdata));
+polyfit(xdata, ydata, N)

### 2018-05-28 VV570/LAB1/lagrinterpol.m

@@ -1,0 +1,24 @@
+function [p]=lagrinterpol(x,y,z)
+%--------------------------------------------------------------------------
+%LAGRINTERPOL   Lagrange polynomial interpolation 
+% Inputs 
+%   x   vector of interpolation nodes
+%   y   vector of funtion values at x
+%   z   vector of points at which the interpolating polynomial need to be
+%       evalauted
+% Outpus
+%   p   vector of polynomial values at z
+%% NUMERICAL METHODS: MATLAB Programs, Mathews & Fink 2004 
+%--------------------------------------------------------------------------
+[m n] = size(y);
+for j = 1:m
+    a (:,1) = y (j,:)';
+    for i = 2:n
+        a (i:n,i) = ( a(i:n,i-1)-a(i-1,i-1) )./(x(i:n)-x(i-1))';
+    end
+    p(j,:) = a(n,n).*(z-x(n-1)) + a(n-1,n-1);
+    for i = 2:n-1
+        p(j,:) = p(j,:).*(z-x(n-i))+a(n-i,n-i);
+    end
+end
+return

### 2018-05-28 VV570/LAB1/lagrinterpolde.m

@@ -1,0 +1,29 @@
+function [C, C1] = lagrinterpolde(X,Y) 
+%--------------------------------------------------------------------------
+%lagrinterpolde   Coefficients of Lagrange polynomial interpolation 
+%                 and coefficients of the first derivative of it
+% Inputs 
+%   X   vector of interpolation nodes
+%   Y   vector of funtion values at X
+% Outpus
+%   C   vector of coefficients of p
+%   C1  vector of coefficients of p'
+%% NUMERICAL METHODS: MATLAB Programs, Mathews & Fink 2004 
+%--------------------------------------------------------------------------
+w = length(X);
+n = w - 1;
+L = zeros(w,w);
+
+for k = 1:n+1
+    V = 1;
+    for j = 1:n+1
+        if k~=j
+            V = conv(V, poly(X(j)))/(X(k)-X(j));
+        end
+    end
+    L(k,:) = V;
+end
+
+C = Y*L;
+C1 = C .* (n:-1:0);
+C1 = C1(1:n);

### 2018-05-28 VV570/HW1/assignment.tex
add another proof for the Cauchy-Schwarz inequality

@@
 
-\date{\normalsize\today} % Today's date or a custom date
+\date{\normalsize May 23, 2018} % Today's date or a custom date
 
@@
 	\item
+		Here I give 2 proofs, the first one comes directly from the class, the other from previous reading.(thanks to Ran Yi for pointing out that)
+
 		\begin{proof}
-			Let $E$ be an inner product space over $\mathbb{C}$, and $u, v\in E$.
+			Let $E$ be an inner product space over $\mathbb{C}$, and $u, v\in E$.\\
 			Given $Y$ defined as below, where $\lambda \in \mathbb{R}$.
@@
 			\end{equation}
+		\end{proof}
 
+		\begin{proof}
+			Let $E$ be an inner product space over $\mathbb{C}$, and $u, v\in E$.\\
+
+			Given $Y$ defined as below, where $\lambda \in \mathbb{R}$.
+
+			\begin{equation}
+				\begin{aligned}
+					Y & = {\vert u-\lambda v \vert}^2 \\
+					  & = <v, v>\lambda^2 -(<u, v>+<v, u>)\lambda + <u, u> \label{lbd}
+				\end{aligned}
+			\end{equation}
+
+			It's obvious that $Y\geq0$ for any $\lambda$. \\
+			Given $\lambda$ as
+			\begin{equation}
+				\lambda = \frac{<u,v>}{<v, v>}
+			\end{equation}
+			Substitude it into (\ref{lbd}), the inequality reads as
+			\begin{equation}
+				<u, u><v,v> - <u, v>(<u, v> + <v, u>) + <u, v>^2 \ \ \geq 0
+			\end{equation}
+			It can be further simplified as
+			\begin{equation}
+				\begin{aligned}
+					<u, u> \cdot <v, v> \ \  & = ||u||^2 \cdot ||v||^2 \\
+								        \ \  & \geq \ \ <u, v> \cdot <v, u>\\
+								        \ \  & = \ \  <u, v> \cdot \overline{<u, v>}\\
+								        \ \  & = \ \ |<u, v>|^2
+				\end{aligned}
+			\end{equation}
+
+			Thus, the Cauchy-Schwarz inequality got proved.
 		\end{proof}

### 2018-05-28 VV570/LAB1/Task2.m
lab1 done!

@@ -20,18 +20,7 @@ tic
 toc
 
 %(c)
-N = 10;
-xdata = linspace(0,1000, N+1);
-rng(0)
-ydata = randn([1,N+1]);
-Cnewton = newpoly(xdata,ydata);
-Clagrange = lagrinterpolde(xdata,ydata);
-x_plot_points = linspace(0,1000,500);
-plot(xdata, ydata,'.')
-figure(1)
-plot(x_plot_points, polyval(Cnewton, x_plot_points ),'b')
-plot(x_plot_points, polyval(Clagrange, x_plot_points), '-.r')
-
+%N = 10;
 N = 30;
 xdata = linspace(0,1000, N+1);
 rng(0)
@@ -40,8 +29,10 @@ Cnewton = newpoly(xdata,ydata);
 Clagrange = lagrinterpolde(xdata,ydata);
 x_plot_points = linspace(0,1000,500);
 plot(xdata, ydata,'.')
-figure(2)
-plot( x_plot_points, polyval(Cnewton, x_plot_points ),'b')
-plot( x_plot_points, polyval(Clagrange, x_plot_points), '-.r')
+hold on
+plot(x_plot_points, polyval(Cnewton, x_plot_points ),'b')
+plot(x_plot_points, polyval(Clagrange, x_plot_points), '-.r')
+hold off
+
 
     

### 2018-05-28 VV570/LAB1/Task3a.m

@@ -1,18 +1,9 @@
-%(a)
 clear all;
 close all;
 
 syms x
 f = symfun(1/(1+25*x^2),x);
 N = 10;
-xdata = linspace(-1, 1, N+1);
-ydata = double(f(xdata));
-polyfit(xdata, ydata, N)
-
-%(b)
-syms x
-f = symfun(1/(1+25*x^2),x);
-N = 20;
 xdata = linspace(-1, 1, N+1);
 ydata = double(f(xdata));
 polyfit(xdata, ydata, N)

### 2018-05-28 VV570/LAB1/Task3b.m

@@ -1,0 +1,16 @@
+syms x
+f = symfun(1/(1+25*x^2),x);
+xdata = linspace(-1, 1, 201);
+ydata = double(f(xdata));
+
+xs1 = linspace(-1,1,21);
+xs2 = linspace(-1,1,41);
+y_interp1 = polyval(polyfit(xs1, double(f(xs1)), 20), xdata);
+y_interp2 = polyval(polyfit(xs2, double(f(xs2)), 40), xdata);
+
+hold on
+axis([-1 1 -5 5]);
+plot(xdata, ydata, '-black');
+plot(xdata, y_interp1, '--r');
+plot(xdata, y_interp2, '-.b');
+hold off

### 2018-05-28 VV570/LAB1/Task3c.m

@@ -1,0 +1,16 @@
+syms x
+f = symfun(1/(1+25*x^2),x);
+xdata = linspace(-1, 1, 201);
+ydata = double(f(xdata));
+
+xs1 = cos(linspace(1,0,21)*pi);
+xs2 = cos(linspace(1,0,41)*pi);
+y_interp1 = polyval(polyfit(xs1, double(f(xs1)), 20), xdata);
+y_interp2 = polyval(polyfit(xs2, double(f(xs2)), 40), xdata);
+
+hold on
+axis([-1 1 -5 5]);
+plot(xdata, ydata, '-black');
+plot(xdata, y_interp1, '--r');
+plot(xdata, y_interp2, '-.b');
+hold off

### 2018-05-28 VV570/LAB1/Task3d.m

@@ -1,0 +1,16 @@
+syms x
+f = symfun(1/(1+25*x^2),x);
+xdata = linspace(-1, 1, 201);
+ydata = double(f(xdata));
+
+hold on
+axis([-1 1 0 1]);
+plot(xdata, ydata, '-black');
+for n = 5:1:20
+    xs = linspace(-1, 1, n+1);
+    ys = double(f(xs));
+    c = newpoly(xs, ys);
+    y_interp = polyval(c, xdata);
+    plot(xdata, y_interp,'-');
+end
+hold off

### 2018-05-28 VV570/LAB1/Task3e.m

@@ -1,0 +1,16 @@
+syms x
+f = symfun(1/(1+25*x^2),x);
+xdata = linspace(-1, 1, 201);
+ydata = double(f(xdata));
+
+hold on
+axis([-1 1 0 1]);
+plot(xdata, ydata, '-black');
+for n = 5:1:20
+    xs = cos(linspace(pi, 0, n+1));
+    ys = double(f(xs));
+    c = newpoly(xs, ys);
+    y_interp = polyval(c, xdata);
+    plot(xdata, y_interp,'-');
+end
+hold off

### 2018-05-28 VV570/LAB1/Task4a.m

@@ -1,0 +1,20 @@
+syms a b c;
+[a, b, c] = solve('(a+b)/(1+c)=atan(1)','(a+2*b)/(1+2*c)=atan(2)','(a+3*b)/(1+3*c)=atan(3)');
+vpa(a, 14)
+vpa(b, 14)
+vpa(c, 14)
+
+N = 10;
+xdata = linspace(1, 3, N+1);
+ydata = double(atan(xdata));
+y_interp = linspace(-5, 5, N+1);
+
+for i = 1:N+1
+    x = xdata(i);
+    y_interp(i) = (-0.64983370679341+2.7942445718816*x)/(1+1.73034871359*x);
+end
+
+hold on
+plot(xdata, ydata,'-^');
+plot(xdata, y_interp, '--r')
+hold off

### 2018-05-28 VV570/LAB1/Task4b.m

@@ -1,0 +1,31 @@
+SP_NUM = 501;
+x = linspace(0,2*pi, SP_NUM);
+y = x;
+for i = 1:SP_NUM
+    y(i) = h(x(i));
+end
+
+PNT_NUM = 21;
+%xs = linspace(0,2*pi, PNT_NUM);
+xs = cos(linspace(pi, 0, PNT_NUM)) * pi + pi;
+ys = xs;
+for i = 1:PNT_NUM
+    ys(i) = h(xs(i));
+end
+
+yspline = spline(xs, ys, x);
+ylagrange = lagrinterpol(xs, ys, x);
+ynewton = polyval(newpoly(xs, ys), x);
+
+hold on
+plot(x, y);
+plot(xs, ys, '^');
+plot(x, yspline,':');
+plot(x, ylagrange, '-.');
+plot(x, ynewton, '--');
+legend('Original','Sample Pts', 'Spline', 'Lagrange', 'Newton');
+hold off
+
+function [ret] = h(x)
+    ret = sin(x) + sin(5*x);
+end

### 2018-05-28 VV570/LAB1/Task2.m
drop png

@@ -20,7 +20,20 @@ tic
 toc
 
 %(c)
-%N = 10;
+N = 10;
+xdata = linspace(0,1000, N+1);
+rng(0)
+ydata = randn([1,N+1]);
+Cnewton = newpoly(xdata,ydata);
+Clagrange = lagrinterpolde(xdata,ydata);
+x_plot_points = linspace(0,1000,500);
+figure(1)
+hold on
+plot(xdata, ydata,'.')
+plot(x_plot_points, polyval(Cnewton, x_plot_points ),'b')
+plot(x_plot_points, polyval(Clagrange, x_plot_points), '-.r')
+hold off
+
 N = 30;
 xdata = linspace(0,1000, N+1);
 rng(0)
@@ -28,8 +41,9 @@ ydata = randn([1,N+1]);
 Cnewton = newpoly(xdata,ydata);
 Clagrange = lagrinterpolde(xdata,ydata);
 x_plot_points = linspace(0,1000,500);
-plot(xdata, ydata,'.')
+figure(2)
 hold on
+plot(xdata, ydata,'.')
 plot(x_plot_points, polyval(Cnewton, x_plot_points ),'b')
 plot(x_plot_points, polyval(Clagrange, x_plot_points), '-.r')
 hold off

### 2018-05-28 VV570/LAB1/Task4a.m

@@ -16,5 +16,6 @@ end
 
 hold on
 plot(xdata, ydata,'-^');
-plot(xdata, y_interp, '--r')
+plot(xdata, y_interp, '--r');
+legend('Original','Rational Approx')
 hold off

### 2018-06-03 VV570/HW2/assignment.tex
under construction...

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages

\usepackage{algorithm, algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}} %Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm

\usepackage{listings}
\lstset{language=Matlab}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Introduction to Numerical Analysis \\ HW2 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yu Cang \\ 018370210001} % Your name

\date{\normalsize \today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title

%----------------------------------------------------------------------------------------
%	PROBLEM 1
%----------------------------------------------------------------------------------------

\section{Connected Space}
\begin{enumerate}
	\item
		\begin{proof}
			\begin{enumerate}
				\item (i) $\Rightarrow$ (ii) \\
					Suppose (ii) is not true, which means $X = U_1 \cup U_2$, $U_1 \cap U_2 = \emptyset$, $U_1 \neq \emptyset$, $U_2 \neq \emptyset$, and both $U_1$ and $U_2$ are open.\\
					Thus, $U_1$ and $U_2$ are closed as $U_1 = U_2^\complement$ and $U_2 = U_1^\complement$.\\
					So, $U_1$ and $U_2$ are both open and closed in $X$, which is contradictory to (i).\\
					Thus the assumption fails and (ii) is true when (i) is true.
				\item (ii) $\Rightarrow$ (i)\\
					Suppose (i) is not true, which means there exists $U$ s.t. $U \subset X$, $U \neq \emptyset$ and $U$ is both open and closed in $X$.\\
					Thus, $U^\complement$ is open as $U$ is closed.\\
					As $X = U \cup U^\complement$, then $X$ can be written as the union of two disjoint, non-empty open subsets, which is contradictory to (ii).\\
					Thus the assumption fails and (i) holds true when (ii) is true. 
				\item (i)$\Rightarrow$(iii)\\
					Suppose (iii) is not true, which means $X = U_1 \cup U_2$, $U_1 \cap U_2 = \emptyset$, $U_1 \neq \emptyset$, $U_2 \neq \emptyset$ and both $U_1$ and $U_2$ are closed.\\
					Thus, $U_1$ and $U_2$ are open as $U_1 = U_2^\complement$ and $U_2 = U_1^\complement$.\\
					So, $U_1$ and $U_2$ are both open and closed in $X$, which is contradictory to (i).\\
					Thus the assumption fails and (iii) is true when (i) is true.
				\item (iii) $\Rightarrow$ (i)\\
					Suppose (i) is not true, which means there exists $U$ s.t. $U \subset X$, $U \neq \emptyset$ and $U$ is both open and closed in $X$.\\
					Thus, $U^\complement$ is closed as $U$ is open.\\
					As $X = U \cup U^\complement$, then $X$ can be written as the union of two disjoint, non-empty closed subsets, which is contradictory to (iii).\\
					Thus the assumption fails and (i) holds true when (iii) is true. 
			\end{enumerate}
		\end{proof}
	\item
		\begin{proof}
			If (iv) is false, then there exists a continuous, surjective application from $X$ into $[0, 1]\subset U$, which can be denoted as $f$.\\
			$[0, 1]$ can be written as $[0, a) \cup [a, 1] \triangleq V_1 \cup V_2$, where $0 < a < 1$, $V_1$ and $V_2$ are closed. Denote $U_1 = f^{-1}(V_1)$ and  $U_2 = f^{-1}(V_2)$. \\
			As $f$ is surjective, it follows that $U_1 \neq \emptyset$, $U_2 \neq \emptyset$ and $U_1 \cap U_2 = \emptyset$. \\
			As $f$ is continous, it follows that $U_1$ and $U_2$ are also closed, $U_1 \cap U_2 = X$.\\
			Thus, it is contradictory to (iii) as $X$ can be written as the union of two disjoint, non-empty closed subsets.\\
			So, if (iv) is not true then (iii) is also false.
		\end{proof}
	\item 
		\begin{proof}
			If (iii) is false, then $X = U_1 \cup U_2$, where $U_1$ and $U_2$ are two disjoint, non-empty closed subsets.\\
			...
		\end{proof}
\end{enumerate}

%----------------------------------------------------------------------------------------
%	PROBLEM 2
%----------------------------------------------------------------------------------------

\section{Intermediate value theorem}

\begin{enumerate}
	\item
      \begin{proof}
      	Suppose $f(A) = V_1 \cup V_2$, where $V_1$ and $V_2$ are two disjoint, non-empty open subsets.
      	Denote $U_1 = f^{-1}(V_1)$, $U_2 = f^{-1}(V_2)$. $A = U_1 \cup U_2$ as each element in $A$ is mapped to either $V_1$ or $V_2$.
      	Further, $U_1$ and $U_2$ are open as $f$ is a continous map. 
      	Thus $A$ can be written as the union of two disjoint, non-empty open subsets, which is contradictory to the fact that $A$ is a connected space. Therefore, $f(A)$ is connected.
      \end{proof}

	\item
	  \begin{proof}
		\begin{enumerate}
			\item
				It's clear that $\emptyset$ is connected as $X$ is itself.\\
				For $A$ containing only 1 element, it is connected as it can no be written as the union of two disjoint non-empty closed subsets.
			\item
				If $A$ is not an interval and the corner cases in a) are excluded, then it can be written as union of non-empty, disjoint closed subsets. Thus $A$ is not connected.
			\item

		\end{enumerate}
	  \end{proof}

\end{enumerate}

%----------------------------------------------------------------------------------------
%	PROBLEM 3
%----------------------------------------------------------------------------------------

\section{Rolle's theorem}
	\begin{proof}
		\begin{enumerate}
			\item 
				For $n=1$, if $f(x)$ has 2 distinct roots in $[a, b]$, then there exists the maximum $M$ and minimum $m$ between $[a, b]$ according to the extream value theorem.\\
				If $M = m$, then $f(x)$ is constant, and it's obvious that for any $c \in [a, b]$, $f\prime(c) = 0$; \\
				If $M \neq m$, then $\exists \xi \in (a, b)$, s.t.  $f(\xi)$ reaches its extream, and equals to 0.
			\item
				As induction hypothesis, assume the statement is true for $n = k$.
			\item 
				For $n = k+1$, where $f(x)$ has $k+2$ distinct roots denoted as $c_0 < c_1 < ... <c_k < c_{k+1}$, applying the results for $n = 1$ on each gap $[c_i, c_{i+1}]\ (i = 0, 1, ... , k)$, then $g(x) \triangleq f'(x)$ has $k+1$ roots in $[c_0, c_{k+1}]$. By induction hypothesis, there exists $c \in [c_0, c_{k+1}]$ s.t. $g^{(k)}(c) = f^{(k+1)} = f^{(n)} 0$. Thus the statement holds true for $n = k+1$.
		\end{enumerate}
	\end{proof}

%----------------------------------------------------------------------------------------
%	PROBLEM 4
%----------------------------------------------------------------------------------------

\section{Extreme value theorem}

\begin{enumerate}
	\item
		\begin{proof}

		\end{proof}

	\item
		\begin{proof}

		\end{proof}

	\item
		\begin{proof}

		\end{proof}
\end{enumerate}

%----------------------------------------------------------------------------------------
%	PROBLEM 5
%----------------------------------------------------------------------------------------

\section{Continuity}

\begin{enumerate}
	\item
		\begin{proof}

		\end{proof}

	\item
		\begin{proof}

		\end{proof}

	\item
		\begin{proof}

		\end{proof}
\end{enumerate}

\end{document}

### 2018-06-04 VV570/HW2/assignment.tex
add ex5

@@
 By induction hypothesis, there exists $c \in [c_0, c_{k+1}]$ s.t.
-$g^{(k)}(c) = f^{(k+1)} = f^{(n)} 0$.
+$g^{(k)}(c) = f^{(k+1)}(c) = f^{(n)}(c)= 0$.
 Thus the statement holds true for $n = k+1$.
@@
 \section{Continuity}
-
 	\begin{enumerate}
@@
 			\begin{proof}
-
+				(i)$\Rightarrow$(ii): For each $ y \in B(f(a), \xi)$, there exists $U_x \subset X, U_x \neq \emptyset$ s.t.
+$y = f(U_x)$.
+Thus, $d(f(x), f(a)) < \xi$ is valid for any $x \in U \triangleq \bigcup\limits_{x \in X} U_x$.
+As indicated by (i), there exists $\eta$ s.t.
+$B(a, \eta) \subset U$.
+Thus, $\eta$ is valid, and $d(a, x)$ for $x \in B(a, \eta)$ is less than $\eta$.\\
+				(ii)$\Rightarrow$(i): As $X$ and $Y$ are two metrix spaces, then the set containing all the elements in $d(x, a) < \eta$ is equivalent to the ball $B(a, \eta) \subset X$.
+It suffices to show that the $\eta$ in (i) exists.
 			\end{proof}
-
 		\item
 			\begin{proof}
-
+				Given $\xi$ where $B(f(a), \xi) \subset V$, then it is indicated by (i) that there exists $\eta$ where $f(B(a, \eta)) \in B(f(a), \xi)$.
+Denote $U = B(a, \eta)$, then $f(U) \subset B(f(a), \xi) \subset V$.
 			\end{proof}
-
 		\item
 			\begin{proof}
-
+				As indicated by (iii), $U$ is a neighborhood of $a$ and $f(U) \subset V$. Since $U \subset f^{-1}(V)$, thus, by observation, $f^{-1}(V)$ is a neighborhood of $a$. 
+			\end{proof}
+		\item
+			\begin{proof}
+				For any $\xi \in \mathbb{R}_+$, take the neighborhood $V$ of $f(a)$ \ s.t.
+$V \subset B(f(a), \xi)$.
+Then, by (iv), $f^{-1}(V)$ is a neighborhood of $a$.
+Thus, there exists $\eta \in \mathbb{R}_+$ s.t.
+$B(a, \eta) \subset f^{-1}(V)$, and it is obvious that $f(B(a, \eta)) \subset B(f(a), \xi)$.
 			\end{proof}

### 2018-06-04 VV570/HW2/assignment.tex
add some fulfillment

@@
 \usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages
+\usepackage{mathrsfs}
 
@@
 			If (iii) is false, then $X = U_1 \cup U_2$, where $U_1$ and $U_2$ are two disjoint, non-empty closed subsets.\\
-			...
+			(haven't figured out yet...)
 		\end{proof}
@@
 			\item
-
+				\begin{enumerate}
+					\item 
+						The continuous bijection mapping $f$ can be given as 
+						\begin{equation}
+							f(x) = \frac{x-I_{min}}{I_{max} - I_{min}} (J_{max} - J{min})
+						\end{equation} 
+						where $I_{min}, I_{max}, J_{max}, J{min}$ are the limits of corresponding interval.\\
+						The inverse continuous bijection can be constructed in the same way, which can be given as
+						\begin{equation}
+							f^{-1}(y) = \frac{y-J_{min}}{J_{max} - J_{min}} (I_{max} - I_{min})
+						\end{equation}
+					\item 
+						Consider open interval $X = (0, 1)$, it is clear that $X$ is connected.
+As there exists a continous bijection mapping which maps $X$ to $\mathbb{R}$, thus $f(A) = \mathbb{R}$ is connected as well.
+					\item 
+						If $U$ is both open and closed, then $U^\complement$ is also both open and closed.
+As there must exist a minimum for a closed and non-empty set, $R = U \cup U^\complement$ is then bounded, which is false.
+Thus, the only subsets that are both open and closed in $\mathbb{R}$ are $\mathbb{R}$ and $\emptyset$, which is equivalent to say $\mathbb{R}$ is connected.
+				\end{enumerate}
 		\end{enumerate}
 	  \end{proof}
-
+	\item 
+		\begin{proof}
+			For any connected set $A$, as is indicated above, $f(A)$ is also connected, where $f$ is a continuous function.\\
+			And the connected subsets of $\mathbb{R}$ are all intervals.\\
+			Then $f(X)$ is an interval of $\mathbb{R}$, which contains both $f(a)$ and $f(b)$.\\
+			Thus, $f(X)$ contains both $f(a)$ and $f(b)$.
+		\end{proof}
 \end{enumerate}
@@
 		\begin{proof}
-
+			\begin{enumerate}
+				\item
+					Given an open covering $\mathscr{U}$ of $A$, an open covering of $X$ by throwing in the open subset $U_0 = X /\ A$.
+Since $X$ is compact, there exists finitely many sets $U_1, U_2, U_3, ...
+, U_n \in \mathscr{U}$ \ s.t.
+$X = U_0 \cup U_1 \cup ...
+\cup U_n$.
+Then $A \subseteq  U_1 \cup ...
+\cup U_n$, proving that $A$ is compact.
+				\item
+					(haven't figured out yet...)
+			\end{enumerate}
 		\end{proof}

### 2018-06-08 VV570/HW3/assignment.tex
HW3 frame

--- 2018-06-03 VV570/HW2/assignment.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Introduction to Numerical Analysis \\ HW2 \\ % The assignment title
+\huge Introduction to Numerical Analysis \\ HW3 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 %----------------------------------------------------------------------------------------
-
-\section{Connected Space}
+\section{Cantor's Set}
 	\begin{enumerate}
 		\item
-		\begin{proof}
-			\begin{enumerate}
-				\item (i) $\Rightarrow$ (ii) \\
-					Suppose (ii) is not true, which means $X = U_1 \cup U_2$, $U_1 \cap U_2 = \emptyset$, $U_1 \neq \emptyset$, $U_2 \neq \emptyset$, and both $U_1$ and $U_2$ are open.\\
-					Thus, $U_1$ and $U_2$ are closed as $U_1 = U_2^\complement$ and $U_2 = U_1^\complement$.\\
-					So, $U_1$ and $U_2$ are both open and closed in $X$, which is contradictory to (i).\\
-					Thus the assumption fails and (ii) is true when (i) is true.
-				\item (ii) $\Rightarrow$ (i)\\
-					Suppose (i) is not true, which means there exists $U$ s.t. $U \subset X$, $U \neq \emptyset$ and $U$ is both open and closed in $X$.\\
-					Thus, $U^\complement$ is open as $U$ is closed.\\
-					As $X = U \cup U^\complement$, then $X$ can be written as the union of two disjoint, non-empty open subsets, which is contradictory to (ii).\\
-					Thus the assumption fails and (i) holds true when (ii) is true. 
-				\item (i)$\Rightarrow$(iii)\\
-					Suppose (iii) is not true, which means $X = U_1 \cup U_2$, $U_1 \cap U_2 = \emptyset$, $U_1 \neq \emptyset$, $U_2 \neq \emptyset$ and both $U_1$ and $U_2$ are closed.\\
-					Thus, $U_1$ and $U_2$ are open as $U_1 = U_2^\complement$ and $U_2 = U_1^\complement$.\\
-					So, $U_1$ and $U_2$ are both open and closed in $X$, which is contradictory to (i).\\
-					Thus the assumption fails and (iii) is true when (i) is true.
-				\item (iii) $\Rightarrow$ (i)\\
-					Suppose (i) is not true, which means there exists $U$ s.t. $U \subset X$, $U \neq \emptyset$ and $U$ is both open and closed in $X$.\\
-					Thus, $U^\complement$ is closed as $U$ is open.\\
-					As $X = U \cup U^\complement$, then $X$ can be written as the union of two disjoint, non-empty closed subsets, which is contradictory to (iii).\\
-					Thus the assumption fails and (i) holds true when (iii) is true. 
-			\end{enumerate}
-		\end{proof}
+
 		\item
-		\begin{proof}
-			If (iv) is false, then there exists a continuous, surjective application from $X$ into $[0, 1]\subset U$, which can be denoted as $f$.\\
-			$[0, 1]$ can be written as $[0, a) \cup [a, 1] \triangleq V_1 \cup V_2$, where $0 < a < 1$, $V_1$ and $V_2$ are closed. Denote $U_1 = f^{-1}(V_1)$ and  $U_2 = f^{-1}(V_2)$. \\
-			As $f$ is surjective, it follows that $U_1 \neq \emptyset$, $U_2 \neq \emptyset$ and $U_1 \cap U_2 = \emptyset$. \\
-			As $f$ is continous, it follows that $U_1$ and $U_2$ are also closed, $U_1 \cap U_2 = X$.\\
-			Thus, it is contradictory to (iii) as $X$ can be written as the union of two disjoint, non-empty closed subsets.\\
-			So, if (iv) is not true then (iii) is also false.
-		\end{proof}
+
 		\item
-		\begin{proof}
-			If (iii) is false, then $X = U_1 \cup U_2$, where $U_1$ and $U_2$ are two disjoint, non-empty closed subsets.\\
-			...
-		\end{proof}
+
+		\item
+
 	\end{enumerate}
@@
 %----------------------------------------------------------------------------------------
-
-\section{Intermediate value theorem}
-
+\section{Cantor's Function}
 	\begin{enumerate}
 		\item
-      \begin{proof}
-      	Suppose $f(A) = V_1 \cup V_2$, where $V_1$ and $V_2$ are two disjoint, non-empty open subsets.
-      	Denote $U_1 = f^{-1}(V_1)$, $U_2 = f^{-1}(V_2)$. $A = U_1 \cup U_2$ as each element in $A$ is mapped to either $V_1$ or $V_2$.
-      	Further, $U_1$ and $U_2$ are open as $f$ is a continous map. 
-      	Thus $A$ can be written as the union of two disjoint, non-empty open subsets, which is contradictory to the fact that $A$ is a connected space. Therefore, $f(A)$ is connected.
-      \end{proof}
 
 		\item
-	  \begin{proof}
-		\begin{enumerate}
-			\item
-				It's clear that $\emptyset$ is connected as $X$ is itself.\\
-				For $A$ containing only 1 element, it is connected as it can no be written as the union of two disjoint non-empty closed subsets.
-			\item
-				If $A$ is not an interval and the corner cases in a) are excluded, then it can be written as union of non-empty, disjoint closed subsets. Thus $A$ is not connected.
+
 		\item
 
-		\end{enumerate}
-	  \end{proof}
+		\item
 
@@
 %----------------------------------------------------------------------------------------
-
-\section{Rolle's theorem}
-	\begin{proof}
+\section{Taylor's theorem}
 	\begin{enumerate}
 		\item
-				For $n=1$, if $f(x)$ has 2 distinct roots in $[a, b]$, then there exists the maximum $M$ and minimum $m$ between $[a, b]$ according to the extream value theorem.\\
-				If $M = m$, then $f(x)$ is constant, and it's obvious that for any $c \in [a, b]$, $f\prime(c) = 0$; \\
-				If $M \neq m$, then $\exists \xi \in (a, b)$, s.t.  $f(\xi)$ reaches its extream, and equals to 0.
+
 		\item
-				As induction hypothesis, assume the statement is true for $n = k$.
-			\item 
-				For $n = k+1$, where $f(x)$ has $k+2$ distinct roots denoted as $c_0 < c_1 < ...
-<c_k < c_{k+1}$, applying the results for $n = 1$ on each gap $[c_i, c_{i+1}]\ (i = 0, 1, ...
-, k)$, then $g(x) \triangleq f'(x)$ has $k+1$ roots in $[c_0, c_{k+1}]$.
-By induction hypothesis, there exists $c \in [c_0, c_{k+1}]$ s.t.
-$g^{(k)}(c) = f^{(k+1)} = f^{(n)} 0$.
-Thus the statement holds true for $n = k+1$.
+
 	\end{enumerate}
-	\end{proof}
 
@@
 %----------------------------------------------------------------------------------------
-
-\section{Extreme value theorem}
-
+\section{Convergence of rationals to irrationals}
 	\begin{enumerate}
 		\item
-		\begin{proof}
-
-		\end{proof}
 
 		\item
-		\begin{proof}
-
-		\end{proof}
 
 		\item
-		\begin{proof}
 
-		\end{proof}
-\end{enumerate}
-
-%----------------------------------------------------------------------------------------
-%	PROBLEM 5
-%----------------------------------------------------------------------------------------
-
-\section{Continuity}
-
-\begin{enumerate}
-	\item
-		\begin{proof}
-
-		\end{proof}
-
-	\item
-		\begin{proof}
-
-		\end{proof}
-
-	\item
-		\begin{proof}
-
-		\end{proof}
 	\end{enumerate}

### 2018-06-10 VV570/HW3/assignment.tex
ex1 done

@@
 		\item
+			\begin{proof}
+				As $C_i$ is closed and $C$ is the intersection of these closed sets, $C$ is closed.\\
+				It's clear that $C$ is bounded. Thus, by Heine-Borel theorem, $C$ is compact.
+			\end{proof}
+		\item
+			\begin{proof}
+				Suppose $x \in C_m$, $y \in C_n$ and $x < y$.
+There are $2^m$ subsets in $C_m$ and the length of each subset is $\frac{1}{3^m}$.
+Also, there are $2^n$ subsets in $C_n$ and the length of each subset is $\frac{1}{3^n}$.
+As $C \subset C_m \cap C_n$, suppose $ m \leq n$, there must exist a subset in $C_n$ s.t.
+$x \in C_n$.
+\\
+				If $x$ and $y$ lie in the same subset of $C_n$, with further division of the subset, there will be a gap between $x$ and $y$, thus, there exists an element $z$ lies in the gap and satisfies $x < z < y$.\\
+				If $x$ and $y$ lie in different subsets of $C_n$, denoted as $C_{n, i}$ and $C_{n, j}$,it's obvious that such a $z$ exists in the gap between $C_{n, i}$ and $C_{n, j}$ and satisfies $x < z < y$.
+			\end{proof}
+		\item 
+			\begin{enumerate}
+				\item
+					0
+				\item
+					\begin{proof}
+						As there are $2^n$ subsets in $C_n$ and the length of each subset is $\frac{1}{3^n}$, thus the Lebesgue measure of $C_n$ is the sum of the Lebesgue measure of each closed subset.
+Thus $\lambda(C_n) = (\frac{2}{3})^n$.\\
+						As $C = \bigcap\limits_{n=1}^{\infty} C_n$, then $\lambda(C) \leq \lambda(C_n) = (\frac{2}{3})^n$, thus $\lambda(C) = 0$.
+					\end{proof}
+			\end{enumerate}
+		\item 
+			\begin{enumerate}
+				\item 
+					\begin{proof}
+						As the end points of each subset in $C_n$ is not removed in any subdivision, thus $C$ is not empty.
+					\end{proof}
+				\item 
+					\begin{equation}
+						x = \sum_{i=1}^{\infty} \frac{a_i}{3^i}, \ \ \text{with $a_i \in \{0, 2\}$}
+					\end{equation}
+				\item 
+					Consider the $i-th$ digit in elemnet $s_i$, it will be possible to construct such an element that the $i-th$ digit is different from that in $s_i$, thus $s$ is not included in the original list.
+				\item 
+					\begin{proof}
+						Suppose $C$ is countable, express each $x \in C$ in ternary form, then each digit in $x$ is either 0 or 2.
+Thus, the choice of each digit appears to be binary.
+Consider the $i-th$ digit in elemnet $x_i$, it will be possible to construct such an element $t$, whose $i-th$ digit is different from that in $x_i$(complementary).
+Thus $t$ is not included in the original list, which implies the assumption fails.
+					\end{proof}
+			\end{enumerate}
 
 		\item 
-
-		\item
-
-		\item
+			Althouth $C$ is uncountable, but the measure of its complement is 1, which is illustrated below, thus the measure of $C$ is 0.		
+			\begin{equation}
+				\begin{aligned}
+					\lambda(C^c) & = \frac{1}{3} + 2 * \frac{1}{9} + ... \\
+					             & = \frac{1}{3}\sum_{i=0}^{\infty} (\frac{2}{3})^n\\
+					             & = \frac{1}{3} \lim\limits_{n\rightarrow\infty}\frac{1-(2/3)^n}{1-(2/3)}\\
+					             & = 1
+          		\end{aligned}
+			\end{equation}
 

### 2018-06-11 VV570/HW3/assignment.tex
add ex2-1

@@
 		\item
-
+			\begin{proof}
+				It's easy to verify that $f_0, f_1$ are monotonically increasing continuous functions.\\
+				Suppose $f_n$ are still monotonically increasing continuous functions for $ n = k$.\\
+				For $n = k+1$, as $f_{k+1}$ is only different from $f_k$ on each closed subset of $C_k$, whose length is $\frac{1}{3^n}$ and is denoted as $I_{k, p} (1\leq p \leq 2^k$) here, it is left to prove that $f_{k+1}$ remains  monotonically increasing continuous on each $I_{k, p}$ after the construction process.\\
+				Since $f_k$ is linear on each $I_{k, p}$, and the recursive construction process doesn't change the values on each ending points, on which the values of $f_k$ is denoted as $a, b$ recursively, the subset of $I_{k, p}$ is valid and the value of $f_{k+1}$ on the central part, whose length is $\frac{1}{3^{k+1}}$, is $\frac{a+b}{2}$.
+As the measure of the remaining parts of $I_{k, p}$ is not 0, the linear function connecting each ending points is obviously valid.
+Thus, the new function $f_{k+1}$ is still  monotonically increasing continuous.
+			\end{proof}
 		\item
-
+			\begin{proof}
+				Let $g_n(x) = \vert f_n(x) - f(x) \vert$, then $g_n(x)$ is positive on $C_n$ and 0 on other places.
+Further, $g_n(x)$ is symmetric around $x = 1/2$, thus, only $[0, 1/2]$ is considered for simplicity.\\
+				Given any $\xi > 0$, it is left to find $N$ s.t. $g_n(x) < \xi$ when $n > N$.
+			\end{proof}
 		\item

### 2018-06-11 VV570/HW3/assignment.tex
add ex4

@@
 			\begin{proof}
-				Let $g_n(x) = \vert f_n(x) - f(x) \vert$, then $g_n(x)$ is positive on $C_n$ and 0 on other places.
-Further, $g_n(x)$ is symmetric around $x = 1/2$, thus, only $[0, 1/2]$ is considered for simplicity.\\
-				Given any $\xi > 0$, it is left to find $N$ s.t. $g_n(x) < \xi$ when $n > N$.
+				Let $g_n(x) = \vert f_n(x) - f(x) \vert$, then $g_n(x)$ is positive on $C_n$ and 0 on other places. Further, $g_n(x)$ holds the same value on each closed subset of $C_n$.\\
+				Given any $\xi > 0$, it is left to find $N$ s.t. $g_n(x) < \xi$ when $n > N$. \\
+				As $g_n(x)$ reaches its extream $\frac{1}{6} \frac{1}{3^n}$ at the $\frac{1}{3}$ and $\frac{2}{3}$ of each compact subset of $C_n$, thus, given any $\xi$
+
+				\begin{equation}
+					\frac{1}{6} \frac{1}{3^n} < \xi
+				\end{equation}
+
+				which is equivalent to
+
+				\begin{equation}
+					n > \frac{ln(\frac{1}{6\xi})}{ln(3)} \triangleq N
+				\end{equation}
+
+				and the target $N$ is given as above.
 			\end{proof}
 		\item 
+			\begin{proof}
+				As $f_c(x)$ is continous over $[0, 1]$, it is left to prove that a continous function on a compact is uniformly continous, which can be proved by contradiction.
+
+			\end{proof}
 
@@
 		\item
+			\begin{proof}
+				As $e$ can be written as 
+				\begin{equation}
+					e = \sum_{i=0}^{\infty} \frac{1}{i!}
+				\end{equation}
+
+				Suppose it is rational, then it can be written as below, where $p, q$ are prime to each other.
+
+				\begin{equation}
+					e = \frac{p}{q} 
+				\end{equation}
+				Thus
+				\begin{equation}
+					p(q-1)! = q! \sum_{i=0}^{q} \frac{1}{i!} +  q! \sum_{i=q+1}^{\infty} \frac{1}{i!} 
+				\end{equation}
+				Since both LHS  and  the first part of RHS are integers, the second part of RHS(denoted as $RHS_2$) should be an integer as well.//
+				$RHS_2$ can be further expanded as below
+				\begin{equation}
+					\begin{aligned}
+						RHS_2 & = \frac{1}{q+1} + \frac{1}{(q+1)(q+2)} + \frac{1}{(q+1)(q+2)(q+3)} + ...\\
+						           & <  \frac{1}{q+1} + \frac{1}{(q+1)^2} + \frac{1}{(q+1)^3} + ...\\
+						           & = \frac{1}{q}\\
+						           & < 1
+					\end{aligned}
+				\end{equation}
+				Therefore $RHS_2$ is not an integer as $RHS_2 > 0$. Thus the assumption fails, and $e$  is irrational.
+			\end{proof}
 
 		\item
+			\begin{proof}
+				It's clear that $u_n$ is increasing, and the limit is $e$, so the maximum distance between 2 element can be denoted as 
+				\begin{equation}
+					d_{max} < e - (1+\frac{1}{n})^n
+				\end{equation}
+
+				For any $\xi > 0$, let $d_{max} < \xi$, it is satisfied when $n > N $, where $N$ is the index of the first element s.t. $u_N > e-\xi$.\\
+				Thus $u_n$ is a cauchy sequence converging to $e$.
+			\end{proof}
 
 		\item
-
+			No, as the limit of a rational sequence may not converging to a rational.
 	\end{enumerate}

### 2018-06-11 VV570/HW3/assignment.tex
all fulfilled

@@
 					             & = \frac{1}{3}\sum_{i=0}^{\infty} (\frac{2}{3})^n\\
-					             & = \frac{1}{3} \lim\limits_{n\rightarrow\infty}\frac{1-(2/3)^n}{1-(2/3)}\\
-					             & = 1
+					             & = \frac{1}{3} \lim\limits_{n\rightarrow\infty}\frac{1-(2/3)^n}{1-(2/3)} = 1
           		\end{aligned}
@@
 		\item 
+			\begin{enumerate}
+				\item 
 					\begin{proof}
-				As $f_c(x)$ is continous over $[0, 1]$, it is left to prove that a continous function on a compact is uniformly continous, which can be proved by contradiction.
-
+						As $f_c(x)$ is continous over $[0, 1]$, it is left to prove that a continous function on a compact is uniformly continous, which can be proved by contradiction.\\
+						(the proof haven't figured out yet...)
 					\end{proof}
@@
 				\item 
+					\begin{proof}
+						For any $x \in (0, 1] \cap C$, $f_c(x)$ can be expressed as below
+
+						\begin{equation}
+							f_c(x) = sup\{ f_c(y) | y < x, y \in [0, 1] \backslash C  \}
+						\end{equation}
+
+						Thus $f_c(x)$ is monotonically increasing.
+					\end{proof}
+
+				\item
+					\begin{proof}
+						As $f_c(x)$ is constant on each segment dropped by $C$, thus $f_c'(x)$ is almost 0 everywhere.
+					\end{proof}
+
+			\end{enumerate}
+
+		\item 
+			\begin{proof}
+				Assume $f_c(x)$  is absolutely continous, then its Riemann integral exists, which can be expressed as 
+				\begin{equation}
+					\int_{0}^{1} f_c'(x) dx = f_c(1) - f_c(0) \label{cantor_rie}
+				\end{equation}
+
+				However, the $LHS$ of (\ref{cantor_rie}) is 0 as $f_c'(x)$ is 0 almost everywhere, while the $RHS$ of (\ref{cantor_rie}) is 1.
+Thus its riemann integral doesn't exist, and therefore the assumption fails.
+
+			\end{proof}
 
@@
 		\item 
+			\begin{proof}
+				For $n=0$, apply the fundamental theorem of calculus to $f(x)$ and its derivatives, $f(x)$ can be written as below. It's clear that the theorem is valid in such case.
+				\begin{equation}
+					f(x) = f(a) + \int_{a}^{x} f'(t) dt
+				\end{equation}
+
+				Suppose the theorem is still valid for $n = k$, then $f(x)$ can be written as 
+				\begin{equation}
+					f(x) = \sum_{i=0}^{k}\frac{f^{i}(a)}{i!}(x-a)^i + \frac{1}{k!}\int_{a}^{x} (x-t)^k f^{(k+1)}(t) dt \label{rhs}
+				\end{equation}
+
+				For $n = k+1$, as $f^{(k+1)}$ is absolutely continous, apply the fundamental theorem of calculus to $f^{(k+1)}$, the second part of RHS of $f(x)$ can be written as below
+				\begin{equation}
+					\begin{aligned}
+						RHS_2 & = \frac{1}{k!}\int_{a}^{x} (x-t)^k [f^{(k+1)}(a) + \int_{a}^{t}f^{(k+2)}(u) du] dt\\
+						           & = \frac{f^{(k+1)}(a)}{k!}\int_{a}^{x}(x-t)^k dt + \frac{1}{k!}\int_{a}^{x}(x-t)^k \int_{a}^{t} f^{(k+2)}(u) du dt\\
+						           & =  \frac{f^{k+1}(a)}{(k+1)!}(x-a)^{k+1} + \frac{1}{k!}\int_{a}^{x}(x-t)^k \int_{a}^{t} f^{(k+2)}(u) du dt
+					\end{aligned}
+				\end{equation}
+				Let
+				\begin{equation}
+					g(t) = \int_{a}^{t} f^{(k+2)}(u) du
+				\end{equation}
+				$RHS_2$ can be further expressed as
+				\begin{equation}
+					\begin{aligned}
+						RHS_2 & =  \frac{f^{k+1}(a)}{(k+1)!}(x-a)^{k+1} + \frac{1}{k!}\int_{a}^{x}(x-t)^k g(t) dt\\
+								   & =  \frac{f^{k+1}(a)}{(k+1)!}(x-a)^{k+1} - \frac{1}{(k+1)!}\int_{a}^{x} g(t) d(x-t)^{k+1}\\
+								   & =  \frac{f^{k+1}(a)}{(k+1)!}(x-a)^{k+1} - \frac{1}{(k+1)!}[\left. (x-t)^{k+1} g(t) \right|_{a}^{x} - \int_{a}^{x}(x-t)^{k+1} g'(t) dt]
+					\end{aligned}
+				\end{equation}
+				As $g(a) = 0$ and $g'(t) = f^{(k+2)}(t)$, $RHS_2$ can be simplified as 
+				\begin{equation}
+					RHS_2 = \frac{f^{k+1}(a)}{(k+1)!}(x-a)^{k+1} + \frac{1}{(k+1)!}\int_{a}^{x}(x-t)^{k+1}  f^{(k+2)}(t)dt \label{rhs2}
+				\end{equation}
+
+				Substitude (\ref{rhs2}) into (\ref{rhs}), $f(x)$ can be expressed as below when $n = k+1$
+				\begin{equation}
+					\begin{aligned}
+						f(x) & = \sum_{i=0}^{k+1}\frac{f^{i}(a)}{i!}(x-a)^i + \frac{1}{(k+1)!}\int_{a}^{x} (x-t)^{k+1} f^{(k+2)}(t) dt\\
+						      & = \sum_{i=0}^{n}\frac{f^{i}(a)}{i!}(x-a)^i + \frac{1}{n!}\int_{a}^{x} (x-t)^{n} f^{(n+1)}(t) dt\\
+					\end{aligned}
+				\end{equation}
+				Thus the theorem is still valid when $n$ is extended to $k+1$.
+			\end{proof}
 
 		\item 
+			\begin{proof}
+				It is left to prove that there exists $c\in [a, x]$ s.t. 
+				\begin{equation}
+					\frac{1}{n!}\int_{a}^{x} (x-t)^{n} f^{(n+1)}(t) dt = \frac{f^{(n+1)}(c)}{(n+1)!}(x-a)^{n+1}
+				\end{equation}
+				which is equal to 
+				\begin{equation}
+					(n+1)\int_{a}^{x} (x-t)^{n} f^{(n+1)}(t) dt = f^{(n+1)}(c)(x-a)^{n+1} \label{target}
+				\end{equation}
+
+				As the LHS of (\ref{target}) can be expanded as below
+				\begin{equation}
+					\begin{aligned}
+						LHS & = - \int_{a}^{x}f^{(n+1)}(t) d(x-t)^{n+1}\\
+							   & = - [\left. (x-t)^{n+1}f^{(n+1)}(t)\right|_{a}^{x} - \int_{a}^{x}(x-t)^{n+1}df^{(n+1)}(t)]
+					\end{aligned}
+				\end{equation}
+
+				Apply the medium value theorem ...(haven't figured out yet...)
+
+			\end{proof}
 
@@
 						           & <  \frac{1}{q+1} + \frac{1}{(q+1)^2} + \frac{1}{(q+1)^3} + ...\\
-						           & = \frac{1}{q}\\
-						           & < 1
+						           & = \frac{1}{q} < 1 \\
 					\end{aligned}

### 2018-06-12 VV570/HW4/assignment.tex
add ex2

--- 2018-06-11 VV570/HW3/assignment.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Introduction to Numerical Analysis \\ HW3 \\ % The assignment title
+\huge Introduction to Numerical Analysis \\ HW4 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 %----------------------------------------------------------------------------------------
-\section{Cantor's Set}
+\section{Legendre Polynomials}
 	\begin{enumerate}
 		\item
-			\begin{proof}
-				As $C_i$ is closed and $C$ is the intersection of these closed sets, $C$ is closed.\\
-				It's clear that $C$ is bounded. Thus, by Heine-Borel theorem, $C$ is compact.
-			\end{proof}
-		\item
-			\begin{proof}
-				Suppose $x \in C_m$, $y \in C_n$ and $x < y$.
-There are $2^m$ subsets in $C_m$ and the length of each subset is $\frac{1}{3^m}$.
-Also, there are $2^n$ subsets in $C_n$ and the length of each subset is $\frac{1}{3^n}$.
-As $C \subset C_m \cap C_n$, suppose $ m \leq n$, there must exist a subset in $C_n$ s.t.
-$x \in C_n$.
-\\
-				If $x$ and $y$ lie in the same subset of $C_n$, with further division of the subset, there will be a gap between $x$ and $y$, thus, there exists an element $z$ lies in the gap and satisfies $x < z < y$.\\
-				If $x$ and $y$ lie in different subsets of $C_n$, denoted as $C_{n, i}$ and $C_{n, j}$,it's obvious that such a $z$ exists in the gap between $C_{n, i}$ and $C_{n, j}$ and satisfies $x < z < y$.
-			\end{proof}
-		\item 
-			\begin{enumerate}
-				\item
-					0
-				\item
-					\begin{proof}
-						As there are $2^n$ subsets in $C_n$ and the length of each subset is $\frac{1}{3^n}$, thus the Lebesgue measure of $C_n$ is the sum of the Lebesgue measure of each closed subset.
-Thus $\lambda(C_n) = (\frac{2}{3})^n$.\\
-						As $C = \bigcap\limits_{n=1}^{\infty} C_n$, then $\lambda(C) \leq \lambda(C_n) = (\frac{2}{3})^n$, thus $\lambda(C) = 0$.
-					\end{proof}
-			\end{enumerate}
-		\item 
-			\begin{enumerate}
-				\item 
-					\begin{proof}
-						As the end points of each subset in $C_n$ is not removed in any subdivision, thus $C$ is not empty.
-					\end{proof}
-				\item 
-					\begin{equation}
-						x = \sum_{i=1}^{\infty} \frac{a_i}{3^i}, \ \ \text{with $a_i \in \{0, 2\}$}
-					\end{equation}
-				\item 
-					Consider the $i-th$ digit in elemnet $s_i$, it will be possible to construct such an element that the $i-th$ digit is different from that in $s_i$, thus $s$ is not included in the original list.
-				\item 
-					\begin{proof}
-						Suppose $C$ is countable, express each $x \in C$ in ternary form, then each digit in $x$ is either 0 or 2.
-Thus, the choice of each digit appears to be binary.
-Consider the $i-th$ digit in elemnet $x_i$, it will be possible to construct such an element $t$, whose $i-th$ digit is different from that in $x_i$(complementary).
-Thus $t$ is not included in the original list, which implies the assumption fails.
-					\end{proof}
-			\end{enumerate}
 
 		\item
-			Althouth $C$ is uncountable, but the measure of its complement is 1, which is illustrated below, thus the measure of $C$ is 0.		
-			\begin{equation}
-				\begin{aligned}
-					\lambda(C^c) & = \frac{1}{3} + 2 * \frac{1}{9} + ... \\
-					             & = \frac{1}{3}\sum_{i=0}^{\infty} (\frac{2}{3})^n\\
-					             & = \frac{1}{3} \lim\limits_{n\rightarrow\infty}\frac{1-(2/3)^n}{1-(2/3)}\\
-					             & = 1
-          		\end{aligned}
-			\end{equation}
 
-	\end{enumerate}
-
-%----------------------------------------------------------------------------------------
-%	PROBLEM 2
-%----------------------------------------------------------------------------------------
-\section{Cantor's Function}
-	\begin{enumerate}
-		\item
-			\begin{proof}
-				It's easy to verify that $f_0, f_1$ are monotonically increasing continuous functions.\\
-				Suppose $f_n$ are still monotonically increasing continuous functions for $ n = k$.\\
-				For $n = k+1$, as $f_{k+1}$ is only different from $f_k$ on each closed subset of $C_k$, whose length is $\frac{1}{3^n}$ and is denoted as $I_{k, p} (1\leq p \leq 2^k$) here, it is left to prove that $f_{k+1}$ remains  monotonically increasing continuous on each $I_{k, p}$ after the construction process.\\
-				Since $f_k$ is linear on each $I_{k, p}$, and the recursive construction process doesn't change the values on each ending points, on which the values of $f_k$ is denoted as $a, b$ recursively, the subset of $I_{k, p}$ is valid and the value of $f_{k+1}$ on the central part, whose length is $\frac{1}{3^{k+1}}$, is $\frac{a+b}{2}$.
-As the measure of the remaining parts of $I_{k, p}$ is not 0, the linear function connecting each ending points is obviously valid.
-Thus, the new function $f_{k+1}$ is still  monotonically increasing continuous.
-			\end{proof}
-		\item
-			\begin{proof}
-				Let $g_n(x) = \vert f_n(x) - f(x) \vert$, then $g_n(x)$ is positive on $C_n$ and 0 on other places.
-Further, $g_n(x)$ is symmetric around $x = 1/2$, thus, only $[0, 1/2]$ is considered for simplicity.\\
-				Given any $\xi > 0$, it is left to find $N$ s.t. $g_n(x) < \xi$ when $n > N$.
-			\end{proof}
 		\item
@@
 %----------------------------------------------------------------------------------------
+%	PROBLEM 2
+%----------------------------------------------------------------------------------------
+\section{Interpolation}
+	$f(2)$ can be determined using the Lagrange interpolation scheme.
+	As the lagrange interpolation polynomial can be written as below, and $n=8$ in this case.
+	\begin{equation}
+		f(x) = \sum_{i=1}^{n}f(x_i) l_i(x)\label{lag_interp}
+	\end{equation}
+
+	$l_i(x)$ are the base functions that can be written as below.
+	\begin{equation}
+		l_i(x) = \frac{(x-x_1)(x-x_2)...(x-x_{i-1})(x-x_{i+1})...(x-x_{n-1})(x-x_n)}{(x_i-x_1)(x_i-x_2)...(x_i-x_{i-1})(x_i-x_{i+1})...(x_i-x_{n-1})(x_i-x_n)}
+	\end{equation}
+
+	$l_i(2)$ are calculated accordingly as below.
+
+	\begin{center}
+		\begin{tabular}{cccc}
+			$l_1(2) = -0.0006$ & $l_2(2) = 0.1224$ & $l_3(2) = -0.5600$ & $l_4(2) = 1.0606$ \\
+			$l_5(2) = 0.4167$ & $l_6(2) = -0.0400$ & $l_7(2) = 0.0012$ & $l_8(2) = -0.0003$\\
+		\end{tabular}
+	\end{center}
+
+	Thus, $f(2)$ is calculated according to (\ref{lag_interp}) as 11.0.
+
+%----------------------------------------------------------------------------------------
 %	PROBLEM 3
 %----------------------------------------------------------------------------------------
-\section{Taylor's theorem}
+\section{Newton's form of interpolation polynomial}
 	\begin{enumerate}
@@
 
-	\end{enumerate}
+		\item
 
-%----------------------------------------------------------------------------------------
-%	PROBLEM 4
-%----------------------------------------------------------------------------------------
-\section{Convergence of rationals to irrationals}
-	\begin{enumerate}
+		\item
+
 		\item

### 2018-06-15 VV570/HW4/assignment.tex
add ex1-1

@@
 		\item
+			\begin{proof}
+				Let
+				\begin{equation}
+					\varphi(x) = (x^2-1)^n
+				\end{equation}
+				then
+				\begin{equation}
+					Q_n(x) = \frac{1}{2^n n!}\varphi^{(n)}(x)
+				\end{equation}
+				and
+				\begin{equation}
+					\varphi^{(k)}(1) = \varphi^{(k)}(-1) = 0 \ \  (\text{$k=0,1, ... , n-1$})
+				\end{equation}
+				Suppose $h(x) \in C^n(-1,1)$, then performing integration by parts
+				\begin{equation}
+					\begin{aligned}
+						\int_{-1}^{1} P_n(x)h(x)dx 
+						& = \frac{1}{2^n n!}\int_{-1}^{1}\varphi^{(n)}(x)h(x)dx \\
+						& = -\frac{1}{2^n n!} \int_{-1}^{1}\varphi^{(n-1)}(x)h'(x)dx \\
+						& = ...\\
+						& = \frac{(-1)^n}{2^n n!}\int_{-1}^{1}\varphi(x)h^{(n)}(x)dx
+					\end{aligned}
+				\end{equation}
+				Thus, the proof can be discussed on 2 cases
 
+				\begin{enumerate}
+					\item 
+						If the order of $g(x)$ is less than $n$, then 
+						\begin{equation}
+							g^{(n)}(x) = 0
+						\end{equation}
+						Thus
+						\begin{equation}
+							\int_{-1}^{1}Q_n(x)Q_m(x)dx = 0 \ \ (\text{$n\neq m$})
+						\end{equation}
+
+					\item
+						If $g(x) = Q_n(x)$, the the $n-th$ derivative of $g(x)$ is
+						\begin{equation}
+							g^{(n)}(x) = Q^{(n)}(x) = \frac{(2n)!}{2^n n!}
+						\end{equation} 
+						Thus
+						\begin{equation}
+							\begin{aligned}
+								\int_{-1}^{1}Q_n(x)Q_m(x)dx	
+								& = \int_{-1}^{1}Q_n^2(x)dx \\
+								& = \frac{(-1)^n (2n)!}{2^{2n}(n!)^2}\int_{-1}^{1}(x^2-1)^n dx\\
+								& = \frac{(2n)!}{2^{2n}(n!)^2}\int_{-1}^{1}(1-x^2)^n dx\\
+								& = \frac{(2n)!}{2^{2n}(n!)^2} \int_{0}^{\pi/2} cos^{2n+1}t dt\\
+								& = \frac{(2n)!}{2^{2n}(n!)^2} \frac{2 \times 4 \times ... \times (2n)}{1\times3\times ... \times (2n+1)}\\
+								& = \frac{2}{2n+1} \ \ (\text{$n = m$})
+							\end{aligned}
+						\end{equation}
+				\end{enumerate}
+
+				Thus, $(Q_n)_{n\in\mathbb{N}}$ are a sequence of orthogonal polynomials.
+
+			\end{proof}
 		\item

### 2018-06-15 VV570/HW4/assignment.tex
add ex1-2

@@
 					\item
-						If $g(x) = Q_n(x)$, the the $n-th$ derivative of $g(x)$ is
+						If $g(x) = Q_n(x)$, then the $n-th$ derivative of $g(x)$ is
 						\begin{equation}
@@
 				Thus, $(Q_n)_{n\in\mathbb{N}}$ are a sequence of orthogonal polynomials.
+			\end{proof}
 
+		\item
+			\begin{proof}
+				Denote
+				\begin{equation}
+				\varphi(x) = (x^2-1)^n
+				\end{equation}
+				then
+				\begin{equation}
+				Q_n(x) = \frac{1}{2^n n!}\varphi^{(n)}(x)
+				\end{equation}
+				As the power of each item in $\varphi(x)$ is even when $\varphi(x)$ is extended, thus $\varphi^{(n)}(x)$ is even function if the order of derivative is even, and $\varphi^{(n)}(x)$ is odd function if the order of derivative is odd.
+\\
+				Therefore $Q_n(x)$ is even function if $n$ is even, and $Q_n(x)$ is odd function if $n$ is odd. So, it can be summarized as $Q_n(-x) = (-1)^n Q_n(x)$. 
 			\end{proof}
-		\item
 

### 2018-06-18 VV570/HW4/assignment.tex
add ex1-3

@@
 					\item 
-						If the order of $g(x)$ is less than $n$, then 
+						If the order of $h(x)$ is less than $n$, then 
 						\begin{equation}
-							g^{(n)}(x) = 0
+							h^{(n)}(x) = 0
 						\end{equation}
@@
 					\item
-						If $g(x) = Q_n(x)$, then the $n-th$ derivative of $g(x)$ is
+						If $h(x) = Q_n(x)$, then the $n-th$ derivative of $g(x)$ is
 						\begin{equation}
-							g^{(n)}(x) = Q^{(n)}(x) = \frac{(2n)!}{2^n n!}
+							h^{(n)}(x) = Q^{(n)}(x) = \frac{(2n)!}{2^n n!}
 						\end{equation} 
@@
 								\int_{-1}^{1}Q_n(x)Q_m(x)dx	
-								& = \int_{-1}^{1}Q_n^2(x)dx \\
+								& = \int_{-1}^{1}Q_n^2(x)dx  \ \ (\text{$n = m$}) \\
 								& = \frac{(-1)^n (2n)!}{2^{2n}(n!)^2}\int_{-1}^{1}(x^2-1)^n dx\\
@@
 								& = \frac{(2n)!}{2^{2n}(n!)^2} \frac{2 \times 4 \times ... \times (2n)}{1\times3\times ... \times (2n+1)}\\
-								& = \frac{2}{2n+1} \ \ (\text{$n = m$})
+								& = \frac{2}{2n+1}
 							\end{aligned}
@@
 		\item
+			\begin{proof}
+				As $xQ_n(x)$ can be written as
+				\begin{equation}
+					xQ_n(x) = \sum_{i=0}^{n+1} a_i Q_i(x)
+				\end{equation}
+				According to the orthogonality of Legendre polynomials, $a_i = 0$ for $i = 0, 1, ... , n-2, n$, as
+				\begin{equation}
+					0 = \int_{-1}^{1}xQ_n(x) Q_i(x) dx = a_i \int_{-1}^{1}Q_i^2(x)dx \ \ (i = 0, 1, ... , n-2, n)
+				\end{equation}
+				Thus,  $xQ_n(x)$ can be written as
+				\begin{equation}
+					xQ_n(x) = a_{n-1} Q_{n-1}(x) + a_{n+1} Q_{n+1}(x)
+				\end{equation}
+				Since the highest order item in $xQ_n(x)$ is $x^{n+1}$ and its coefficient is $\frac{(2n)!}{2^n (n!)^2}$, thus
+				\begin{equation}
+					\frac{(2n)!}{2^n (n!)^2} = a_{n+1} \frac{(2n+2)!}{2^{n+1} (n+1)!^2}
+				\end{equation}
+				which implies that
+				\begin{equation}
+					a_{n+1} = \frac{n+1}{2n+1} 
+				\end{equation}
+				Denote
+				\begin{equation}
+					I_n = \int_{-1}^{1} xQ_{n-1}(x)Q_{n}(x)dx
+ 				\end{equation}
+ 				Then
+ 				\begin{equation}
+ 					I_n = a_{n-1}\int_{-1}^{1} Q_{n-1}^2(x)dx = a_{n-1} \frac{2}{2n-1}
+ 				\end{equation}
+ 				As
+ 				\begin{equation}
+ 					I_{n+1} = a_{n+1}\int_{-1}^{1}Q_{n+1}^2(x)dx = a_{n+1} \frac{2}{2n+3} = \frac{2(n+1)}{(2n+1)(2n+3)}
+ 				\end{equation}
+ 				Thus
+ 				\begin{equation}
+ 					I_n = \frac{2n}{(2n-1)(2n+1)}
+ 				\end{equation}
+ 				which implies that
+ 				\begin{equation}
+ 					a_{n-1} = \frac{n}{2n+1}
+ 				\end{equation}
+ 				Hence
+ 				\begin{equation}
+ 					(2n+1)xQ_n(x) = nQ_{n-1}(x) + (n+1)Q_{n+1}(x)
+ 				\end{equation}
+			\end{proof}
 
 		\item
+			\begin{proof}
+
+			\end{proof}
 

### 2018-06-19 VV570/HW4/assignment.tex
ex1 done!
ex3 done

@@
 			\begin{proof}
-
+				As 
+				\begin{equation}
+					\begin{aligned}
+						Q_n(x) & = \frac{1}{2^n n!}[(x+1)^n(x-1)^n]^{(n)} \\
+							   & = \frac{2^n}{n!}[(\frac{x+1}{2})^n(\frac{x-1}{2})^n]^{(n)}
+					\end{aligned}
+				\end{equation}
+				Denote
+				\begin{equation}
+					f(x) = (\frac{x+1}{2})^n
+				\end{equation}
+				and
+				\begin{equation}
+					g(x) = (\frac{x-1}{2})^n
+				\end{equation}
+				Then
+				\begin{equation}
+					f^{(k)}(x) = \frac{n!}{2^k (n-k)!} (\frac{x+1}{2})^{n-k}
+				\end{equation}
+				and
+				\begin{equation}
+					g^{(k)}(x) = \frac{n!}{2^k (n-k)!} (\frac{x-1}{2})^{n-k}
+				\end{equation}
+				Since
+				\begin{equation}
+					(fg)^{(n)} = \sum_{k=0}^{n} C_n^k f^{(k)}g^{(n-k)}
+				\end{equation}
+				Thus
+				\begin{equation}
+					\begin{aligned}
+						Q_n(x) & = \frac{2^n}{n!} \sum_{k=0}^{n} C_n^k f^{(k)}(x) g^{(n-k)}(x)\\
+							   & = \frac{2^n}{n!} \sum_{k=0}^{n} C_n^k \frac{n!}{2^k (n-k)!} (\frac{x+1}{2})^{n-k} \frac{n!}{2^{n-k} k!} (\frac{x-1}{2})^k \\
+							   & = \sum_{k=0}^{n} C_n^k \frac{n!}{(n-k)!k!} (\frac{x+1}{2})^{n-k} (\frac{x-1}{2})^k\\
+							   & = \sum_{k=0}^{n} (C_n^k)^2 (\frac{x+1}{2})^{n-k} (\frac{x-1}{2})^k\\
+							   &= \sum_{k=0}^{n} (-1)^k \binom{n}{k}^2 (\frac{1+x}{2})^{n-k} (\frac{1-x}{2})^k
+					\end{aligned}
+				\end{equation}
 			\end{proof}
@@
 		\item 
+			\begin{enumerate}
+				\item
+					\begin{proof}
+						Denote $P^1(x) = a_0 + a_1 x$, where $a_0$ and $a_1$ are coefficients to be determined.Then
+						\begin{equation}
+							\left\{
+							\begin{aligned}
+								f(x_0) & = a_0 + a_1 x_0 \\
+								f(x_1) & = a_0 + a_1 x_1
+							\end{aligned}
+							\right.
+						\end{equation}
+						$a_0$ and $a_1$ are solved as below
+						\begin{equation}
+							\left\{
+							\begin{aligned}
+								a_0 & = \frac{x_1 f(x_0) - x_0 f(x_1)}{x_1 - x_0}\\
+								a_1 & = \frac{f(x_1)-f(x_0)}{x_1 - x_0}
+							\end{aligned}
+							\right.
+						\end{equation}
+						Thus
+						\begin{equation}
+							\begin{aligned}
+								P^1(x) & = \frac{x_1 f(x_0) - x_0 f(x_1)}{x_1 - x_0} + \frac{f(x_1) - f(x_0)}{x_1 - x_0} x \\
+									   & = \frac{(x_1 - x_0)f(x_0) - x_0 (f(x_1) - f(x_0))}{x_1 - x_0} + \frac{f(x_1) - f(x_0)}{x_1 - x_0}x \\
+									   & = f(x_0) + \frac{f(x_1) - f(x_0)}{x_1 - x_0} (x-x_0)\\
+									   & = P^0(x) + \frac{f(x_1) - f(x_0)}{x_1 - x_0} (x-x_0)
+							\end{aligned}
+						\end{equation}
+					\end{proof}
 
 				\item 
+					If $P^2(x) = P^1(x) + R(x)$, then $R(x_0) = 0$ and $R(x_1) = 0$, thus $R(x) = c(x-x_1)(x-x_0)$, where $c$ is the coefficient to be determined. 
+					Since
+					\begin{equation}
+						R(x_2) = P^2(x_2) - P^1(x_2) 
+					\end{equation}
+					Thus
+					\begin{equation}
+						c(x_2 - x_1)(x_2 - x_0) = f(x_2) - [f(x_0) + \frac{f(x_1) - f(x_0)}{x_1 - x_0}(x_2 - x_0)]
+					\end{equation}
+					$c$ is solved as 
+					\begin{equation}
+						c = \frac{1}{x_2 - x_0} [\frac{f(x_2) - f(x_1)}{x_2 -x_1} - \frac{f(x_1) - f(x_0)}{x_1 - x_0}]
+					\end{equation}
+					Hence
+					\begin{equation}
+						R(x) = \frac{1}{x_2 - x_0} [\frac{f(x_2) - f(x_1)}{x_2 -x_1} - \frac{f(x_1) - f(x_0)}{x_1 - x_0}] (x-x_1)(x-x_0)
+					\end{equation}
 
 				\item
+					\begin{proof}
+						As have been shown above, the statement is valid for $j = 1, 2$. Suppose it's still valid for $j = n$, then
+						\begin{equation}
+							P^n(x) = P^{n-1}(x) + a_n \prod_{k=0}^{n-1}(x - x_k)
+						\end{equation}
+						where $a_n$ depends only on $a_0, a_1, ... , a_n$.\\
+						Let $P^{n+1}(x) = P^n(x) + R(x)$, then $R(x_k) = 0$ for $k = 0, 1, 2, ... , n$, thus
+						\begin{equation}
+							R(x) = a_{n+1} \prod_{k=0}^{n}(x-x_k)
+						\end{equation}
+						Then $a_{n+1}$ is solved as
+						\begin{equation}
+							a_{n+1} = \frac{f(x_{n+1}) - P^n(x_{n+1})}{\prod_{k=0}^{n}(x-x_k)}
+						\end{equation}
+						As $a_n$ only depends on $a_0, a_1, ... , a_n$, $P^n(x_{n+1})$ only depends on $x_0, x_1, ... , x_n, x_{n+1}$, thus $a_{n+1}$ only depends on $a_0, a_1, ... , a_n, a_{n+1}$.
+					\end{proof}
+
+			\end{enumerate}
 
 		\item
+			\begin{proof}
+				As
+				\begin{equation}
+					P^j(x) = P^{j-1}(x) + a_j \prod_{k=0}^{j-1}(x - x_k)
+				\end{equation}
+				Thus, by recursion, $P^j(x)$ can be written as
+				\begin{equation}
+					P^n(x) = P^0(x) + \sum_{j=1}^{n} a_j \prod_{k=0}^{j-1}(x-x_k)
+				\end{equation}
+			\end{proof}
 
 		\item 
+			\begin{proof}
+				(haven't figured out yet...)
+			\end{proof}
 
 		\item 
+			Algorithm that calculate the approximation of $f(x)$ is given as below
+
+			\begin{algorithm}
+			\caption{Calculation of the approximated value of $f(x)$}
+			\begin{algorithmic}[1]
+				\REQUIRE $x$, $n$, $x[i]$, $f[i]$ ($i = 0, 1, ... , n$)
+				\ENSURE $P^n(x) \approx f(x)$
+				\STATE $ret \gets 0$
+				\STATE $prod \gets 1$
+
+				\FOR{$i=0 \to n$}
+					\STATE $coef[i] \gets f[i]$
+				\ENDFOR
+
+				\FOR{$i=0 \to n$}
+					\STATE $ret \gets coef[i] * prod$
+					\STATE $prod \gets prod * (x-x_i)$
+
+					\FOR{$j= n \to i+1$}
+						\STATE $coef[j] \gets \frac{coef[j] - coef[j-1]}{x[j] - x[j-(i+1)]}$
+					\ENDFOR
+
+				\ENDFOR
+
+				\RETURN ret
+			\end{algorithmic}  
+			\end{algorithm}
+		\item 
+			\begin{proof}
+				As
+				\begin{equation}
+					f[x_k, x_{k+1}] = \frac{f_{k+1}-f_k}{x_{k+1} - x_k} = \frac{\triangledown f_k}{h}
+				\end{equation}
+				The statement is valid for $m = 1$.\\
+				Assume it is still valid for $m = n$, then
+				\begin{equation}
+					f[x_i, x_{i+1}, ... , x_{i+n}] = \frac{\triangledown^n f_i}{n! h^n}
+				\end{equation}
+				Consider $m = n+1$, by the definition of $f[x_i, x_{i+1}, ... , x_{i+n+1}]$
+				\begin{equation}
+					f[x_i, x_{i+1}, ... , x_{i+n+1}] = \frac{f[x_{i+1}, ... , x_{i+n+1}]-f[x_i, x_{i+1}, ... , x_n]}{x_{i+n+1} - x_i}
+				\end{equation}
+				By the induction hypothesis, it can be simplified as
+				\begin{equation}
+					f[x_i, x_{i+1}, ... , x_{i+n+1}] = \frac{1}{(n+1)h} \frac{1}{n! h^n} [\triangledown^n f_{i+1} - \triangledown^n f_i]
+				\end{equation}
+				By the definition of operator $\triangledown$, it can be further simplified as
+				\begin{equation}
+					f[x_i, x_{i+1}, ... , x_{i+n+1}] = \frac{\triangledown^{n+1} f_i}{(n+1)! h^{n+1}}
+				\end{equation}
+				Thus, the statement is valid for all $m \geq 1$.
+
+			\end{proof}
+		\item 
+			(haven't figured out yet...)
 
 		\item 
+		Algorithm that calculate the approximation of $f(x)$ with equidistant nodes is given as below
+
+		\begin{algorithm}
+			\caption{Calculation of the approximated value of $f(x)$ with equidistant nodes}
+			\begin{algorithmic}[1]
+				\REQUIRE $h$, $n$, $x$, $f[i]$ ($i = 0, 1, ... , n$)
+				\ENSURE $P^n(x) \approx f(x)$
+				\STATE $ret \gets 0$
+				\STATE $prod \gets 1$
+				\STATE $t \gets \frac{x-x_0}{h}$
+
+				\FOR{$i=0 \to n$}
+					\STATE $coef[i] \gets f[i]$
+				\ENDFOR
+
+				\FOR{$i=0 \to n$}
+					\STATE $ret \gets coef[i] \times prod$
+					\STATE $prod \gets prod \times \frac{t- i}{i+1}$
+
+					\FOR{$j= n \to i+1$}
+						\STATE $coef[j] \gets coef[j] - coef[j-1]$
+					\ENDFOR
+				\ENDFOR
+
+				\RETURN ret
+			\end{algorithmic}  
+		\end{algorithm}
 

### 2018-06-23 VV570/HW5/assignment.tex
import homework discriptions

--- 2018-06-15 VV570/HW4/assignment.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Introduction to Numerical Analysis \\ HW4 \\ % The assignment title
+\huge Introduction to Numerical Analysis \\ HW5 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 %----------------------------------------------------------------------------------------
-\section{Legendre Polynomials}
-	\begin{enumerate}
-		\item
-			\begin{proof}
-				Let
-				\begin{equation}
-					\varphi(x) = (x^2-1)^n
-				\end{equation}
-				then
-				\begin{equation}
-					Q_n(x) = \frac{1}{2^n n!}\varphi^{(n)}(x)
-				\end{equation}
-				and
-				\begin{equation}
-					\varphi^{(k)}(1) = \varphi^{(k)}(-1) = 0 \ \  (\text{$k=0,1, ... , n-1$})
-				\end{equation}
-				Suppose $h(x) \in C^n(-1,1)$, then performing integration by parts
-				\begin{equation}
-					\begin{aligned}
-						\int_{-1}^{1} P_n(x)h(x)dx 
-						& = \frac{1}{2^n n!}\int_{-1}^{1}\varphi^{(n)}(x)h(x)dx \\
-						& = -\frac{1}{2^n n!} \int_{-1}^{1}\varphi^{(n-1)}(x)h'(x)dx \\
-						& = ...\\
-						& = \frac{(-1)^n}{2^n n!}\int_{-1}^{1}\varphi(x)h^{(n)}(x)dx
-					\end{aligned}
-				\end{equation}
-				Thus, the proof can be discussed on 2 cases
-
-				\begin{enumerate}
-					\item 
-						If the order of $g(x)$ is less than $n$, then 
-						\begin{equation}
-							g^{(n)}(x) = 0
-						\end{equation}
-						Thus
-						\begin{equation}
-							\int_{-1}^{1}Q_n(x)Q_m(x)dx = 0 \ \ (\text{$n\neq m$})
-						\end{equation}
-
-					\item
-						If $g(x) = Q_n(x)$, then the $n-th$ derivative of $g(x)$ is
-						\begin{equation}
-							g^{(n)}(x) = Q^{(n)}(x) = \frac{(2n)!}{2^n n!}
-						\end{equation} 
-						Thus
-						\begin{equation}
-							\begin{aligned}
-								\int_{-1}^{1}Q_n(x)Q_m(x)dx	
-								& = \int_{-1}^{1}Q_n^2(x)dx \\
-								& = \frac{(-1)^n (2n)!}{2^{2n}(n!)^2}\int_{-1}^{1}(x^2-1)^n dx\\
-								& = \frac{(2n)!}{2^{2n}(n!)^2}\int_{-1}^{1}(1-x^2)^n dx\\
-								& = \frac{(2n)!}{2^{2n}(n!)^2} \int_{0}^{\pi/2} cos^{2n+1}t dt\\
-								& = \frac{(2n)!}{2^{2n}(n!)^2} \frac{2 \times 4 \times ... \times (2n)}{1\times3\times ... \times (2n+1)}\\
-								& = \frac{2}{2n+1} \ \ (\text{$n = m$})
-							\end{aligned}
-						\end{equation}
-				\end{enumerate}
-
-				Thus, $(Q_n)_{n\in\mathbb{N}}$ are a sequence of orthogonal polynomials.
-			\end{proof}
-
-		\item
-			\begin{proof}
-				Denote
-				\begin{equation}
-				\varphi(x) = (x^2-1)^n
-				\end{equation}
-				then
-				\begin{equation}
-				Q_n(x) = \frac{1}{2^n n!}\varphi^{(n)}(x)
-				\end{equation}
-				As the power of each item in $\varphi(x)$ is even when $\varphi(x)$ is extended, thus $\varphi^{(n)}(x)$ is even function if the order of derivative is even, and $\varphi^{(n)}(x)$ is odd function if the order of derivative is odd.
-\\
-				Therefore $Q_n(x)$ is even function if $n$ is even, and $Q_n(x)$ is odd function if $n$ is odd. So, it can be summarized as $Q_n(-x) = (-1)^n Q_n(x)$. 
-			\end{proof}
-
-		\item
-
-		\item
-
-	\end{enumerate}
+\section{Lebesgue constant for Chebyshev nodes}
 
@@
 \section{Interpolation}
-	$f(2)$ can be determined using the Lagrange interpolation scheme.
-	As the lagrange interpolation polynomial can be written as below, and $n=8$ in this case.
-	\begin{equation}
-		f(x) = \sum_{i=1}^{n}f(x_i) l_i(x)\label{lag_interp}
-	\end{equation}
-
-	$l_i(x)$ are the base functions that can be written as below.
-	\begin{equation}
-		l_i(x) = \frac{(x-x_1)(x-x_2)...(x-x_{i-1})(x-x_{i+1})...(x-x_{n-1})(x-x_n)}{(x_i-x_1)(x_i-x_2)...(x_i-x_{i-1})(x_i-x_{i+1})...(x_i-x_{n-1})(x_i-x_n)}
-	\end{equation}
-
-	$l_i(2)$ are calculated accordingly as below.
-
-	\begin{center}
-		\begin{tabular}{cccc}
-			$l_1(2) = -0.0006$ & $l_2(2) = 0.1224$ & $l_3(2) = -0.5600$ & $l_4(2) = 1.0606$ \\
-			$l_5(2) = 0.4167$ & $l_6(2) = -0.0400$ & $l_7(2) = 0.0012$ & $l_8(2) = -0.0003$\\
-		\end{tabular}
-	\end{center}
-
-	Thus, $f(2)$ is calculated according to (\ref{lag_interp}) as 11.0.
 
@@
 %----------------------------------------------------------------------------------------
-\section{Newton's form of interpolation polynomial}
-	\begin{enumerate}
-		\item
-
-		\item
-
-		\item
-
-		\item
-
-		\item
-
-		\item
-
-		\item
-
-	\end{enumerate}
+\section{Trigonometric polynomials}
 

### 2018-06-23 VV570/HW1/submission.tex
rename for clearity

--- 2018-05-28 VV570/HW1/assignment.tex
@@
 
-\date{\normalsize May 23, 2018} % Today's date or a custom date
+\date{\normalsize \today} % Today's date or a custom date
 
@@
 			Let $E$ be an inner product space over $\mathbb{C}$, and $u, v\in E$.\\
-			Given $Y$ defined as below, where $\lambda \in \mathbb{R}$.
+			Given $Y$ defined as below, where $\lambda \in \mathbb{C}$.
 
@@
 
-			Given $Y$ defined as below, where $\lambda \in \mathbb{R}$.
+			Given $Y$ defined as below, where $\lambda \in \mathbb{C}$.
 
@@
 			\begin{equation}
-				\lim\limits_{n->+\infty} \vert x_1-x_0 \vert = 0
+				\lim\limits_{n \rightarrow +\infty} \vert x_1-x_0 \vert = 0
 			\end{equation}
 			\begin{equation}
-				\lim\limits_{n->+\infty} \vert df_n(x_1) - df_n(x_0) \vert = \vert 0-dx \vert = |dx| \neq 0
+				\lim\limits_{n \rightarrow +\infty} \vert df_n(x_1) - df_n(x_0) \vert = \vert 0-dx \vert = |dx| \neq 0
 			\end{equation}

### 2018-06-23 VV570/HW5/submission.tex
ex-1 basically ok

--- 2018-06-15 VV570/HW4/assignment.tex
@@
 %----------------------------------------------------------------------------------------
-\section{Legendre Polynomials}
+\section{Lebesgue constant for Chebyshev nodes}
+\begin{enumerate}
+	\item 
 		\begin{enumerate}
@@
 				\begin{proof}
-				Let
+					Denote
 					\begin{equation}
-					\varphi(x) = (x^2-1)^n
+						\begin{aligned}
+							LHS &\triangleq (x-x_i)l_i(x) \\
+							RHS &\triangleq \frac{T_{n+1}(x)}{T_{n+1}'(x_i)}
+						\end{aligned}
 					\end{equation}
-				then
+					It is left to prove $LHS = RHS$.\\
+					The left part can be written as
 					\begin{equation}
-					Q_n(x) = \frac{1}{2^n n!}\varphi^{(n)}(x)
+						LHS = c_l \omega(x)
+					\end{equation}
+					where 
+					\begin{equation}
+						\omega(x) = \prod_{i=0}^{n}(x-x_i)
 					\end{equation}
@@
 					\begin{equation}
-					\varphi^{(k)}(1) = \varphi^{(k)}(-1) = 0 \ \  (\text{$k=0,1, ... , n-1$})
+						c_l = \frac{1}{\prod_{k=0, k\neq i}^{n}(x_i - x_k)} 
 					\end{equation}
-				Suppose $h(x) \in C^n(-1,1)$, then performing integration by parts
+
+					Since both $LHS$ and $RHS$ are polynomials of order $n+1$, they are equivalent iff. they have same roots and leading coefficients.\\
+					On the one hand,as for all $x_i$, where $i = 0, 1, ... , n$
+					\begin{equation}
+						T_{n+1}(x_i) = cos((n+1)\theta_i) = cos(\frac{2i+1}{2}\pi) = 0
+					\end{equation}
+					Thus, $LHS$ and $RHS$ have same roots. $RHS$ can therefore be written as
+					\begin{equation}
+						RHS(x) = c_r \omega(x)
+					\end{equation}
+					On the other hand, since
+					\begin{equation}
+						LHS'(x)|_{x=x_i} = (l_i(x) + (x-x_i)l_i'(x))|_{x=x_i} = 1
+					\end{equation}
+					and
+					\begin{equation}
+						RHS'(x)|_{x=x_i} = \frac{T'_{n+1}(x)}{T_{n+1}'(x_i)}\Big|_{x=x_i} = 1
+					\end{equation}
+					Thus, the leading coefficients of $LHS$ and $RHS$ are equal, namely $c_l = c_r$.\\
+					Hence, $LHS=RHS$.
+				\end{proof}
+			\item 
+				\begin{proof}
 					\begin{equation}
 						\begin{aligned}
-						\int_{-1}^{1} P_n(x)h(x)dx 
-						& = \frac{1}{2^n n!}\int_{-1}^{1}\varphi^{(n)}(x)h(x)dx \\
-						& = -\frac{1}{2^n n!} \int_{-1}^{1}\varphi^{(n-1)}(x)h'(x)dx \\
-						& = ...\\
-						& = \frac{(-1)^n}{2^n n!}\int_{-1}^{1}\varphi(x)h^{(n)}(x)dx
+							T'_{n+1}(x) & = (cos((n+1)arccos(x)))'\\
+							            & = sin((n+1)arccos(x)) (n+1) \frac{1}{\sqrt{1-x^2}}\\
+							            & = \frac{n+1}{\sqrt{1-cos^2(\theta)}} sin((n+1)\theta) 
 						\end{aligned}
 					\end{equation}
-				Thus, the proof can be discussed on 2 cases
-
-				\begin{enumerate}
+					As $\theta_k = \frac{2k+1}{2(n+1)}\pi$, thus, $sin(\theta_k) > 0$, and
+					\begin{equation}
+						T'_{n+1}(x_k) = \frac{n+1}{sin(\theta_k)} sin(\frac{2k+1}{2}\pi) = {(-1)}^k \frac{n+1}{sin(\theta_k)}
+					\end{equation}
+				\end{proof}
 			\item
-						If the order of $g(x)$ is less than $n$, then 
+				\begin{proof}
+					As
 					\begin{equation}
-							g^{(n)}(x) = 0
-						\end{equation}
-						Thus
-						\begin{equation}
-							\int_{-1}^{1}Q_n(x)Q_m(x)dx = 0 \ \ (\text{$n\neq m$})
-						\end{equation}
-
-					\item
-						If $g(x) = Q_n(x)$, then the $n-th$ derivative of $g(x)$ is
-						\begin{equation}
-							g^{(n)}(x) = Q^{(n)}(x) = \frac{(2n)!}{2^n n!}
+						T_{n+1}(1) = cos((n+1)arccos(1)) = 1	
 					\end{equation}
@@
 						\begin{aligned}
-								\int_{-1}^{1}Q_n(x)Q_m(x)dx	
-								& = \int_{-1}^{1}Q_n^2(x)dx \\
-								& = \frac{(-1)^n (2n)!}{2^{2n}(n!)^2}\int_{-1}^{1}(x^2-1)^n dx\\
-								& = \frac{(2n)!}{2^{2n}(n!)^2}\int_{-1}^{1}(1-x^2)^n dx\\
-								& = \frac{(2n)!}{2^{2n}(n!)^2} \int_{0}^{\pi/2} cos^{2n+1}t dt\\
-								& = \frac{(2n)!}{2^{2n}(n!)^2} \frac{2 \times 4 \times ... \times (2n)}{1\times3\times ... \times (2n+1)}\\
-								& = \frac{2}{2n+1} \ \ (\text{$n = m$})
+							\sum_{i=0}^{n}|l_i(1)| & = \sum_{i=0}^{n}\Bigg|\frac{T_{n+1}(1)}{(1-x_i)T'_{n+1}(x_i)}\Bigg| \\
+												   & = \sum_{i=0}^{n} \frac{1}{\Big|(1-x_i)T'_{n+1}(x_i)\Big|}\\
+												   & = \frac{1}{n+1} \sum_{i=0}^{n} \bigg|\frac{sin\theta_i}{(1-cos\theta_i)} \bigg|\\
+												   & = \frac{1}{n+1} \sum_{i=0}^{n} \bigg|\frac{sin\theta_i}{2sin^2(\frac{\theta_i}{2})} \bigg|\\
+												   & \geq  \frac{1}{n+1} \sum_{i=0}^{n} cot(\frac{\theta_i}{2})\\
 						\end{aligned}
 					\end{equation}
+				\end{proof} 			
 		\end{enumerate}
-
-				Thus, $(Q_n)_{n\in\mathbb{N}}$ are a sequence of orthogonal polynomials.
+	\item 
+		\begin{enumerate}
+			\item 
+				\begin{proof}
+					According to the mean value theorem, there exists $\theta \in [\frac{\theta_k}{2}, \frac{\theta_{k+1}}{2}]$, s.t.
+					\begin{equation}
+						\int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt = \frac{\theta_{k+1} - \theta_k}{2} cot(\theta)
+					\end{equation}
+					As $cot'(t) = -\frac{1}{sin^2(t)} < 0$, and $\theta_k \leq \theta \leq \theta_{k+1}$, thus
+					\begin{equation}
+						cot(\theta) \leq cot(\theta_k)
+					\end{equation}
+					Therefore
+					\begin{equation}
+						\int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt \leq \frac{\theta_{k+1} - \theta_k}{2} cot(\theta_k)
+					\end{equation}
 				\end{proof}
@@
 				\begin{proof}
-				Denote
+					As $\theta_{k+1} - \theta_k = \frac{\pi}{n+1}$ and according to the result that have been proved above
 					\begin{equation}
-				\varphi(x) = (x^2-1)^n
+						\begin{aligned}
+							\sum_{k=0}^{n} \int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt 
+							& \leq \sum_{k=0}^{n} \frac{\theta_{k+1} - \theta_k}{2}cot(\frac{\theta_k}{2})\\
+							& = \frac{\pi}{2(n+1)} \sum_{k=0}^{n} cot(\frac{\theta_k}{2})
+						\end{aligned}
 					\end{equation}
-				then
-				\begin{equation}
-				Q_n(x) = \frac{1}{2^n n!}\varphi^{(n)}(x)
-				\end{equation}
-				As the power of each item in $\varphi(x)$ is even when $\varphi(x)$ is extended, thus $\varphi^{(n)}(x)$ is even function if the order of derivative is even, and $\varphi^{(n)}(x)$ is odd function if the order of derivative is odd.
-\\
-				Therefore $Q_n(x)$ is even function if $n$ is even, and $Q_n(x)$ is odd function if $n$ is odd. So, it can be summarized as $Q_n(-x) = (-1)^n Q_n(x)$. 
 				\end{proof}
@@
 			\item 
+				\begin{proof}
+					As $\theta_n = \frac{2n+1}{2n+2}\pi < \pi$, $\theta_{n+1} = \frac{2n+3}{2n+2} > \pi$, and $cot(x)$ is positive over $(0, \frac{\pi}{2})$, while negative otherwise.
+					Thus
+					\begin{equation}
+							\int_{\frac{\theta_0}{2}}^{\frac{\pi}{2}} cot(t) dt 
+							\leq \int_{\frac{\theta_0}{2}}^{\frac{\theta_n}{2}} cot(t) dt
+							= \sum_{k=0}^{n-1} \int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt
+					\end{equation}
+					Hence
+					\begin{equation}
+						\int_{\frac{\theta_0}{2}}^{\frac{\pi}{2}} cot(t) dt \leq \frac{\pi}{2(n+1)} \sum_{i=0}^{n}cot(\frac{\theta_i}{2})
+					\end{equation}
+					(... not fine)
+				\end{proof}
+
+		\end{enumerate}
 
 	\item 
+		\begin{proof}
+			\begin{equation}
+				\begin{aligned}
+					\Lambda_n & = \max_{x \in [a, b]} \sum_{i=0}^{n} |l_i(x)|\\
+							  & \geq \sum_{i=0}^{n} |l_i(1)|\\
+							  & \geq \frac{1}{n+1} \sum_{i=0}^{n} cot(\frac{\theta_i}{2})\\
+							  & \geq \frac{2}{\pi} \int_{\theta_0 / 2}^{\pi/2} cot(t)dt\\
+							  & = \frac{2}{\pi} ln(|sin(t)|) \Bigg| _{\theta_0/2}^{\pi/2}\\
+							  & = - \frac{2}{\pi} ln(sin(\frac{\theta_0}{2}))\\
+							  & \geq \frac{2}{\pi} ln(\frac{2}{\theta_0}) = \frac{2}{\pi} ln(\frac{4(n+1)}{\pi})\\
+							  & \ge \frac{2}{\pi} ln(n)
+				\end{aligned}
+			\end{equation}
+		\end{proof}
 

### 2018-06-25 VV570/HW5/submission.tex
basically done

@@
 \section{Interpolation}
+\begin{enumerate}
+	\item 
+		\begin{proof}
+			Since $\Phi(f)=0$, $f(x_k) + f(y_k) = 0$ is valid for any $k$.\\
+			Thus $f(x_k) = f(y_k) = 0$ or $f(x_k)$ and $f(y_k)$ have different signs.\\
+			In the first case, take $\xi_k = x_k$ or $\xi_k = y_k$;\\
+			In the second case, as $f$ is continous over $[a, b]$, according to the  intermediate value theorem, there exists $\xi_k \in [x_k, y_k]$ s.t. $f(\xi_k) = 0$.
+		\end{proof}
+
+	\item 
+		\begin{proof}
+			Let $h_1(x) \in \mathbb{R}_n [x]$, $h_2(x) \in \mathbb{R}_n [x]$ and  $h_1(x) \neq h_2(x)$. They can be written as
+			\begin{equation}
+				h_1(x) = \sum_{i=0}^{n} a_i x^i
+			\end{equation}
+			\begin{equation}
+				h_2(x) = \sum_{i=0}^{n} b_i x^i
+			\end{equation}
+			Assume $\Phi(h_1) = \Phi(h_2)$, then
+			\begin{equation}
+				h_1(x_k) + h_1(y_k) = h_2(x_k) + h_2(y_k) \ \ (k=0, 1, ... , n)
+			\end{equation}
+			Thus
+			\begin{equation}
+				 \begin{bmatrix}
+					(1+1) & (x_0 + y_0) &  (x_0^2 + y_0^2) & ... & (x_0^n + y_0^n)\\
+					(1+1) & (x_1 + y_1)  &  (x_1^2 + y_1^2) & ... & (x_1^n  + y_1^n)\\
+					\vdots  & \vdots    & \vdots & \ddots & \vdots \\
+					(1+1) & (x_n + y_n) & (x_n^2 + y_n^2) & ... & (x_n^n + y_n^n)\\
+				\end{bmatrix}
+				\begin{bmatrix}
+					a_0 - b_0\\
+					a_1 - b_1\\
+					\vdots \\
+					a_n - b_n\\
+				\end{bmatrix}
+				=
+				\begin{bmatrix}
+					0\\
+					0\\
+					\vdots \\
+					0\\
+				\end{bmatrix}
+			\end{equation}
+			The determinant of the coefficient matrix above is positive as it is the sum of $2^{n+1}$ determinents, each of these be positive as $x_0 < y_0 < x_1 < y_1 < ...
+< x_n < y_n$.
+Thus, solution to this linear system is $x = [0, 0, ...
+, 0]^T$, which means
+			\begin{equation}
+				a_i = b_i \ \ (i=0, 1, ... , n)
+			\end{equation}
+			So, the hypothsis fails as $h_1(x) = h_2(x)$. Hence, $\Phi(f) \neq \Phi(g)$, which means $\Phi$ is injective.\\
+			Assume $\Phi(P1) = \Phi(f)$, $\Phi(P2) = \Phi(f)$, according to the converse-negative proposition of the injective property, there should be $P1 = P2$, thus the unicity is proved.
+		\end{proof}
+
+	\item 
+		\begin{proof}
+			Let $P_n(x) = a_n x^n + a_{n-1} x^{n-1} + ... + a_1 x + a_0$, denote $h(x) = P_n(x) - f(x)$. As $\Phi(P_n) = \Phi(f)$, then
+			\begin{equation}
+			h(x_k) + h(y_k) = 0
+			\end{equation}
+			Thus, there exists $\xi_k \in [x_k, y_k]$ s.t. $h(\xi_k) = 0$. So
+			\begin{equation}
+			\sum_{i=0}^{n}a_i \xi_k ^ i = f(\xi_k) \ \ (k=0, 1, ... , n)
+			\end{equation}
+			which can be written as matrix form
+			\begin{equation}
+			\begin{bmatrix}
+				1 & \xi_0 & \xi_0^2 & ... & \xi_0^n \\
+				1 & \xi_1 & \xi_1^2 & ... & \xi_1^n \\
+				\vdots  & \vdots & \vdots & \ddots & \vdots \\
+				1 & \xi_n & \xi_n^2 & ... & \xi_n^n \\
+			\end{bmatrix}
+			\begin{bmatrix}
+				a_0\\
+				a_1\\
+				\vdots \\
+				a_n\\
+			\end{bmatrix}
+			=
+			\begin{bmatrix}
+				f(\xi_0)\\
+				f(\xi_1)\\
+				\vdots \\
+				f(\xi_n)\\
+			\end{bmatrix}
+			\end{equation}
+			The determinant of the coefficient matrix is the so called Vandermonde determinant, and $\xi_j > \xi_i$ when $j>i$.
+Thus, determinant of the coefficient matrix is positive, which means there exist $n+1$ points in $[a, b]$, denoted as $\xi_i$, s.t.
+$P(\xi_i) = f(\xi_i)$.
+Thus $P_n$ is the interpolation polynomial of $f$.\\
+
+			Applying the Taylor theorem, it's clear that 
+			\begin{equation}
+				f(x)-P_n(x) = \frac{(x-a)^{n+1}}{(n+1)!}f^{(n+1)}(\xi)
+			\end{equation}
+			Thus
+			\begin{equation}
+				\lVert f- p_n \rVert_\infty = \max_{x \in [a, b]} |f-P_n| \leq \frac{(b-a)^{n+1}}{(n+1)!}\sup_{x \in [a, b]}|f^{(n+1)}(x)|
+			\end{equation}
+
+		\end{proof}
+
+\end{enumerate}
 
@@
 \section{Trigonometric polynomials}
+\begin{enumerate}
+	\item 
+		\begin{proof}
+			It's clear that the statement holds when $k=0, 1$ as $1$ and $cos \theta$ are in $T_0$ and $T_1$ respectively.\\
+			Suppose the statement is still valid when $k = n-1$, thus, there exists $Q_{n-1}$ s.t.
+			\begin{equation}
+				(cos\theta)^{n-1} = Q_{n-1}
+			\end{equation}
+			When it comes to $k = n$, with the induction hypothesis,
+			\begin{equation}
+				\begin{aligned}
+						(cos\theta)^n & =  Q_{n-1} \times cos\theta\\
+						                     & = (\frac{a_0}{\sqrt{2}} + \sum_{k=1}^{n-1}a_k cosk\theta) cos\theta\\
+						                     & = \frac{a_0}{\sqrt{2}}cos\theta + \sum_{k=1}^{n-1}a_k (\frac{cos(k+1)\theta + cos(k-1)\theta}{2})\\
+						                     & = \frac{b_0}{\sqrt{2}} + \sum_{k=0}^{n} b_k cosk\theta \triangleq Q_n
+				\end{aligned}
+			\end{equation}
+			Thus, $(cos\theta)^n$ is in $T_n$. Hence, for any $0 \leq k \leq n$, $(cos\theta)^k$ is in $T_n$ as $T_k \subseteq T_n$.\\
+
+			(the bijection part haven't figured out yet ...)
+
+		\end{proof}
+	\item 
+		\begin{proof}
+			As $Q_n(\theta_i) = F(\theta_i)$, the existence of $Q_n \in T_n$ is equivalent to the existence of solution of the linear system given as below
+			\begin{equation}
+				\begin{bmatrix}
+					\frac{1}{\sqrt{2}} & cos(\theta_0) & cos(2\theta_0) & ... & cos(n\theta_0) \\
+					\frac{1}{\sqrt{2}} & cos(\theta_1) & cos(2\theta_1) & ... & cos(n\theta_1) \\
+					\vdots                 & \vdots           & \vdots             & \ddots  & \vdots     \\
+					\frac{1}{\sqrt{2}} & cos(\theta_n) & cos(2\theta_n) & ... & cos(n\theta_n) \\
+				\end{bmatrix}
+				\begin{bmatrix}
+					a_0 \\ a_1 \\ a_2 \\ \vdots \\ a_n\\
+				\end{bmatrix}
+				=
+				\begin{bmatrix}
+					F(\theta_0) \\ F(\theta_1) \\ F(\theta_2) \\ \vdots \\ F(\theta_n)\\
+				\end{bmatrix}
+			\end{equation}
+			Thus, it's left to prove the determinant of the coefficient matrix is non-zero, which can be denoted as $\det(A)$.\\
+			As $cos(k\theta)$ can be written as
+			\begin{equation}
+				cos(k\theta) = \sum_{n=0}^{k} b_n(cos\theta)^n
+			\end{equation}
+			Thus, $\det(A)$ can be simplified as below, where $C$ is an non-zero factor.
+			\begin{equation}
+				\det(A) = C \det
+				\begin{bmatrix}
+					1 & cos(\theta_0) & cos^2(\theta_0) & ... & cos^n(\theta_0) \\
+					1 & cos(\theta_1) & cos^2(\theta_1) & ... & cos^n(\theta_1) \\
+					\vdots                 & \vdots           & \vdots             & \ddots  & \vdots     \\
+					1 & cos(\theta_n) & cos^2(\theta_n) & ... & cos^n(\theta_n) \\
+				\end{bmatrix}
+			\end{equation}
+			With $\theta_i = \frac{2i+1}{2(n+1)}\pi$, it's clear that $\det(A)\neq0$ as its Vandermon derterminant part is non-zero. Thus the existence of $Q_n$ is valid.
+		\end{proof}
+
+	\item 
+		\begin{proof}
+			It has been exactly proved above.
+		\end{proof}
+
+	\item 
+		\begin{proof}
+
+		\end{proof}
+
+\end{enumerate}
 

### 2018-06-29 VM532/HW1/submission.tex
add ex1-1

--- 2018-06-23 VV570/HW5/submission.tex
@@
-%----------------------------------------------------------------------------------------
-%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
-%----------------------------------------------------------------------------------------
-
 \documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size
-
 \usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
@@
 \usepackage{mathrsfs}
-
 \usepackage{algorithm, algorithmic}
@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm  
-
 \usepackage{listings}
 \lstset{language=Matlab}
-
 \usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
-
 \usepackage{sectsty} % Allows customizing section commands
 \allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps
-
 \usepackage{fancyhdr} % Custom headers and footers
@@
 \setlength{\headheight}{13.6pt} % Customize the height of the header
-
 \numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
@@
 \numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
-
 \setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text
-
-%----------------------------------------------------------------------------------------
-%	TITLE SECTION
-%----------------------------------------------------------------------------------------
-
 \newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height
 
-\title{	
-\normalfont \normalsize 
-\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
-\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Introduction to Numerical Analysis \\ HW5 \\ % The assignment title
-\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
-}
+\title{\normalfont \normalsize 
+	\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt]
+	\horrule{0.5pt} \\[0.4cm] 
+	\huge Advanced Convection \\ HW1 \\
+	\horrule{2pt} \\[0.5cm]}
 
-\author{Yu Cang \\ 018370210001} % Your name
-
-\date{\normalsize \today} % Today's date or a custom date
+\author{Yu Cang \\ 018370210001}
+\date{\normalsize \today}
 
@@
 
-\maketitle % Print the title
+\maketitle
 
-%----------------------------------------------------------------------------------------
-%	PROBLEM 1
-%----------------------------------------------------------------------------------------
-\section{Lebesgue constant for Chebyshev nodes}
-\begin{enumerate}
-	\item 
-		\begin{enumerate}
-			\item 
-				\begin{proof}
-					Denote
+\section{PROBLEM 1}
+When $u_2= 0$ and the flow is entirely in the x-direction, the governing equations can be simplified as follows
 \begin{equation}
-						\begin{aligned}
-							LHS &\triangleq (x-x_i)l_i(x) \\
-							RHS &\triangleq \frac{T_{n+1}(x)}{T_{n+1}'(x_i)}
-						\end{aligned}
+	u_1 \frac{\partial u_1}{\partial x_1} + \frac{1}{\rho}\frac{\partial p}{\partial x_1} = 0
 \end{equation}
-					It is left to prove $LHS = RHS$.\\
-					The left part can be written as
 \begin{equation}
-						LHS = c_l \omega(x)
+	\frac{\partial p}{\partial x_2} = 0
 \end{equation}
-					where 
-					\begin{equation}
-						\omega(x) = \prod_{i=0}^{n}(x-x_i)
-					\end{equation}
-					and
-					\begin{equation}
-						c_l = \frac{1}{\prod_{k=0, k\neq i}^{n}(x_i - x_k)} 
-					\end{equation}
+where the body-force are neglected.\\
+It can be concluded that pressure doesn't change in y-direction when x is fixed.\\
+Also, pressure gradient in x-direction is the driven force of the fluids.
 
-					Since both $LHS$ and $RHS$ are polynomials of order $n+1$, they are equivalent iff. they have same roots and leading coefficients.\\
-					On the one hand,as for all $x_i$, where $i = 0, 1, ... , n$
-					\begin{equation}
-						T_{n+1}(x_i) = cos((n+1)\theta_i) = cos(\frac{2i+1}{2}\pi) = 0
-					\end{equation}
-					Thus, $LHS$ and $RHS$ have same roots. $RHS$ can therefore be written as
-					\begin{equation}
-						RHS(x) = c_r \omega(x)
-					\end{equation}
-					On the other hand, since
-					\begin{equation}
-						LHS'(x)|_{x=x_i} = (l_i(x) + (x-x_i)l_i'(x))|_{x=x_i} = 1
-					\end{equation}
-					and
-					\begin{equation}
-						RHS'(x)|_{x=x_i} = \frac{T'_{n+1}(x)}{T_{n+1}'(x_i)}\Big|_{x=x_i} = 1
-					\end{equation}
-					Thus, the leading coefficients of $LHS$ and $RHS$ are equal, namely $c_l = c_r$.\\
-					Hence, $LHS=RHS$.
-				\end{proof}
-			\item 
-				\begin{proof}
-					\begin{equation}
-						\begin{aligned}
-							T'_{n+1}(x) & = (cos((n+1)arccos(x)))'\\
-							            & = sin((n+1)arccos(x)) (n+1) \frac{1}{\sqrt{1-x^2}}\\
-							            & = \frac{n+1}{\sqrt{1-cos^2(\theta)}} sin((n+1)\theta) 
-						\end{aligned}
-					\end{equation}
-					As $\theta_k = \frac{2k+1}{2(n+1)}\pi$, thus, $sin(\theta_k) > 0$, and
-					\begin{equation}
-						T'_{n+1}(x_k) = \frac{n+1}{sin(\theta_k)} sin(\frac{2k+1}{2}\pi) = {(-1)}^k \frac{n+1}{sin(\theta_k)}
-					\end{equation}
-				\end{proof}
-			\item
-				\begin{proof}
-					As
-					\begin{equation}
-						T_{n+1}(1) = cos((n+1)arccos(1)) = 1	
-					\end{equation}
-					Thus
-					\begin{equation}
-						\begin{aligned}
-							\sum_{i=0}^{n}|l_i(1)| & = \sum_{i=0}^{n}\Bigg|\frac{T_{n+1}(1)}{(1-x_i)T'_{n+1}(x_i)}\Bigg| \\
-												   & = \sum_{i=0}^{n} \frac{1}{\Big|(1-x_i)T'_{n+1}(x_i)\Big|}\\
-												   & = \frac{1}{n+1} \sum_{i=0}^{n} \bigg|\frac{sin\theta_i}{(1-cos\theta_i)} \bigg|\\
-												   & = \frac{1}{n+1} \sum_{i=0}^{n} \bigg|\frac{sin\theta_i}{2sin^2(\frac{\theta_i}{2})} \bigg|\\
-												   & \geq  \frac{1}{n+1} \sum_{i=0}^{n} cot(\frac{\theta_i}{2})\\
-						\end{aligned}
-					\end{equation}
-				\end{proof} 			
-		\end{enumerate}
-	\item 
-		\begin{enumerate}
-			\item 
-				\begin{proof}
-					According to the mean value theorem, there exists $\theta \in [\frac{\theta_k}{2}, \frac{\theta_{k+1}}{2}]$, s.t.
-					\begin{equation}
-						\int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt = \frac{\theta_{k+1} - \theta_k}{2} cot(\theta)
-					\end{equation}
-					As $cot'(t) = -\frac{1}{sin^2(t)} < 0$, and $\theta_k \leq \theta \leq \theta_{k+1}$, thus
-					\begin{equation}
-						cot(\theta) \leq cot(\theta_k)
-					\end{equation}
-					Therefore
-					\begin{equation}
-						\int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt \leq \frac{\theta_{k+1} - \theta_k}{2} cot(\theta_k)
-					\end{equation}
-				\end{proof}
+\section{PROBLEM 2}
 
-			\item 
-				\begin{proof}
-					As $\theta_{k+1} - \theta_k = \frac{\pi}{n+1}$ and according to the result that have been proved above
-					\begin{equation}
-						\begin{aligned}
-							\sum_{k=0}^{n} \int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt 
-							& \leq \sum_{k=0}^{n} \frac{\theta_{k+1} - \theta_k}{2}cot(\frac{\theta_k}{2})\\
-							& = \frac{\pi}{2(n+1)} \sum_{k=0}^{n} cot(\frac{\theta_k}{2})
-						\end{aligned}
-					\end{equation}
-				\end{proof}
-
-			\item 
-				\begin{proof}
-					As $\theta_n = \frac{2n+1}{2n+2}\pi < \pi$, $\theta_{n+1} = \frac{2n+3}{2n+2} > \pi$, and $cot(x)$ is positive over $(0, \frac{\pi}{2})$, while negative otherwise.
-					Thus
-					\begin{equation}
-							\int_{\frac{\theta_0}{2}}^{\frac{\pi}{2}} cot(t) dt 
-							\leq \int_{\frac{\theta_0}{2}}^{\frac{\theta_n}{2}} cot(t) dt
-							= \sum_{k=0}^{n-1} \int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt
-					\end{equation}
-					Hence
-					\begin{equation}
-						\int_{\frac{\theta_0}{2}}^{\frac{\pi}{2}} cot(t) dt \leq \frac{\pi}{2(n+1)} \sum_{i=0}^{n}cot(\frac{\theta_i}{2})
-					\end{equation}
-					(... not fine)
-				\end{proof}
-
-		\end{enumerate}
-
-	\item 
-		\begin{proof}
-			\begin{equation}
-				\begin{aligned}
-					\Lambda_n & = \max_{x \in [a, b]} \sum_{i=0}^{n} |l_i(x)|\\
-							  & \geq \sum_{i=0}^{n} |l_i(1)|\\
-							  & \geq \frac{1}{n+1} \sum_{i=0}^{n} cot(\frac{\theta_i}{2})\\
-							  & \geq \frac{2}{\pi} \int_{\theta_0 / 2}^{\pi/2} cot(t)dt\\
-							  & = \frac{2}{\pi} ln(|sin(t)|) \Bigg| _{\theta_0/2}^{\pi/2}\\
-							  & = - \frac{2}{\pi} ln(sin(\frac{\theta_0}{2}))\\
-							  & \geq \frac{2}{\pi} ln(\frac{2}{\theta_0}) = \frac{2}{\pi} ln(\frac{4(n+1)}{\pi})\\
-							  & \ge \frac{2}{\pi} ln(n)
-				\end{aligned}
-			\end{equation}
-		\end{proof}
-
-\end{enumerate}
-
-%----------------------------------------------------------------------------------------
-%	PROBLEM 2
-%----------------------------------------------------------------------------------------
-\section{Interpolation}
-
-%----------------------------------------------------------------------------------------
-%	PROBLEM 3
-%----------------------------------------------------------------------------------------
-\section{Trigonometric polynomials}
+\section{PROBLEM 3}
 

### 2018-06-30 VV570/HW6/submission.tex
new start...

--- 2018-06-23 VV570/HW5/submission.tex
@@
 %----------------------------------------------------------------------------------------
-
 \newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Introduction to Numerical Analysis \\ HW5 \\ % The assignment title
+\huge Introduction to Numerical Analysis \\ HW6 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 %----------------------------------------------------------------------------------------
-\section{Lebesgue constant for Chebyshev nodes}
-\begin{enumerate}
-	\item 
-		\begin{enumerate}
-			\item 
-				\begin{proof}
-					Denote
-					\begin{equation}
-						\begin{aligned}
-							LHS &\triangleq (x-x_i)l_i(x) \\
-							RHS &\triangleq \frac{T_{n+1}(x)}{T_{n+1}'(x_i)}
-						\end{aligned}
-					\end{equation}
-					It is left to prove $LHS = RHS$.\\
-					The left part can be written as
-					\begin{equation}
-						LHS = c_l \omega(x)
-					\end{equation}
-					where 
-					\begin{equation}
-						\omega(x) = \prod_{i=0}^{n}(x-x_i)
-					\end{equation}
-					and
-					\begin{equation}
-						c_l = \frac{1}{\prod_{k=0, k\neq i}^{n}(x_i - x_k)} 
-					\end{equation}
-
-					Since both $LHS$ and $RHS$ are polynomials of order $n+1$, they are equivalent iff. they have same roots and leading coefficients.\\
-					On the one hand,as for all $x_i$, where $i = 0, 1, ... , n$
-					\begin{equation}
-						T_{n+1}(x_i) = cos((n+1)\theta_i) = cos(\frac{2i+1}{2}\pi) = 0
-					\end{equation}
-					Thus, $LHS$ and $RHS$ have same roots. $RHS$ can therefore be written as
-					\begin{equation}
-						RHS(x) = c_r \omega(x)
-					\end{equation}
-					On the other hand, since
-					\begin{equation}
-						LHS'(x)|_{x=x_i} = (l_i(x) + (x-x_i)l_i'(x))|_{x=x_i} = 1
-					\end{equation}
-					and
-					\begin{equation}
-						RHS'(x)|_{x=x_i} = \frac{T'_{n+1}(x)}{T_{n+1}'(x_i)}\Big|_{x=x_i} = 1
-					\end{equation}
-					Thus, the leading coefficients of $LHS$ and $RHS$ are equal, namely $c_l = c_r$.\\
-					Hence, $LHS=RHS$.
-				\end{proof}
-			\item 
-				\begin{proof}
-					\begin{equation}
-						\begin{aligned}
-							T'_{n+1}(x) & = (cos((n+1)arccos(x)))'\\
-							            & = sin((n+1)arccos(x)) (n+1) \frac{1}{\sqrt{1-x^2}}\\
-							            & = \frac{n+1}{\sqrt{1-cos^2(\theta)}} sin((n+1)\theta) 
-						\end{aligned}
-					\end{equation}
-					As $\theta_k = \frac{2k+1}{2(n+1)}\pi$, thus, $sin(\theta_k) > 0$, and
-					\begin{equation}
-						T'_{n+1}(x_k) = \frac{n+1}{sin(\theta_k)} sin(\frac{2k+1}{2}\pi) = {(-1)}^k \frac{n+1}{sin(\theta_k)}
-					\end{equation}
-				\end{proof}
-			\item
-				\begin{proof}
-					As
-					\begin{equation}
-						T_{n+1}(1) = cos((n+1)arccos(1)) = 1	
-					\end{equation}
-					Thus
-					\begin{equation}
-						\begin{aligned}
-							\sum_{i=0}^{n}|l_i(1)| & = \sum_{i=0}^{n}\Bigg|\frac{T_{n+1}(1)}{(1-x_i)T'_{n+1}(x_i)}\Bigg| \\
-												   & = \sum_{i=0}^{n} \frac{1}{\Big|(1-x_i)T'_{n+1}(x_i)\Big|}\\
-												   & = \frac{1}{n+1} \sum_{i=0}^{n} \bigg|\frac{sin\theta_i}{(1-cos\theta_i)} \bigg|\\
-												   & = \frac{1}{n+1} \sum_{i=0}^{n} \bigg|\frac{sin\theta_i}{2sin^2(\frac{\theta_i}{2})} \bigg|\\
-												   & \geq  \frac{1}{n+1} \sum_{i=0}^{n} cot(\frac{\theta_i}{2})\\
-						\end{aligned}
-					\end{equation}
-				\end{proof} 			
-		\end{enumerate}
-	\item 
-		\begin{enumerate}
-			\item 
-				\begin{proof}
-					According to the mean value theorem, there exists $\theta \in [\frac{\theta_k}{2}, \frac{\theta_{k+1}}{2}]$, s.t.
-					\begin{equation}
-						\int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt = \frac{\theta_{k+1} - \theta_k}{2} cot(\theta)
-					\end{equation}
-					As $cot'(t) = -\frac{1}{sin^2(t)} < 0$, and $\theta_k \leq \theta \leq \theta_{k+1}$, thus
-					\begin{equation}
-						cot(\theta) \leq cot(\theta_k)
-					\end{equation}
-					Therefore
-					\begin{equation}
-						\int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt \leq \frac{\theta_{k+1} - \theta_k}{2} cot(\theta_k)
-					\end{equation}
-				\end{proof}
-
-			\item 
-				\begin{proof}
-					As $\theta_{k+1} - \theta_k = \frac{\pi}{n+1}$ and according to the result that have been proved above
-					\begin{equation}
-						\begin{aligned}
-							\sum_{k=0}^{n} \int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt 
-							& \leq \sum_{k=0}^{n} \frac{\theta_{k+1} - \theta_k}{2}cot(\frac{\theta_k}{2})\\
-							& = \frac{\pi}{2(n+1)} \sum_{k=0}^{n} cot(\frac{\theta_k}{2})
-						\end{aligned}
-					\end{equation}
-				\end{proof}
-
-			\item 
-				\begin{proof}
-					As $\theta_n = \frac{2n+1}{2n+2}\pi < \pi$, $\theta_{n+1} = \frac{2n+3}{2n+2} > \pi$, and $cot(x)$ is positive over $(0, \frac{\pi}{2})$, while negative otherwise.
-					Thus
-					\begin{equation}
-							\int_{\frac{\theta_0}{2}}^{\frac{\pi}{2}} cot(t) dt 
-							\leq \int_{\frac{\theta_0}{2}}^{\frac{\theta_n}{2}} cot(t) dt
-							= \sum_{k=0}^{n-1} \int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt
-					\end{equation}
-					Hence
-					\begin{equation}
-						\int_{\frac{\theta_0}{2}}^{\frac{\pi}{2}} cot(t) dt \leq \frac{\pi}{2(n+1)} \sum_{i=0}^{n}cot(\frac{\theta_i}{2})
-					\end{equation}
-					(... not fine)
-				\end{proof}
-
-		\end{enumerate}
-
-	\item 
-		\begin{proof}
-			\begin{equation}
-				\begin{aligned}
-					\Lambda_n & = \max_{x \in [a, b]} \sum_{i=0}^{n} |l_i(x)|\\
-							  & \geq \sum_{i=0}^{n} |l_i(1)|\\
-							  & \geq \frac{1}{n+1} \sum_{i=0}^{n} cot(\frac{\theta_i}{2})\\
-							  & \geq \frac{2}{\pi} \int_{\theta_0 / 2}^{\pi/2} cot(t)dt\\
-							  & = \frac{2}{\pi} ln(|sin(t)|) \Bigg| _{\theta_0/2}^{\pi/2}\\
-							  & = - \frac{2}{\pi} ln(sin(\frac{\theta_0}{2}))\\
-							  & \geq \frac{2}{\pi} ln(\frac{2}{\theta_0}) = \frac{2}{\pi} ln(\frac{4(n+1)}{\pi})\\
-							  & \ge \frac{2}{\pi} ln(n)
-				\end{aligned}
-			\end{equation}
-		\end{proof}
-
-\end{enumerate}
+\section{Richardson Extrapolation}
 
@@
 %----------------------------------------------------------------------------------------
-\section{Interpolation}
+\section{Integration}
 
@@
 %----------------------------------------------------------------------------------------
-\section{Trigonometric polynomials}
+\section{Gauss's method}
 

### 2018-06-30 VV570/LAB2/Task1_a.m

@@ -1,0 +1,9 @@
+syms x
+fsym = symfun(1/(1+25*x^2),x);
+fsym(-1:1:1)
+fano = @(x) 1./(1+25*x.^2);
+fano(-1:1:1)
+exactf = int(fsym, -1, 1);
+format longE
+eval(exactf)
+format short

### 2018-06-30 VV570/LAB2/Task1_b.m

@@ -1,0 +1,10 @@
+function [quad] = midpointquad(f,a,b,n)
+xpts = linspace(a, b, n);
+h = (b-a)/(n-1);
+xmidpts = zeros(1, n-1);
+for i = 1:n-1
+    xmidpts(i) = f((xpts(i) + xpts(i+1))/2);
+end
+quad = h * sum(xmidpts);
+end
+

### 2018-07-02 VV570/LAB2/CompoundSimpsonQuad.m
LAB2 done

@@ -1,0 +1,9 @@
+function [quad] = CompoundSimpsonQuad(f, a, b, n)
+    quad = 0;
+    xpts = linspace(a, b, n+1);
+    h = (b-a)/n;
+    for i = 1:n
+        quad = quad + f(xpts(i)) + f(xpts(i+1)) + 4*f((xpts(i)+xpts(i+1))/2);
+    end
+    quad = quad * h/6;
+end

### 2018-07-02 VV570/LAB2/Task3_a.m

@@ -1,0 +1,16 @@
+clear all
+syms x
+N = 5;
+miderror = zeros(1, N);
+traperror = zeros(1, N);
+simerror = zeros(1, N);
+for i = 1:N
+    fsym = symfun(i*x^(i-1), x);
+    miderror(i) = midpointquad(fsym,0,1,i)-1;
+    traperror(i) = trapezoidalquad(fsym, 0, 1, i)-1;
+    simerror(i) = simpsonquad(fsym, 0, 1, i)-1;
+end
+format long
+monomial = {'$1$';'$2x$';'$3x^2$';'$4x^3$';'$5x^4$'};
+T = table(monomial, miderror', traperror', simerror', 'VariableNames', {'func' 'Midpointerror' 'TrapezoidalError' 'SimpsonError'})
+format short

### 2018-07-02 VV570/LAB2/Task3_b.m

@@ -1,0 +1,23 @@
+clear all
+syms x
+N = 5;
+miderror = zeros(1, N);
+traperror = zeros(1, N);
+simerror = zeros(1, N);
+clencurterror = zeros(1, N);
+lgwterror = zeros(1, N);
+for i = 1:N
+    fsym = symfun(i*x.^(i-1), x);
+    fano = @(t) i*t.^(i-1);
+    miderror(i) = midpointquad(fsym,0,1,i)-1;
+    traperror(i) = trapezoidalquad(fsym, 0, 1, i)-1;
+    simerror(i) = simpsonquad(fsym, 0, 1, i)-1;
+    [xpts, w] = fclencurt(i+2, 0, 1);
+    clencurterror(i) = sum(fano(xpts).*w)-1;
+    [xpts, w] = lgwt(i, 0, 1);
+    lgwterror(i) = sum(fano(xpts).*w)-1;
+end
+format long
+monomial = {'$1$';'$2x$';'$3x^2$';'$4x^3$';'$5x^4$'};
+T = table(monomial, miderror', traperror', simerror', clencurterror', lgwterror', 'VariableNames', {'func' 'Midpointerror' 'TrapezoidalError' 'SimpsonError' 'ClenshawCurtisError' 'GaussLegendreError'})
+format short

### 2018-07-02 VV570/LAB2/Task4_a.m

@@ -1,0 +1,11 @@
+syms x
+fsym = symfun(1/(1+25*x^2),x);
+fano = @(x) 1./(1+25*x.^2);
+exactf = int(fsym, -1, 1);
+format longE
+eval(exactf)
+format short
+
+n = 20;
+quad = CompoundSimpsonQuad(fano, -1, 1, n)
+err = eval(quad - exactf)

### 2018-07-02 VV570/HW6/submission.tex
ex1 and 3 basically ok

@@
 \section{Richardson Extrapolation}
+\begin{enumerate}
+	\item 
+		\begin{proof}
+			When $k = 0$, it's clear that $A_0(t) = a_0 + O(t)$.\\
+			Assume that the statement is still valid when $k=n-1$, which means $A_{n-1} = a_0 + O(t^n)$\\
+			Thus, when $k = n$, apply the induction hypothesis
+			\begin{equation}
+				\begin{aligned}
+					A_n(t) & = \frac{r^n A_{n-1}(t) - A_{n-1}(rt)}{r^n-1}\\
+					          & = \frac{r^n (a_0 + O(t^n)) - (a_0 + r^n O(t^n))}{r^n-1}\\
+					          & = a_0 + \frac{r^n}{r^n-1} (O(t^n) - O(t^n))\\
+					          & = a_0 + O(t^{n+1})
+				\end{aligned}
+			\end{equation}
+			Hence, the statement is valid.
+		\end{proof}
+	\item
+		\begin{enumerate}
+			\item 
+				\begin{proof}
+					When $t_m = \frac{t_0}{r_0^m}$, and $r_0 > 1$
+					\begin{equation}
+						\lim\limits_{m\rightarrow\infty} A_n(t_m) = a_0 + O((\frac{t_0}{r_0^m})^{n+1}) = a_0 + \frac{O(t_0 ^ {n+1})}{r_0^{m(n+1)}} = 0
+					\end{equation}
+					The equation above is valid as $O(t_0 ^{n+1})$ is finite.
+			\end{proof}
+
+			\item 
+				\begin{proof}
+					As $O(t_0 ^{n+1})$ is finite, it's clear that
+					\begin{equation}
+						 A_n(t_m) = a_0 + O((\frac{t_0}{r_0^m})^{n+1}) = a_0 + O(r_0^{-m(n+1)})
+					\end{equation}
+				\end{proof}
+
+		\end{enumerate}
+	\item
+		Algorithm used to do extrapolation is given as below.
+
+		\begin{algorithm}
+		\caption{Calculation of the extrapolation matrix and the improved quadrature}
+			\begin{algorithmic}[1]
+				\REQUIRE $A(t)$, $n$, $m$, $a$, $b$, $r_0$
+				\ENSURE $M$, $a_0$
+				\STATE $h \gets b-a$
+				\STATE $i \gets 0$
+				\WHILE {$i \neq m$}
+					\STATE $M[i][0] \gets A(\frac{h}{2^i})$
+					\STATE $i \gets i + 1$
+				\ENDWHILE
+				\STATE $j \gets 1$
+				\WHILE {$j \neq n$}
+					\STATE $i \gets j$
+					\WHILE {$i \neq m$}
+						\STATE $M[i][j] \gets \frac{r_0^i}{r_0^i - 1} M[i][j-1] - \frac{1}{r_0^i -1} M[i-1][j-1]$
+						\STATE $i \gets i+1$
+					\ENDWHILE
+					\STATE $j \gets j+1$
+				\ENDWHILE
+				\STATE $a_0 \gets M[m-1][n-1]$
+				\RETURN $M$, $a_0$
+			\end{algorithmic}
+		\end{algorithm}
+
+	\item
+		\begin{enumerate}
+			\item 
+				With proper combination, lower-order terms inside original quadratures can be eliminated when generating the new quadrature.
+			\item 
+				Consider the Runge's Function
+				\begin{equation}
+					f(x) = \frac{1}{1+25x^2}
+				\end{equation}
+				(to be added...)
+		\end{enumerate}
+
+\end{enumerate}
 
@@
 \section{Gauss's method}
+\begin{enumerate}
+	\item 
+		\begin{enumerate}
+			\item 
+				\begin{proof}
+					It's clear that $w(x)$ is positive.\\
+					And
+					\begin{equation}
+						\int_{-1}^{1} w(x) dx = \int_{-1}^{1} \sqrt{1-x^2}dx = \int_{-\pi/2}^{\pi/2} cos^2\theta d\theta = \frac{\pi}{2}
+					\end{equation}
+					Thus, $w(x)$ is a weight function.
+				\end{proof}
+			\item 
+				\begin{proof}
+					Since
+					\begin{equation}
+						\begin{aligned}
+							\int_{-1}^{1}w(x)q_m(x)q_n(x)dx 
+							& = \int_{\pi}^{0} \sqrt{1-cos^2\theta} \frac{sin(m+1)\theta}{sin\theta} \frac{sin(n+1)\theta}{sin\theta}(-sin\theta)d\theta\\
+							& = \int_{0}^{\pi} sin(m+1)\theta sin(n+1)\theta d\theta
+						\end{aligned}
+					\end{equation}
+					It's clear that when $n=m$, the value of the equation above is $\frac{\pi}{2}$, and is $0$ when $n \neq m$.
+					Thus, $q_k\  (k\in \mathbb{N})$ defines a sequence of orthogonal polynomials for weight function $w(x)$.
+				\end{proof}
+			\item
+				\begin{equation}
+					p_k(x) = \sqrt{\frac{2}{\pi}} q_k(x)
+				\end{equation} 
+		\end{enumerate}
+	\item 
+		\begin{enumerate}
+			\item 
+				$x_k$ are roots of orthogonal polynomial over $[a, b]$, whose order is $n+1$ and weight is $w(x)$.
+			\item 
+				With the Lagrange interpolation function $f(x) = \sum_{i=0}^{n} l_i(x)f(x_i)$, $A_k$ can be determined as
+				\begin{equation}
+					A_k = \int_{-1}^{1} l_k(x)w(x)dx
+				\end{equation}
+				As $x_k = cos(\frac{k\pi}{n+2})$, it can be further resolved that $A_k = \frac{\pi}{n+2}sin^2\frac{(k+1)\pi}{n+2}$.
+			\item 
+				\begin{proof}
+					Apply Hermitan interpolation polynomials $H_{2n+1}(x)$ onto $f(x_k)$ s.t. for $k = 0, 1, ... , n$
+					\begin{equation}
+						H_{2n+1}(x_k) = f(x_k) 
+					\end{equation}
+					and
+					\begin{equation}
+						H'_{2n+1}(x_k) = f'(x_k)
+					\end{equation}
+					Thus
+					\begin{equation}
+						f(x) = H_{2n+1}(x) + \frac{f^{(2n+2)}(\xi)}{(2n+2)!}\omega^2(x)
+					\end{equation}
+					Then integrate over $[-1, 1]$ with weight $w(x)$
+					\begin{equation}
+						I = \int_{-1}^{1} f(x) w(x) dx = \int_{-1}^{1} H_{2n+1}(x) w(x)dx + R_n[f]
+					\end{equation}
+					Thus
+					\begin{equation}
+						R_n[f] = I- \sum_{k=0}^{n}A_k f(x_k) = \int_{-1}^{1}\frac{f^{(2n+2)}(\xi)}{(2n+2)!}\omega^2(x)w(x)dx
+					\end{equation}
+					Since $\omega^2(x)w(x) \geq 0$, it can be concluded from the first intermediate value theorem that
+					\begin{equation}
+						R_n[f] = \frac{f^{(2n+2)}(\eta)}{(2n+2)!}\int_{-1}^{1}\omega^2(x)w(x)dx \triangleq c  \frac{f^{(2n+2)}(\eta)}{(2n+2)!}
+					\end{equation}
+
+				\end{proof}
+
+		\end{enumerate}
+\end{enumerate}
 

### 2018-07-02 VV570/LAB2/Task3_a.m
fix misunderstanding

@@ -6,9 +6,9 @@ traperror = zeros(1, N);
 simerror = zeros(1, N);
 for i = 1:N
     fsym = symfun(i*x^(i-1), x);
-    miderror(i) = midpointquad(fsym,0,1,i)-1;
-    traperror(i) = trapezoidalquad(fsym, 0, 1, i)-1;
-    simerror(i) = simpsonquad(fsym, 0, 1, i)-1;
+    miderror(i) = midpointquad(fsym,0,1,1)-1;
+    traperror(i) = trapezoidalquad(fsym, 0, 1, 1)-1;
+    simerror(i) = simpsonquad(fsym, 0, 1, 1)-1;
 end
 format long
 monomial = {'$1$';'$2x$';'$3x^2$';'$4x^3$';'$5x^4$'};

### 2018-07-08 VV570/PROJ1/article/article.tex
begining

%% This is file `elsarticle-template-1-num.tex',
%%
%% Copyright 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%
%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%%
%% $Id: elsarticle-template-1-num.tex 149 2009-10-08 05:01:15Z rishi $
%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-1-num.tex $
%%
\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
%% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Linear Prediction of Speech}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author{Yu Cang}
\address{Shanghai Jiao Tong University, China}

\begin{abstract}
%% Text of abstract
A model was established for predicting a speech linearly. Two strategies are developed to determine the coefficients. One is windowing the error and the Cholesky decomposition is applied. The other is windowing the signal and the Topelitz equations are solved iteratively. The two strategies are compared using a sample speech finally.
\end{abstract}

\begin{keyword}
Speech \sep Prediction \sep Cholesky \sep Topelitz
%% keywords here, in the form: keyword \sep keyword

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
\linenumbers

%% main text
\section{Background and Principles}
\label{S:1}
In a simplified situation, the speech can be linearly predicted from the previous $p$ samples as
\begin{equation}
	\hat{x}(n) =  \sum_{i=1}^{p} a_i x(n-i)
\end{equation}
where $a_i$ are the linear prediction coefficients. Then the error between the signal $x(n)$ and the predicted value $\hat{x}(n)$ is given as
\begin{equation}
	e(n) = x(n) - \hat{x}(n) = -\sum_{i=0}^{p}a_i x(n-i)
\end{equation}
where $a_0 = -1$. The minimum mean square error(MMSE) is adopted as the principle to determine these coefficients $a_i$.\\
The square error of the prediction is defined as
\begin{equation}
	E = \sum_{n}e^2(n) = \sum_{n}[x(n) - \sum_{i=1}^{p}a_i x(n-i)]^2
\end{equation}
To minimize $E$, each coefficient $a_i\ (i = 1, 2, ..., p)$ is determined as
\begin{equation}
	\frac{\partial E}{\partial a_i} = 2(\sum_{n}x(n)x(n-j) - \sum_{min}^{max})=0
\end{equation}
Thus
\begin{equation}
	content...
\end{equation}

\section{The Second Section}
\label{S:2}

Reference to Section \ref{S:1}. Etiam congue sollicitudin diam non porttitor. Etiam turpis nulla, auctor a pretium non, luctus quis ipsum. Fusce pretium gravida libero non accumsan. Donec eget augue ut nulla placerat hendrerit ac ut mi. Phasellus euismod ornare mollis. Proin tempus fringilla ultricies. Donec pretium feugiat libero quis convallis. Nam interdum ante sed magna congue eu semper tellus sagittis. Curabitur eu augue elit.

Aenean eleifend purus et massa consequat facilisis. Etiam volutpat placerat dignissim. Ut nec nibh nulla. Aliquam erat volutpat. Nam at massa velit, eu malesuada augue. Maecenas sit amet nunc mauris. Maecenas eu ligula quis turpis molestie elementum nec at est. Sed adipiscing neque ac sapien viverra sit amet vestibulum arcu rhoncus.

Vivamus pharetra nibh in orci euismod congue. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Quisque lacus diam, congue vel laoreet id, iaculis eu sapien. In id risus ac leo pellentesque pellentesque et in dui. Etiam tincidunt quam ut ante vestibulum ultricies. Nam at rutrum lectus. Aenean non justo tortor, nec mattis justo. Aliquam erat volutpat. Nullam ac viverra augue. In tempus venenatis nibh quis semper. Maecenas ac nisl eu ligula dictum lobortis. Sed lacus ante, tempor eu dictum eu, accumsan in velit. Integer accumsan convallis porttitor. Maecenas pretium tincidunt metus sit amet gravida. Maecenas pretium blandit felis, ac interdum ante semper sed.

In auctor ultrices elit, vel feugiat ligula aliquam sed. Curabitur aliquam elit sed dui rhoncus consectetur. Cras elit ipsum, lobortis a tempor at, viverra vitae mi. Cras sed urna sed eros bibendum faucibus. Morbi vel leo orci, vel faucibus orci. Vivamus urna nisl, sodales vitae posuere in, tempus vel tellus. Donec magna est, luctus non commodo sit amet, placerat et enim.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}          ==>>  [#]
%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
%%   \citet{key}         ==>>  Author [#]

%% References with bibTeX database:

\bibliographystyle{model1-num-names}
\bibliography{sample.bib}

%% Authors are advised to submit their bibtex database files. They are
%% requested to list a bibtex style file in the manuscript if they do
%% not want to use model1-num-names.bst.

%% References without bibTeX database:

% \begin{thebibliography}{00}

%% \bibitem must have the following form:
%%   \bibitem{key}...
%%

% \bibitem{}

% \end{thebibliography}

\end{document}

%%
%% End of file `elsarticle-template-1-num.tex'.

### 2018-07-08 VV570/PROJ1/code/solve_topelitz.m

@@ -1,0 +1,3 @@
+function [X] = solve_topelitz(A,b)
+    
+end

### 2018-07-08 VV570/PROJ1/article/article.tex
section 1 and 2 done

@@
 %% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
+\usepackage{amssymb, amsmath}
 %% The amsthm package provides extended theorem environments
@@
 %% main text
-\section{Background and Principles}
+\section{Background and Basic Equations}
 \label{S:1}
-In a simplified situation, the speech can be linearly predicted from the previous $p$ samples as
+In a simplified situation, a speech can be linearly predicted from the previous $p$ samples as
 \begin{equation}
@@
 \begin{equation}
-	\frac{\partial E}{\partial a_i} = 2(\sum_{n}x(n)x(n-j) - \sum_{min}^{max})=0
+	\frac{\partial E}{\partial a_i} = 0
 \end{equation}
-Thus
+Which is equivalent to
+\begin{equation}\label{coef_eqn}
+	\sum_{j=1}^{p}a_j \sum_{n}x(n-j)x(n-i) = \sum_{n}x(n)x(n-i)
+\end{equation}
+where $i= 1, 2, ..., p$. \\
+Denote $\phi(i,j)$ as
+\begin{equation}\label{phi_def}
+	\phi(i, j) = \sum_{n}x(n-i)x(n-j) 
+\end{equation}
+it's clear that $\phi(i,j) = \phi(j, i)$, and (\ref{coef_eqn}) can be written as
 \begin{equation}
-	content...
+	\sum_{j=1}^{p} \phi(j, i)a_j = \phi(0, i)
 \end{equation}
+where $i= 1, 2, ..., p$.\\
+Hence, it is left to determine $\phi(j, i)$ and then $a_j$ can be resolved.
+However, there're different ways to determine the bounds of $n$ when calculating $\phi(j, i)$, which led to different strategies of linear prediction.
 
-\section{The Second Section}
-\label{S:2}
+\section{The Autocorrelation Method}\label{S:2}
+The autocorrelation method aims to minimize the error over the whole timespan, and it's assumed that $x(n)$ is 0 when $n \notin [0,N-1]$.
+Thus, $x(n)$ is windowed with finite length, and the autocorrelation function of $x(n)$ is defined as
+\begin{equation}
+	r(j) = \sum_{n=-\infty}^{+\infty} x(n)x(n-j) \ \ (j \in [1, p])
+\end{equation}
+It can be concluded that, from (\ref{phi_def}), $r(|j-i|) = \phi(j, i)$. Thus, (\ref{coef_eqn}) can be expressed as
+\begin{equation}
+	\begin{bmatrix}
+		r(0) & r(1) & r(2) & ... & r(p-1) \\ 
+		r(1) & r(0) & r(1) & ... & r(p-2) \\
+		r(2) & r(1) & r(0) & ... & r(p-3) \\
+		\vdots & \vdots & \vdots & \ddots & \vdots \\
+		r(p-1) & r(p-2) & r(p-3) & ... & r(0)
+	\end{bmatrix}
+	\begin{bmatrix}
+	a_1 \\ a_2 \\ a_3 \\ \vdots \\ a_p
+	\end{bmatrix}
+	=
+	\begin{bmatrix}
+		r(1) \\ r(2) \\ r(3) \\ \vdots \\ r(p)
+	\end{bmatrix}
+\end{equation}
+It can be observed that the coefficient matrix is the so called Toeplitz matrix, where elements are symmetry and  each descending diagonal from left to right is constant.\\
+Suppose $a_i^{(k)} \ (i=1, 2, ... ,k)$ is the solution for $k-th$ iteration for $p=k$, which implies
+\begin{equation}
+	\begin{bmatrix}
+		r(0) & r(1) & r(2) & ... & r(k-1) \\ 
+		r(1) & r(0) & r(1) & ... & r(k-2) \\
+		r(2) & r(1) & r(0) & ... & r(k-3) \\
+		\vdots & \vdots & \vdots & \ddots & \vdots \\
+		r(k-1) & r(k-2) & r(k-3) & ... & r(0)
+	\end{bmatrix}
+	\begin{bmatrix}
+		a_1^{(k)} \\ a_2^{(k)} \\ a_3^{(k)} \\ \vdots \\ a_k^{(k)}
+	\end{bmatrix}
+	=
+	\begin{bmatrix}
+		r(1) \\ r(2) \\ r(3) \\ \vdots \\ r(k)
+	\end{bmatrix}
+\end{equation}
+Thus, when $p=k+1$, two equation sets can be constructed as
+\begin{equation}
+	\begin{bmatrix}
+		r(0) & r(1) & ... & r(k)\\ 
+		r(1) & r(0) & ... & r(k-1)\\
+		r(2) & r(1) & ... & r(k-2)\\
+		\vdots & \vdots & \ddots & \vdots \\
+		r(k-1) & r(k-2) & ... & r(1)\\
+		r(k) & r(k-1) & ... & r(0)\\
+	\end{bmatrix}
+	\begin{bmatrix}
+		a_1^{(k)} \\ a_2^{(k)} \\ a_3^{(k)} \\ \vdots \\ a_k^{(k)} \\ -\lambda
+	\end{bmatrix}
+	=
+	\begin{bmatrix}
+		r(1) - \lambda r(k) \\
+		r(2) - \lambda r(k-1) \\
+		r(3) - \lambda r(k-2) \\
+		\vdots \\
+		r(k) - \lambda r(1) \\
+		\sum_{i=1}^{k}a_i^{(k)} r(k+1-i)-\lambda r(0)
+	\end{bmatrix}
+\end{equation}
+and
+\begin{equation}
+	\begin{bmatrix}
+		r(0) & r(1) & ... & r(k)\\ 
+		r(1) & r(0) & ... & r(k-1)\\
+		r(2) & r(1) & ... & r(k-2)\\
+		\vdots & \vdots & \ddots & \vdots \\
+		r(k-1) & r(k-2) & ... & r(1)\\
+		r(k) & r(k-1) & ... & r(0)\\
+	\end{bmatrix}
+	\begin{bmatrix}
+		\lambda a_k^{(k)} \\
+		\lambda a_{k-1}^{(k)} \\
+		\lambda a_{k-2}^{(k)} \\
+		\vdots \\
+		\lambda a_1^{(k)} \\
+		0
+	\end{bmatrix}
+	=
+	\begin{bmatrix}
+		\lambda r(k) \\
+		\lambda r(k-1) \\
+		\lambda r(k-2) \\
+		\vdots \\
+		\lambda r(1) \\
+		\lambda\sum_{i=1}^{k}a_i^{(k)} r(i)
+	\end{bmatrix}
+\end{equation}
+Let $\lambda$ satisfy
+\begin{equation}
+	\sum_{i=1}^{k}a_i^{(k)} r(k+1-i)-\lambda r(0) + \lambda\sum_{i=1}^{k}a_i^{(k)} r(i) = r(k+1)
+\end{equation}
+namely
+\begin{equation}
+	\lambda = \frac{r(k+1) - \sum_{i=1}^{k}a_i^{(k)} r(k+1-i)}{\sum_{i=0}^{k}a_i^{(k)}r(i)}
+\end{equation}
+where $a_0^{(k)} = -1$. Then $a_i^{(k+1)}$ can be given as
+\begin{equation}
+	\{a_i^{(k+1)}\} = 
+	\begin{bmatrix}
+		a_1^{(k)} + \lambda a_k^{(k)} & a_2^{(k)} + \lambda a_{k-1}^{(k)} & ... & a_k^{(k)} + \lambda a_1^{(k)} & -\lambda  
+	\end{bmatrix}^T
+\end{equation}
+And it can be easily verified that the recursion formula is also valid when $k=1,2$, thus this solution is justified by induction. \\
+Further, this is the so-called Levinson-Durbin algorithm, with time complexity $O(n^2)$, and it is much faster than solving it directly where time complexity is $O(n^3)$.
 
-Reference to Section \ref{S:1}.
-Etiam congue sollicitudin diam non porttitor.
-Etiam turpis nulla, auctor a pretium non, luctus quis ipsum.
-Fusce pretium gravida libero non accumsan.
-Donec eget augue ut nulla placerat hendrerit ac ut mi.
-Phasellus euismod ornare mollis.
-Proin tempus fringilla ultricies.
-Donec pretium feugiat libero quis convallis.
-Nam interdum ante sed magna congue eu semper tellus sagittis.
-Curabitur eu augue elit.
-
-Aenean eleifend purus et massa consequat facilisis.
-Etiam volutpat placerat dignissim.
-Ut nec nibh nulla.
-Aliquam erat volutpat.
-Nam at massa velit, eu malesuada augue.
-Maecenas sit amet nunc mauris.
-Maecenas eu ligula quis turpis molestie elementum nec at est.
-Sed adipiscing neque ac sapien viverra sit amet vestibulum arcu rhoncus.
-
-Vivamus pharetra nibh in orci euismod congue.
-Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
-Quisque lacus diam, congue vel laoreet id, iaculis eu sapien.
-In id risus ac leo pellentesque pellentesque et in dui.
-Etiam tincidunt quam ut ante vestibulum ultricies.
-Nam at rutrum lectus.
-Aenean non justo tortor, nec mattis justo.
-Aliquam erat volutpat.
-Nullam ac viverra augue.
-In tempus venenatis nibh quis semper.
-Maecenas ac nisl eu ligula dictum lobortis.
-Sed lacus ante, tempor eu dictum eu, accumsan in velit.
-Integer accumsan convallis porttitor.
-Maecenas pretium tincidunt metus sit amet gravida.
-Maecenas pretium blandit felis, ac interdum ante semper sed.
-
-In auctor ultrices elit, vel feugiat ligula aliquam sed.
-Curabitur aliquam elit sed dui rhoncus consectetur.
-Cras elit ipsum, lobortis a tempor at, viverra vitae mi.
-Cras sed urna sed eros bibendum faucibus.
-Morbi vel leo orci, vel faucibus orci.
-Vivamus urna nisl, sodales vitae posuere in, tempus vel tellus.
-Donec magna est, luctus non commodo sit amet, placerat et enim.
+\section{The Covariance Method}
 

### 2018-07-08 VV570/PROJ1/article/article.tex
section 3 basically written

@@
 \section{The Covariance Method}
+In constrast to the previous method, the covariance method doesn't windowed the signal. Instead, the amount of points used to calculate the error is fixed. And it aims to minimize the error\\
+Suppose the amount of points to calculate $r(j)$ is $N$, then by definition
+\begin{equation}
+	r(j) = \sum_{n=0}^{N-1}x(n)x(n-j) \ \ (j = 0, 1, ... , p)
+\end{equation}
+Thus, $N+p$ samples are needed for calculating all $r(j)$. And $r(j-i)$ can be expressed as 
+\begin{equation}
+	r(j-i) = \sum_{n=0}^{N-1} x(n-j)x(n-i) \triangleq c(j, i) \ \ (j = 0, 1, ... , p) 
+\end{equation}
+Thus, the prediction equation (\ref{coef_eqn}) can be written as
+\begin{equation}
+	\begin{bmatrix}
+		c(1, 1) & c(1, 2) & ... & c(1, p)\\
+		c(2, 1) & c(2, 2) & ... & c(2, p)\\
+		\vdots  & \vdots  & \ddots & \vdots\\
+		c(p, 1) & c(p, 2) & ... & c(p, p)\\
+	\end{bmatrix}
+	\begin{bmatrix}
+		a_1 \\ a_2 \\ \vdots \\ a_p
+	\end{bmatrix}
+	=
+	\begin{bmatrix}
+		c(1, 0) \\ c(2, 0) \\ \vdots \\ c(p, 0)
+	\end{bmatrix}
+\end{equation}
+Since $c(i, j) \neq c(i+k, j+k)$, the coefficient matrix above is no longer the Toeplitz matrix, and different scheme should be employed to solve this linear system.\\
+It's clear that $c(i, j) = c(j, i)$, so it can be solved using the Cholesky decomposition. And the coefficient matrix can be decomposed as
+\begin{equation}
+	C = L L^T
+\end{equation}
+where $L$ is a lower triangle matrix.
+
+\section{Numerical Experiment}
 

### 2018-07-09 VV570/PROJ1/code/solve_toeplitz.m
toeplitz solver ok!

@@ -1,0 +1,33 @@
+function [a] = solve_toeplitz(t)
+    p = length(t)-1;
+    r0 = t(1);
+    r = t(:,2:p+1);
+    a = zeros(1, p);
+    
+    for k = 1:p
+        up = r(k);
+        for i = 1:k-1
+            up = up - a(i)*r(k-i);
+        end
+        
+        down = -r0;
+        for i = 1:k-1
+            down = down + a(i)*r(i);
+        end
+        
+        lambda = up/down;
+        
+        a(k) = -lambda;
+        left =1;
+        right = k-1;
+        while(left<=right)
+            tmp = a(left);
+            a(left) = a(left) + lambda * a(right);
+            if(left~=right)
+                a(right) = a(right) + lambda * tmp;
+            end
+            left = left+1;
+            right = right-1;
+        end
+    end
+end

### 2018-07-09 VV570/PROJ1/code/solve_topelitz.m

@@ -1,3 +1,0 @@
-function [X] = solve_topelitz(A,b)
-    
-end

### 2018-07-09 VV570/PROJ1/code/test_cholesky.m
add testing cases

@@ -1,0 +1,7 @@
+N = 5;
+D = diag(rand(N,1))
+U = orth(rand(N,N))
+A = U' * D * U
+
+l1 = chol(A)'
+l2 = cholesky_decomp(A)

### 2018-07-09 VV570/PROJ1/code/test_toeplitz.m

@@ -1,0 +1,6 @@
+p = 10;
+r = rand(1, p+1)
+T = toeplitz(r(:,1:p))
+b = r(:,2:p+1)
+a1 = inv(T)*b'
+a2 = solve_toeplitz(r)'

### 2018-07-09 VV570/PROJ1/code/solve_toeplitz.m
minor opt

@@ -20,14 +20,15 @@ function [a] = solve_toeplitz(t)
         a(k) = -lambda;
         left =1;
         right = k-1;
-        while(left<=right)
+        while(left<right)
             tmp = a(left);
             a(left) = a(left) + lambda * a(right);
-            if(left~=right)
-                a(right) = a(right) + lambda * tmp;
-            end
+            a(right) = a(right) + lambda * tmp;
             left = left+1;
             right = right-1;
+        end
+        if(left==right)
+            a(right) = (1+lambda)*a(right);
         end
     end
 end

### 2018-07-09 VV570/PROJ1/code/test_toeplitz.m
test revised

@@ -1,6 +1,11 @@
-p = 10;
-r = rand(1, p+1)
-T = toeplitz(r(:,1:p))
-b = r(:,2:p+1)
-a1 = inv(T)*b'
-a2 = solve_toeplitz(r)'
+p = 1000;
+r = rand(1, p+1);
+T = toeplitz(r(:,1:p));
+b = r(:,2:p+1);
+tic
+    a1 = inv(T)*b';
+toc
+
+tic
+    a2 = solve_toeplitz(r)';
+toc

### 2018-07-09 VV570/PROJ1/code/calc_autocorrelation.m
part1 experiment ok

@@ -1,0 +1,8 @@
+function [r] = calc_autocorrelation(s, j)
+    n = length(s);
+    r = 0;
+    for i = 1:n-j
+        r = r + s(i) * s(i+j);
+    end
+end
+

### 2018-07-09 VV570/PROJ1/code/main.m

@@ -1,0 +1,35 @@
+clear all;
+close all;
+clc;
+
+file_path = '../resource/clip.mp3';
+info = audioinfo(file_path);
+[y,Fs] = audioread(file_path);
+L = 2000-1;
+begin = 18000;
+y = y(begin:begin+L); 
+t = 0:length(y)-1;
+p = 12;
+
+%Autocorrelation
+r = zeros(1, p+1);
+for j = 1:p+1
+    r(j) = calc_autocorrelation(y, j-1);
+end
+a = solve_toeplitz(r);
+est = zeros(1, length(y));
+for i = p+1:length(est)
+    est(i) = a*y(i-p:i-1)';
+end
+err = y-est;
+for i = 1:p
+    err(i)=0;
+end
+
+plot(t, y)
+xlabel('Time')
+ylabel('Audio Signal')
+hold on
+plot(t, est)
+hold off
+

### 2018-07-09 VV570/PROJ1/code/calc_covariance.m
experiment basically all done!

@@ -1,0 +1,7 @@
+function [c] = calc_covariance(s, a, b, j, i)
+    c = 0;
+    for n=a:b
+        c = c+s(n-j)*s(n-i);
+    end
+end
+

### 2018-07-09 VV570/PROJ1/code/main.m

@@ -1,35 +1,0 @@
-clear all;
-close all;
-clc;
-
-file_path = '../resource/clip.mp3';
-info = audioinfo(file_path);
-[y,Fs] = audioread(file_path);
-L = 2000-1;
-begin = 18000;
-y = y(begin:begin+L); 
-t = 0:length(y)-1;
-p = 12;
-
-%Autocorrelation
-r = zeros(1, p+1);
-for j = 1:p+1
-    r(j) = calc_autocorrelation(y, j-1);
-end
-a = solve_toeplitz(r);
-est = zeros(1, length(y));
-for i = p+1:length(est)
-    est(i) = a*y(i-p:i-1)';
-end
-err = y-est;
-for i = 1:p
-    err(i)=0;
-end
-
-plot(t, y)
-xlabel('Time')
-ylabel('Audio Signal')
-hold on
-plot(t, est)
-hold off
-

### 2018-07-09 VV570/PROJ1/code/main1.m

@@ -1,0 +1,35 @@
+function main1
+    file_path = '../resource/clip.mp3';
+    [y,~] = audioread(file_path);
+    len = 240;
+    beg_idx = 18000;
+    end_idx = beg_idx+len-1;
+    ysp = y(beg_idx:end_idx); 
+    t = 0:len-1;
+    p = 12;
+    
+    r = zeros(1, p+1);
+    for j = 1:p+1
+        r(j) = calc_autocorrelation(ysp, j-1);
+    end
+    a = solve_toeplitz(r);
+    
+    est = zeros(1, len);
+    for n = beg_idx:end_idx
+        tmp = 0;
+        for j = 1:p
+            tmp = tmp + a(j) * y(n-j);
+        end
+        est(n-beg_idx+1) = tmp;
+    end
+    
+    err = ysp-est;
+
+    plot(t, ysp)
+    xlabel('Time')
+    ylabel('Audio Signal')
+    hold on
+    plot(t, est)
+    legend('Original','Predicted')
+    hold off
+end

### 2018-07-09 VV570/PROJ1/code/main2.m

@@ -1,0 +1,46 @@
+function main2
+    file_path = '../resource/clip.mp3';
+    [y,~] = audioread(file_path);
+    len = 240;
+    beg_idx = 18000;
+    end_idx = beg_idx+len-1;
+    ysp = y(beg_idx:end_idx); 
+    t = 0:len-1;
+    p = 12;
+    
+    c = zeros(p, p);
+    b = zeros(p, 1);
+    for i = 1:p
+        b(i) = calc_covariance(y, beg_idx, end_idx, 0, i);
+        for j = 1:i
+            tmp = calc_covariance(y, beg_idx, end_idx, j, i);
+            c(i, j) = tmp;
+            c(j, i) = tmp;
+        end
+    end
+    
+    L = cholesky_decomp(c);
+    opts.LT = true; 
+    opts.UT = false;
+    tmp = linsolve(L, b,opts);
+    opts.LT = false;
+    opts.UT = true;
+    a = linsolve(L',tmp, opts);
+    
+    est = zeros(1, len);
+    for n = beg_idx : end_idx
+        tmp = 0;
+        for j = 1:p
+            tmp = tmp + a(j) * y(n-j);
+        end
+        est(n-beg_idx+1) = tmp;
+    end
+
+    plot(t, ysp)
+    xlabel('Time')
+    ylabel('Audio Signal')
+    hold on
+    plot(t, est)
+    legend('Original','Predicted')
+    hold off
+end

### 2018-07-09 VV570/PROJ1/article/article.tex
toeplitz solver ok!
part1 experiment ok
summary part1 ok

@@
 \usepackage{lineno}
+
+%use graph format
+\usepackage{graphicx} 
+\usepackage{epstopdf}
 
@@
 %%
-\linenumbers
+%\linenumbers
 
 %% main text
-\section{Background and Basic Equations}
+\section{Basic Equations}
 \label{S:1}
@@
 \end{equation}
-where $a_0 = -1$. The minimum mean square error(MMSE) is adopted as the principle to determine these coefficients $a_i$.\\
+where $a_0 = -1$. The minimum mean square error(MMSE) is adopted as the principle to determine these coefficients $a_i$.
+
 The square error of the prediction is defined as
@@
 \end{equation}
-where $i= 1, 2, ..., p$. \\
+where $i= 1, 2, ..., p$.
+
 Denote $\phi(i,j)$ as
@@
 \end{equation}
-where $i= 1, 2, ..., p$.\\
+where $i= 1, 2, ..., p$.
+
 Hence, it is left to determine $\phi(j, i)$ and then $a_j$ can be resolved.
@@
 \end{equation}
-It can be observed that the coefficient matrix is the so called Toeplitz matrix, where elements are symmetry and  each descending diagonal from left to right is constant.\\
+It can be observed that the coefficient matrix is the so called Toeplitz matrix, where elements are symmetry and  each descending diagonal from left to right is constant.
+
 Suppose $a_i^{(k)} \ (i=1, 2, ... ,k)$ is the solution for $k-th$ iteration for $p=k$, which implies
@@
 \end{equation}
-And it can be easily verified that the recursion formula is also valid when $k=1,2$, thus this solution is justified by induction. \\
+And it can be easily verified that the recursion formula is also valid when $k=1,2$, thus this solution is justified by induction.
+
 Further, this is the so-called Levinson-Durbin algorithm, with time complexity $O(n^2)$, and it is much faster than solving it directly where time complexity is $O(n^3)$.
@@
 \section{The Covariance Method}
-In constrast to the previous method, the covariance method doesn't windowed the signal. Instead, the amount of points used to calculate the error is fixed. And it aims to minimize the error\\
+In constrast to the previous method, the covariance method doesn't windowed the signal. Instead, the amount of points used to calculate the error is fixed. And it aims to minimize the error.
+
 Suppose the amount of points to calculate $r(j)$ is $N$, then by definition
@@
 \end{equation}
-Since $c(i, j) \neq c(i+k, j+k)$, the coefficient matrix above is no longer the Toeplitz matrix, and different scheme should be employed to solve this linear system.\\
+Since $c(i, j) \neq c(i+k, j+k)$, the coefficient matrix above is no longer the Toeplitz matrix, and different scheme should be employed to solve this linear system.
+
 It's clear that $c(i, j) = c(j, i)$, so it can be solved using the Cholesky decomposition. And the coefficient matrix can be decomposed as
@@
 \end{equation}
-where $L$ is a lower triangle matrix.
+where $L$ is a lower triangle matrix. Onece $L$ is obtained, targeting $a_i$ can be easily calculated by
+\begin{equation}
+	\begin{aligned}
+		y & = linsolve(L, b)\\
+		{a_i} & = linsolve(L^T, y)
+	\end{aligned}
+\end{equation}
 
 \section{Numerical Experiment}
+A segment of audio is taken as the original signal, where $len = 120$ samples are included. 
+\subsection{Comparison between the autocorrelation and covariance}
+Numerical experiments indicates that the covariance method performs better than the autocorrelation method when $p$ is fixed($p=6$).
+
+The autocorrelation method is examined in Fig(\ref{fig:performance_auto}).
+It can be seen from the left figure that the predicted signals fit the original signals well, only with slightly difference.
+The error between is much more apparent at peak area.
+Details of performance is given in the right figure.
+
+\begin{figure}[!htbp]\centering	
+	\begin{minipage}{6.5cm}
+		\centering
+		\includegraphics[height=6cm,width=7cm]{../pic/autocorrelation_120_6.eps}
+	\end{minipage}
+	\begin{minipage}{6.5cm}
+		\centering
+		\includegraphics[height=6cm,width=7cm]{../pic/autocorrelation_err_120_6.eps}
+	\end{minipage}
+	\caption{Performance of the Autocorrelation Method}\label{fig:performance_auto}
+\end{figure}
+
+The covariance method is investigated in Fig(\ref{fig:performance_cov}).
+It can be seen from the left figure that the predicted signals meet the original signals very well and the error between is significantly eliminated compared to the autocorrelation method.
+It can be seen from the right figure that the error is lower by an order of magnitude.
+
+\begin{figure}[!htbp]\centering	
+	\begin{minipage}{6.5cm}
+		\centering
+		\includegraphics[height=6cm,width=7cm]{../pic/covariance_120_6.eps}
+	\end{minipage}
+	\begin{minipage}{6.5cm}
+		\centering
+		\includegraphics[height=6cm,width=7cm]{../pic/covariance_err_120_6.eps}
+	\end{minipage}
+	\caption{Performance of the Covariance Method}\label{fig:performance_cov}
+\end{figure}
+
+The difference can be explained as the bounds of $n$ are different.
+There're $p$ more points used in the covariance method when calculating the linear prediction coefficients, and hence, it's more likely that the covariance method out-performs the autocorrelation method.
+
+\subsection{Relation between the error and $p$}
 

### 2018-07-09 VV570/PROJ1/code/main1.m

@@ -1,19 +1,22 @@
 function main1
+    %提取音频数据
     file_path = '../resource/clip.mp3';
     [y,~] = audioread(file_path);
-    len = 240;
+    len = 120;
     beg_idx = 18000;
     end_idx = beg_idx+len-1;
     ysp = y(beg_idx:end_idx); 
     t = 0:len-1;
-    p = 12;
+    p = 6;
     
+    %求解线性预测系数
     r = zeros(1, p+1);
     for j = 1:p+1
         r(j) = calc_autocorrelation(ysp, j-1);
     end
     a = solve_toeplitz(r);
     
+    %估算
     est = zeros(1, len);
     for n = beg_idx:end_idx
         tmp = 0;
@@ -23,8 +26,10 @@ function main1
         est(n-beg_idx+1) = tmp;
     end
     
-    err = ysp-est;
-
+    err = abs(ysp-est);
+    
+    %画图
+    figure(1)
     plot(t, ysp)
     xlabel('Time')
     ylabel('Audio Signal')
@@ -32,4 +37,10 @@ function main1
     plot(t, est)
     legend('Original','Predicted')
     hold off
+    
+    figure(2)
+    plot(t, err)
+    ylim([0 0.2])
+    xlabel('Time')
+    ylabel('Absolute Error')
 end

### 2018-07-09 VV570/PROJ1/code/main2.m

@@ -1,13 +1,15 @@
 function main2
+    %提取音频数据
     file_path = '../resource/clip.mp3';
     [y,~] = audioread(file_path);
-    len = 240;
+    len = 120;
     beg_idx = 18000;
     end_idx = beg_idx+len-1;
     ysp = y(beg_idx:end_idx); 
     t = 0:len-1;
-    p = 12;
+    p = 6;
     
+    %构造系数矩阵
     c = zeros(p, p);
     b = zeros(p, 1);
     for i = 1:p
@@ -19,6 +21,7 @@ function main2
         end
     end
     
+    %通过Cholesky分解求线性预测系数
     L = cholesky_decomp(c);
     opts.LT = true; 
     opts.UT = false;
@@ -27,6 +30,7 @@ function main2
     opts.UT = true;
     a = linsolve(L',tmp, opts);
     
+    %估算
     est = zeros(1, len);
     for n = beg_idx : end_idx
         tmp = 0;
@@ -36,6 +40,10 @@ function main2
         est(n-beg_idx+1) = tmp;
     end
 
+    err = abs(est - ysp);
+    
+    %画图
+    figure(1)
     plot(t, ysp)
     xlabel('Time')
     ylabel('Audio Signal')
@@ -43,4 +51,10 @@ function main2
     plot(t, est)
     legend('Original','Predicted')
     hold off
+    
+    figure(2)
+    plot(t, err)
+    ylim([0 0.2])
+    xlabel('Time')
+    ylabel('Absolute Error')
 end

### 2018-07-09 VV570/PROJ1/code/main2.m
all done!

@@ -1,4 +1,20 @@
 function main2
+    x = 2:2:50;
+    y = zeros(1, length(x));
+    
+    for idx = 1:length(x)
+        error = lpc_covariance(x(idx));
+        y(idx) = norm(error,2);
+    end
+    
+    y = log(y);
+    plot(x, y);
+    xlabel('p');
+    ylabel('log(||e||)');
+    
+end
+
+function[err] = lpc_covariance(p)
     %提取音频数据
     file_path = '../resource/clip.mp3';
     [y,~] = audioread(file_path);
@@ -7,7 +23,6 @@ function main2
     end_idx = beg_idx+len-1;
     ysp = y(beg_idx:end_idx); 
     t = 0:len-1;
-    p = 6;
     
     %构造系数矩阵
     c = zeros(p, p);
@@ -57,4 +72,6 @@ function main2
     ylim([0 0.2])
     xlabel('Time')
     ylabel('Absolute Error')
+    fn = sprintf('../pic/covariance_err_%d_%d', len, p);
+%     saveas(gcf,fn,'eps');
 end

### 2018-07-11 VV570/HW7/submission.tex
HW7 Q1 ok

--- 2018-06-23 VV570/HW5/submission.tex
@@
 %----------------------------------------------------------------------------------------
-
 \documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size
@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm  
-
 \usepackage{listings}
 \lstset{language=Matlab}
+\usepackage{enumerate}
 
 \usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
-
 \usepackage{sectsty} % Allows customizing section commands
 \allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps
-
 \usepackage{fancyhdr} % Custom headers and footers
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Introduction to Numerical Analysis \\ HW5 \\ % The assignment title
+\huge Introduction to Numerical Analysis \\ HW7 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 %----------------------------------------------------------------------------------------
-\section{Lebesgue constant for Chebyshev nodes}
-\begin{enumerate}
+\section{Question 1}
+	\begin{enumerate}[(a)]
 		\item 
-		\begin{enumerate}
+			For example
+			\begin{equation}
+				y = tan(x), \ \ x\in (-\frac{\pi}{2}, \frac{\pi}{2})
+			\end{equation}
+			It's differentiable over $(-\frac{\pi}{2}, \frac{\pi}{2})$, and the derivative is 
+			\begin{equation}
+				y' = \frac{1}{cos^2(x)}
+			\end{equation}
+			It's obvious that $y' \rightarrow \infty$ when $x \rightarrow \frac{\pi}{2}$.
 		\item 
 			\begin{proof}
-					Denote
+				Denote $g(x)$ over $[x_1, x_2]$ as
 				\begin{equation}
-						\begin{aligned}
-							LHS &\triangleq (x-x_i)l_i(x) \\
-							RHS &\triangleq \frac{T_{n+1}(x)}{T_{n+1}'(x_i)}
-						\end{aligned}
+					g(x) = f(x) - f(x_1) - \frac{f(x_2)-f(x_1)}{x_2-x_1}(x-x_1) 
 				\end{equation}
-					It is left to prove $LHS = RHS$.\\
-					The left part can be written as
+				where $a< x_1 < x_2 < b$. Then, $g(x_1) = 0$ and $g(x_2)=0$.
+
+				Thus, from Rolle's theorem, there exists $\xi \in (x_1, x_2)$ s.t. 
 				\begin{equation}
-						LHS = c_l \omega(x)
+					g'(\xi)= 0
 				\end{equation}
-					where 
+				namely
 				\begin{equation}
-						\omega(x) = \prod_{i=0}^{n}(x-x_i)
+					\frac{f(x_2) - f(x_1)}{x_2-x_1} = f'(\xi)
 				\end{equation}
-					and
+				Since $f'$ is bounded, then $|f'(\xi)| \leq M$. Thus
 				\begin{equation}
-						c_l = \frac{1}{\prod_{k=0, k\neq i}^{n}(x_i - x_k)} 
+					|f(x_2) - f(x_1)| \leq M |x_2 - x_1|
 				\end{equation}
-
-					Since both $LHS$ and $RHS$ are polynomials of order $n+1$, they are equivalent iff. they have same roots and leading coefficients.\\
-					On the one hand,as for all $x_i$, where $i = 0, 1, ... , n$
-					\begin{equation}
-						T_{n+1}(x_i) = cos((n+1)\theta_i) = cos(\frac{2i+1}{2}\pi) = 0
-					\end{equation}
-					Thus, $LHS$ and $RHS$ have same roots. $RHS$ can therefore be written as
-					\begin{equation}
-						RHS(x) = c_r \omega(x)
-					\end{equation}
-					On the other hand, since
-					\begin{equation}
-						LHS'(x)|_{x=x_i} = (l_i(x) + (x-x_i)l_i'(x))|_{x=x_i} = 1
-					\end{equation}
-					and
-					\begin{equation}
-						RHS'(x)|_{x=x_i} = \frac{T'_{n+1}(x)}{T_{n+1}'(x_i)}\Big|_{x=x_i} = 1
-					\end{equation}
-					Thus, the leading coefficients of $LHS$ and $RHS$ are equal, namely $c_l = c_r$.\\
-					Hence, $LHS=RHS$.
+				which means that $f(x)$ is Lipschitz continous.
 			\end{proof}
 		\item 
-				\begin{proof}
+			For example
 			\begin{equation}
-						\begin{aligned}
-							T'_{n+1}(x) & = (cos((n+1)arccos(x)))'\\
-							            & = sin((n+1)arccos(x)) (n+1) \frac{1}{\sqrt{1-x^2}}\\
-							            & = \frac{n+1}{\sqrt{1-cos^2(\theta)}} sin((n+1)\theta) 
-						\end{aligned}
+				y = \frac{1}{x}, \ \ x \in (0, 1)
 			\end{equation}
-					As $\theta_k = \frac{2k+1}{2(n+1)}\pi$, thus, $sin(\theta_k) > 0$, and
+			$y$ is obviously differentiable and its derivative is
 			\begin{equation}
-						T'_{n+1}(x_k) = \frac{n+1}{sin(\theta_k)} sin(\frac{2k+1}{2}\pi) = {(-1)}^k \frac{n+1}{sin(\theta_k)}
+				y' = -\frac{1}{x^2}, \ \ x \in (0, 1)
 			\end{equation}
-				\end{proof}
+			Suppose there exist a constant $c>0$ s.t. 
+			\begin{equation}
+				|y_2 - y_1| \leq c|x_2 - x_1|
+			\end{equation}
+			is valid for all $0 < x_1 < x_2 < 1$.
+			Let $y(b) - y(a) = c(b-a)$, where $a < b$then
+			\begin{equation}
+				c = \frac{1}{ab}
+			\end{equation}
+			Take the mid-point of $a, b$, then
+			\begin{equation}
+				\frac{y(a)-y(\frac{b+a}{2})}{\frac{b+a}{2}-a} = \frac{1}{a(\frac{b+a}{2})} > \frac{1}{ab} = c
+			\end{equation}
+			Thus, the assumption fails, which means that $y$ is not Lipschitz continous.
 		\item 
-				\begin{proof}
-					As
+			For example
 			\begin{equation}
-						T_{n+1}(1) = cos((n+1)arccos(1)) = 1	
+				y = |x|, \ \ x \in (-1, 1)
 			\end{equation}
-					Thus
+			It's Lipschitz continous as for any $-1 < x_1 < x_2 < 1$
 			\begin{equation}
-						\begin{aligned}
-							\sum_{i=0}^{n}|l_i(1)| & = \sum_{i=0}^{n}\Bigg|\frac{T_{n+1}(1)}{(1-x_i)T'_{n+1}(x_i)}\Bigg| \\
-												   & = \sum_{i=0}^{n} \frac{1}{\Big|(1-x_i)T'_{n+1}(x_i)\Big|}\\
-												   & = \frac{1}{n+1} \sum_{i=0}^{n} \bigg|\frac{sin\theta_i}{(1-cos\theta_i)} \bigg|\\
-												   & = \frac{1}{n+1} \sum_{i=0}^{n} \bigg|\frac{sin\theta_i}{2sin^2(\frac{\theta_i}{2})} \bigg|\\
-												   & \geq  \frac{1}{n+1} \sum_{i=0}^{n} cot(\frac{\theta_i}{2})\\
-						\end{aligned}
+				\frac{|y(x_2)-y(x_1)|}{|x_2 - x_1|} \leq 1
 			\end{equation}
-				\end{proof} 			
-		\end{enumerate}
-	\item 
-		\begin{enumerate}
-			\item 
-				\begin{proof}
-					According to the mean value theorem, there exists $\theta \in [\frac{\theta_k}{2}, \frac{\theta_{k+1}}{2}]$, s.t.
-					\begin{equation}
-						\int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt = \frac{\theta_{k+1} - \theta_k}{2} cot(\theta)
-					\end{equation}
-					As $cot'(t) = -\frac{1}{sin^2(t)} < 0$, and $\theta_k \leq \theta \leq \theta_{k+1}$, thus
-					\begin{equation}
-						cot(\theta) \leq cot(\theta_k)
-					\end{equation}
-					Therefore
-					\begin{equation}
-						\int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt \leq \frac{\theta_{k+1} - \theta_k}{2} cot(\theta_k)
-					\end{equation}
-				\end{proof}
-
-			\item 
-				\begin{proof}
-					As $\theta_{k+1} - \theta_k = \frac{\pi}{n+1}$ and according to the result that have been proved above
-					\begin{equation}
-						\begin{aligned}
-							\sum_{k=0}^{n} \int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt 
-							& \leq \sum_{k=0}^{n} \frac{\theta_{k+1} - \theta_k}{2}cot(\frac{\theta_k}{2})\\
-							& = \frac{\pi}{2(n+1)} \sum_{k=0}^{n} cot(\frac{\theta_k}{2})
-						\end{aligned}
-					\end{equation}
-				\end{proof}
-
-			\item 
-				\begin{proof}
-					As $\theta_n = \frac{2n+1}{2n+2}\pi < \pi$, $\theta_{n+1} = \frac{2n+3}{2n+2} > \pi$, and $cot(x)$ is positive over $(0, \frac{\pi}{2})$, while negative otherwise.
-					Thus
-					\begin{equation}
-							\int_{\frac{\theta_0}{2}}^{\frac{\pi}{2}} cot(t) dt 
-							\leq \int_{\frac{\theta_0}{2}}^{\frac{\theta_n}{2}} cot(t) dt
-							= \sum_{k=0}^{n-1} \int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt
-					\end{equation}
-					Hence
-					\begin{equation}
-						\int_{\frac{\theta_0}{2}}^{\frac{\pi}{2}} cot(t) dt \leq \frac{\pi}{2(n+1)} \sum_{i=0}^{n}cot(\frac{\theta_i}{2})
-					\end{equation}
-					(... not fine)
-				\end{proof}
-
-		\end{enumerate}
-
-	\item 
-		\begin{proof}
-			\begin{equation}
-				\begin{aligned}
-					\Lambda_n & = \max_{x \in [a, b]} \sum_{i=0}^{n} |l_i(x)|\\
-							  & \geq \sum_{i=0}^{n} |l_i(1)|\\
-							  & \geq \frac{1}{n+1} \sum_{i=0}^{n} cot(\frac{\theta_i}{2})\\
-							  & \geq \frac{2}{\pi} \int_{\theta_0 / 2}^{\pi/2} cot(t)dt\\
-							  & = \frac{2}{\pi} ln(|sin(t)|) \Bigg| _{\theta_0/2}^{\pi/2}\\
-							  & = - \frac{2}{\pi} ln(sin(\frac{\theta_0}{2}))\\
-							  & \geq \frac{2}{\pi} ln(\frac{2}{\theta_0}) = \frac{2}{\pi} ln(\frac{4(n+1)}{\pi})\\
-							  & \ge \frac{2}{\pi} ln(n)
-				\end{aligned}
-			\end{equation}
-		\end{proof}
+			but it is not differentiable at $x=0$.
 
@@
 %----------------------------------------------------------------------------------------
-\section{Interpolation}
+\section{Question 2}
 
@@
 %----------------------------------------------------------------------------------------
-\section{Trigonometric polynomials}
+\section{Question 3}
 

### 2018-07-14 VV570/HW7/tex/submission.tex
some relief...

--- 2018-07-11 VV570/HW7/submission.tex
@@
 \section{Question 2}
+	\begin{enumerate}
+		\item 
+			\begin{proof}
+				Since $|g'(x)|<1$, there exists $0<L<1$ s.t. $|g'(x)| \leq L$.
+				Then, according to the Lagrange intermediate value theorem
+				\begin{equation}
+					\begin{aligned}
+						|g(x_j) - g(x_i)| &= |g'(\xi)||x_j - x_i|\\
+										  &\leq L|x_j - x_i|
+					\end{aligned}
+				\end{equation}
+				As $g(x^*) = x^*$, applying the fixed point iteration, then
+				\begin{equation}
+					\begin{aligned}
+						|x_{k+1} - x^*| & = |g(x_k) - g(x^*)|\\
+										& \leq L|x_k - x^*|\\
+										& = L |(x_{k+1}-x^*) - (x_{k+1} - x_k)|\\
+										& \leq L|x_{k+1}-x^*| + L|x_{k+1} - x_k|
+					\end{aligned}
+				\end{equation}
+				Thus
+				\begin{equation}
+					\begin{aligned}
+						|x_{k+1} - x^*| & \leq \frac{L}{1-L} |x_{k+1} - x_k|\\
+						                & \leq \frac{L^2}{1-L}|x_k - x_{k-1}|\\
+						                & \leq ...\\
+						                & \leq \frac{L^{k+1}}{1-L} |x_1 - x_0|
+					\end{aligned}
+				\end{equation}
+				Since $0<L<1$, and $|x_1 - x_0|$ is finite, it indicates that
+				\begin{equation}
+					\lim\limits_{k\rightarrow\infty}|x_{k+1} - x^*| = 0
+				\end{equation}
+				Hence, the fixed-point iteration will converge to the unique fixed point $x^*$.
+			\end{proof}
 
+		\item 
+			\begin{proof}
+				Since $|g'(x)|>1$, there exists $L>1$ s.t. $|g'(x)| \geq L$.
+				Then, according to the Lagrange intermediate value theorem
+				\begin{equation}
+					\begin{aligned}
+						|g(x_j) - g(x_i)| &= |g'(\xi)||x_j - x_i|\\
+										  &\geq L|x_j - x_i|
+					\end{aligned}
+				\end{equation}
+				As $g(x^*) = x^*$, applying the fixed point iteration, then
+				\begin{equation}
+					\begin{aligned}
+					|x_{k+1} - x^*| & = |g(x_k) - g(x^*)|\\
+									& \geq L|x_k - x^*|\\
+									& = L |(x_{k+1} - x_k)-(x_{k+1}-x^*)|\\
+									& \geq L(|x_{k+1} - x_k|-|x_{k+1}-x^*|)\\
+					\end{aligned}
+				\end{equation}
+				Thus
+				\begin{equation}
+					\begin{aligned}
+						|x_{k+1} - x^*| & \geq \frac{L}{1+L} |x_{k+1} - x_k|\\
+										& \geq \frac{L^2}{1+L}|x_k - x_{k-1}|\\
+										& \geq ...\\
+										& \geq \frac{L^{k+1}}{1+L} |x_1 - x_0|
+					\end{aligned}
+				\end{equation}
+						Since $L>1$, and $|x_1 - x_0|$ is finite, it indicates that
+				\begin{equation}
+				\lim\limits_{k\rightarrow\infty}|x_{k+1} - x^*| = \infty
+				\end{equation}
+				Hence, the fixed-point iteration will never converge to the unique fixed point $x^*$.
+			\end{proof}
+
+	\end{enumerate}
 %----------------------------------------------------------------------------------------
@@
 \section{Question 3}
+\begin{enumerate}
+	\item 
+		For resolving the smallest positive root, the equation can be reformed as
+		\begin{equation}
+			x = tg^{-1}(4x) \triangleq g(x)
+		\end{equation}
+		It can be easily observed that the root lies in $(1, \frac{\pi}{2})$.
+
+		Applying the fundamental inequality, $g'(x)$ can be further determined as
+		\begin{equation}
+			0 < g'(x) = \frac{4}{1+(4x)^2} = \frac{1}{\frac{1}{4}+ 4x^2} \leq \frac{1}{x} < 1
+		\end{equation}
+		Thus, the fixed-point iteration can be employed to resolve the result. The starting value is given as
+		\begin{equation}
+			x_0 = \frac{1+\frac{\pi}{2}}{2}
+		\end{equation}
+		A python script is written to perform the numerical iteration, and the final result is
+		\begin{equation}
+			x^* \approx 1.393
+		\end{equation}
+	\item 
+		For resolving the second smallest positive root, the original coordinate axes $Oxy$ can be transfromed to $O'xy$ to simplify to equation, where $(\pi, 0)$ in origial coordinate is selected as the transformed origin.
+Thus, it's equivalent to solve
+		\begin{equation}
+			tg(x) = 4(x+\pi)
+		\end{equation}
+		For similar consideration, the equation is reformed as
+		\begin{equation}
+			x = tg^{-1}(4(x+\pi)) \triangleq g(x)
+		\end{equation}
+		Obviously, the root is located in $(1, \frac{\pi}{2})$ in the transformed coordinate.Similarly, the range of $g'(x)$ is examined as
+		\begin{equation}
+			0<g'(x)=\frac{4}{1+16(x+\pi)^2} = \frac{1}{\frac{1}{4} + 4(x+\pi)^2} <\frac{1}{\frac{1}{4}+4x^2} <\frac{1}{x} < 1
+		\end{equation}
+		Thus, the fixed-point iteration can be employed to resolve the result. The starting value is given as
+		\begin{equation}
+			x'_0 = \frac{1+\frac{\pi}{2}}{2}
+		\end{equation}
+		A python script is written to perform the numerical iteration, and the final result is
+		\begin{equation}
+			x^* = x'^* + \pi \approx 1.517 + \pi \approx 4.659 
+		\end{equation}
+\end{enumerate}
+%----------------------------------------------------------------------------------------
+%	PROBLEM 6
+%----------------------------------------------------------------------------------------
+\section{Question 6}
+	\begin{enumerate}
+		\item 
+			For example, $e^x = x+1$ over $[-1, 1]$ can be solved by bisection, but $g'(x) \triangleq (e^x-1)' = e^x > 1$ when $x>0$.
+Thus the fixed-point iteration will diverge if the initial value is given as $x_0 > 0$.
+		\item 
+			For example, $cos(x) = 0$ over $[0, \frac{\pi}{2}]$.
+Let $g'(x)\triangleq (cos(x)+x)' = 1-sin(x)$, it's clear that $0 \leq g'(x) \leq 1$, thus, it can be resolved by the fixed-point iteration given an starting value $x_0 \in (0, \frac{\pi}{2})$ .
+However, the Newton method would fail if $x_0$ is very close to $0$.
+This is caused as $cos'(x) = sin(x) \rightarrow 0$, which lead to the further displacement of $x_1$ as $\frac{f(x_0)}{f'(x_0)}\rightarrow\infty$.
+
+	\end{enumerate}
 

### 2018-07-14 VM532/HW3/code/Task1.py

@@ -1,0 +1,69 @@
+import numpy as np
+from matplotlib import pyplot as plt
+from math import pow
+from scipy.integrate import quad
+from scipy.special import betainc, beta
+
+t0 = 0
+t_inf = -7
+u_inf = 7.6
+p = 101325
+
+L = 0.15
+xi1 = 0.05
+xi2 = 0.075
+
+rho = 1.326
+mu = 1.7894e-5
+
+Cp = 1.005e3
+k = 2.44e-2
+Pr = mu * Cp / k
+print(Pr)
+Rex = rho * u_inf * L / mu
+print(Rex)
+
+
+def u1(x):
+    return 1 - pow(xi1 / x, 3 / 4)
+
+
+def u2(x):
+    return 1 - pow(xi2 / x, 3 / 4)
+
+
+def h(x):
+    return -4 / 3 * x * (betainc(1 / 3, 4 / 3, u2(x)) - betainc(1 / 3, 4 / 3, u1(x))) * beta(1 / 3, 4 / 3)
+
+
+q0 = (t0 - t_inf) * k * pow(Pr, 1 / 3) * pow(Rex, 1 / 2) / (0.623 * h(L))
+print(q0)
+
+
+def t(x: float):
+    if x <= xi1:
+        return t_inf
+    elif x <= xi2:
+        return t_inf + f(x, x)
+    else:
+        return t_inf + f(xi2, x)
+
+
+def f(up: float, x: float):
+    ret = 0.623 / k * pow(Pr, -1 / 3) * pow(Rex, -1 / 2) * q0
+
+    def g(s):
+        return pow(1 - pow(s / x, 3 / 4), -2 / 3)
+
+    ri, err = quad(g, xi1, up)
+    ret *= ri
+
+    return ret
+
+
+N = 101
+x_val = np.linspace(0, L, N)
+y_val = np.array([t(e) for e in x_val])
+
+plt.plot(x_val, y_val)
+plt.show()

### 2018-07-14 VM532/HW3/code/Task3.py

@@ -1,0 +1,69 @@
+import numpy as np
+from matplotlib import pyplot as plt
+from math import pow
+from scipy.integrate import quad
+from scipy.special import betainc, beta
+
+t0 = 0
+t_inf = -7
+u_inf = 46
+p = 101325
+
+L = 1.8
+xi1 = 0
+xi2 = 0.6
+
+rho = 1.326
+mu = 1.7894e-5
+
+Cp = 1.005e3
+k = 2.44e-2
+Pr = mu * Cp / k
+print(Pr)
+Rex = rho * u_inf * L / mu
+print(Rex)
+
+
+def u1(x):
+    return 1 - pow(xi1 / x, 3 / 4)
+
+
+def u2(x):
+    return 1 - pow(xi2 / x, 3 / 4)
+
+
+def h(x):
+    return -4 / 3 * x * (betainc(1 / 3, 4 / 3, u2(x)) - betainc(1 / 3, 4 / 3, u1(x))) * beta(1 / 3, 4 / 3)
+
+
+q0 = (t0 - t_inf) * k * pow(Pr, 1 / 3) * pow(Rex, 1 / 2) / (0.623 * h(L))
+print(q0)
+
+
+def t(x: float):
+    if x <= xi1:
+        return t_inf
+    elif x <= xi2:
+        return t_inf + f(x, x)
+    else:
+        return t_inf + f(xi2, x)
+
+
+def f(up: float, x: float):
+    ret = 0.623 / k * pow(Pr, -1 / 3) * pow(Rex, -1 / 2) * q0
+
+    def g(s):
+        return pow(1 - pow(s / x, 3 / 4), -2 / 3)
+
+    ri, err = quad(g, xi1, up)
+    ret *= ri
+
+    return ret
+
+
+N = 101
+x_val = np.linspace(0, L, N)
+y_val = np.array([t(e) for e in x_val])
+
+plt.plot(x_val, y_val)
+plt.show()

### 2018-07-14 VV570/HW7/code/Question3a.py

@@ -1,0 +1,23 @@
+import math
+import numpy as np
+
+a = 1
+b = math.pi / 2
+
+
+def g(x):
+    return math.atan(4 * x)
+
+
+N = 21
+x = np.zeros(N)
+x[0] = (a + b) / 2
+
+for i in range(1, N):
+    x[i] = g(x[i - 1])
+
+print(x)
+xs = x[-1]
+print(xs)
+print(math.tan(xs))
+print(4 * xs)

### 2018-07-14 VV570/HW7/code/Question3b.py

@@ -1,0 +1,23 @@
+import math
+import numpy as np
+
+a = 1
+b = math.pi / 2
+
+
+def g(x):
+    return math.atan(4 * (x + math.pi))
+
+
+N = 21
+x = np.zeros(N)
+x[0] = (a + b) / 2
+
+for i in range(1, N):
+    x[i] = g(x[i - 1])
+
+print(x)
+xs = x[-1] + math.pi
+print(xs)
+print(math.tan(xs))
+print(4 * xs)

### 2018-07-19 VV570/LAB3/myFP.m
remane

@@ -8,8 +8,8 @@ function [xvec] = myFP( f, x0, tol, nmax, varargin)
 %   varargin: Custom plotting parameters.
 %Output:
 %   xvec: Intermediate iteration records.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%       
-    
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
     function outputlocalfunc()
             plot(0:(length(xvec)-1), xvec, varargin{2:end});            
             h = xlabel('$n$' );

### 2018-07-19 VV570/LAB3/myplot.m

@@ -1,6 +1,7 @@
 function myplot( x, y, varargin )
 %Illusration of varargin using plot
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
     plot(x, y, varargin{2:end});
     
     h = line([min(x) max(x)], [0 0]);

### 2018-07-19 VV570/LAB3/Task2.m
task2 ok

@@ -1,0 +1,16 @@
+clear all;
+close all;
+
+func = @(x) atan((x-0.4)*(x-0.7));
+xvec = myFP(func, 0, 1e-10, 50, 'Numerical solutions to $\tan(x)=(x-0.4)*(x-0.7)$','b--o');
+n = length(xvec);
+
+E = zeros(1, n);
+eps = zeros(1, n);
+
+for i = 2:n
+    E(i) = abs(xvec(i) - xvec(i-1));
+    eps(i) = abs(E(i)/xvec(i));
+end
+
+table((1:n)', xvec', E', eps', 'VariableNames', {'n', 'xvec', 'E', 'eps'})

### 2018-07-19 VV570/LAB3/Task3a.m
task3 ok

@@ -1,0 +1,17 @@
+clear all; close all; clc;
+
+f = @(x) exp(x)-4*x.^2;
+N = 101;
+x1 = linspace(-1,0, N);
+y1 = f(x1);
+x2 = linspace(0,1, N);
+y2 = f(x2);
+x3 = linspace(4, 4.5);
+y3 = f(x3);
+
+subplot(1,3,1);
+plot(x1, y1);
+subplot(1,3,2);
+plot(x2, y2);
+subplot(1,3,3);
+plot(x3, y3);

### 2018-07-19 VV570/LAB3/Task3b.m

@@ -1,0 +1,9 @@
+clear all; close all; clc;
+
+f = @(x) exp(x)-4*x.^2;
+
+a = -1;
+b = 0;
+eps = 1e-10;
+
+[xval, err, yval] = bisect(f, a, b, eps)

### 2018-07-19 VV570/LAB3/Task3c.m

@@ -1,0 +1,13 @@
+clear all; close all; clc;
+
+f = @(x) exp(x)-4*x.^2;
+df = @(x) exp(x) - 8*x;
+
+a = -1;
+b = 0;
+x0 = (a+b)/2;
+eps_x = 1e-10;
+eps_y = 1e-10;
+max_iter = 20;
+
+[xval, x_err,iter_num yval] = newton(f, df, x0, eps_x, eps_y, max_iter)

### 2018-07-19 VV570/LAB3/Task3d.m

@@ -1,0 +1,9 @@
+clear all; close all; clc;
+
+g = @(x) -0.5*exp(0.5*x);
+ 
+x0 = -0.5;
+tol = 1e-10;
+max_iter = 20;
+
+[iter_num, xval, x_err, pn] = fixpt(g, x0, tol, max_iter)

### 2018-07-19 VV570/LAB3/Task4a.m
add task4”

@@ -1,0 +1,21 @@
+clear all; close all; clc;
+
+f = @(x) exp(x)*(x-2).^3;
+df = @(x) exp(x)*((x-2).^3 + 3*(x-2).^2);
+
+N = 101;
+x = linspace(0, 3, N);
+y = zeros(1, N);
+dy = zeros(1, N);
+
+for i = 1:N
+    y(i) = f(x(i));
+    dy(i) = df(x(i));
+end
+
+subplot(2,1,1)
+plot(x, y)
+title('f(x)')
+subplot(2,1,2)
+plot(x, dy)
+title('Derivative of f(x)')

### 2018-07-19 VV570/LAB3/Task4b.m

@@ -1,0 +1,13 @@
+clear all; close all; clc;
+
+f = @(x) exp(x)*(x-2).^3;
+df = @(x) exp(x)*((x-2).^3 + 3*(x-2).^2);
+
+a = 0;
+b = 3;
+x0 = (a+b)/2;
+eps_x = 1e-10;
+eps_y = 1e-10;
+max_iter = 51;
+
+[xval, x_err,iter_num yval] = newton(f, df, x0, eps_x, eps_y, max_iter)

### 2018-07-19 VV570/LAB3/Task4a.m
task4 ok

@@ -2,20 +2,35 @@ clear all; close all; clc;
 
 f = @(x) exp(x)*(x-2).^3;
 df = @(x) exp(x)*((x-2).^3 + 3*(x-2).^2);
+ddf = @(x) exp(x)*((x-2).^3 + 6*(x-2).^2 + 6*(x-2));
+dddf = @(x) exp(x)*((x-2).^3 + 9*(x-2).^2 + 18*(x-2) + 6);
 
-N = 101;
+N = 301;
 x = linspace(0, 3, N);
 y = zeros(1, N);
 dy = zeros(1, N);
+ddy = zeros(1, N);
+dddy = zeros(1, N);
 
 for i = 1:N
     y(i) = f(x(i));
     dy(i) = df(x(i));
+    ddy(i) = ddf(x(i));
+    dddy(i) = dddf(x(i));
 end
 
-subplot(2,1,1)
+subplot(4,1,1)
 plot(x, y)
 title('f(x)')
-subplot(2,1,2)
+
+subplot(4,1,2)
 plot(x, dy)
-title('Derivative of f(x)')
+title('1st order derivative of f(x)')
+
+subplot(4, 1, 3)
+plot(x, ddy);
+title('2nd order derivative of f(x)')
+
+subplot(4, 1, 4)
+plot(x, dddy);
+title('3rd order derivative of f(x)')

### 2018-07-19 VV570/LAB3/Task4b.m

@@ -6,8 +6,17 @@ df = @(x) exp(x)*((x-2).^3 + 3*(x-2).^2);
 a = 0;
 b = 3;
 x0 = (a+b)/2;
-eps_x = 1e-10;
-eps_y = 1e-10;
-max_iter = 51;
+max_iter = 50;
 
-[xval, x_err,iter_num yval] = newton(f, df, x0, eps_x, eps_y, max_iter)
+x(1) = x0;
+for i = 1:max_iter
+    x(i+1) = x(i) - f(x(i))/df(x(i));
+end
+
+n = length(x);
+m = zeros(1, n);
+for i = 2:n-1
+    m(i+1) = -(x(i)-x(i-1))/(x(i+1) - 2*x(i) + x(i-1));
+end
+
+table((1:n)', x', m', 'VariableNames', {'n', 'x', 'm'})

### 2018-07-19 VV570/LAB3/Task5a.m
task5 ok

@@ -1,0 +1,6 @@
+clear all; close all; clc;
+
+f = @(x) x.^2 - sin(x+1);
+df = @(x) 2*x - cos(x+1);
+
+[x_val, x_err, iter_num, y_val] = newton(f, df, 0.5, 1e-10, 1e-10, 50)

### 2018-07-19 VV570/LAB3/Task5b.m

@@ -1,0 +1,5 @@
+clear all; close all; clc;
+
+f = @(x) x.^2 - sin(x+1);
+
+[x_val, x_err, iter_num, y_val] = secant(f, 0.5, 0.75, 1e-10, 1e-10, 50)

### 2018-07-19 VV570/LAB3/Task5c.m

@@ -1,0 +1,5 @@
+clear all; close all; clc;
+
+f = @(x) x.^2 - sin(x+1);
+
+[b,fval,exitflag,output] = fzero(f, 0.5)

### 2018-07-19 VV570/LAB3/Task6.m
add task6 not solved

@@ -1,0 +1,12 @@
+clear all; close all; clc;
+
+syms x
+h = @(a) int(x/(exp(x)-1), x, [0, a]);
+f = @(a) 1-2/a*(1/a*eval(h(a)) + a/6 -1) - 0.7;
+
+a_val = linspace(40, 80, 11);
+for i = 1:length(a_val)
+    y_val(i) = f(a_val(i));
+end
+
+ plot(a_val, y_val)

### 2018-07-19 VV570/HW8/submission.tex
HW8 start

--- 2018-07-11 VV570/HW7/submission.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Introduction to Numerical Analysis \\ HW7 \\ % The assignment title
+\huge Introduction to Numerical Analysis \\ HW8 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 		\item
-			For example
+			It's convex as $f''(x) = e^x > 0$.
+		\item 
+			It's concave as
 			\begin{equation}
-				y = tan(x), \ \ x\in (-\frac{\pi}{2}, \frac{\pi}{2})
+				\begin{aligned}
+				  RHS-LHS & = t f(x) + (1-t)f(y) - f(tx+(1-t)y)\\
+						  & = [t x_1 x_2 + (1-t)y_1 y_2] -[t x_1 + (1-t)y_1][t x_2 + (1-t)y_2]\\
+						  & = -t(1-t)(x_1 y_2 + x_2 y_1) < 0
+				\end{aligned}
 			\end{equation}
-			It's differentiable over $(-\frac{\pi}{2}, \frac{\pi}{2})$, and the derivative is 
-			\begin{equation}
-				y' = \frac{1}{cos^2(x)}
-			\end{equation}
-			It's obvious that $y' \rightarrow \infty$ when $x \rightarrow \frac{\pi}{2}$.
-		\item 
-			\begin{proof}
-				Denote $g(x)$ over $[x_1, x_2]$ as
-				\begin{equation}
-					g(x) = f(x) - f(x_1) - \frac{f(x_2)-f(x_1)}{x_2-x_1}(x-x_1) 
-				\end{equation}
-				where $a< x_1 < x_2 < b$. Then, $g(x_1) = 0$ and $g(x_2)=0$.
-
-				Thus, from Rolle's theorem, there exists $\xi \in (x_1, x_2)$ s.t. 
-				\begin{equation}
-					g'(\xi)= 0
-				\end{equation}
-				namely
-				\begin{equation}
-					\frac{f(x_2) - f(x_1)}{x_2-x_1} = f'(\xi)
-				\end{equation}
-				Since $f'$ is bounded, then $|f'(\xi)| \leq M$. Thus
-				\begin{equation}
-					|f(x_2) - f(x_1)| \leq M |x_2 - x_1|
-				\end{equation}
-				which means that $f(x)$ is Lipschitz continous.
-			\end{proof}
-		\item 
-			For example
-			\begin{equation}
-				y = \frac{1}{x}, \ \ x \in (0, 1)
-			\end{equation}
-			$y$ is obviously differentiable and its derivative is
-			\begin{equation}
-				y' = -\frac{1}{x^2}, \ \ x \in (0, 1)
-			\end{equation}
-			Suppose there exist a constant $c>0$ s.t. 
-			\begin{equation}
-				|y_2 - y_1| \leq c|x_2 - x_1|
-			\end{equation}
-			is valid for all $0 < x_1 < x_2 < 1$.
-			Let $y(b) - y(a) = c(b-a)$, where $a < b$then
-			\begin{equation}
-				c = \frac{1}{ab}
-			\end{equation}
-			Take the mid-point of $a, b$, then
-			\begin{equation}
-				\frac{y(a)-y(\frac{b+a}{2})}{\frac{b+a}{2}-a} = \frac{1}{a(\frac{b+a}{2})} > \frac{1}{ab} = c
-			\end{equation}
-			Thus, the assumption fails, which means that $y$ is not Lipschitz continous.
-		\item 
-			For example
-			\begin{equation}
-				y = |x|, \ \ x \in (-1, 1)
-			\end{equation}
-			It's Lipschitz continous as for any $-1 < x_1 < x_2 < 1$
-			\begin{equation}
-				\frac{|y(x_2)-y(x_1)|}{|x_2 - x_1|} \leq 1
-			\end{equation}
-			but it is not differentiable at $x=0$.
 
@@
 \section{Question 2}
+	\begin{enumerate}
+		\item
 
+	\end{enumerate}
 %----------------------------------------------------------------------------------------
@@
 \section{Question 3}
+\begin{enumerate}
+	\item
+
+\end{enumerate}
+%----------------------------------------------------------------------------------------
+%	PROBLEM 6
+%----------------------------------------------------------------------------------------
+\section{Question 6}
+	\begin{enumerate}
+		\item
+
+	\end{enumerate}
 

### 2018-07-19 VV570/PROJ2/code/multi_var_fp.m
proj2 start

@@ -1,0 +1,10 @@
+function [x] = multi_var_fp(g, x0, tol, custom_norm)
+    
+    x = g(x0);
+    err = abs(x - x0);
+    while(err > tol)
+        cur = g(x);
+        err = custom_norm(cur-x);
+        x = cur;
+    end
+end

### 2018-07-19 VV570/PROJ2/code/multi_var_newton.m

@@ -1,0 +1,16 @@
+function [x] = multi_var_newton(F, dF, x0, tol, custom_norm)
+    x = x0;
+    fx = F(x);
+    dfx = dF(x);
+    delta_x = linsolve(dfx, -fx);
+    x = x + delta_x;
+    err = custom_norm(delta_x);
+    while(err > tol)
+        fx = F(x);
+        dfx = dF(x);
+        delta_x = linsolve(dfx, -fx);
+        x = x + delta_x;
+        err = custom_norm(delta_x);
+    end
+end
+

### 2018-07-28 VV570/HW9/submission.tex
hw9 start

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages
\usepackage{mathrsfs}
\usepackage{algorithm, algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}} %Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm  
\usepackage{listings}
\lstset{language=Matlab}
\usepackage{enumerate}
\usepackage{graphicx}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps
\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------
\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Introduction to Numerical Analysis \\ HW9 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yu Cang \\ 018370210001} % Your name

\date{\normalsize \today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title

\section{Question 1}
	\begin{enumerate}[(a)]
		\item
			It's convex as $f''(x) = e^x > 0$.
		\item 
			Let
			\begin{equation}
				RHS \triangleq t f(x) + (1-t)f(y)
			\end{equation}
			\begin{equation}
				LHS \triangleq - f(tx+(1-t)y)
			\end{equation}
			It's concave as
			\begin{equation}
				\begin{aligned}
				  & RHS-LHS\\
						   = &[t x_1 x_2 + (1-t)y_1 y_2] -[t x_1 + (1-t)y_1][t x_2 + (1-t)y_2]\\
						   = &-t(1-t)(x_1 y_2 + x_2 y_1) < 0
				\end{aligned}
			\end{equation}
		\item 
			Convex.

		\item 
			Convex.

		\item 
			Convex.

		\item 
			Concave.

	\end{enumerate}

\section{Question 2}
	\begin{enumerate}[(a)]
		\item 
			\begin{proof}
				Suppose $x = (x_1, x_2, ... , x_m)$, then it's left to prove that
				\begin{equation}
					\frac{\partial f}{\partial x_i} = 0
				\end{equation}
				for $i=1,2, ... , m$ at $x=x^*$.
			\end{proof}
			The partial derivative of $f$ at $x=x^*$ is defined as
			\begin{equation}
				\frac{\partial f}{\partial x_i}\Big|_{x=x^*} = 
				\lim\limits_{\Delta x_i \rightarrow 0}\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i}
			\end{equation}
			Since $f(x^*)$ is the local minimum, $f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) \geq f(x_1, x_2, ... ,x_i^*, ... , x_m)$ however $\Delta x_i$ changes.\\
			Thus
			\begin{equation}
				\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i} \leq 0
			\end{equation} 
			if $\Delta x_i < 0$.\\
			And
			\begin{equation}
				\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i} \geq 0
			\end{equation}  
			if $\Delta x_i > 0$.\\
			Hence, $\frac{\partial f}{\partial x_i}\Big|_{x=x^*} = 0$ as $f$ is continuously differentiable.
			Therefore, $\triangledown f(x^*) =0$.
		\item 
			\begin{proof}
				With taylor expansion of $f(x)$ at $x=x^*$
				\begin{equation}
					\begin{aligned}
						  &f(x) - f(x^*) \geq 0 \quad \quad (\text{$f(x^*)$ is the local minimum})\\
		  \Leftrightarrow &\triangledown f(x^*) \Delta x + \frac{1}{2} \Delta \xi H(x^*) \Delta \xi ^T \geq 0\\
		  \Leftrightarrow &\frac{1}{2} \Delta \xi H(x^*) \Delta \xi ^T \geq 0 \quad \quad (\text{gradient be 0})
					\end{aligned}
				\end{equation}
				where $d(\Delta \xi, x^*) \leq d(x, x^*)$, and the gradient is $0$ as been proved above.
				Thus, $ \Delta \xi H(x^*) \Delta \xi ^T \geq 0$ for any $\Delta \xi$ within the local neighbourhood of $x=x^*$.\\
				Hence $H(x^*)$ is semi-positive finite.

			\end{proof}
		\item 
			\begin{proof}
				($\Leftarrow$)The global minimum must be a local minimum, and the gradient is therefore 0 as $f$ is differentiable.

				($\Rightarrow$)As has been proved above, $\triangledown f(x^*)=0$ indicates that $f(x^*)$ is the local minimum. It's left to prove that local minimum is also global minimum for a convex function.
				Suppose there exist $x'$ s.t. 
				\begin{equation}
					f(x') < f(x^*)
				\end{equation}
				Then, by convexity
				\begin{equation}
					f(t x' + (1-t)x^*) \leq t f(x') + (1-t) f(x^*) < \leq t f(x^*) + (1-t) f(x^*) = f(x^*)
				\end{equation}
				When $t\rightarrow1$, the inequality above contradicts local optimality of $x^*$.\\
				Thus, the assumption fails, which indicates that $f(x^*)$ is the global minimum for $f$.

			\end{proof}
		\item
			\begin{proof}
				($\Rightarrow$)By Taylor expansion
				\begin{equation}
					f(x+ d) = f(x) + \triangledown f(x) d + \frac{1}{2} d^T H(x) d + O(||d||^2)
				\end{equation}
				If the Hessian matrix $H$ is semi-definite positive, then
				\begin{equation}
					d^T H(x) d \geq 0
				\end{equation}
				Thus
				\begin{equation}
					f(x+ d) \geq f(x) + \triangledown f(x) d
				\end{equation}
				which is the so called 1-st order condition, and it implies that the function $f$ is convex.

				($\Leftarrow$)By Taylor expansion
				\begin{equation}
					f(x+ t d) = f(x) + t \triangledown f(x) d + \frac{t^2}{2} d^T H(x) d + O(||d||^2)
				\end{equation}
				With the 1-st order condition
				\begin{equation}
					f(x+ t d) \geq f(x) + t \triangledown f(x) d
				\end{equation}
				Thus
				\begin{equation}
					\frac{t^2}{2} d^T H(x) d + O(t||d||^2) \geq 0
				\end{equation}
				Dividing it by $\frac{t^2}{2}$ and set $t \rightarrow 0$, it gives out that for any $d\in \mathbb{R}^n$, $d^T H(x) d \geq 0$.

			\end{proof}

	\end{enumerate}

\section{Question 4}
	The genetic algorithm is adopted as there exists intensive oscillation when $x$ approaches $0$, and optimization algorithms dependent on the gradient info are easy to fall into local minimum.\\
	The global minimum found is $x_0=0.217, f(x_0)=-0.0249$.

\section{Question 6}
	The plot of $g(y)$ is given as follows
	\begin{figure}[!htbp]
		\centering
		\includegraphics[width=15cm]{../pic/Task6.eps}
	\end{figure}

\section{Question 7}
	According to the geometric relations, the allowable length of the ladder is given as
	\begin{equation}
		L(\alpha) = \min\limits_{\beta} (\frac{1}{sin(\beta)} + \frac{1}{sin(\alpha + \beta)})
	\end{equation}
	By solving the minimisation problem, the plot of $L$ versus $\alpha$ is given as follows
	\begin{figure}[!htbp]
		\centering
		\includegraphics[width=15cm]{../pic/Task7.eps}	
	\end{figure}

\end{document}

### 2018-07-30 VV570/HW9/submission.tex
question 1 done

@@
 		\item
-			It's convex as $f''(x) = e^x > 0$.
+			\begin{proof}
+				As $\mathcal{A}$ is convex, the mean value theorem can be applied in terms of $y$ s.t.
+				\begin{equation}
+					\Phi(t, y_2) - \Phi(t, y_1) = (y_2 - y_1) \frac{\partial \Phi(t, y)}{\partial y}\Big|_{y=\xi} 
+				\end{equation}
+				where $\xi \in (y_1, y_2)$.\\
+				Since the there exists $c>0$ s.t. for all $(t, y)\in \mathcal{A}$
+				\begin{equation}
+					\Big| \frac{\partial \Phi(t, y)}{\partial y} \Big| \leq c
+				\end{equation}
+				Thus
+				\begin{equation}
+					\begin{aligned}
+						& |\Phi(t, y_2) - \Phi(t, y_1)|\\
+					  = & |y_2 - y_1| \Bigg| \frac{\partial \Phi(t, y)}{\partial y}\Big|_{y=\xi} \Bigg|\\
+				   \leq & c |y_2 - y_1|	
+					\end{aligned}
+				\end{equation}
+				which implies that $\Phi(t, y)$ satisfies Lipschitz condition in $y$ on $\mathcal{A}$.
+			\end{proof}
+
 		\item 
+			\begin{proof}
+				Let $P_1 = (t_1, y_1)$ and $P_2 = (t_2, y_2)$. Then any point $P'$ lies on the line segment joining $P_1$ and $P_2$ can be expressed as
+				\begin{equation}
+					\begin{aligned}
+						P & = (1-\alpha)P_1 + \alpha P_2\\
+						  & = ((1-\alpha)t_1 + \alpha t_2, (1-\alpha)y_1 + \alpha y_2)\\
+						  & \triangleq (t', y')
+					\end{aligned}
+				\end{equation} 
+				where $\alpha \in [0, 1]$.\\
+				It's clear that $t_1$ and $t_2$ lies between $t_0$ and $T$, and $t'$ lies between $t_1$ and $t_2$. Thus, $t'$ also lies between $t_0$ and $T$.\\
+				Further, it's also clear that $-\infty < y' < +\infty$.\\
+				Hence $P \in \mathcal{D}$, which implies that $\mathcal{D}$ is convex.
+			\end{proof}
+
+		\item
+			\begin{proof}
 				Let
 				\begin{equation}
-				RHS \triangleq t f(x) + (1-t)f(y)
+					\Phi(t, y) = \frac{4t^3y}{1+t^4}
 				\end{equation}
+				Then
 				\begin{equation}
-				LHS \triangleq - f(tx+(1-t)y)
+					\frac{\partial \Phi(t, y)}{\partial y} = \frac{4t^3}{1+t^4} =\frac{4 t}{t^2 + \frac{1}{t^2}} < \frac{4}{t^2 + \frac{1}{t^2}} < \frac{4}{2 \sqrt{t^2 \frac{1}{t^2}}} = 2
 				\end{equation}
-			It's concave as
-			\begin{equation}
-				\begin{aligned}
-				  & RHS-LHS\\
-						   = &[t x_1 x_2 + (1-t)y_1 y_2] -[t x_1 + (1-t)y_1][t x_2 + (1-t)y_2]\\
-						   = &-t(1-t)(x_1 y_2 + x_2 y_1) < 0
-				\end{aligned}
-			\end{equation}
-		\item 
-			Convex.
+				as $t\in (0,1)$.\\ 
+				which implies that $\Phi(t, y)$ satisfies a Lipschitz condition in $y$.\\
+				Thus, the given IVP problem has a unique solution.
+			\end{proof}
 
 		\item 
-			Convex.
-
-		\item 
-			Convex.
-
-		\item 
-			Concave.
-
+			Definitely not recommended.\\
+			As $\Phi(t, y) = 1 + y^2$, then
+			\begin{equation}
+				\frac{\partial \Phi}{\partial y} = 2 y \triangleq \lambda y
+			\end{equation}
+			Here $\lambda > 0$, and the Euler's method is not stable as the error will be amplified at each iteration step. Finally the calculation will diverge.
 	\end{enumerate}
@@
 		\item
-			\begin{proof}
-				Suppose $x = (x_1, x_2, ... , x_m)$, then it's left to prove that
-				\begin{equation}
-					\frac{\partial f}{\partial x_i} = 0
-				\end{equation}
-				for $i=1,2, ... , m$ at $x=x^*$.
-			\end{proof}
-			The partial derivative of $f$ at $x=x^*$ is defined as
-			\begin{equation}
-				\frac{\partial f}{\partial x_i}\Big|_{x=x^*} = 
-				\lim\limits_{\Delta x_i \rightarrow 0}\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i}
-			\end{equation}
-			Since $f(x^*)$ is the local minimum, $f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) \geq f(x_1, x_2, ... ,x_i^*, ... , x_m)$ however $\Delta x_i$ changes.\\
-			Thus
-			\begin{equation}
-				\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i} \leq 0
-			\end{equation} 
-			if $\Delta x_i < 0$.\\
-			And
-			\begin{equation}
-				\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i} \geq 0
-			\end{equation}  
-			if $\Delta x_i > 0$.\\
-			Hence, $\frac{\partial f}{\partial x_i}\Big|_{x=x^*} = 0$ as $f$ is continuously differentiable.
-			Therefore, $\triangledown f(x^*) =0$.
-		\item 
-			\begin{proof}
-				With taylor expansion of $f(x)$ at $x=x^*$
-				\begin{equation}
-					\begin{aligned}
-						  &f(x) - f(x^*) \geq 0 \quad \quad (\text{$f(x^*)$ is the local minimum})\\
-		  \Leftrightarrow &\triangledown f(x^*) \Delta x + \frac{1}{2} \Delta \xi H(x^*) \Delta \xi ^T \geq 0\\
-		  \Leftrightarrow &\frac{1}{2} \Delta \xi H(x^*) \Delta \xi ^T \geq 0 \quad \quad (\text{gradient be 0})
-					\end{aligned}
-				\end{equation}
-				where $d(\Delta \xi, x^*) \leq d(x, x^*)$, and the gradient is $0$ as been proved above.
-				Thus, $ \Delta \xi H(x^*) \Delta \xi ^T \geq 0$ for any $\Delta \xi$ within the local neighbourhood of $x=x^*$.\\
-				Hence $H(x^*)$ is semi-positive finite.
-
-			\end{proof}
-		\item 
-			\begin{proof}
-				($\Leftarrow$)The global minimum must be a local minimum, and the gradient is therefore 0 as $f$ is differentiable.
-
-				($\Rightarrow$)As has been proved above, $\triangledown f(x^*)=0$ indicates that $f(x^*)$ is the local minimum. It's left to prove that local minimum is also global minimum for a convex function.
-				Suppose there exist $x'$ s.t. 
-				\begin{equation}
-					f(x') < f(x^*)
-				\end{equation}
-				Then, by convexity
-				\begin{equation}
-					f(t x' + (1-t)x^*) \leq t f(x') + (1-t) f(x^*) < \leq t f(x^*) + (1-t) f(x^*) = f(x^*)
-				\end{equation}
-				When $t\rightarrow1$, the inequality above contradicts local optimality of $x^*$.\\
-				Thus, the assumption fails, which indicates that $f(x^*)$ is the global minimum for $f$.
-
-			\end{proof}
-		\item
-			\begin{proof}
-				($\Rightarrow$)By Taylor expansion
-				\begin{equation}
-					f(x+ d) = f(x) + \triangledown f(x) d + \frac{1}{2} d^T H(x) d + O(||d||^2)
-				\end{equation}
-				If the Hessian matrix $H$ is semi-definite positive, then
-				\begin{equation}
-					d^T H(x) d \geq 0
-				\end{equation}
-				Thus
-				\begin{equation}
-					f(x+ d) \geq f(x) + \triangledown f(x) d
-				\end{equation}
-				which is the so called 1-st order condition, and it implies that the function $f$ is convex.
-
-				($\Leftarrow$)By Taylor expansion
-				\begin{equation}
-					f(x+ t d) = f(x) + t \triangledown f(x) d + \frac{t^2}{2} d^T H(x) d + O(||d||^2)
-				\end{equation}
-				With the 1-st order condition
-				\begin{equation}
-					f(x+ t d) \geq f(x) + t \triangledown f(x) d
-				\end{equation}
-				Thus
-				\begin{equation}
-					\frac{t^2}{2} d^T H(x) d + O(t||d||^2) \geq 0
-				\end{equation}
-				Dividing it by $\frac{t^2}{2}$ and set $t \rightarrow 0$, it gives out that for any $d\in \mathbb{R}^n$, $d^T H(x) d \geq 0$.
-
-			\end{proof}
 
@@
 \section{Question 4}
-	The genetic algorithm is adopted as there exists intensive oscillation when $x$ approaches $0$, and optimization algorithms dependent on the gradient info are easy to fall into local minimum.\\
-	The global minimum found is $x_0=0.217, f(x_0)=-0.0249$.
 
 \section{Question 6}
-	The plot of $g(y)$ is given as follows
-	\begin{figure}[!htbp]
-		\centering
-		\includegraphics[width=15cm]{../pic/Task6.eps}
-	\end{figure}
-
-\section{Question 7}
-	According to the geometric relations, the allowable length of the ladder is given as
-	\begin{equation}
-		L(\alpha) = \min\limits_{\beta} (\frac{1}{sin(\beta)} + \frac{1}{sin(\alpha + \beta)})
-	\end{equation}
-	By solving the minimisation problem, the plot of $L$ versus $\alpha$ is given as follows
-	\begin{figure}[!htbp]
-		\centering
-		\includegraphics[width=15cm]{../pic/Task7.eps}	
-	\end{figure}
 

### 2018-07-30 VV570/PROJ2/code/task2.m
task2 begin

@@ -1,0 +1,6 @@
+f = @(x) [3*x(1) - cos(x(2)*x(3))-0.5; 
+          x(1)^2 - 625*x(2)^2 - 0.25;
+          exp(-x(1)*x(2))+20*x(3) - (3-10*pi)/3];
+Jf = @(x) [3, x(3)*sin(x(2)*x(3)), x(2)*sin(x(2)*x(3));
+           2*x(1), -1250*x(2), 0;
+           -x(2)*exp(-x(1)*x(2)), -x(1)*exp(-x(1)*x(2)), 20];

### 2018-07-30 VV570/HW9/code/Q3_a.m
start

@@ -1,0 +1,3 @@
+phi = @(t, y) (2+0.01*t^2)*y;
+
+t_val = linspace(0, 15);

### 2018-07-30 VV570/HW9/code/Q3_b.m
hw9 basically done

@@ -8,9 +8,18 @@ t_val = linspace(0, 15, N);
 y_val = zeros(size(t_val));
 y_val(1) = 4;
 
-%Iteration using Euler's method.
+% Generate the initial value using Euler's method.
 for i = 2:N
     y_val(i) = y_val(i-1) + h * phi(t_val(i-1), y_val(i-1));
+end
+
+%Iterate using back-ward Euler's method.
+for k = 1:5
+    for i = N:2
+        y_val(i) = y_val(i-1) + h * phi(t_val(i), y_val(i));
+    end
+    disp(k);
+    disp(y_val);
 end
 plot(t_val, log(y_val),'^-')
 xlabel('t')

### 2018-07-30 VV570/HW9/code/Q3_c.m

@@ -1,0 +1,21 @@
+clear all; close all; clc;
+
+phi = @(t, y) (2+0.01*t^2)*y;
+phi_t = @(t, y) 0.02*t*y;
+phi_y = @(t, y) 2+0.01*t^2;
+dphi = @(t, y) phi_t(t, y) + phi_y(t, y) * phi(t, y);
+
+N = 16;
+h = 1;
+t_val = linspace(0, 15, N);
+y_val = zeros(size(t_val));
+y_val(1) = 4;
+
+%Iteration with the 2nd-order Taylor.
+for i = 2:N
+    y_val(i) = y_val(i-1) + h * phi(t_val(i-1), y_val(i-1)) + h^2/2 * dphi(t_val(i-1), y_val(i-1));
+end
+disp(y_val);
+plot(t_val, log(y_val),'^-')
+xlabel('t')
+ylabel('log(y)')

### 2018-07-30 VV570/HW9/code/Q3_d.m

@@ -8,10 +8,13 @@ t_val = linspace(0, 15, N);
 y_val = zeros(size(t_val));
 y_val(1) = 4;
 
-%Iteration using Euler's method.
+% Iteration with Heun's method.
 for i = 2:N
-    y_val(i) = y_val(i-1) + h * phi(t_val(i-1), y_val(i-1));
+    k1 = phi(t_val(i-1), y_val(i-1));
+    ystar = y_val(i-1) + h * k1;
+    y_val(i) = y_val(i-1) + h/2 * (k1 + phi(t_val(i), ystar)); 
 end
+disp(y_val);
 plot(t_val, log(y_val),'^-')
 xlabel('t')
 ylabel('log(y)')

### 2018-07-30 VV570/HW9/code/Q3_e.m

@@ -1,0 +1,23 @@
+clear all; close all; clc;
+
+phi = @(t, y) (2+0.01*t^2)*y;
+
+N = 16;
+h = 1;
+t_val = linspace(0, 15, N);
+y_val = zeros(size(t_val));
+
+% Initialization
+y_val(1) = 4;
+y_val(2) = y_val(1) + h * phi(t_val(1), y_val(1));
+
+% Iteration with the 2-step Adams-Bashforth method
+for i = 3:N
+    k1 = phi(t_val(i-1), y_val(i-1));
+    k2 = phi(t_val(i-2), y_val(i-2));
+    y_val(i) = y_val(i-1) + h/2 * (3*k1 - k2); 
+end
+disp(y_val);
+plot(t_val, log(y_val),'^-')
+xlabel('t')
+ylabel('log(y)')

### 2018-07-30 VV570/LAB4/Task1_a.m
lab4 start

@@ -1,0 +1,10 @@
+clear all; close all; clc;
+
+eqn = 'Dy = (y+t)/(y-t)';
+init = 'y(0) = 1';
+y = dsolve(eqn, init, 't');
+pretty(y)
+t = linspace(0, 1, 20);
+expr = vectorize(y);
+z = eval(expr);
+plot(t, z)

### 2018-07-30 VV570/LAB4/ab2.m

@@ -1,0 +1,34 @@
+function [ x, y ] = ab2 ( f, xRange, yInitial, numSteps )
+% [ x, y ] = ab2 ( f, xRange, yInitial, numSteps ) uses
+% Adams-Bashforth second-order method to solve a system
+% of first-order ODEs y?=f(x,y).
+% f = name of an m-file with signature
+% yprime = f(x,y)
+% to compute the right side of the ODE as a row vector
+%
+% xRange = [x1,x2] where the solution is sought on x1<=x<=x2
+% yInitial = column vector of initial values for y at x1
+% numSteps = number of equally-sized steps to take from x1 to x2
+% x = column vector of values of x
+% y = matrix whose k-th row is the approximate solution at x(k).
+x=zeros(numSteps+1,1);
+x(1) = xRange(1);
+h = ( xRange(2) - xRange(1) ) / numSteps;
+y(1,:) = transpose(yInitial);
+yprime(1,:) = transpose(feval ( f, x(1), y(1,:) ));
+k = 1;
+xhalf = x(k) + 0.5 * h;
+yhalf = y(k,:) + 0.5 * h * yprime(k,:);
+yprime1 = transpose(feval ( f, xhalf, yhalf ));
+x(k+1) = x(k) + h;
+y(k+1,:) = y(k,:) + h * yprime1;
+yprime(k+1,:) = transpose(feval ( f, x(k+1), y(k+1,:) ));
+for k = 2 : numSteps
+x(k+1) = x(k) + h;
+y(k+1,:) = y(k,:) + ...
+h * ( 3.0 * yprime(k,:) - yprime(k-1,:) ) / 2.0;
+if k<numSteps
+yprime(k+1,:) = transpose(feval ( f, x(k+1), y(k+1,:) ));
+end
+end
+

### 2018-07-30 VV570/LAB4/butcher.m

@@ -1,0 +1,10 @@
+function ydot = butcher( t, y )
+% ydot = butcher( t, y ) is the right side function for
+% the ODE y'= (y+t)/(y-t) 
+% t is the independent variable
+% y is the dependent variable
+% ydot is y?
+
+ydot = (y+t)/(y-t) ;
+
+end

### 2018-07-30 VV570/LAB4/stiff2ode.m

@@ -1,0 +1,12 @@
+function f = stiff2ode ( x, y )
+% f = stiff2_ode ( x, y )
+% computes the right side of the ODE
+% dy/dx=f(x,y)=lambda*(-y+sin(x)) for lambda = 2
+% x is independent variable
+% y is dependent variable
+% output, f is the value of f(x,y).
+LAMBDA=2;
+f = LAMBDA * ( -y + sin(x) );
+
+end
+

### 2018-07-30 VV570/LAB4/stiff2solution.m

@@ -1,0 +1,11 @@
+function y = stiff2solution ( x )
+% y = stiff2_solution ( x )
+% computes the solution of the ODE
+% dy/dx=f(x,y)=lambda*(-y+sin(x)) for lambda = 2
+% and initial condition y=0 at x=0
+% x is the independent variable
+% y is the solution value
+LAMBDA=2;
+y = (LAMBDA^2/(1+LAMBDA^2))*sin(x) + ...
+(LAMBDA /(1+LAMBDA^2))*(exp(-LAMBDA*x)-cos(x));
+end

### 2018-08-01 VV570/PROJ2/code/multi_var_broyden.m
task1 done

@@ -1,22 +1,20 @@
-function [x] = multi_var_broyden(f, x0, A0, x_tol, y_tol, custom_norm)
-    x = x0;
-    fx = f(x);
-    y_err = custom_norm(fx);
-    if(y_err <= y_tol)
-        return;
-    end
-    
-    A_inv = inv(A0);
-    x_err = 0;
-    while(x_err > x_tol || y_err > y_tol)
-        w = A_inv * fx;
-        x_err = custom_norm(w);
-        x = x-w;
-        s = -w;
-        cfx = f(x);
-        y = cfx-fx;
-        y_err = custom_norm(y);
+function [x] = multi_var_broyden(f, x0, A_inv, tol, custom_norm)
+    % 先用牛顿法算出x1
+    x_pre = x0;
+    fx_pre = f(x_pre);
+    w = A_inv*(-fx_pre);
+    err = custom_norm(w);
+    x = x_pre + w;
+    % 迭代
+    while(err > tol)
+        s = x - x_pre;
+        fx_cur = f(x);
+        y = fx_cur - fx_pre;
         A_inv = A_inv + (s-A_inv*y)*s'*A_inv/(s'*A_inv*y);
-        fx = cfx;
+        w = A_inv*fx_cur;
+        err = custom_norm(w);
+        x_pre = x;
+        x = x-w;
+        fx_pre = fx_cur;
     end
 end

### 2018-08-01 VV570/PROJ2/code/multi_var_fp.m

@@ -1,15 +1,9 @@
-function [x] = multi_var_fp(g, x0, x_tol, y_tol, custom_norm)
+function [x] = multi_var_fp(g, x0, tol, custom_norm)
     x = x0;
-    y_err = g(x0);
-    if(y_err <= y_tol)
-        return;
-    end
-    x_err = 0;
-    
-    while(x_err > x_tol || y_err > y_tol)
+    err = tol+1;
+    while(err > tol)
         cx = g(x);
-        y_err = custom_norm(cx);
-        x_err = custom_norm(cx-x);
+        err = custom_norm(cx-x);
         x = cx;
     end
 end

### 2018-08-01 VV570/PROJ2/code/multi_var_newton.m

@@ -1,16 +1,10 @@
-function [x] = multi_var_newton(f, Jf, x0, x_tol, y_tol, custom_norm)
+function [x] = multi_var_newton(f, Jf, x0, tol, custom_norm)
     x = x0;
-    y_err = custom_norm(f(x));
-    if(y_err <= y_tol)
-        return;
-    end
-
-    x_err = 0;
-    while(x_err > x_tol || y_err > y_tol)
+    err = tol + 1;
+    while(err > tol)
         dx = linsolve(Jf(x), -f(x));
-        x_err = custom_norm(dx);
+        err = custom_norm(dx);
         x = x + dx;
-        y_err = custom_norm(f(x));
     end
 end
 

### 2018-08-01 VV570/PROJ2/code/task1_benchmark.m

@@ -1,21 +1,27 @@
 clear all; close all; clc;
 
-f = @(x) [x(1)^2 - x(2); x(1)^2 + x(2)^2 -1];
+f = @(x) [(x(1,1).^2 - x(2,1)); (x(1,1).^2 + x(2,1).^2 -1)];
 Jf = @(x) [2*x(1), -1; 2*x(1), 2*x(2)];
-norm_func = @(x) norm(x, 2);
-
-x0 = [sqrt(2)/2; sqrt(2)/2];
-x_tol = 1e-7;
-y_tol = 1e-7;
 
 tic
-    x_fp = multi_var_fp(f, x0, x_tol, y_tol, norm_func);
+    g = @(x) [sqrt(x(2)); sqrt(1-x(1)^2)];
+    x0 = [sqrt(2)/2; sqrt(2)/2];
+    tol = 1e-10;
+    f_nm = @(x) norm(x, 2);
+    x_fp = multi_var_fp(g, x0, tol, f_nm);
 toc
 
 tic
-    x_nt = multi_var_newton(f, Jf, x0, x_tol, y_tol, norm_func);
+    x0 = [sqrt(2)/2; sqrt(2)/2];
+    tol = 1e-10;
+    f_nm = @(x) norm(x, 2);
+    x_nt = multi_var_newton(f, Jf, x0, tol, f_nm);
 toc
 
 tic
-    x_bd = multi_var_broyden(f, x0, x_tol, y_tol, norm_func);
+    x0 = [sqrt(2)/2; sqrt(2)/2];
+    A0_inv = Jf(x0)^-1;
+    tol = 1e-10;
+    f_nm = @(x) norm(x, 2);
+    x_bd = multi_var_broyden(f, x0, A0_inv, tol, f_nm);
 toc

### 2018-08-01 VV570/PROJ2/tex/report.tex
task2 done!

--- 2018-07-30 VV570/HW9/submission.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Introduction to Numerical Analysis \\ HW9 \\ % The assignment title
+\huge Introduction to Numerical Analysis \\ Project2 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\section{Question 1}
+\section{Task 1}
+	Note the symmetry of $x_1$, for any solution $(a, b)$, $(-a, b)$ is also valid.\\
+	If no special claim, the norm function for a vector is taken as the 2-norm.
 	\begin{enumerate}[(a)]
 		\item
-			\begin{proof}
-				As $\mathcal{A}$ is convex, the mean value theorem can be applied in terms of $y$ s.t.
+			For fixed-point iteration, the iteration function $G$ is taken as
 			\begin{equation}
-					\Phi(t, y_2) - \Phi(t, y_1) = (y_2 - y_1) \frac{\partial \Phi(t, y)}{\partial y}\Big|_{y=\xi} 
+				G \triangleq
+				\begin{bmatrix}
+					\sqrt{x_2}\\
+					\sqrt{1-x_1^2}
+				\end{bmatrix}
+				=
+				\begin{bmatrix}
+					x_1\\
+					x_2\\
+				\end{bmatrix}
+				=x
 			\end{equation}
-				where $\xi \in (y_1, y_2)$.\\
-				Since the there exists $c>0$ s.t. for all $(t, y)\in \mathcal{A}$
+			The iteration converges to $(0.7862, 0.6180)$ with intial guess $x_{init} = [\frac{1}{\sqrt{2}}, \frac{1}{\sqrt{2}}]^T$ and tolerance set to $10^{-10}$. 
+		\item 
+			The newton iteration is implemented as mentioned in the project sheet, each time the linear system
 			\begin{equation}
-					\Big| \frac{\partial \Phi(t, y)}{\partial y} \Big| \leq c
+				J_F(x_k) w_k = y_k
 			\end{equation}
-				Thus
+			is solved with the built-in function 'linsolve' inside matlab.\\
+			The iteration converges to $(0.7862, 0.6180)$ with intial guess $x_{init} = [\frac{1}{\sqrt{2}}, \frac{1}{\sqrt{2}}]^T$ and tolerance set to $10^{-10}$. 
+		\item
+			The input of the Broyden's method is a little bit different from that in newton or fixed-point. The initial Jacobi matrix should be provided, denoted as $A_0$. In my implementation, it is given as
 			\begin{equation}
-					\begin{aligned}
-						& |\Phi(t, y_2) - \Phi(t, y_1)|\\
-					  = & |y_2 - y_1| \Bigg| \frac{\partial \Phi(t, y)}{\partial y}\Big|_{y=\xi} \Bigg|\\
-				   \leq & c |y_2 - y_1|	
-					\end{aligned}
+				A_0 = J_F(x_0)
 			\end{equation}
-				which implies that $\Phi(t, y)$ satisfies Lipschitz condition in $y$ on $\mathcal{A}$.
-			\end{proof}
+			An extra calculation on $x_1$ should be done before the iteration loop as the iteration process requires both $x_0$ and $x_1$. It is approximated through newton's method in my implementation as
+			\begin{equation}
+				x_1 \approxeq x_0 - A_0^{-1}F(x_0)
+			\end{equation}
+			After all the preparation work, the iteration loop can be carried out as mentioned in the project sheet, and the key part is the application of Sherman-Morrison's formula to calculated the inverse of $A_k$ iteratively as
+			\begin{equation}
+				A_k^{-1} = A_{k-1}^{-1} + \frac{(s_k^T A_{k-1}^{-1} y_k)s_k^T A_{k-1}^{-1}}{s_k^T A_{k-1}^{-1} y_k}
+			\end{equation}
+			where $s_k = x_k - x_{k-1}$ and $y_k = F(x_k) - F(x_{k-1})$. And the iteration of $x_k$ is given as
+			\begin{equation}
+				x_{k+1} = x_k - A_k^{-1}F(x_k)
+			\end{equation}
+			The iteration converges to $(0.7862, 0.6180)$ with intial guess $x_{init} = [\frac{1}{\sqrt{2}}, \frac{1}{\sqrt{2}}]^T$ and tolerance set to $10^{-10}$. 
+		\item 
+			With numerical tests, newton's method out-performs the other two in terms of time cost.
+
+	\end{enumerate}
+
+\section{Task 2}
+	With trival inequality analysis, the exact solution is given as $x=[0.5, 0, -\frac{\pi}{6}]$, which can be used for varification.\\
+	In general, the initial value for such a non-linear system is hard to know, even the range for each component is hard to estimate.
+In this case, the downhill simplex method can be applied to produce a fine inital guess for further calculation like newton or quasi-newton.\\
+	Numerical experiments were done to identify the difference in terms of time cost.
+
+	\begin{center}
+		\begin{tabular}{ccc}
+			\hline
+			\quad       & Without initialization & With initialization\\
+			\hline
+			fixed-point & $4.033 ms$             & $3.970 ms$\\
+			neweon      & $4.661 ms$             & $0.679 ms$\\
+			broyden     & $4.447 ms$             & $0.799 ms$\\
+			\hline
+		\end{tabular}
+	\end{center}
+
+	It can be observed from the table that the downhill simplex initialization process does help a lot to reduce time cost for further newton or broyden calculation as it provide a better initial guess.
+\\
+	However, the time cost is almost equivalent for the fixed-point iteration, which indicates that it does not benefit from the downhill simplex initialization.
+
+\section{Task 3}
+	\begin{enumerate}[(a)]
+		\item
 
 		\item
-			\begin{proof}
-				Let $P_1 = (t_1, y_1)$ and $P_2 = (t_2, y_2)$. Then any point $P'$ lies on the line segment joining $P_1$ and $P_2$ can be expressed as
-				\begin{equation}
-					\begin{aligned}
-						P & = (1-\alpha)P_1 + \alpha P_2\\
-						  & = ((1-\alpha)t_1 + \alpha t_2, (1-\alpha)y_1 + \alpha y_2)\\
-						  & \triangleq (t', y')
-					\end{aligned}
-				\end{equation} 
-				where $\alpha \in [0, 1]$.\\
-				It's clear that $t_1$ and $t_2$ lies between $t_0$ and $T$, and $t'$ lies between $t_1$ and $t_2$. Thus, $t'$ also lies between $t_0$ and $T$.\\
-				Further, it's also clear that $-\infty < y' < +\infty$.\\
-				Hence $P \in \mathcal{D}$, which implies that $\mathcal{D}$ is convex.
-			\end{proof}
 
 		\item
-			\begin{proof}
-				Let
-				\begin{equation}
-					\Phi(t, y) = \frac{4t^3y}{1+t^4}
-				\end{equation}
-				Then
-				\begin{equation}
-					\frac{\partial \Phi(t, y)}{\partial y} = \frac{4t^3}{1+t^4} =\frac{4 t}{t^2 + \frac{1}{t^2}} < \frac{4}{t^2 + \frac{1}{t^2}} < \frac{4}{2 \sqrt{t^2 \frac{1}{t^2}}} = 2
-				\end{equation}
-				as $t\in (0,1)$.\\ 
-				which implies that $\Phi(t, y)$ satisfies a Lipschitz condition in $y$.\\
-				Thus, the given IVP problem has a unique solution.
-			\end{proof}
 
 		\item
-			Definitely not recommended.\\
-			As $\Phi(t, y) = 1 + y^2$, then
-			\begin{equation}
-				\frac{\partial \Phi}{\partial y} = 2 y \triangleq \lambda y
-			\end{equation}
-			Here $\lambda > 0$, and the Euler's method is not stable as the error will be amplified at each iteration step. Finally the calculation will diverge.
-	\end{enumerate}
 
-\section{Question 2}
-	\begin{enumerate}[(a)]
 		\item
@@
 
-\section{Question 4}
-
-\section{Question 6}
-
 \end{document}

### 2018-08-01 VV570/PROJ2/code/downhill_simplex.m

@@ -1,0 +1,82 @@
+function [x_opt] = downhill_simplex(f, x0, lambda, tol, custom_norm)
+    % Initialization
+    N = length(x0);
+    for i = 1:N+1
+        s(i).x = x0;
+    end
+    for i = 1:N
+        s(i+1).x(i) = s(i+1).x(i) + lambda;
+    end
+    for i = 1:N+1
+        s(i).y = f(s(i).x);
+    end
+    [~, idx] = sort([s.y]);
+    s = s(idx);
+    
+    err = tol +1;
+    % Iteration
+    while (err > tol)
+        x_avg = zeros(1, N);
+        for i = 1:N
+            x_avg = x_avg + s(i).x;
+        end
+        x_mir = 2*x_avg - s(N+1).x;
+        y_mir = f(x_mir);
+        
+        best = s(1).y;
+        last_but_one = s(N).y;
+        worst = s(N+1).y;
+        flag = 0;
+        if((y_mir >= best) && (y_mir < last_but_one)) %介于最好与次差之间
+            s(N+1).x = x_mir;
+            s(N+1).y = y_mir;
+            disp('a');
+        elseif(y_mir < best) %优于最好
+            x_guess = 3*x_avg - 2 * s(N+1).x;
+            y_guess = f(x_guess);
+            if(y_guess < y_mir)
+                s(N+1).x = x_guess;
+                s(N+1).y = y_guess;
+                disp('b');
+            else
+                s(N+1).x = x_mir;
+                s(N+1).y = y_mir;
+                disp('c');
+            end
+        elseif((y_mir <= worst) && (y_mir >= last_but_one)) %介于最差与次差之间
+            x_guess = 1.5*x_avg-0.5*s(N+1).x;
+            y_guess = f(x_guess);
+            if(y_guess < y_mir)
+                s(N+1).x = x_guess;
+                s(N+1).y = y_guess;
+                disp('d');
+            else
+                flag = 1;
+                disp('e');
+            end
+        else % 比最差点还差
+            x_guess = 0.5*x_avg + 0.5*s(N+1).x;
+            y_guess = f(x_guess);
+            if(y_guess < y_mir)
+                s(N+1).x = x_guess;
+                s(N+1).y = y_guess;
+                disp('f');
+            else
+                flag = 1;
+                disp('g');
+            end
+        end
+        if(flag) %全体向当前最优点收缩
+            for i = 2:N+1
[…]

### 2018-08-01 VV570/PROJ2/code/task2.m

@@ -1,6 +1,75 @@
+clear all; close all; clc;
+
 f = @(x) [3*x(1) - cos(x(2)*x(3))-0.5; 
           x(1)^2 - 625*x(2)^2 - 0.25;
           exp(-x(1)*x(2))+20*x(3) - (3-10*pi)/3];
 Jf = @(x) [3, x(3)*sin(x(2)*x(3)), x(2)*sin(x(2)*x(3));
            2*x(1), -1250*x(2), 0;
            -x(2)*exp(-x(1)*x(2)), -x(1)*exp(-x(1)*x(2)), 20];
+
+g = @(x) [(1/2+cos(x(2)*x(3)))/3; sqrt(1/4-x(1)^2)/25; ((3-10*pi)/3-exp(-x(1)*x(2)))/20];
+
+x_exact = [0.5, 0, -pi/6];
+
+%--------------------------------------------------------------------------
+disp('Without downhill simplex initialization');
+%--------------------------------------------------------------------------
+disp('fixed-point');
+tic
+    x_init = [0.1; 0.1; 0.1];
+    tol = 1e-10;
+    f_norm = @(x) norm(x, 2);
+    x_fp = multi_var_fp(g, x_init, tol, f_norm);
+toc
+
+disp('newton');
+tic
+    x_init = [0.1; 0.1; 0.1];
+    tol = 1e-10;
+    f_norm = @(x) norm(x, 2);
+    x_nt = multi_var_newton(f, Jf, x_init, tol, f_norm);
+toc
+
+disp('broyden');
+tic
+    x_init = [0.1; 0.1; 0.1];
+    tol = 1e-10;
+    A0_inv = inv(Jf(x_init));
+    f_norm = @(x) norm(x, 2);
+    x_bd = multi_var_broyden(f, x_init, A0_inv, tol, f_norm);
+toc
+
+%--------------------------------------------------------------------------
+disp('With downhill simplex initialization');
+%--------------------------------------------------------------------------
+x0 = [0.1; 0.1; 0.1];
+lambda = 1;
+tol = 1e-7;
+f_eval = @(x) norm(f(x),2);
+f_norm =  @(x) norm(x, 2);
+x_init = downhill_simplex(f_eval, x0, lambda, tol, f_norm);
+
+
+disp('fixed-point');
+tic
+    tol = 1e-10;
+    f_norm = @(x) norm(x, 2);
+    x_fp = multi_var_fp(g, x_init, tol, f_norm);
+toc
+
[…]

### 2018-08-01 VV570/PROJ2/tex/report.tex
task3 partly ok

@@
 \section{Task 2}
-	With trival inequality analysis, the exact solution is given as $x=[0.5, 0, -\frac{\pi}{6}]$, which can be used for varification.\\
+	With trival inequality analysis, the exact solution is given as $x=[0.5, 0, -\frac{\pi}{6}]$, which can be used for varification.
+	\subsection{Solve directly}
+		Applying the fixed-point iteration, newton's method and the broyden's method to this non-linear system respectively, ...(TODO)
+	\subsection{Downhill simplex algorithm}
 	In general, the initial value for such a non-linear system is hard to know, even the range for each component is hard to estimate.
-In this case, the downhill simplex method can be applied to produce a fine inital guess for further calculation like newton or quasi-newton.\\
+In this case, the downhill simplex method can be applied to produce a fine inital guess for further calculation like newton or quasi-newton.
+	\subsection{Solve with initialization}
+
 	Numerical experiments were done to identify the difference in terms of time cost.

### 2018-08-01 VV570/PROJ2/code/task1.m

@@ -6,6 +6,7 @@ Jf = @(x) [2*x(1), -1; 2*x(1), 2*x(2)];
 tic
     g = @(x) [sqrt(x(2)); sqrt(1-x(1)^2)];
     x0 = [sqrt(2)/2; sqrt(2)/2];
+    %x0 = [0.5; 0.5];
     tol = 1e-10;
     f_nm = @(x) norm(x, 2);
     x_fp = multi_var_fp(g, x0, tol, f_nm);

### 2018-08-01 VV570/PROJ2/code/task3.m

@@ -1,0 +1,74 @@
+clear all; close all; clc;
+
+alpha = 0.1;
+gamma = 0.2;
+phi = @(t, x) [gamma-alpha*x(1)^2*x(2); alpha*x(1)^2*x(2)-x(2)/(1+x(2))];
+x0 = [1;1];
+
+%--------------------------------------------------------------------------
+disp('Part (a)');
+%Calculate x(t) and n(t) using RK-4
+%--------------------------------------------------------------------------
+N = 501;
+a = 0;
+b = 200;
+dt = (b-a)/(N-1);
+sol = ode45(phi, [a,b], x0);
+t = linspace(a,b,N);
+y = deval(sol, t);
+n = y(1,:);
+x = y(2,:);
+
+figure(1)
+plot(t, n)
+xlabel('t');
+ylabel('n(t)');
+
+figure(2)
+plot(t, x)
+xlabel('t');
+ylabel('x(t)');
+
+%--------------------------------------------------------------------------
+disp('Part (b)');
+% Approximate alpha and gamma at each point using central difference
+%--------------------------------------------------------------------------
+alpha_sol = zeros(1, N);
+gamma_sol = zeros(1, N);
+
+for i = 2:N-1
+    np = 0.5*(n(i+1)-n(i-1))/dt;
+    xp = 0.5*(x(i+1)-x(i-1))/dt;
+    alpha_sol(i) = (xp+x(i)/(1+x(i)))/(n(i)^2*x(i));
+    gamma_sol(i) = np+alpha_sol(i)*n(i)^2*x(i);
+end
+
+alpha_est = mean(alpha_sol(2:N-1));
+gamma_est = mean(gamma_sol(2:N-1));
+fprintf('estimated alpha: %f\n', alpha_est);
+fprintf('estimated gamma: %f\n', gamma_est);
+
+%--------------------------------------------------------------------------
+disp('Part (c)');
+%--------------------------------------------------------------------------
+eta = normrnd(0, sqrt(0.1), 1, N);
+mu = normrnd(0, sqrt(0.001), 1, N);
+ns = n + eta;
+xs = x + mu;
+
+figure(3)
+plot(t, ns)
+xlabel('t');
+ylabel('n^*(t)');
+
+figure(4)
+plot(t, xs)
+xlabel('t');
+ylabel('x^*(t)');
+
+%--------------------------------------------------------------------------
+disp('Part (d)');
+%--------------------------------------------------------------------------
+
+
+

### 2018-08-02 VV570/PROJ2/code/gauss_filter_1d.m
add some stuff...

@@ -1,0 +1,11 @@
+function y_filtered = gauss_filter_1d(y, sigma, r)
+    gauss_template =ones(1,2*r-1);
+    for i =1:length(gauss_template)
+        gauss_template(i) = exp(-(i-r)^2/(2*sigma^2))/(sigma*sqrt(2*pi));
+    end
+    
+    y_filtered = y;
+    for i = r : length(y)-r
+        y_filtered(i) = y(i-r+1 : i+r-1)*gauss_template';
+    end
+end

### 2018-08-02 VV570/PROJ2/code/task3.m

@@ -19,16 +19,6 @@ y = deval(sol, t);
 n = y(1,:);
 x = y(2,:);
 
-figure(1)
-plot(t, n)
-xlabel('t');
-ylabel('n(t)');
-
-figure(2)
-plot(t, x)
-xlabel('t');
-ylabel('x(t)');
-
 %--------------------------------------------------------------------------
 disp('Part (b)');
 % Approximate alpha and gamma at each point using central difference
@@ -51,24 +41,58 @@ fprintf('estimated gamma: %f\n', gamma_est);
 %--------------------------------------------------------------------------
 disp('Part (c)');
 %--------------------------------------------------------------------------
-eta = normrnd(0, sqrt(0.1), 1, N);
-mu = normrnd(0, sqrt(0.001), 1, N);
+sigma1 = sqrt(0.1);
+sigma2 = sqrt(0.001);
+eta = normrnd(0, sigma1, 1, N);
+mu = normrnd(0, sigma2, 1, N);
 ns = n + eta;
 xs = x + mu;
-
-figure(3)
-plot(t, ns)
-xlabel('t');
-ylabel('n^*(t)');
-
-figure(4)
-plot(t, xs)
-xlabel('t');
-ylabel('x^*(t)');
 
 %--------------------------------------------------------------------------
 disp('Part (d)');
 %--------------------------------------------------------------------------
+r1 = 15;
+r2 = 15;
+nf = gauss_filter_1d(ns, sigma1, r1);
+xf = gauss_filter_1d(xs, sigma2, r2);
 
+%--------------------------------------------------------------------------
+disp('Part (e)');
+%--------------------------------------------------------------------------
 
+%--------------------------------------------------------------------------
+disp('Plotting...');
+%--------------------------------------------------------------------------
+figure(1)
+subplot(3,1,1)
+plot(t, n)
+xlabel('t');
+ylabel('n(t)');
+title('original n(t)')
+subplot(3,1,2)
+plot(t, ns)
+xlabel('t');
+ylabel('n^*(t)');
+title('n(t) with noise');
+subplot(3,1,3)
+plot(t, nf)
+xlabel('t');
+ylabel('n^*(t)');
+title('filtered n^*(t)');
 
+figure(2)
+subplot(3,1,1)
+plot(t, x)
+xlabel('t');
+ylabel('x(t)');
+title('original x(t)')
+subplot(3,1,2)
[…]

### 2018-08-02 VV570/PROJ2/code/test_gauss_filter.m

@@ -1,0 +1,15 @@
+clear all; close all; clc;
+
+% 测试数据
+x = 1:50;
+y = x + rand(1,50)*10;
+ 
+% 设置高斯模板大小和标准差
+r        = 3;
+sigma    = 1;
+y_filted = gauss_filter_1d(y, sigma, r);
+ 
+% 作图对比
+plot(x, y,'^-', x, y_filted,'o-');
+title('高斯滤波');
+legend('滤波前','滤波后','Location','northwest')

### 2018-08-02 VV570/PROJ2/code/gauss_filter_1d.m
task3 part(d) ok

@@ -1,11 +1,0 @@
-function y_filtered = gauss_filter_1d(y, sigma, r)
-    gauss_template =ones(1,2*r-1);
-    for i =1:length(gauss_template)
-        gauss_template(i) = exp(-(i-r)^2/(2*sigma^2))/(sigma*sqrt(2*pi));
-    end
-    
-    y_filtered = y;
-    for i = r : length(y)-r
-        y_filtered(i) = y(i-r+1 : i+r-1)*gauss_template';
-    end
-end

### 2018-08-02 VV570/PROJ2/code/task3.m

@@ -6,8 +6,7 @@ phi = @(t, x) [gamma-alpha*x(1)^2*x(2); alpha*x(1)^2*x(2)-x(2)/(1+x(2))];
 x0 = [1;1];
 
 %--------------------------------------------------------------------------
-disp('Part (a)');
-%Calculate x(t) and n(t) using RK-4
+disp('Part (a) -- x(t) and n(t) are calculated with ode45');
 %--------------------------------------------------------------------------
 N = 501;
 a = 0;
@@ -18,28 +17,20 @@ t = linspace(a,b,N);
 y = deval(sol, t);
 n = y(1,:);
 x = y(2,:);
-
 %--------------------------------------------------------------------------
-disp('Part (b)');
-% Approximate alpha and gamma at each point using central difference
+disp('Part (b) -- alpha and gamma are approximated at each point using central difference');
 %--------------------------------------------------------------------------
-alpha_sol = zeros(1, N);
-gamma_sol = zeros(1, N);
-
+alpha_sol1 = zeros(1, N);
+gamma_sol1 = zeros(1, N);
 for i = 2:N-1
-    np = 0.5*(n(i+1)-n(i-1))/dt;
-    xp = 0.5*(x(i+1)-x(i-1))/dt;
-    alpha_sol(i) = (xp+x(i)/(1+x(i)))/(n(i)^2*x(i));
-    gamma_sol(i) = np+alpha_sol(i)*n(i)^2*x(i);
+    [alpha_sol1(i), gamma_sol1(i)] = central_diff_param_solve(n, x, i ,dt);
 end
-
-alpha_est = mean(alpha_sol(2:N-1));
-gamma_est = mean(gamma_sol(2:N-1));
-fprintf('estimated alpha: %f\n', alpha_est);
-fprintf('estimated gamma: %f\n', gamma_est);
-
+alpha_est1 = mean(alpha_sol1(2:N-1));
+gamma_est1 = mean(gamma_sol1(2:N-1));
+fprintf('  estimated alpha: %f\n', alpha_est1);
+fprintf('  estimated gamma: %f\n', gamma_est1);
 %--------------------------------------------------------------------------
-disp('Part (c)');
+disp('Part (c) -- noise signals are generated using normrnd');
 %--------------------------------------------------------------------------
[…]

### 2018-08-02 VV570/PROJ2/code/test_gauss_filter.m

@@ -1,15 +1,0 @@
-clear all; close all; clc;
-
-% 测试数据
-x = 1:50;
-y = x + rand(1,50)*10;
- 
-% 设置高斯模板大小和标准差
-r        = 3;
-sigma    = 1;
-y_filted = gauss_filter_1d(y, sigma, r);
- 
-% 作图对比
-plot(x, y,'^-', x, y_filted,'o-');
-title('高斯滤波');
-legend('滤波前','滤波后','Location','northwest')

### 2018-08-02 VV570/PROJ2/code/task3.m
task3 ok

@@ -4,9 +4,8 @@ alpha = 0.1;
 gamma = 0.2;
 phi = @(t, x) [gamma-alpha*x(1)^2*x(2); alpha*x(1)^2*x(2)-x(2)/(1+x(2))];
 x0 = [1;1];
-
 %--------------------------------------------------------------------------
-disp('Part (a) -- x(t) and n(t) are calculated with ode45');
+disp('Part(a) -- x(t) and n(t) are calculated with ode45');
 %--------------------------------------------------------------------------
 N = 501;
 a = 0;
@@ -18,7 +17,7 @@ y = deval(sol, t);
 n = y(1,:);
 x = y(2,:);
 %--------------------------------------------------------------------------
-disp('Part (b) -- alpha and gamma are approximated at each point using central difference');
+disp('Part(b) -- alpha and gamma are approximated at each point using central difference');
 %--------------------------------------------------------------------------
 alpha_sol1 = zeros(1, N);
 gamma_sol1 = zeros(1, N);
@@ -30,7 +29,7 @@ gamma_est1 = mean(gamma_sol1(2:N-1));
 fprintf('  estimated alpha: %f\n', alpha_est1);
 fprintf('  estimated gamma: %f\n', gamma_est1);
 %--------------------------------------------------------------------------
-disp('Part (c) -- noise signals are generated using normrnd');
+disp('Part(c) -- noise signals are generated using normrnd');
 %--------------------------------------------------------------------------
 sigma1 = sqrt(0.1);
 sigma2 = sqrt(0.001);
@@ -38,8 +37,32 @@ eta = normrnd(0, sigma1, 1, N);
 mu = normrnd(0, sigma2, 1, N);
 ns = n + eta;
 xs = x + mu;
+
+figure(1)
+subplot(2,1,1)
+plot(t, n)
+xlabel('t');
+ylabel('n(t)');
+title('original n(t)')
+subplot(2,1,2)
+plot(t, ns)
+xlabel('t');
+ylabel('n^*(t)');
+title('n(t) with noise');
+
+figure(2)
+subplot(2,1,1)
+plot(t, x)
+xlabel('t');
+ylabel('x(t)');
+title('original x(t)')
+subplot(2,1,2)
+plot(t, xs)
+xlabel('t');
+ylabel('x^*(t)');
+title('x(t) with noise');
[…]

### 2018-08-02 VV570/PROJ2/tex/report.tex
add task3 report

@@
 		\item 
+			Denote $y_1(t) \triangleq n(t)$, $y_2(t) \triangleq x(t)$ and
+			\begin{equation}
+				\Phi \triangleq
+				\begin{bmatrix}
+					\dot{y_1}\\
+					 \dot{y_2}	
+				\end{bmatrix}
+				=
+				\begin{bmatrix}
+					\gamma - \alpha y_2^2 y_1\\
+					\alpha y_2^2 y_1 - \frac{y_1}{1+y_1}
+				\end{bmatrix}
+			\end{equation}
+			Then, the synthetic data for $n$ and $x$ can be calculated iteratively.
+To make it more accurate, the Runge-Kutta 4-stage method was adopted.
+The matlab built-in function 'ode45' was used in my implementation.
+\\
+			Plot of $n(t)$ and $x(t)$ were generated as follows
+			\begin{figure}[htbp]\centering
+				\begin{minipage}{7.5cm}
+					\centering
+					\includegraphics[height=7cm,width=7cm]{../pic/n_and_ns.eps}
+				\end{minipage}%
+				\begin{minipage}{7.5cm}
+					\centering
+					\includegraphics[height=7cm,width=7cm]{../pic/x_and_xs.eps}
+				\end{minipage}
+			\end{figure}
+
+			Plot of $n(t)$ and $x(t)$ with noise were also generated here to make a clear comparsion.
+		\item 
+			At each point (except the two boundary points), the 1st-order derivative of $n(t)$ and $x(t)$ can be approximated using central difference as
+			\begin{equation}
+				\dot{n_k} = \frac{n_{k+1}-n_{k-1}}{2 \Delta t} \label{si_eq1}
+			\end{equation}
+			\begin{equation}
+				\dot{x_k} = \frac{x_{k+1}-x_{k-1}}{2 \Delta t} \label{si_eq2}
+			\end{equation}
+			Thus a pair of $\alpha$ and $\gamma$ can be solved at each point as
+			\begin{equation}
+				\alpha_k = \frac{\dot{x_k} + \frac{x_k}{1+x_k}}{n_k^2x_k}
+			\end{equation}
+			\begin{equation}
+				\gamma_k = \dot{x_k} + \dot{n_k} + \frac{x_k}{1+x_k}
+			\end{equation}
+			for $k=2,3,...,N-1$.\\
+			Finally, the estimated $\alpha$ and $\gamma$ can be calculated as
+			\begin{equation}
+				\hat{\alpha} = \frac{\sum_{k=2}^{N-1}\alpha_k}{N-2}
+			\end{equation}
+			\begin{equation}
+				\hat{\gamma} = \frac{\sum_{k=2}^{N-1}\gamma_k}{N-2}
+			\end{equation}
+			Numerical experiment shows that $\hat{\alpha} = 0.099824$ and $\hat{\gamma} = 0.199699$, which implies that $\hat{\alpha}$ and $\hat{\gamma}$ agree well with $\alpha$ and $\gamma$.
+		\item 
+			The noise is generated with the built-in function 'normrnd' of matlab in my code, plots are given in part(a).
 
 		\item 
+			Considering the mathmatical expect of $Eq(\ref{si_eq1})$ and $Eq(\ref{si_eq2})$ as
+			\begin{equation}
+				\begin{aligned}
+					E(\dot{n}) & = \gamma - \alpha E(n^2 x)\\
+					E(\dot{x}) & = \alpha E(n^2 x) - E(\frac{x}{1+x})
+				\end{aligned}
+			\end{equation}
+			Then $\alpha$ and $\gamma$ can be resolved as
+			\begin{equation}
+				\begin{aligned}
+					\hat{\alpha} & = \frac{E(\dot{x}) + E(\frac{x}{1+x})}{E(n^2 x)}\\
+					\hat{\gamma} & = E(\dot{x}) + E(\dot{n}) + E(\frac{x}{1+x})
+				\end{aligned}
+			\end{equation}
+			But the signal we have is not clean, what we can obtain from the data are quantities with noise like $E(\dot{n^*})$, $E(\dot{x^*})$, $E({n^*}^2 x^*)$, and $E(\frac{x^*}{1+x^*})$.
+These clean quantities like $E(\dot{n})$, $E(\dot{x})$, $E(n^2 x)$, and $E(\frac{x}{1+x})$ should be approximated from these polluted quantities so that $\hat{\alpha}$ and $\hat{\gamma}$ can be resolved.\\
+			As $\epsilon \sim N(0, 0.01)$ and $\nu \sim N(0, 0.001)$, then $E(\epsilon) = 0$, $E(\nu) = 0$ and $E(\epsilon^2) = 0.01$, $E(\nu^2)=0.001$.
+			Since $n^* = n + \epsilon$ and $x^* = x + \nu$, then
+			\begin{equation}
+				\begin{aligned}
+					E(n^*) & = E(n) + E(\epsilon) = E(n)\\
+					E(x^*) & = E(x) + E(\nu) = E(x)
+				\end{aligned}
+			\end{equation}
+			As $\epsilon$ and $\nu$ are independent, thus
+			\begin{equation}
+				\begin{aligned}
+					E({n^*}^2 x^*) & = E(n^2 x + 2nx\epsilon + x\epsilon^2 + n^2\nu + 2n\epsilon\nu + \epsilon^2 \nu)\\
+					               & = E(n^2 x) + E(x)E(\epsilon^2)
+				\end{aligned}
+			\end{equation}
+			and
+			\begin{equation}
+				E(\frac{x^*}{1+x^*}) = E(\frac{x}{1+x^*}) \approxeq E(\frac{x}{1+x})
+			\end{equation}
+			For derivatives, similiar relation can be concluded as
+			\begin{equation}
+				\begin{aligned}
+					E(\dot{n_k^*}) & = \frac{E(n_{k+1}^*) - E(n_{k-1}^*)}{2 \Delta t} = \frac{E(n_{k+1}) - E(n_{k-1})}{2 \Delta t} = E(\dot{n_k})\\
+					E(\dot{x_k^*}) & = \frac{E(x_{k+1}^*) - E(x_{k-1}^*)}{2 \Delta t} = \frac{E(x_{k+1}) - E(x_{k-1})}{2 \Delta t} = E(\dot{x_k})
+				\end{aligned}
+			\end{equation}
+			Hence these clean quantities can be approximated as
+			\begin{equation}
+				\begin{aligned}
+					E(n) & = E(n^*)\\
+					E(x) & = E(x^*)\\
+					E(\dot{n}) & = E(\dot{n^*}) = \frac{\sum_{k=2}^{N-1}\dot{n_k^*}}{N-2}\\
+					E(\dot{x}) & = E(\dot{x^*}) = \frac{\sum_{k=2}^{N-1}\dot{x_k^*}}{N-2}\\
+					E(n^2 x) & = E({n^*}^2 x^*) - E(x)E(\epsilon^2)\\
+					E(\frac{x}{1+x}) & = E(\frac{x^*}{1+x^*})
+				\end{aligned}
+			\end{equation}
+			where the properties of the noise is utilized.\\
+			In this way, $\hat{\alpha}$ and $\hat{\gamma}$ were resolved in numerical experiment as
+			\begin{equation}
+				\begin{aligned}
+					\hat{\alpha} & = 0.102744\\
+					\hat{\gamma} & = 0.201082
+				\end{aligned}
+			\end{equation}
+			The result has been validated for about 20 times, although the noise is different at each time, as well as $\hat{\alpha}$ and $\hat{\gamma}$, but each time the result was quite stable.
+		\item 
+			If the properties of noise are not available, some approximations or assumptions can not be made finely.\\
+			At first, a distinct attempt is to treat $n^*$ and $x^*$ like what we have done in part(b).
+			\begin{equation}
+				\hat{\alpha} = \frac{\sum_{k=2}^{N-1}\alpha_k^*}{N-2}
+			\end{equation}
+			\begin{equation}
+				\hat{\gamma} = \frac{\sum_{k=2}^{N-1}\gamma_k^*}{N-2}
+			\end{equation}
+			In this way, the only difference is the input data sequence, as the input in part(b) is clean but here is polluted. \\
+			Numerical experiments were done for 200 times to illustrate the initial guess(Fig\ref{coarse_ag}) and the variance(Fig\ref{err_ag}) of $\hat{\alpha}$ and $\hat{\gamma}$.
+			\begin{figure}[!htbp]\centering
+				\includegraphics[height=10cm]{../pic/coarse_estimation.eps}
+				\caption{Coarse estimation} 
+				\label{coarse_ag}
+			\end{figure}
+			\begin{figure}[!htbp]\centering
+				\includegraphics[height=10cm]{../pic/coarse_estimation_err.eps}
+				\caption{Error of estimation}
+				\label{err_ag}
+			\end{figure}
 
-		\item
+			It can be seen from Fig\ref{err_ag} that the error of $\hat{\gamma}$ is about 3\% relative to $\bar{\gamma}$, which is quite nice.
+But the error of $\hat{\alpha}$ is about 200\% relative to $\bar{\alpha}$, which means that the estimation of $\alpha$ fails in this manner.
+			Hence, more sophisticated estimation need to be adopted, although this coarse approach gives relative precise estimation of $\gamma$.\\
+			Considering the approach in part(e), where $E(n^2 x)$ is estimated utilizing the info of the noise, similiar approximations can be made as
+			\begin{equation}
+				E(n^2 x) = E({n^*}^2 x^*) = \frac{\sum_{k=1}^{N}{n_k^*}^2 x_k^*}{N}
+			\end{equation}
+			and
+			\begin{equation}
+				E(\dot{n}) = E(\dot{n^*}) = \frac{\sum_{k=2}^{N-1}\dot{n_k^*}}{N-2}
+			\end{equation}
+			Here, no assumption of the distribution of the noise was made. With $\hat{\gamma}$ given by the coarse estimation, a relative finer estimation of $\hat{\alpha}$ can be calculated as
+			\begin{equation}
+				\hat{\alpha} = \frac{\hat{\gamma} - E(\dot{n^*})}{E({n^*}^2 x^*)}
+			\end{equation} 
+			Numerical experiment was carried to verifiy the approximations. This time, the relative error of $\hat{\alpha}$ is satisfying, and the estimation result is
+			\begin{equation}
+				\begin{aligned}
+					\hat{\alpha} & = 0.100805\\
+					\hat{\gamma} & = 0.198847
+				\end{aligned}
+			\end{equation}
 
-		\item
-
-		\item
-
+			Further, we can apply the scheme described in part(e) without tuning  $E(n^2 x)$ finely, just take it as $E({n^*}^2 x^*)$, which also gives similiar result.
+But these trival stuff will not be discussed here as it has been clear enough for this problem...
 	\end{enumerate}

### 2018-08-02 VV570/PROJ2/code/task3.m

@@ -133,12 +133,12 @@ subplot(2,1,1)
 plot(alpha_est3_err);
 xlabel('Numerical Experiment Cnt')
 ylabel('Relative error of \alpha')
-title('Coarse estimation of \alpha')
+title('Error of \alpha')
 subplot(2,1,2)
 plot(gamma_est3_err);
 xlabel('Numerical Experiment Cnt')
 ylabel('Relative error of \gamma')
-title('Coarse estimation of \gamma')
+title('Error of \gamma')
 
 gamma_est4 = ensp+exsp+exo1xs;
 alpha_est4 = (gamma_est4-ensp)/en2xs;

### 2018-09-17 VV556/HW1/submission.tex
inital setup

--- 2018-05-23 VV570/HW1/assignment.tex
@@
-%----------------------------------------------------------------------------------------
-%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
-%----------------------------------------------------------------------------------------
-
 \documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Introduction to Numerical Analysis \\ HW1 \\ % The assignment title
+\huge Methods of Applied Mathematics I\\ HW1 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\date{\normalsize\today} % Today's date or a custom date
+\date{\normalsize \today} % Today's date or a custom date
 
@@
 \section{Metric Space}
-\begin{enumerate}
-	\item
-		\begin{proof}
-			Since there's no elements in $\emptyset$, so $\emptyset$ is open, as $X^\complement = \emptyset$, so $X$ is closed.\\
-			$X$ is open as it contains all the elemnets, since $\emptyset^\complement = X$, thus $\emptyset$ is closed. 
-		\end{proof}
-	\item
-		\begin{proof}
-			Since
-			\begin{equation}
-				T \triangleq (U_1 \cap U_2 \cap ... \cap U_m)^\complement = U_1^\complement \cup U_2^\complement \cup ... \cup U_m^\complement
-			\end{equation}
-			And ${U_i}^\complement$ is open, as $U_i$ is closed.\\
-			Thus, $T$ is open, and therefore the intersection is closed. 
-		\end{proof}
-	\item 
-		\begin{proof}
-			Since
-			\begin{equation}
-				T \triangleq (U_1 \cup U_2 \cup ... \cup U_m)^\complement = U_1^\complement \cap U_2^\complement \cap ... \cap U_m^\complement
-			\end{equation}
-			And ${U_i}^\complement$ is open, as $U_i$ is closed.\\
-			Thus, $T$ is open, and therefore the intersection is closed. 
-		\end{proof}
-
-\end{enumerate}
 
@@
 
-\begin{enumerate}
-\item $y=\frac{1}{x}$ is continuous over $(0, +\infty)$, but not uniform continuous.
-      \begin{proof}
-      	Let $x_1 = \frac{1}{n+1}$,  $x_2 = \frac{1}{n}$. 
-      	Then $\lim\limits_{n \rightarrow +\infty} \vert x_2-x_1 \vert = \frac{1}{n(n+1)} = 0 $.
-      	But $\lim\limits_{n \rightarrow +\infty} \vert y_2- y_1 \vert = 1 \neq 0 $.
-      	Thus it is not uniform continuous.
-      \end{proof}
-\item $y=\sqrt{x}$ is uniform continuous over $(0, +\infty)$ but not Lipschitz continuous.
-	  \begin{proof}
-	  	As $y\prime = \frac{1}{2\sqrt{x}}$, 
-	  	the slope tends towards infty when $x$ approaches 0, 
-	  	thus it is not Lipschitz continuous.  
-	  \end{proof}
-\end{enumerate}
-
 %----------------------------------------------------------------------------------------
@@
 \section{Cardinalty}
-\begin{enumerate}
-	\item 
-		\begin{proof}
-			The following function is a one-to-one mapping from N to Z, thus N and Z have the same number of elements.
-
-			\begin{equation}
-			f(n) = 
-				\begin{cases}
-					-\frac{n}{2} & \text{n is even}\\
-					\frac{n+1}{2} & \text{n is odd}
-				\end{cases}
-			\end{equation}
-
-			Arange the elements in N and Q in the pascal triangle style as below, and it is clear enough to see the one-to-one mapping from N to Q with rationals are grouped according to the sum of dividend and divisor.
-Thus N and Q have the same number of elements.
-
-			\begin{tabular}{c|c}
-				\begin{tabular}{rccccccccc}
-					&&&&&1\\\noalign{\smallskip\smallskip}
-					&&&&2&&3\\\noalign{\smallskip\smallskip}
-					&&&4&&&&5\\\noalign{\smallskip\smallskip}
-					&&6&&7&&8&&9\\\noalign{\smallskip\smallskip}
-					&10&&&&&&&&11\\\noalign{\smallskip\smallskip}
-					&&&&&...\\\noalign{\smallskip\smallskip}
-				\end{tabular} &
-				\begin{tabular}{rccccccccc}
-					&&&&&$\frac{1}{1}$ \\\noalign{\smallskip\smallskip}
-					&&&&$\frac{1}{2}$&&$\frac{2}{1}$\\\noalign{\smallskip\smallskip}
-					&&&$\frac{1}{3}$&&&&$\frac{3}{1}$\\\noalign{\smallskip\smallskip}
-					&&$\frac{1}{4}$&&$\frac{2}{3}$&&$\frac{3}{2}$&&$\frac{4}{1}$\\\noalign{\smallskip\smallskip}
-					&$\frac{1}{5}$&&&&&&&&$\frac{5}{1}$\\\noalign{\smallskip\smallskip}
-					&&&&&...\\\noalign{\smallskip\smallskip}
-				\end{tabular}
-			\end{tabular}
-
-		\end{proof}	
-	\item 
-		\begin{proof}
-			The following function is a one-to-one mapping from [0, 1] to R, thus they have the same number of elements.
-
-			\begin{equation}
-				f(x) = 
-				\begin{cases}
-				-\infty& \text{x=0}\\
-				tan[\pi(x-0.5)] & \text{0 < x < 1}\\
-				+\infty& \text{x=1}
-				\end{cases}
-			\end{equation}
-
-		\end{proof}
-	\item
-		\begin{proof}
-			Suppose all the real numbers can be listed, and each one is marked as $r_i$, where $i=1,2,3...$.
-Given a real number $r\prime$ such that its \textbf{i-th} digit is different from that in $r_i$, it's obvious that $r\prime$ is not included in the real numbers listed above, which is contradictory to the hypothesis.
-Thus real numbers can not be listed and it contains more elements than N.
-		\end{proof}
-\end{enumerate}
-
-%----------------------------------------------------------------------------------------
-%	PROBLEM 4
-%----------------------------------------------------------------------------------------
-
-\section{Slides}
-
-\begin{enumerate}
-	\item
-		\begin{proof}
-			Let $E$ be an inner product space over $\mathbb{C}$, and $u, v\in E$.
-			Given $Y$ defined as below, where $\lambda \in \mathbb{R}$.
-
-			\begin{equation}
-				Y = {\vert u-\lambda v \vert}^2
-			\end{equation}
-
-			It's obvious that $Y\geq0$. Expand the squares according to the definition of inner products, the inequality can be written as below.
-
-			\begin{equation}
-				<v, v>\lambda^2 -(<u, v>+<v, u>)\lambda + <u, u> \ \ \geq \ 0
-			\end{equation}
-
-			The LHS of the inequality can be viewed as a quadratic function where $\lambda$ is the variable. Thus, the discriminant is semi-negative definite, which can be written as below.
-
-			\begin{equation}
-				\Delta = (<u, v>+<v, u>)^2 - 4<u,u><v,v> \ \ \leq \ 0
-			\end{equation}
-
-			As $<v, u> = \overline{<u, v>}$, the inequality above can be simplified as below.
-
-			\begin{equation}
-				<u, v>^2 + {\overline{<u, v>}}^2 + 2{\vert <u,v> \vert}^2 \ \ \leq \ 4 \lVert u \rVert^2 \lVert v \rVert^2 \label{cs}			
-			\end{equation}
-
-			For $x \in \mathbb{C}$, the following equality is justified.
-			\begin{equation}
-				x^2 + \bar{x}^2 = \frac{1}{2}[(x+\bar{x})^2+(x-\bar{x})^2] = \frac{1}{2}[(2Re(x))^2+(2Im(x))^2] = 2 {\vert x \vert}^2 \label{der}
-			\end{equation}
-
-			Since $<u, v>$ is an complex number, apply (\ref{der}) into (\ref{cs}) and eliminate the constant 4, the Cauchy-Schwarz inequality is obtained at last.
-
-			\begin{equation}
-				{\vert <u,v> \vert}^2 \leq \lVert u \rVert^2 \lVert v \rVert^2
-			\end{equation}
-
-		\end{proof}
-
-	\item
-		\begin{proof}
-			$d(x, y)$ is non-negative follows from the definition of metric space.
-			\begin{equation}
-				\begin{aligned}
-					d(x, y) & = \frac{1}{2}(d(x, y) + d(x, y)) \\
-							& = \frac{1}{2}(d(x, y) + d(y, x)) &\text{By symmetry}\\
-							& \geq \frac{1}{2} d(x, x)         &\text{By triangle inequality} \\
-							& = 0                              &\text{By identity of indiscernible}
-				\end{aligned}
-			\end{equation}
-
-		\end{proof}
-\end{enumerate}
-
-%----------------------------------------------------------------------------------------
-%	PROBLEM 5
-%----------------------------------------------------------------------------------------
-
-\section{Linear Algebra}
-
-\begin{enumerate}
-	\item
-		\begin{proof}
-			Suppose $\{u_1, u_2, ...
-, u_m \}$ forms the basis of Ker($f$), and it can be extended to form the basis of $V_1$, which is denoted as $\{u_1, u_2, ...
-, u_m, v_1, v_2, ...
-, v_n \}$.
-It's clear that the dimension of Ker($f$) is $m$ and the dimension of $V_1$ is $m+n$.
-So, it is left to prove that the dimension of $V_2$ is $n$.
-
-			The dimension of $V_2$ is $n$ means $\{f(v_1), f(v_2), ...
-, f(v_n)\}$ forms a basis of $V_2$.
-To see that, let $w$ be an arbitary vector in $V_1$, thus, there exist unique scalars $a_i$, $b_j$ such that
-			\begin{equation}
-				w = a_1 u_1 + a_2 u_2 + ... + a_m u_m + b_1 v_1 + b_2 v_2 + ... + b_n v_n
-			\end{equation}
-
-			The image of $w$ under mapping $f$ is given as below.
-			\begin{equation}
-				\begin{aligned}
-					f(w) & = \sum_{i=1}^{m}a_i f(u_i) + \sum_{j=1}^{m}b_j f(v_j) \\
-						 & = \sum_{j=1}^{m}b_j f(v_j)  \ \ \ \  \text{As $f(u_i) = 0$}
-				\end{aligned}
-			\end{equation}
-
-			Thus $\{f(v_1), f(v_2), ... , f(v_n)\}$ spans $V_2$. It is left to show that they are linearly independent, which means there's no redundancy in the list.
-
-			Given coefficents $c_i$ such that
-			\begin{equation}
-				c_1 f(v_1) + c_2 f(v_2) + ... + c_n f(v_n) = 0 \label{cdis}
-			\end{equation}
-
-			Since $f$ is a linear mapping, (\ref{cdis}) can be grouped as below.
-			\begin{equation}
-				f(c_1 v_1 + c_2 v_2 + ... + c_n v_n) = 0
-			\end{equation}
-
-			Thus $c_1 v_1 + c_2 v_2 + ... + c_n v_n \in Ker(f)$. As $\{u_1, u_2, ... , u_m \}$ forms the basis of Ker($f$), there exists coefficients $d_i$ such that
-			\begin{equation}
-				c_1 v_1 + c_2 v_2 + ... + c_n v_n = d_1 u_1 + d_2 u_2 + ... + d_m u_m \label{diff}
-			\end{equation}
-
-			Since $\{u_1, u_2, ...
-, u_m, v_1, v_2, ...
-, v_n \}$ forms the basis of $V_1$, all the coefficients in (\ref{diff}) should be 0.
-Thus, (\ref{cdis}) is valid if and only if all the coefficents $c_i$ is 0, which implies that $\{f(v_1), f(v_2), ...
-, f(v_n)\}$ are linearly independent.
-
-			Thus, $\{f(v_1), f(v_2), ... , f(v_n)\}$ forms the basis of $V_2$, and the dimension of $V_2$ is therefore $n$. The rank-nullity theorem written as below is proved.
-			\begin{equation}
-				dim(V_1) = dim(ker(f)) + dim(V_2)
-			\end{equation}
-		\end{proof}
-
-	\item
-		\begin{proof}
-			Let $U, V, W$ be vector spaces over the same field $K$, function $f$ be a linear map from $U$ to $V$ and function $g$ be a linear map from $V$ to $W$.
-It's left to show that the composition of $f$ and $g$, denoted as $h$, which maps a vector in $U$ to $W$, is still a linear map.
-
-			Given $u_1, u_2 \in U$ and any scalar $c \in \mathbb{K}$, then
-			\begin{equation}
-				\begin{aligned}
-					h(u_1 + u_2) & = g(f(u_1 + u_2)) \\
-								 & = g(f(u_1) + f(u_2)) \\
-								 & = g(f(u_1)) + g(f(u_2)) \\
-								 & = h(u_1) + h(u_2)
-				\end{aligned}
-			\end{equation}
-
-			\begin{equation}
-				\begin{aligned}
-					h(c u_1) & = g(f(c u_1)) \\
-							 & = g(c f(u_1)) \\
-						     & = c g(f(u_1)) \\
-							 & = c h(u_1)
-				\end{aligned}
-			\end{equation}
-
-			Thus, the composition of two linear maps is still a linear map.
-		\end{proof}
-
-	\item
-		\begin{proof}
-			Let $U, V$ be vector spaces over the same field $K$, function $f$ be linear maps from $U$ to $V$.
-It's left to show that the inverse of $f$, denoted as $f^{-1}$, which maps a vector in $V$ to $U$ is still a linear map.
-
-			By inverse, it means that
-			\begin{equation}
-				f(f^{-1}(x)) = f^{-1}(f(x)) = x
-			\end{equation}
-
-			Given $u_1, u_2 \in U$ and any scalar $c \in \mathbb{K}$, denote the counterpart of $u_1, u_2$ in $V$ as $v_1, v_2$ under the linear mapping function $f$. Then
-
-			\begin{equation}
-				\begin{aligned}
-					f^{-1}(v_1 + v_2) & = f^{-1}(f(u_1) + f(u_2)) \\
-									  & = f^{-1}(f(u_1 + u_2)) \\
-									  & = u_1 + u_2 \\
-									  & = f^{-1}(v_1) + f^{-1}(v_2)
-				\end{aligned}
-			\end{equation}
-
-			\begin{equation}
-				\begin{aligned}
-					f^{-1}(c v_1) & = f^{-1}(c f(u_1)) \\
-							      & = f^{-1}(f(c u_1)) \\
-								  & = c u_1 \\
-								  & = c f^{-1}(v_1)
-				\end{aligned}
-			\end{equation}
-
-			Thus, the inverse of a linear map is still a linear map.
-		\end{proof}
-\end{enumerate}
-
-%----------------------------------------------------------------------------------------
-%	PROBLEM 6
-%----------------------------------------------------------------------------------------
-
-\section{Discontinuous linear maps}
-\begin{enumerate}
-	\item 
-		\begin{proof}
-			The $k$ times derivative of $f_n(x)$ can be written as below.
-			\begin{equation}
-				f_n^{(k)}(x) = n^{k-1} sin(nx+ \frac{k\pi}{2}) \ \ \ \ k = 0, 1, 2, 3, ...
-			\end{equation}
-			It's clear that $f_n^{(k)}(x)$ is continous for any $k$, thus $f_n(x) \in C^\infty(\mathbb{R})$.
-		\end{proof}
-	\item 
-		\begin{equation}
-			d f_n(x) = cos(nx) dx
-		\end{equation}
-	\item
-		\begin{proof}
-			Let $x_0 = 0, x_1 = \frac{\pi}{2n}$, then
-			\begin{equation}
-				\lim\limits_{n->+\infty} \vert x_1-x_0 \vert = 0
-			\end{equation}
-			\begin{equation}
-				\lim\limits_{n->+\infty} \vert df_n(x_1) - df_n(x_0) \vert = \vert 0-dx \vert = |dx| \neq 0
-			\end{equation}
-			Thus, the differential is not continous when n tends to infty.
-		\end{proof}
-	\item 
-		Sorry, haven't figured out yet...
-
-\end{enumerate}
-
-%----------------------------------------------------------------------------------------
-%	PROBLEM 7
-%----------------------------------------------------------------------------------------
-
-\section{pi}
-\begin{enumerate}
-	\item 
-		The main program(see Algorithm\ref{machin}) adopts Machin's formula to calculate $\pi$.
-		\begin{equation}
-			\pi = 4[4atan(\frac{1}{5}) - atan(\frac{1}{239})]
-		\end{equation}
-
-		Subroutine(see Algorithm\ref{atan_inv}) calculating $atan(\frac{1}{x})$ is used by the main program. Since
-		\begin{equation}
-			atan(x) = \frac{1}{1}x - \frac{1}{3}x^3 + \frac{1}{5}x^5 - \frac{1}{7} x^7 + ...
-		\end{equation}
-
-		Therefore
-		\begin{equation}
-			atan(\frac{1}{x}) = \frac{1}{x} - \frac{1}{3x^3} + \frac{1}{5x^5} - \frac{1}{7x^7} + ...
-		\end{equation}
-
-		\begin{algorithm}
-			\caption{Calculation of $\pi$ using Machin's formula}  
-			\label{machin}
-			\begin{algorithmic}[1]
-				\REQUIRE
-				None.
-				\ENSURE
-				The value of $\pi$ with approximation.
-				\RETURN $4[4 atan(1/5) - atan(1/239)]$
-			\end{algorithmic}  
-		\end{algorithm}
-
-		\begin{algorithm}
-			\caption{Calculation of $atan(\frac{1}{x})$}
-			\label{atan_inv}
-			\begin{algorithmic}[1]
-				\REQUIRE x
-				\ENSURE $atan(\frac{1}{x})$
-				\STATE $ret \gets 0$
-				\STATE $e \gets 1/x$
-				\STATE $s \gets - x^2$
-				\STATE $c \gets 1$
-				\WHILE {$e \neq 0$}
-				\STATE $ret \gets ret + e/c$
-				\STATE $e \gets e/s$
-				\STATE $c \gets c + 2$
-				\ENDWHILE
-				\RETURN ret
-			\end{algorithmic}  
-		\end{algorithm}
-
-	\newpage
-
-	\item
-		The matlab code is given as below.
-		\begin{verbatim}
-			function [pi] = pi_machin()
-			pi = 4*(4*atan_inv(5) - atan_inv(239));
-
-			function [r] = atan_inv(x)
-			r = 0;
-			e = 1/x;
-			s = - x*x;
-			c = 1;
-			while (e ~= 0)
-			r = r + e/c;
-			e = e/s;
-			c = c+2;
-			end
-		\end{verbatim}	
-\end{enumerate}
-
-%----------------------------------------------------------------------------------------
 

### 2018-09-20 VV556/HW1/submission.tex
ex1 ok
add ex3

@@
 
-%----------------------------------------------------------------------------------------
-%	PROBLEM 1
-%----------------------------------------------------------------------------------------
+\section{Exercise1.1}
+\begin{enumerate}
+	\item 
+		\begin{equation}
+			\dim{U} = 2
+		\end{equation}
+		As there are 4 components within $x$, and 2 constraints.
+	\item 
+		\begin{equation}
+			\dim{U} = 3
+		\end{equation}
+		As there are 4 components within $x$, and 1 constraint.
+	\item 
+		\begin{equation}
+			\begin{aligned}
+				\dim{U+V} & = \dim{U} + \dim{V} - \dim{U \cap V} \\
+				          & = 2 + 3 - 2 \\
+				          & = 3
+			\end{aligned}
+		\end{equation}
+		The dimension of $U \cap V$ can be observed from
+		\begin{equation}
+			\begin{aligned}
+				U \cap V & = \{x\in \mathbb{R}^4| x_1 + x_2 + x_3 = 0, x_1 + 3 x_2 = x_4, x_1 = x_4\}\\
+				         & = \{x\in \mathbb{R}^4| x_2 = 0, x_1 + x_3 = 0\}
+			\end{aligned}
+		\end{equation}
+\end{enumerate}
 
-\section{Metric Space}
+\section{Exercise1.2}
+\begin{enumerate}
+	\item
+		The pointwise limit is given as follows
+		\begin{equation}
+			f = \left\{\begin{aligned}
+			0, & x = 0\\
+			1, & x\in(0,1]
+			\end{aligned}
+			\right.
+		\end{equation}
+		It's of uniform convergence as
+		\begin{equation}
+			\begin{aligned}
+				&  \lim\limits_{n\rightarrow\infty} \sup_{x\in[0, 1]} |f_n(x) - f(x)|\\
+				&=\left\{
+					\begin{aligned}
+						&0,  &x=0\\ 
+						&\lim\limits_{x\rightarrow 0,  n \rightarrow \infty} |x^{\frac{1}{n}} - 1|, & x \in (0, 1]
+					\end{aligned}
+					\right.\\
+				&=0
+			\end{aligned}
+		\end{equation}
+	\item 
+		The pointwise limit is given as
+		\begin{equation}
+			f(x) = x
+		\end{equation}
+		It's not of uniform convergence.
+	\item 
+		The pointwise limit is given as
+		\begin{equation}
+			f(x) = 0
+		\end{equation}
+		It's of uniform convergence as
+		\begin{equation}
+			\begin{aligned}
+				&	\lim\limits_{n\rightarrow\infty}\sup_{x\in(0, \infty)}|f_n(x) - f(x)|\\
+				& =\lim\limits_{n\rightarrow\infty}\sup_{x\in(0, \infty)}\Biggl|\sqrt{\frac{1}{n} + x} - \sqrt{x}\Biggr|\\
+				& =\lim\limits_{n\rightarrow\infty}\sup_{x\in(0, \infty)}\Biggl|\frac{1}{n(\sqrt{\frac{1}{n} + x} + \sqrt{x})}\Biggr|\\
+				& = \lim\limits_{n\rightarrow\infty, x \rightarrow 0}\frac{1}{n(\sqrt{\frac{1}{n} + x} + \sqrt{x})}\\
+				& = \lim\limits_{n\rightarrow\infty, x \rightarrow 0}\frac{1}{2n\sqrt{x}} = 0
+			\end{aligned}
+		\end{equation}
+\end{enumerate}
 
-%----------------------------------------------------------------------------------------
-%	PROBLEM 2
-%----------------------------------------------------------------------------------------
-
-\section{Continuity}
-
-%----------------------------------------------------------------------------------------
-%	PROBLEM 3
-%----------------------------------------------------------------------------------------
-
-\section{Cardinalty}
+\section{Exercise1.3}
+	\begin{enumerate}
+		\item 
+			Not figured out...
+		\item 
+			For example
+			\begin{equation}
+				a_n = \frac{1}{n}
+			\end{equation}
+		\item 
+			Consider a sequence constructed as follows
+			\begin{equation}
+				\begin{aligned}
+					& x_1 = \frac{1}{1} & (1^1=1 \ item)\\
+					& x_2 = ... = x_5 = \frac{1}{2} & (2^2=4 \ items)\\
+					& x_6 = ... = x_{32} = \frac{1}{3} & (3^3=27 \ items)\\
+					& ...
+				\end{aligned}
+			\end{equation}
+			This sequence certainly converges to 0. But not in $L^p$ for any $p>=1$ as
+			\begin{equation}
+				\sum_{n=1}^{\infty} = 1 + \frac{2^2}{2^p} + \frac{3^3}{3^p} + ... + \frac{n^n}{n^p} + ...
+			\end{equation}
+			for any $n > p$, $\frac{n^n}{n^p} > 1$.
+	\end{enumerate}
 

### 2018-09-23 VV556/HW2/submission.tex
add part of ex11

--- 2018-06-23 VV570/HW5/submission.tex
@@
 \usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages
-\usepackage{mathrsfs}
 
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Introduction to Numerical Analysis \\ HW5 \\ % The assignment title
+\huge Methods of Applied Mathematics I\\ HW2 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-%----------------------------------------------------------------------------------------
-%	PROBLEM 1
-%----------------------------------------------------------------------------------------
-\section{Lebesgue constant for Chebyshev nodes}
-\begin{enumerate}
-	\item 
+\section{Exercis2.1}
 	\begin{enumerate}
@@
 			\begin{proof}
-					Denote
 				\begin{equation}
 					\begin{aligned}
-							LHS &\triangleq (x-x_i)l_i(x) \\
-							RHS &\triangleq \frac{T_{n+1}(x)}{T_{n+1}'(x_i)}
+						RHS & = \frac{1}{4} (||x+y||^2  - ||x-y||^2)\\
+						    & = \frac{1}{4} (<x+y, x+y> - <x-y, x-y>)\\
+						    & = \frac{1}{4} (<x+y, x> + <x+y, y> - <x-y, x> - <x-y, -y>)\\
+						    & = \frac{1}{4} (\overline{<x, x+y>} + \overline{<y, x+y>} - \overline{<x, x-y>} + \overline{<y, x-y>})\\
+						    & = \frac{1}{4} (\overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} + \overline{<y, y>} - \overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} - \overline{<y, y>})\\
+						    & = \frac{1}{2}(\overline{<x,y>} + \overline{<y, x>})\\
+						    & = \frac{1}{2}(<x, y> + <y, x>)\\
+						    & = <x, y> = LHS
 					\end{aligned}
 				\end{equation}
-					It is left to prove $LHS = RHS$.\\
-					The left part can be written as
+				The last line is valid as the inner-product is defined on real space s.t. $<x, y>=<y, x>$.
+			\end{proof}
+		\item 
+			\begin{proof}
+				As have been proved aboved
 				\begin{equation}
-						LHS = c_l \omega(x)
+					\begin{aligned}
+						   & \frac{1}{4} (||x+y||^2  - ||x-y||^2)\\
+						=  & \frac{1}{2}(<x, y> + <y, x>)
+					\end{aligned}
 				\end{equation}
-					where 
+				Also, replace $y$ with $iy$ yields
 				\begin{equation}
-						\omega(x) = \prod_{i=0}^{n}(x-x_i)
+					\begin{aligned}
+						  & \frac{i}{4} (||x+iy||^2  - ||x-iy||^2)\\
+						= & \frac{i}{2} (<x, iy> + <iy, x>)\\
+						= & \frac{i}{2} (i<x, y> + \overline{i}<y, x>)\\
+						= & \frac{1}{2} (-<x, y> + <y,x>)
+					\end{aligned}
 				\end{equation}
-					and
+				Thus
 				\begin{equation}
-						c_l = \frac{1}{\prod_{k=0, k\neq i}^{n}(x_i - x_k)} 
+					\begin{aligned}
+						RHS & = \frac{1}{4} (||x+y||^2  - ||x-y||^2) - \frac{i}{4} (||x+iy||^2  - ||x-iy||^2)\\
+						    & = \frac{1}{2}(<x, y> + <y, x>) - \frac{1}{2} (-<x, y> + <y,x>)\\
+						    & = <x, y> = LHS
+					\end{aligned}
 				\end{equation}
-
-					Since both $LHS$ and $RHS$ are polynomials of order $n+1$, they are equivalent iff. they have same roots and leading coefficients.\\
-					On the one hand,as for all $x_i$, where $i = 0, 1, ... , n$
-					\begin{equation}
-						T_{n+1}(x_i) = cos((n+1)\theta_i) = cos(\frac{2i+1}{2}\pi) = 0
-					\end{equation}
-					Thus, $LHS$ and $RHS$ have same roots. $RHS$ can therefore be written as
-					\begin{equation}
-						RHS(x) = c_r \omega(x)
-					\end{equation}
-					On the other hand, since
-					\begin{equation}
-						LHS'(x)|_{x=x_i} = (l_i(x) + (x-x_i)l_i'(x))|_{x=x_i} = 1
-					\end{equation}
-					and
-					\begin{equation}
-						RHS'(x)|_{x=x_i} = \frac{T'_{n+1}(x)}{T_{n+1}'(x_i)}\Big|_{x=x_i} = 1
-					\end{equation}
-					Thus, the leading coefficients of $LHS$ and $RHS$ are equal, namely $c_l = c_r$.\\
-					Hence, $LHS=RHS$.
 			\end{proof}
@@
 					\begin{aligned}
-							T'_{n+1}(x) & = (cos((n+1)arccos(x)))'\\
-							            & = sin((n+1)arccos(x)) (n+1) \frac{1}{\sqrt{1-x^2}}\\
-							            & = \frac{n+1}{\sqrt{1-cos^2(\theta)}} sin((n+1)\theta) 
+						LHS & = ||x+y||^2 + ||x-y||^2\\
+						    & = <x+y, x+y> + <x-y, x-y>\\
+						    & = <x+y, x> + <x+y, y> + <x-y, x> - <x-y, y>\\
+						    & = \overline{<x, x+y>} + \overline{<y, x+y>} + \overline{<x, x-y>} - \overline{<y, x-y>}\\
+						    & = \overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} + \overline{<y, y>} + \overline{<x, x>} - \overline{<x, y>} - \overline{<y, x>} + \overline{<y, y>}\\
+						    & = 2(<x, x>+<y, y>)\\
+						    & = 2(||x||^2 + ||y||^2) = RHS
 					\end{aligned}
-					\end{equation}
-					As $\theta_k = \frac{2k+1}{2(n+1)}\pi$, thus, $sin(\theta_k) > 0$, and
-					\begin{equation}
-						T'_{n+1}(x_k) = \frac{n+1}{sin(\theta_k)} sin(\frac{2k+1}{2}\pi) = {(-1)}^k \frac{n+1}{sin(\theta_k)}
 				\end{equation}
@@
 			\begin{proof}
-					As
-					\begin{equation}
-						T_{n+1}(1) = cos((n+1)arccos(1)) = 1	
-					\end{equation}
-					Thus
-					\begin{equation}
-						\begin{aligned}
-							\sum_{i=0}^{n}|l_i(1)| & = \sum_{i=0}^{n}\Bigg|\frac{T_{n+1}(1)}{(1-x_i)T'_{n+1}(x_i)}\Bigg| \\
-												   & = \sum_{i=0}^{n} \frac{1}{\Big|(1-x_i)T'_{n+1}(x_i)\Big|}\\
-												   & = \frac{1}{n+1} \sum_{i=0}^{n} \bigg|\frac{sin\theta_i}{(1-cos\theta_i)} \bigg|\\
-												   & = \frac{1}{n+1} \sum_{i=0}^{n} \bigg|\frac{sin\theta_i}{2sin^2(\frac{\theta_i}{2})} \bigg|\\
-												   & \geq  \frac{1}{n+1} \sum_{i=0}^{n} cot(\frac{\theta_i}{2})\\
-						\end{aligned}
-					\end{equation}
-				\end{proof} 			
-		\end{enumerate}
-	\item 
-		\begin{enumerate}
-			\item 
-				\begin{proof}
-					According to the mean value theorem, there exists $\theta \in [\frac{\theta_k}{2}, \frac{\theta_{k+1}}{2}]$, s.t.
-					\begin{equation}
-						\int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt = \frac{\theta_{k+1} - \theta_k}{2} cot(\theta)
-					\end{equation}
-					As $cot'(t) = -\frac{1}{sin^2(t)} < 0$, and $\theta_k \leq \theta \leq \theta_{k+1}$, thus
-					\begin{equation}
-						cot(\theta) \leq cot(\theta_k)
-					\end{equation}
-					Therefore
-					\begin{equation}
-						\int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt \leq \frac{\theta_{k+1} - \theta_k}{2} cot(\theta_k)
-					\end{equation}
+
 			\end{proof}
@@
 		\item
-				\begin{proof}
-					As $\theta_{k+1} - \theta_k = \frac{\pi}{n+1}$ and according to the result that have been proved above
-					\begin{equation}
-						\begin{aligned}
-							\sum_{k=0}^{n} \int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt 
-							& \leq \sum_{k=0}^{n} \frac{\theta_{k+1} - \theta_k}{2}cot(\frac{\theta_k}{2})\\
-							& = \frac{\pi}{2(n+1)} \sum_{k=0}^{n} cot(\frac{\theta_k}{2})
-						\end{aligned}
-					\end{equation}
-				\end{proof}
-
-			\item 
-				\begin{proof}
-					As $\theta_n = \frac{2n+1}{2n+2}\pi < \pi$, $\theta_{n+1} = \frac{2n+3}{2n+2} > \pi$, and $cot(x)$ is positive over $(0, \frac{\pi}{2})$, while negative otherwise.
-					Thus
-					\begin{equation}
-							\int_{\frac{\theta_0}{2}}^{\frac{\pi}{2}} cot(t) dt 
-							\leq \int_{\frac{\theta_0}{2}}^{\frac{\theta_n}{2}} cot(t) dt
-							= \sum_{k=0}^{n-1} \int_{\frac{\theta_k}{2}}^{\frac{\theta_{k+1}}{2}} cot(t) dt
-					\end{equation}
-					Hence
-					\begin{equation}
-						\int_{\frac{\theta_0}{2}}^{\frac{\pi}{2}} cot(t) dt \leq \frac{\pi}{2(n+1)} \sum_{i=0}^{n}cot(\frac{\theta_i}{2})
-					\end{equation}
-					(... not fine)
-				\end{proof}
 
@@
 
+\section{Exercise2.2}
+	\begin{enumerate}
 		\item
-		\begin{proof}
-			\begin{equation}
-				\begin{aligned}
-					\Lambda_n & = \max_{x \in [a, b]} \sum_{i=0}^{n} |l_i(x)|\\
-							  & \geq \sum_{i=0}^{n} |l_i(1)|\\
-							  & \geq \frac{1}{n+1} \sum_{i=0}^{n} cot(\frac{\theta_i}{2})\\
-							  & \geq \frac{2}{\pi} \int_{\theta_0 / 2}^{\pi/2} cot(t)dt\\
-							  & = \frac{2}{\pi} ln(|sin(t)|) \Bigg| _{\theta_0/2}^{\pi/2}\\
-							  & = - \frac{2}{\pi} ln(sin(\frac{\theta_0}{2}))\\
-							  & \geq \frac{2}{\pi} ln(\frac{2}{\theta_0}) = \frac{2}{\pi} ln(\frac{4(n+1)}{\pi})\\
-							  & \ge \frac{2}{\pi} ln(n)
-				\end{aligned}
-			\end{equation}
-		\end{proof}
 
@@
 
-%----------------------------------------------------------------------------------------
-%	PROBLEM 2
-%----------------------------------------------------------------------------------------
-\section{Interpolation}
-
-%----------------------------------------------------------------------------------------
-%	PROBLEM 3
-%----------------------------------------------------------------------------------------
-\section{Trigonometric polynomials}
-
 \end{document}

### 2018-09-24 VV556/HW2/submission.tex
add part of proof

@@
 			\begin{proof}
-
+				As any norm induced by inner product should satisfy the parallelogram law, it's easy to show that the norm $||.||_\infty : f\mapsto \sup_{x\in [a, b]} |f(x)|$ on $C[a, b]$ can not be induced by any inner product since it does not satisfy the parallelogram law.
+For example, let
+				\begin{equation}
+					f(x) = \frac{x-a}{b-a}
+				\end{equation}
+				and
+				\begin{equation}
+					g(x) = (\frac{x-a}{b-a})^2
+				\end{equation}
+				then
+				\begin{equation}
+					||f+g|| = \max_{x\in[a, b]} |(f+g)(x)| = |(f+g)(b)| = 2
+				\end{equation}
+				\begin{equation}
+					||f-g|| = \max_{x\in[a, b]} |(f-g)(x)| = |(f-g)(\frac{a+b}{2})| = \frac{1}{4}
+				\end{equation}
+				\begin{equation}
+					||f|| = \max_{x\in[a, b]} |f(x)| = |f(b)| = 1
+				\end{equation}
+				\begin{equation}
+					||g|| = \max_{x\in[a, b]} |g(x)| = |g(b)| = 1
+				\end{equation}
+				It's obvious that
+				\begin{equation}
+					||f+g||^2 + ||f-g||^2 = \frac{65}{4} \neq 2(||f||^2 + ||g||^2) = 4
+				\end{equation}
 			\end{proof}
@@
 		\item 
+			Assume the norm satisfies the parallelogram law, that is
+			\begin{equation}
+				||x+y||^2 + ||x-y||^2 = 2(||x||^2 + ||y||^2)
+			\end{equation}
+			Let
+			\begin{equation}
+				<x, y> \triangleq \frac{1}{4}(||x+y||^2 - ||x-y||^2)
+			\end{equation}
+			it's left to prove that $<x, y>$ is an inner product.\\
+			Firstly, $<x, y+z>$ can be expanded according to the definition as follows
+			\begin{equation}
+				\begin{aligned}
+					<x, y+z> & = \frac{1}{4}(||x+y+z||^2 - ||x-(y+z)||^2)\\
+					         & = \frac{1}{4}(||y+z+x||^2 - ||y+z-x||^2)
+				\end{aligned}
+			\end{equation}
+			Since
+			\begin{equation}
+				||y+z+x||^2 + ||y-z+x||^2 = 2(||y+x||^2 + ||z||^2)
+			\end{equation}
+			Then
+			\begin{equation}
+				||y+z+x||^2 = 2(||y+x||^2 + ||z||^2) - ||y-z+x||^2
+			\end{equation}
+			Swap $y$ and $z$ yields
+			\begin{equation}
+				||x+y+z||^2 = 2(||z+x||^2 + ||y||^2) - ||z-y+x||^2
+			\end{equation}
+			Adding the two equations above and divided by 2 yields
+			\begin{equation}
+				||y+z+x||^2 = ||y||^2 + ||z||^2 + ||x+y||^2 + ||x+z||^2 -\frac{1}{2}(||y-z+x||^2 + ||z-y+x||^2)
+			\end{equation}
+			Replace $x$ with $-x$
+			\begin{equation}
+				||y+z-x||^2 = ||y||^2 + ||z||^2 + ||x-y||^2 + ||x-z||^2 -\frac{1}{2}(||y-z-x||^2 + ||z-y-x||^2)
+			\end{equation}
+			Hence
+			\begin{equation}
+				||y+z+x||^2 + ||y+z-x||^2 = (||x+y||^2 - ||x-y||^2) + (||x+z||^2 - ||x-z||^2)
+			\end{equation}
+			As
+			\begin{equation}
+				<x, y> = \frac{1}{4} (||x+y||^2 - ||x-y||^2)
+			\end{equation}
+			and
+			\begin{equation}
+				<x, z> = \frac{1}{4} (||x+z||^2 - ||x-z||^2)
+			\end{equation}
+			It's therefore can be concluded that
+			\begin{equation}
+				<x, y+z> = <x, y> + <x, z>
+			\end{equation}
+			Secondly,
 

### 2018-09-27 VV556/HW2/submission.tex
add ex2

@@
 \section{Exercise2.2}
+	Denote $c_0 = \{(a_n)_{n\in\mathbb{N}}: \lim\limits_{n \rightarrow \infty} a_n = 0\}$ and $l^1 = \{(b_n)_{n\in\mathbb{N}}: \sum_{n=0}^{\infty} |b_n| \le \infty\}$
 	\begin{enumerate}
 		\item
+		YES
+		\begin{proof}
+			For any $(a_n) \in c_0$ and $\epsilon > 0$, $\exists N_1$ s.t. when $n > N_1$, $|a_n| \le \frac{\epsilon}{2}$.\\
+			Also, a sequence $(b_n) \in l^1$ can be found s.t.
+$|b_n| \le \frac{\epsilon}{2}$ when $n > N_2$, and $b_n = a_n$ for $n \leq N_3 \triangleq \max(N_1, N_2)$.
+This does not violate requirement for $(b_n)$ as the sum of $|b_n|$ here is finite.\\
+			Thus, $||(a_n) - (b_n)||_\infty = \sup_{n \in \mathbb{N}} |a_n - b_n| \leq |a_n| + |b_n| \leq \frac{\epsilon}{2} + \frac{\epsilon}{2} = \epsilon$ when $n > N_3$.
+And it implies that $l^1$ is dense in $c_0$ under the $||.||_\infty$ norm.
+		\end{proof}
+		\item 
+		NO
+		\begin{proof}
+			For example, pick a sequence $(a_n) \in c_0$ s.t.
+$a_n = \frac{1}{n+1}$, for any sequence $(b_n) \in l^1$.
+The norm $||(a_n) - (b_n)|| = \sum_{n=0}^{\infty} |a_n - b_n| \geq \sum_{n=0}^{\infty} (|a_n| - |b_n|) = (\sum_{n=0}^{\infty}|a_n|) - (\sum_{n=0}^{\infty}|b_n|)$ diverges as $\sum_{n=0}^{\infty}|a_n|$ goes infinite and $\sum_{n=0}^{\infty}|b_n|$ is finite.
+		\end{proof}
 

### 2018-10-05 VM524/HW1/submission.tex
ex1 ok

--- 2018-07-11 VV570/HW7/submission.tex
@@
-%----------------------------------------------------------------------------------------
-%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
-%----------------------------------------------------------------------------------------
 \documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size
@@
 \usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages
-\usepackage{mathrsfs}
+
 \usepackage{algorithm, algorithmic}
@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm
+
 \usepackage{listings}
 \lstset{language=Matlab}
-\usepackage{enumerate}
 
 \usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
+
 \usepackage{sectsty} % Allows customizing section commands
 \allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps
+
 \usepackage{fancyhdr} % Custom headers and footers
@@
 %----------------------------------------------------------------------------------------
+
 \newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Introduction to Numerical Analysis \\ HW7 \\ % The assignment title
+\huge Turbulence \\ HW1 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-%----------------------------------------------------------------------------------------
-%	PROBLEM 1
-%----------------------------------------------------------------------------------------
-\section{Question 1}
-	\begin{enumerate}[(a)]
-		\item 
-			For example
+\section{Exercise1}
+  Let
   \begin{equation}
-				y = tan(x), \ \ x\in (-\frac{\pi}{2}, \frac{\pi}{2})
+  	\Phi = \oiiint_\Omega \phi dv
   \end{equation}
-			It's differentiable over $(-\frac{\pi}{2}, \frac{\pi}{2})$, and the derivative is 
+  where $\phi$ is the passive scalar, and $\Omega$ is the control volume. \\
+  Then the change of $\Phi$ is due to the gradiant diffusion through boundary of $\Omega$, which can be written as
   \begin{equation}
-				y' = \frac{1}{cos^2(x)}
+  	\frac{D}{Dt} \Phi = \oiint_{\partial \Omega} \Gamma \nabla \phi d\vec{S}
   \end{equation}
-			It's obvious that $y' \rightarrow \infty$ when $x \rightarrow \frac{\pi}{2}$.
-		\item 
-			\begin{proof}
-				Denote $g(x)$ over $[x_1, x_2]$ as
+  where $\Gamma$ indicates the diffusivity, with unit of $m^2/s$.\\
+  The material derivative of $\Phi$ in Euler field is given as follows using RTT
   \begin{equation}
-					g(x) = f(x) - f(x_1) - \frac{f(x_2)-f(x_1)}{x_2-x_1}(x-x_1) 
+  	\frac{D}{Dt} \Phi = \oiiint_\Omega \frac{\partial \phi}{\partial t} dv + \oiint_{\partial \Omega} \phi \vec{U} \cdot d\vec{S}
   \end{equation}
-				where $a< x_1 < x_2 < b$. Then, $g(x_1) = 0$ and $g(x_2)=0$.
-
-				Thus, from Rolle's theorem, there exists $\xi \in (x_1, x_2)$ s.t. 
+  When field of $\phi$ is assumed to be smooth enough, the divergence theorem can be applied, which yields
   \begin{equation}
-					g'(\xi)= 0
+  	\oiiint_\Omega \frac{\partial \phi}{\partial t} dv + \oiiint_\Omega \nabla \cdot (\phi \vec{U}) dv = \oiiint_\Omega \nabla \cdot (\Gamma \nabla \phi) dv
   \end{equation}
@@
   \begin{equation}
-					\frac{f(x_2) - f(x_1)}{x_2-x_1} = f'(\xi)
+  	\frac{\partial \phi}{\partial t} + \nabla \cdot (\phi \vec{U}) = \nabla \cdot (\Gamma \nabla \phi)
   \end{equation}
-				Since $f'$ is bounded, then $|f'(\xi)| \leq M$. Thus
+  The equation can be further simplified when the flow is assumed to be both incompressible and constant-property.
   \begin{equation}
-					|f(x_2) - f(x_1)| \leq M |x_2 - x_1|
+  		\frac{\partial \phi}{\partial t} + \vec{U} \cdot \nabla \phi = \Gamma \nabla^2 \phi
   \end{equation}
-				which means that $f(x)$ is Lipschitz continous.
-			\end{proof}
-		\item 
-			For example
+  which can be written in material derivative format as
   \begin{equation}
-				y = \frac{1}{x}, \ \ x \in (0, 1)
+  	\frac{D\phi}{Dt} = \Gamma \nabla^2 \phi
   \end{equation}
-			$y$ is obviously differentiable and its derivative is
-			\begin{equation}
-				y' = -\frac{1}{x^2}, \ \ x \in (0, 1)
-			\end{equation}
-			Suppose there exist a constant $c>0$ s.t. 
-			\begin{equation}
-				|y_2 - y_1| \leq c|x_2 - x_1|
-			\end{equation}
-			is valid for all $0 < x_1 < x_2 < 1$.
-			Let $y(b) - y(a) = c(b-a)$, where $a < b$then
-			\begin{equation}
-				c = \frac{1}{ab}
-			\end{equation}
-			Take the mid-point of $a, b$, then
-			\begin{equation}
-				\frac{y(a)-y(\frac{b+a}{2})}{\frac{b+a}{2}-a} = \frac{1}{a(\frac{b+a}{2})} > \frac{1}{ab} = c
-			\end{equation}
-			Thus, the assumption fails, which means that $y$ is not Lipschitz continous.
-		\item 
-			For example
-			\begin{equation}
-				y = |x|, \ \ x \in (-1, 1)
-			\end{equation}
-			It's Lipschitz continous as for any $-1 < x_1 < x_2 < 1$
-			\begin{equation}
-				\frac{|y(x_2)-y(x_1)|}{|x_2 - x_1|} \leq 1
-			\end{equation}
-			but it is not differentiable at $x=0$.
 
-	\end{enumerate}
+\section{Exercise2}
 
-%----------------------------------------------------------------------------------------
-%	PROBLEM 2
-%----------------------------------------------------------------------------------------
-\section{Question 2}
+\section{Exercise3}
 
-%----------------------------------------------------------------------------------------
-%	PROBLEM 3
-%----------------------------------------------------------------------------------------
-\section{Question 3}
+\section{Exercise4}
 

### 2018-10-05 VM524/HW1/submission.tex
ex2 ok

@@
   \begin{equation}
-  	\frac{D\phi}{Dt} = \Gamma \nabla^2 \phi
+  	\frac{D}{Dt}\phi = \Gamma \nabla^2 \phi
   \end{equation}
@@
 \section{Exercise2}
-
+  Let $X$ and $Y$ be 2 sequences of random numbers, the correlation coefficient of these 2 random variables is calculated as
+  \begin{equation}
+  	\rho_{XY} = \frac{cov(X, Y)}{\sqrt{E[X^2] E[Y^2]}}
+  \end{equation}
+  the covariance of $X$ and $Y$ is calculated as
+  \begin{equation}
+  	cov(X, Y) = E[(X-E[X])(Y-E[Y])] = E[XY] - E[X]E[Y]
+  \end{equation}
+  With $E[XY], E[X], E[Y], E[X^2], E[Y^2]$ provided, the correlation coefficient can be therefore calculated.
 \section{Exercise3}

### 2018-10-05 VM524/HW1/CalcCovCoef.py

@@ -1,0 +1,24 @@
+import os
+import numpy as np
+import math
+
+N = 100
+
+X = np.random.rand(N)
+Y = np.random.rand(N)
+
+XY = X*Y
+X2 = X*X
+Y2 = Y*Y
+
+E_XY = sum(XY)/N
+E_X2 = sum(X2)/N
+E_Y2 = sum(Y2)/N
+E_X = sum(X)/N
+E_Y = sum(Y)/N
+
+rho_xy = (E_XY - E_X * E_Y)/math.sqrt(E_X2 * E_Y2)
+
+print(rho_xy)
+
+os.system('pause')

### 2018-10-06 VV556/HW3/submission.tex
fix header

--- 2018-10-05 VM524/HW1/submission.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Turbulence \\ HW1 \\ % The assignment title
+\huge Methods of Applied Mathematics I\\ HW3 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\section{Exercise1}
-  Let
-  \begin{equation}
-  	\Phi = \oiiint_\Omega \phi dv
-  \end{equation}
-  where $\phi$ is the passive scalar, and $\Omega$ is the control volume. \\
-  Then the change of $\Phi$ is due to the gradiant diffusion through boundary of $\Omega$, which can be written as
-  \begin{equation}
-  	\frac{D}{Dt} \Phi = \oiint_{\partial \Omega} \Gamma \nabla \phi d\vec{S}
-  \end{equation}
-  where $\Gamma$ indicates the diffusivity, with unit of $m^2/s$.\\
-  The material derivative of $\Phi$ in Euler field is given as follows using RTT
-  \begin{equation}
-  	\frac{D}{Dt} \Phi = \oiiint_\Omega \frac{\partial \phi}{\partial t} dv + \oiint_{\partial \Omega} \phi \vec{U} \cdot d\vec{S}
-  \end{equation}
-  When field of $\phi$ is assumed to be smooth enough, the divergence theorem can be applied, which yields
-  \begin{equation}
-  	\oiiint_\Omega \frac{\partial \phi}{\partial t} dv + \oiiint_\Omega \nabla \cdot (\phi \vec{U}) dv = \oiiint_\Omega \nabla \cdot (\Gamma \nabla \phi) dv
-  \end{equation}
-  namely
-  \begin{equation}
-  	\frac{\partial \phi}{\partial t} + \nabla \cdot (\phi \vec{U}) = \nabla \cdot (\Gamma \nabla \phi)
-  \end{equation}
-  The equation can be further simplified when the flow is assumed to be both incompressible and constant-property.
-  \begin{equation}
-  		\frac{\partial \phi}{\partial t} + \vec{U} \cdot \nabla \phi = \Gamma \nabla^2 \phi
-  \end{equation}
-  which can be written in material derivative format as
-  \begin{equation}
-  	\frac{D\phi}{Dt} = \Gamma \nabla^2 \phi
-  \end{equation}
+\section{Exercise3.1}
 
-\section{Exercise2}
+\section{Exercise3.2}
 
-\section{Exercise3}
-
-\section{Exercise4}
+\section{Exercise3.3}
 

### 2018-10-06 VV556/HW3/submission.tex
ex1 ok

@@
 \section{Exercise3.1}
+	\begin{proof}
+		Let $\phi(x) = (x^2 - 1)^n$, then
+		\begin{equation}
+			\phi(\pm 1) = \phi^{(1)}(\pm 1) = \cdots = \phi^{(n-1)}(\pm 1) = 0
+		\end{equation}
+		The $L^2$ norm of $P_n(x)$ is
+		\begin{equation}
+			\begin{aligned}
+				||P_n||_2  & = \sqrt{\int_{-1}^{1} P_n^2(x) dx}\\
+						   & = \sqrt{(\frac{1}{2^n n!})^2 \int_{-1}^{1} [\phi^{(n)}(x)]^2 dx}\\
+						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n \int_{-1}^{1} \phi^{(2n)}(x) \phi(x) dx} \quad \text{(Integrate by parts)}\\
+						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n (2n)! \int_{-1}^{1} (x^2 - 1)^n dx}\\
+						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n (2n)! \cdot 2 \int_{0}^{\frac{\pi}{2}} (sin^2(x) - 1)^n cos(x) dx}\\
+						   & = \sqrt{(\frac{1}{2^n n!})^2 (2n)! \cdot 2 \int_{0}^{\frac{\pi}{2}} cos^{2n+1}(x) dx}\\
+			\end{aligned}
+		\end{equation}
+		Since
+		\begin{equation}
+			\int_{0}^{\frac{\pi}{2}} cos^{2n+1}(x) dx = \frac{2 \times 4 \times \cdots \times (2n)}{1\times3\times \cdots \times (2n+1)} 
+		\end{equation}
+		substitute it into the norm equation of $P_n$ yields
+		\begin{equation}
+			||P_n||_2 = \sqrt{(\frac{1}{2^n n!})^2 (2n)! \cdot 2 \cdot \frac{2 \times 4 \times \cdots \times (2n)}{1\times3\times \cdots \times(2n+1)}} = \sqrt{\frac{2}{2n+1}}
+		\end{equation}
+	\end{proof}
 

### 2018-10-06 VV556/HW3/submission.tex
ex2 ok

@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm
+
+\usepackage{graphicx}
 
@@
 \section{Exercise3.2}
+	\begin{enumerate}
+		\item 
+			Consider the projection of $f(x)$ onto $P_0(x)$, $P_1(x)$ and $P_2(x)$ correspondingly
+			\begin{equation}
+				(f, P_0) = \int_{-1}^{1} e^x dx = e - \frac{1}{e}
+			\end{equation}
+
+			\begin{equation}
+				(f, P_1) = \int_{-1}^{1} x e^x dx = \frac{2}{e}
+			\end{equation}
+
+			\begin{equation}
+				(f, P_2) = \int_{-1}^{1} \frac{3x^2 -1}{2} e^x dx = e - \frac{7}{e}
+			\end{equation}
+			As $(P_i, P_j)=0$ when $i \neq j$, $p(x)$ can be written as linear combination of $P_i$
+			\begin{equation}
+				p(x) = a_0 P_0(x) + a_1 P_1(x) + a_2 P_2(x)
+			\end{equation}
+			with coefficient $a_i$ given as
+			\begin{equation}
+				a_i = \frac{(f, P_i)}{(P_i, P_i)} = \frac{2i+1}{2} (f, P_i)
+			\end{equation}
+			Finally
+			\begin{equation}
+				p(x) = 1.1752 P_0(x) + 1.1036 P_1(x) + 0.3578 P_2(x)
+			\end{equation}
+
+		\item 
+		The plot(Fig \ref{fig:comp}) is provided for comparsion.
+
+		\begin{figure}[!htbp]
+			\centering
+			\includegraphics[]{ApproximationCompare.png}
+			\caption{Comparsion of different approximation for $e^x$}
+			\label{fig:comp}
+		\end{figure}
+
+		The distinction is quite obvious and Legendre polynomials does better than taylor series expansion at zero point.
+
+	\end{enumerate}
 
 \section{Exercise3.3}
+	\begin{enumerate}
+		\item
+
+		\item
+
+	\end{enumerate}
 

### 2018-10-06 VV556/HW3/LegendreApproxmation.py

@@ -1,0 +1,27 @@
+import numpy as np
+from matplotlib import pyplot as plt
+import math
+
+
+def f(x):
+    return math.exp(x)
+
+def f_taylor(t):
+    return 1+t+math.pow(t, 2)
+
+def f_legendre(x):
+    return 1.1752 + 1.1036 * x + 0.3578 * (3*math.pow(x, 2) -1)/2
+
+
+N = 501
+
+x = np.linspace(-1, 1, N)
+ex = np.array([f(t) for t in x])
+taylor = np.array([f_taylor(t) for t in x])
+legendre = np.array([f_legendre(t) for t in x])
+
+plt.plot(x, ex, label=r'$f(x)$')
+plt.plot(x, taylor, label=r'Taylor series of $f(x)$ at $x=0$')
+plt.plot(x, legendre, label=r'$p(x)$')
+plt.legend()
+plt.show()

### 2018-10-06 VV556/HW3/LegendreApproxmation.py
add error estimation

@@ -9,8 +9,12 @@ def f(x):
 def f_taylor(t):
     return 1+t+math.pow(t, 2)
 
+a0 = 1.1752
+a1 = 1.1036
+a2 = 0.3578
+
 def f_legendre(x):
-    return 1.1752 + 1.1036 * x + 0.3578 * (3*math.pow(x, 2) -1)/2
+    return a0 + a1 * x + a2 * (3*math.pow(x, 2) -1)/2
 
 
 N = 501
@@ -25,3 +29,5 @@ plt.plot(x, taylor, label=r'Taylor series of $f(x)$ at $x=0$')
 plt.plot(x, legendre, label=r'$p(x)$')
 plt.legend()
 plt.show()
+
+print('Approximation Error: {}'.format(math.sqrt(0.5*(math.exp(2) - math.exp(-2)) - 2 * a0**2 - 2/3 * a1**2 - 2/5 * a2**2)))

### 2018-10-07 VV556/HW3/tex/submission.tex
sepearte folders

--- 2018-10-06 VV556/HW3/submission.tex
@@
 
-		The distinction is quite obvious and Legendre polynomials does better than taylor series expansion at zero point.
+		The distinction is quite obvious and Legendre polynomials does better than taylor series expansion at zero point.\\
+		Further analysis indicates that the approximation error of $p(x)$ is given by
+		\begin{equation}
+			||\delta_2(x)||_2 = ||e^x - p(x)||_2 = \sqrt{\int_{-1}^{1} e^2(x) dx - \sum_{i=0}^{2} \frac{2 a_i ^2}{2i + 1}} = 0.0388
+		\end{equation}
 

### 2018-10-07 VV556/HW3/tex/submission.tex
ex3 ok

@@
 
-		\begin{figure}[!htbp]
+		\begin{figure}[ht]
 			\centering
-			\includegraphics[]{ApproximationCompare.png}
+			\includegraphics[]{../pic/ApproximationCompare.png}
 			\caption{Comparsion of different approximation for $e^x$}
@@
 		\item 
-
+			\begin{proof}
+				Firstly
+				\begin{equation}
+					\int_{-1}^{1} \frac{1}{\sqrt{2}} cos(n \pi x) dx = \frac{1}{\sqrt{2} n \pi} \int_{-n\pi}^{n \pi} cos(x) dx = 0
+				\end{equation}
+				\begin{equation}
+					\int_{-1}^{1} \frac{1}{\sqrt{2}} sin(n \pi x) dx = \frac{1}{\sqrt{2} n \pi} \int_{-n\pi}^{n \pi} sin(x) dx = 0
+				\end{equation}
+				\begin{equation}
+					\int_{-1}^{1} \frac{1}{\sqrt{2}} \frac{1}{\sqrt{2}} dx = \frac{1}{2} \int_{-1}^{1} dx = 1
+				\end{equation}
+				Secondly, when $n \neq m$
+				\begin{equation}
+					\begin{aligned}
+						& \int_{-1}^{1} cos(n \pi x) cos(m \pi x) dx\\
+					  = & \frac{1}{2} \int_{-1}^{1} cos[(n+m) \pi x] + cos[(n-m) \pi x] dx\\
+					  = & \frac{1}{2} [\frac{1}{(n+m)\pi} \int_{-(n+m)\pi}^{(n+m)\pi} cos(x) dx + \frac{1}{(n-m)\pi} \int_{-(n-m)\pi}^{(n-m)\pi} cos(x) dx] = 0
+					\end{aligned}
+				\end{equation}
+				and
+				\begin{equation}
+					\begin{aligned}
+						& \int_{-1}^{1} sin(n \pi x) sin(m \pi x) dx\\
+					  = & - \frac{1}{2} \int_{-1}^{1} cos[(n+m) \pi x] - cos[(n-m) \pi x] dx\\
+					  = & - \frac{1}{2} [\frac{1}{(n+m)\pi} \int_{-(n+m)\pi}^{(n+m)\pi} cos(x) dx - \frac{1}{(n-m)\pi} \int_{-(n-m)\pi}^{(n-m)\pi} cos(x) dx] = 0
+					\end{aligned}
+				\end{equation}
+				Then, when $n = m$ it's obvious that
+				\begin{equation}
+					\int_{-1}^{1} cos(n \pi x) cos(m \pi x) dx = \int_{-1}^{1} cos^2(n \pi x) dx > 0 
+				\end{equation}
+				and
+				\begin{equation}
+					\int_{-1}^{1} sin(n \pi x) sin(m \pi x) dx = \int_{-1}^{1} sin^2(n \pi x) dx > 0 
+				\end{equation}
+				Finally, no matter $n$ equals $m$ or not
+				\begin{equation}
+					\begin{aligned}
+						& \int_{-1}^{1} sin(n \pi x) cos(m \pi x) dx \\
+					  = & \frac{1}{2} [\int_{-1}^{1} sin[(n+m) \pi x] dx + \int_{-1}^{1} sin[(n-m) \pi x] dx]\\
+					  = & \frac{1}{2} [\int_{-(n+m)\pi}^{(n+m)\pi} sin(x) dx + \int_{-(n-m)\pi}^{(n-m)\pi} sin(x) dx]\\
+					  = & 0
+					\end{aligned}
+				\end{equation}
+			\end{proof}
 		\item 
+			\begin{proof}
+				Let
+				\begin{equation}
+					t = \frac{x - (b+a)/2}{(b-a)/2}
+				\end{equation}
+				Then $ dt = \frac{2}{b-a} dx $. With $\{ e_n\}$ being an orthonormal system
+				\begin{equation}
+					\begin{aligned}
+						\int_{a}^{b} \tilde{e}_i(x) \tilde{e}_j(x) dx & = \frac{2}{b-a} \int_{a}^{b} e_i(\frac{x - (b+a)/2}{(b-a)/2}) e_j(\frac{x - (b+a)/2}{(b-a)/2}) dx\\
+						& = \int_{-1}^{1} e_i(t) e_j(t) dt = \delta_{ij}
+					\end{aligned}
+				\end{equation}
+			\end{proof}
 

### 2018-10-07 VM432/HW2/AdiabaticFlameTemp.py
cantera startt

@@ -1,0 +1,10 @@
+import numpy as np
+import cantera as ct
+
+co2 = ct.CarbonDioxide()
+ch4 = ct.Methane()
+o2 = ct.Oxygen()
+h2o = ct.Water()
+n2 = ct.Nitrogen()
+
+co2.TP = 1000, 101325

### 2018-10-09 VM432/HW2/AdiabaticFlameTemp.py
m524 ex2 and 4 ok

@@ -1,10 +1,96 @@
 import numpy as np
 import cantera as ct
+from matplotlib import pyplot as plt
+from scipy import optimize
 
-co2 = ct.CarbonDioxide()
-ch4 = ct.Methane()
-o2 = ct.Oxygen()
-h2o = ct.Water()
-n2 = ct.Nitrogen()
+# Mechane and Air
+# CH4 + 2(O2 + 3.76 N2) -> CO2 + 2 H2O + 2*3.76 N2
+m = 1
+n = 4
+species = [ct.Methane(), ct.Oxygen(), ct.CarbonDioxide(), ct.Water(), ct.Nitrogen()]
+w = np.array([16, 32, 44, 18, 28])
+T_ref = 298
+P_ref = 101325
 
-co2.TP = 1000, 101325
+# Mass ratio of oxidizer and fuel at stoichiometry
+mu = 2 * w[1] / (1 * w[0])
+
+# Mass fraction of fuel in fuel stream
+Yf_1 = 1.0
+
+# Mass fraction of oxidizer in air stream
+Yo_2 = 0.232
+
+# Mixture fraction at stoichiometry
+Zst = 1 / (1 + mu * Yf_1 / Yo_2)
+
+# Mass fraction of CO2 at stoichiometry
+Yco2_st = Yf_1 * Zst * m * w[2] / w[0]
+
+# Mass fraction of H2O at stoichiometry
+Yh2o_st = Yf_1 * Zst * n / 2 * w[3] / w[0]
+
+
+# Equivalence ratio
+def phi(Z):
+    return Z / (1 - Z) * (1 - Zst) / Zst
+
+
+# Unburned mass fraction
+def Y_u(z):
+    y_ch4 = Yf_1 * z
+    y_o2 = Yo_2 * (1 - z)
+    y_co2 = 0
+    y_h2o = 0
+    y_n2 = (1 - Yo_2) * (1 - z)
+    return np.array([y_ch4, y_o2, y_co2, y_h2o, y_n2])
+
+
+# Burned mass fraction
+def Y_b(Z):
+    if Z < Zst:
+        # Fuel deficient
+        y_ch4 = 0
+        y_o2 = Yo_2 * (1 - Z / Zst)
+        y_co2 = Yco2_st * Z / Zst
+        y_h2o = Yh2o_st * Z / Zst
+        y_n2 = (1 - Yo_2) * (1 - Z)
+    else:
+        # Fuel rich
+        y_ch4 = Yf_1 * (Z - Zst) / (1 - Zst)
[…]

### 2018-10-09 VM524/HW1/CalcCovCoef.py

@@ -1,24 +1,31 @@
 import os
 import numpy as np
 import math
+from matplotlib import pyplot as plt
 
-N = 100
+def f():
+    N = 100
 
-X = np.random.rand(N)
-Y = np.random.rand(N)
+    X = np.random.rand(N)
+    Y = np.random.rand(N)
 
-XY = X*Y
-X2 = X*X
-Y2 = Y*Y
+    XY = X*Y
+    X2 = X*X
+    Y2 = Y*Y
 
-E_XY = sum(XY)/N
-E_X2 = sum(X2)/N
-E_Y2 = sum(Y2)/N
-E_X = sum(X)/N
-E_Y = sum(Y)/N
+    E_XY = sum(XY)/N
+    E_X2 = sum(X2)/N
+    E_Y2 = sum(Y2)/N
+    E_X = sum(X)/N
+    E_Y = sum(Y)/N
 
-rho_xy = (E_XY - E_X * E_Y)/math.sqrt(E_X2 * E_Y2)
+    rho_xy = (E_XY - E_X * E_Y)/math.sqrt(E_X2 * E_Y2)
 
-print(rho_xy)
+    return rho_xy
 
-os.system('pause')
+if __name__ == '__main__':
+    seq = [f() for i in range(501)]
+    plt.xlabel('Index')
+    plt.ylabel(r'$\rho_{XY}$')
+    plt.plot(seq)
+    plt.show()

### 2018-10-09 VM524/HW1/CalcEnergySpectrum.py

@@ -1,0 +1,28 @@
+import numpy as np
+from scipy.fftpack import fft,ifft
+import matplotlib.pyplot as plt
+
+fig, ax = plt.subplots(2, 1)
+
+U = np.loadtxt('t3.txt')
+n = len(U)
+
+ax[0].set_xlabel('Sample Index')
+ax[0].set_ylabel('U')
+ax[0].set_title('Original Signal')
+ax[0].plot(U)
+
+uf = fft(U)
+Ek = 0.5 * abs(uf)**2
+
+n2 = int(n/2)
+Ek2 = Ek[range(n2)]
+
+ax[1].set_xscale("log")
+ax[1].set_yscale("log")
+ax[1].set_xlabel('Frequence')
+ax[1].set_ylabel('E')
+ax[1].set_title('Energy Spectrum')
+ax[1].plot(Ek2)
+
+plt.show()

### 2018-10-14 VM524/HW1/tex/submission.tex
20181014

--- 2018-10-05 VM524/HW1/submission.tex
@@
 \usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages
+
+\usepackage{caption}
+\usepackage{graphicx, subfig}
 
@@
   \end{equation}
-  With $E[XY], E[X], E[Y], E[X^2], E[Y^2]$ provided, the correlation coefficient can be therefore calculated.
+  With $E[XY], E[X], E[Y], E[X^2], E[Y^2]$ provided, the correlation coefficient can be therefore calculated. And
+  numerical experiment has been done with 500 times trial.
+   \begin{figure}[H]
+	  	\centering
+	  	\includegraphics[height=10cm]{CovPlot.png}
+	  	\caption{Covariance of random numbers}
+	  	\label{img:cov}
+  	\end{figure}
 \section{Exercise3}
+	Assume the angular speed of the motion is $\omega = 4\pi rad/s$, with radius $r = \frac{d}{2} = \frac{l}{2} = 5cm$, the  mean velocity can be calculated as 
+	\begin{equation}
+		u = \frac{1}{2} \omega  r = 0.1\pi m/s
+	\end{equation}
+	Thus, the energy input rate is estimated as
+	\begin{equation}
+		\epsilon \sim \frac{u^3}{l} \approxeq 9.8696\times10^{-1} (m^2 \cdot s^{-3})
+	\end{equation}
+	With the kinematic viscosity of water taken as $\nu = 1.006\times10^{-6}  (m^2 \cdot s^{-1})$, the Kolmogorov scale is estimated as
+	\begin{equation}
+		\eta \sim (\frac{\nu^3}{\epsilon})^{\frac{1}{4}} \approxeq 3.187\times10^{-2}mm
+	\end{equation}
 
 \section{Exercise4}
-
+	Load the give txt datafile, denote the input 1D data as $u$, then perform FFT on $u$ yields $u^*$. The energy spectrum is calculated as
+	$E(k) = \frac{1}{2} u^*(k)^2$ for each $u^*$. The log plot of the energy spectrum is provided.
+	\begin{figure}[]
+		\centering
+		\includegraphics[angle=90, width=12cm]{EnergySpectrum.png}
+		\caption{Energy Spectrum}
+		\label{img:es}
+	\end{figure}
 \end{document}

### 2018-10-14 VV556/HW4/submission.tex
20181014

--- 2018-09-23 VV556/HW2/submission.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Methods of Applied Mathematics I\\ HW2 \\ % The assignment title
+\huge Methods of Applied Mathematics I\\ HW4 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\section{Exercis2.1}
-	\begin{enumerate}
-		\item 
-			\begin{proof}
+\section{Exercise4.1}
+	Let $f(x)$ be extended as
+	\begin{equation}
+		f(x) = \left\{
+			\begin{aligned}
+				x(\pi - x) & x\in [2n\pi, (2n+1)\pi] \\
+				-x(\pi - x) & x\in [-(2n-1)\pi, 2n\pi] \\
+			\end{aligned}
+		\right.
+	\end{equation}
+	Then $f(x)$ is both odd and periodic. Thus fouier-sine series can be employed.
+	\begin{equation}
+		f(x) = \sum_{n=1}^{\infty} b_n sin(nx)
+	\end{equation} 
+	Coefficients $b_n$ are calculated by
 	\begin{equation}
 		\begin{aligned}
-						RHS & = \frac{1}{4} (||x+y||^2  - ||x-y||^2)\\
-						    & = \frac{1}{4} (<x+y, x+y> - <x-y, x-y>)\\
-						    & = \frac{1}{4} (<x+y, x> + <x+y, y> - <x-y, x> - <x-y, -y>)\\
-						    & = \frac{1}{4} (\overline{<x, x+y>} + \overline{<y, x+y>} - \overline{<x, x-y>} + \overline{<y, x-y>})\\
-						    & = \frac{1}{4} (\overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} + \overline{<y, y>} - \overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} - \overline{<y, y>})\\
-						    & = \frac{1}{2}(\overline{<x,y>} + \overline{<y, x>})\\
-						    & = \frac{1}{2}(<x, y> + <y, x>)\\
-						    & = <x, y> = LHS
-					\end{aligned}
-				\end{equation}
-				The last line is valid as the inner-product is defined on real space s.t. $<x, y>=<y, x>$.
-			\end{proof}
-		\item 
-			\begin{proof}
-				As have been proved aboved
-				\begin{equation}
-					\begin{aligned}
-						   & \frac{1}{4} (||x+y||^2  - ||x-y||^2)\\
-						=  & \frac{1}{2}(<x, y> + <y, x>)
-					\end{aligned}
-				\end{equation}
-				Also, replace $y$ with $iy$ yields
-				\begin{equation}
-					\begin{aligned}
-						  & \frac{i}{4} (||x+iy||^2  - ||x-iy||^2)\\
-						= & \frac{i}{2} (<x, iy> + <iy, x>)\\
-						= & \frac{i}{2} (i<x, y> + \overline{i}<y, x>)\\
-						= & \frac{1}{2} (-<x, y> + <y,x>)
+			b_n  & = \frac{2}{\pi} \int_{0}^{\pi} f(x) sin(nx) dx \\
+				 & = \frac{2}{\pi} \int_{0}^{\pi} x(\pi - x) sin(nx) dx \\
+			     & = \frac{4[1-(-1)^n]}{n^3 \pi} \quad \text{(Integrate by parts)}
 		\end{aligned}
@@
 	\begin{equation}
-					\begin{aligned}
-						RHS & = \frac{1}{4} (||x+y||^2  - ||x-y||^2) - \frac{i}{4} (||x+iy||^2  - ||x-iy||^2)\\
-						    & = \frac{1}{2}(<x, y> + <y, x>) - \frac{1}{2} (-<x, y> + <y,x>)\\
-						    & = <x, y> = LHS
-					\end{aligned}
+		f(x) = \sum_{k=0}^{\infty} \frac{8 sin(2k+1)x}{\pi (2k+1)^3}
 	\end{equation}
-			\end{proof}
+	Taking $x = \frac{\pi}{2}$ yields
+	\begin{equation}
+		\sum_{k=0}^{\infty} \frac{(-1)^k}{(2k+1)^3} = \frac{\pi^3}{32}
+	\end{equation}
+
+\section{Exercise4.2}
+	\begin{enumerate}
 		\item 
 			\begin{proof}
+				The orthogonal property is justified as
 				\begin{equation}
-					\begin{aligned}
-						LHS & = ||x+y||^2 + ||x-y||^2\\
-						    & = <x+y, x+y> + <x-y, x-y>\\
-						    & = <x+y, x> + <x+y, y> + <x-y, x> - <x-y, y>\\
-						    & = \overline{<x, x+y>} + \overline{<y, x+y>} + \overline{<x, x-y>} - \overline{<y, x-y>}\\
-						    & = \overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} + \overline{<y, y>} + \overline{<x, x>} - \overline{<x, y>} - \overline{<y, x>} + \overline{<y, y>}\\
-						    & = 2(<x, x>+<y, y>)\\
-						    & = 2(||x||^2 + ||y||^2) = RHS
-					\end{aligned}
+					\int_{0}^{\pi} (\frac{1}{\sqrt{\pi}})^2 dx = \frac{1}{\pi} \int_{0}^{\pi} dx = 1
+				\end{equation}
+				\begin{equation}
+					\int_{0}^{\pi} (\sqrt{\frac{2}{\pi}}cos(nx))^2 dx = \frac{2}{\pi} \int_{0}^{\pi} cos^2(nx)dx = 1
+				\end{equation}
+				\begin{equation}
+					\int_{0}^{\pi} \frac{1}{\sqrt{\pi}} \sqrt{\frac{2}{\pi}}cos(nx) dx = 0
+				\end{equation}
+				\begin{equation}
+					\int_{0}^{\pi} \sqrt{\frac{2}{\pi}}cos(nx) \sqrt{\frac{2}{\pi}}cos(mx) dx = \frac{2}{\pi} \int_{0}^{\pi} cos(nx) cos(mx) dx = 0
 				\end{equation}
@@
 
-	\end{enumerate}
+		\item
 
-\section{Exercise2.2}
-	\begin{enumerate}
+		\item
+
 		\item

### 2018-10-16 VV556/HW4/submission.tex
4.2-2 basically ok

@@
 				\begin{equation}
-					\int_{0}^{\pi} (\sqrt{\frac{2}{\pi}}cos(nx))^2 dx = \frac{2}{\pi} \int_{0}^{\pi} cos^2(nx)dx = 1
+					\int_{0}^{\pi} (\sqrt{\frac{2}{\pi}}cos(nx))^2 dx = \frac{2}{\pi} \int_{0}^{\pi} cos^2(nx)dx = \frac{1}{\pi} \int_{0}^{\pi} (cos(2nx) + 1) dx = 1
 				\end{equation}
@@
 			\begin{proof}
-
+				It's trival to show both $K=0$ and $K=1$ are valid, and $K=2$ is also justified as
+				\begin{equation}
+					cos^2(x) = \frac{1+cos(2x)}{2}
+				\end{equation}
+				Assume the proposition is also valid for $K=n$, that means
+				\begin{equation}
+					span\{1, cos(x), cos(2x), ... cos(nx)\} = span\{1, cos(x), cos^2(x), ... cos^n(x)\}
+				\end{equation}
+				which indicates that $\exists a_k$ and $b_k (k=0, 1, ..., n)$ s.t. 
+				\begin{equation}
+					cos^n(x) = \sum_{k=0}^{n} a^{(n)}_k \cdot cos(kx)
+				\end{equation}
+				\begin{equation}
+					cos(nx) = \sum_{k=0}^{n} b^{(n)}_k \cdot cos^k(x)
+				\end{equation}
+				When $K = n+1$, the proposition is still valid as
+				\begin{equation}
+					\begin{aligned}
+						cos^{n+1}(x) & = cos(x) \sum_{k=0}^{n} a_k cos(kx)\\
+									 & = a_0 cos(x) + cos(x) \sum_{k=1}^{n-1} a_k cos(kx) + a_n cos(x) cos(nx)\\
+									 & = a_0 cos(x) + \sum_{k=1}^{n-1} \frac{a_k}{2} [cos(k-1)x + cos(k+1)x] + \frac{a_n}{2} [cos(n-1)x + cos(n+1)x]\\
+									 & = \frac{a_1}{2} + (a_0 + \frac{a_2}{2}) cos(x) + \sum_{k=2}^{n-1}\frac{a_{k-1} + a_{k+1}}{2} cos(kx) + \frac{a_n}{2} cos(n+1)x
+					\end{aligned}
+				\end{equation}
+				and
+				\begin{equation}
+					\begin{aligned}
+						cos(n+1)x & = 2 cos(nx)cos(x) - cos(n-1)x\\
+								  & = 2 cos(x)\sum_{k=0}^{n} b^{(n)}_k cos^k(x) - \sum_{k=0}^{n-1} b^{(n-1)}_k cos^k(x)\\
+								  & = -b^{(n-1)}_0 + \sum_{k=0}^{n-1} (2b^{(n)}_k - b^{(n-1)}_k) cos^{k+1}(x) + 2b^{(n)}_k cos^{n+1}(x)
+					\end{aligned}
+				\end{equation}
 			\end{proof}
-
 		\item

### 2018-10-18 VV556/HW4/submission.tex
add ex4 except the last one

@@
 				\end{equation}
-				which indicates that $\exists a_k$ and $b_k (k=0, 1, ..., n)$ s.t. 
+				which indicates that $\exists a^{(n)}_k$ and $b^{(n)}_k (k=0, 1, ..., n)$ s.t. 
 				\begin{equation}
@@
 				\end{equation}
+				and
 				\begin{equation}
@@
 				When $K = n+1$, the proposition is still valid as
+
 				\begin{equation}
 					\begin{aligned}
-						cos^{n+1}(x) & = cos(x) \sum_{k=0}^{n} a_k cos(kx)\\
-									 & = a_0 cos(x) + cos(x) \sum_{k=1}^{n-1} a_k cos(kx) + a_n cos(x) cos(nx)\\
-									 & = a_0 cos(x) + \sum_{k=1}^{n-1} \frac{a_k}{2} [cos(k-1)x + cos(k+1)x] + \frac{a_n}{2} [cos(n-1)x + cos(n+1)x]\\
-									 & = \frac{a_1}{2} + (a_0 + \frac{a_2}{2}) cos(x) + \sum_{k=2}^{n-1}\frac{a_{k-1} + a_{k+1}}{2} cos(kx) + \frac{a_n}{2} cos(n+1)x
+						 cos^{n+1}(x) & = cos(x) cos^n(x)\\
+						 			  & = cos(x) \sum_{k=0}^{n} a^{(n)}_k cos(kx)\\
+									  & = a^{(n)}_0 cos(x) + cos(x) \sum_{k=1}^{n-1} a^{(n)}_k cos(kx) + a^{(n)}_n cos(x) cos(nx)\\
+									  & = a^{(n)}_0 cos(x) + \sum_{k=1}^{n-1} \frac{a^{(n)}_k}{2} [cos(k-1)x + cos(k+1)x] + \frac{a^{(n)}_n}{2} [cos(n-1)x + cos(n+1)x]\\
+									  & = \frac{a^{(n)}_1}{2} + (a^{(n)}_0 + \frac{a^{(n)}_2}{2}) cos(x) + \sum_{k=2}^{n-1}\frac{a^{(n)}_{k-1} + a^{(n)}_{k+1}}{2} cos(kx) + \frac{a^{(n)}_{n-1}}{2}cos(nx) + \frac{a^{(n)}_n}{2} cos(n+1)x\\
+									  & \triangleq \sum_{k=0}^{n+1} a^{(n+1)}_k cos(kx)
 					\end{aligned}
@@
 								  & = 2 cos(x)\sum_{k=0}^{n} b^{(n)}_k cos^k(x) - \sum_{k=0}^{n-1} b^{(n-1)}_k cos^k(x)\\
-								  & = -b^{(n-1)}_0 + \sum_{k=0}^{n-1} (2b^{(n)}_k - b^{(n-1)}_k) cos^{k+1}(x) + 2b^{(n)}_k cos^{n+1}(x)
+								  & = 2 \sum_{k=0}^{n} b^{(n)}_k cos^{k+1}(x) - \sum_{k=0}^{n-1} b^{(n-1)}_k cos^k(x)\\
+								  & = 2 \sum_{k=1}^{n+1} b^{(n)}_{k-1} cos^{k}(x) - [b^{(n-1)}_0 +\sum_{k=1}^{n-1} b^{(n-1)}_k cos^k(x)]\\
+								  & = -b^{(n-1)}_0 + \sum_{k=1}^{n-1} (2b^{(n)}_{k-1} - b^{(n-1)}_k) cos^{k}(x) + 2b^{(n)}_{n-1} cos^{n}(x) + 2b^{(n)}_{n} cos^{n+1}(x)\\
+								  & \triangleq \sum_{k=0}^{n+1}b^{(n+1)}_k cos^k(x)
 					\end{aligned}
 				\end{equation}
+				Thus
+				\begin{equation}
+					span\{1, cos(x), cos(2x), ... , cos(n+1)x\} = span\{1, cos(x), cos^2(x), ... , cos^{n+1}(x)\}
+				\end{equation}
+				Hence, by induction hypothesis, the proposition is valid for all $k\in N$.
 			\end{proof}
 		\item 
-
+			\begin{proof}
+				Given any continous function $f$ over $[-1, 1]$, by Weierstras Approximation Theorem, $\exists p(x)$ over $[-1, 1]$ s.t.
+				\begin{equation}
+					||f-p||_\infty < \epsilon
+				\end{equation}
+				for any $\epsilon > 0$.\\
+				Assume $p$ can be writte as
+				\begin{equation}
+					p(x) = \sum_{i=0}^{N} a_i x^i
+				\end{equation}
+				Then with the change of variables $y = cos(x)$
+				\begin{equation}
+					f(x) = \tilde{f}(y) \approxeq p(y) = \sum_{i=0}^{N} a_i y^i = \sum_{i=0}^{N} a_i cos^i(x)
+				\end{equation}
+				As $cos^i(x)$ can be expressed as the sum of $1, cos(x), cos(2x), ...
+, cos(ix)$ with proper coefficients, $f(x)$ is therefore can be approximated uniformly by finite linear combinations of $1, cos(x), cos(2x), ...
+$.
+			\end{proof}
 		\item 
-
+			\begin{proof}
+				As have been proved above, for any continous function $f$ over $[0,\pi]$, it can be approximated by linear combinations of $1, cos(x), cos(2x), ...
+$, which means that $\exists g \in span\{B\}$ s.t.
+				\begin{equation}
+					||f-g||_\infty < \epsilon
+				\end{equation}
+				for any $\epsilon > 0$.\\
+				Thus, span\{B\} is dense in $C([0, \pi])$ in the $||\cdot||_\infty$ norm.
+			\end{proof}
 		\item 
-
+			\begin{proof}
+				As have been proved aboved, $\forall f \in C[a, b]$, $\exists p \in \mathbb{P}[a, b]$ s.t.
+				\begin{equation}
+					||f-p||_\infty = \sup_{x\in[a, b]}|f(x)-p(x)| < \frac{\epsilon}{\sqrt{b-a}}
+				\end{equation}
+				for any $\epsilon > 0$.\\
+				Then for the $L^2$ norm
+				\begin{equation}
+					||f-p||_2 = \sqrt{\int_{a}^{b} (f(x) - p(x))^2 dx} \leq \sqrt{(b-a) \cdot \max_{x\in[a, b]}(f(x)-p(x))^2} < \epsilon
+				\end{equation}
+				Thus, span\{B\} is dense in $C([0, \pi])$ in the $||\cdot||_2$ norm.
+			\end{proof}
 		\item 
-
+			Not figured out...
 	\end{enumerate}

### 2018-10-21 VM432/HW2/AdiabaticFlameTemp.py
fix mole to mass

@@ -73,7 +73,7 @@ def Y_b(Z):
 def species_enthalpy(T):
     for k in range(len(spec)):
         spec[k].TP = T, P_ref
-    return np.array([c.enthalpy_mole for c in spec])
+    return np.array([c.enthalpy_mass for c in spec])
 
 
 def calc_temp(Z):

### 2018-10-24 VV556/HW5/submission.tex
add ex1 & 2

--- 2018-10-14 VV556/HW4/submission.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Methods of Applied Mathematics I\\ HW4 \\ % The assignment title
+\huge Methods of Applied Mathematics I\\ HW5 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\section{Exercise4.1}
-	Let $f(x)$ be extended as
-	\begin{equation}
-		f(x) = \left\{
-			\begin{aligned}
-				x(\pi - x) & x\in [2n\pi, (2n+1)\pi] \\
-				-x(\pi - x) & x\in [-(2n-1)\pi, 2n\pi] \\
-			\end{aligned}
-		\right.
-	\end{equation}
-	Then $f(x)$ is both odd and periodic. Thus fouier-sine series can be employed.
-	\begin{equation}
-		f(x) = \sum_{n=1}^{\infty} b_n sin(nx)
-	\end{equation} 
-	Coefficients $b_n$ are calculated by
+\section{Exercise5.1}
+	\begin{proof}
+		Suppose $\dim(U) = N$ and $\dim(V)=M$. Since all the norm are equivalent in finite-dimension spaces, the linear operator $L$ can be represented in matrix form as $\{l_{ji}\}$. Then
 		\begin{equation}
 			\begin{aligned}
-			b_n  & = \frac{2}{\pi} \int_{0}^{\pi} f(x) sin(nx) dx \\
-				 & = \frac{2}{\pi} \int_{0}^{\pi} x(\pi - x) sin(nx) dx \\
-			     & = \frac{4[1-(-1)^n]}{n^3 \pi} \quad \text{(Integrate by parts)}
+				||Lu|| & = \sqrt{\sum_{j=1}^{M}\Big|\sum_{i=1}^{N}l_{ji} u_i\Big|^2}\\
+					   & \leq \sqrt{\sum_{j=1}^{M} \Big[\sum_{i=1}^{N} l_{ji}^2 \sum_{i=1}^{N} u_{i}^2\Big]} \quad \text{(Cauchy-Schwartz)}\\
+					   & = \sqrt{\sum_{j=1}^{M} ||u||^2\sum_{i=1}^{N} l_{ji}^2}
+					    = ||u||\sqrt{\sum_{j=1}^{M}\sum_{i=1}^{N} l_{ji}^2}
 			\end{aligned}
 		\end{equation}
-	Thus
+		Hence, $L$ is bounded.
+	\end{proof}
+
+\section{Exercise5.2}
+	\begin{proof}
+		Denote $w = \alpha u + \beta v$, then
 		\begin{equation}
-		f(x) = \sum_{k=0}^{\infty} \frac{8 sin(2k+1)x}{\pi (2k+1)^3}
+			(Tw)(x) = xw(x) = x(\alpha u(x) + \beta v(x)) = \alpha xu(x) + \beta xv(x) = \alpha (Tu)(x) + \beta (Tv)(x)
 		\end{equation}
-	Taking $x = \frac{\pi}{2}$ yields
+		Hence, $T$ is linear.\\ Further
 		\begin{equation}
-		\sum_{k=0}^{\infty} \frac{(-1)^k}{(2k+1)^3} = \frac{\pi^3}{32}
-	\end{equation}
-
-\section{Exercise4.2}
-	\begin{enumerate}
-		\item 
-			\begin{proof}
-				The orthogonal property is justified as
-				\begin{equation}
-					\int_{0}^{\pi} (\frac{1}{\sqrt{\pi}})^2 dx = \frac{1}{\pi} \int_{0}^{\pi} dx = 1
-				\end{equation}
-				\begin{equation}
-					\int_{0}^{\pi} (\sqrt{\frac{2}{\pi}}cos(nx))^2 dx = \frac{2}{\pi} \int_{0}^{\pi} cos^2(nx)dx = 1
-				\end{equation}
-				\begin{equation}
-					\int_{0}^{\pi} \frac{1}{\sqrt{\pi}} \sqrt{\frac{2}{\pi}}cos(nx) dx = 0
-				\end{equation}
-				\begin{equation}
-					\int_{0}^{\pi} \sqrt{\frac{2}{\pi}}cos(nx) \sqrt{\frac{2}{\pi}}cos(mx) dx = \frac{2}{\pi} \int_{0}^{\pi} cos(nx) cos(mx) dx = 0
+			||T|| = \sup_{u\in\mathbb{C}[0, 1]}\frac{||Tu||}{||u||} = \sup_{u\in\mathbb{C}[0, 1]} \frac{\sup_{x\in[0, 1]}|xu(x)|}{\sup_{x\in[0, 1]}|u(x)|} = \sup_{u\in\mathbb{C}[0, 1]} \frac{\sup_{x\in[0, 1]}|u(x)|}{\sup_{x\in[0, 1]}|u(x)|} = 1
 		\end{equation}
 	\end{proof}
-		\item 
-			\begin{proof}
 
-			\end{proof}
-
-		\item
-
-		\item
-
-		\item
-
-		\item
-
-	\end{enumerate}
+\section{Exercise5.3}
 

### 2018-11-06 VM524/HW3/submission.tex
Q1 ok

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages
\usepackage{extarrows}

\usepackage{caption}
\usepackage{graphicx, subfig}

\usepackage{algorithm, algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}} %Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm

\usepackage{listings}
\lstset{language=Matlab}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Turbulence \\ HW3 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yu Cang \\ 018370210001}

\date{\normalsize \today}

\begin{document}

\maketitle

\section{Exercise1}
	When the gravity is considered, the N-S equation is written as
	\begin{equation}
		\rho \frac{\partial u_j}{\partial t} + \rho u_k \frac{\partial u_j}{\partial x_k} = -\frac{\partial p}{\partial x_j} + \mu \frac{\partial^2 u_j}{\partial x_k \partial x_k} + \rho g_j
	\end{equation}
	Decompose the density into mean and fluctuation as $\rho = \rho_0 + \tilde{\rho}$, and substitute into the equation above yields
	\begin{equation}\label{eq:raw}
		\rho_0 \frac{\partial u_j}{\partial t} + \tilde{\rho} \frac{\partial u_j}{\partial t} + \rho_0 u_k \frac{\partial u_j}{\partial x_k} + \tilde{\rho} \frac{\partial u_j}{\partial x_k} = -\frac{\partial p}{\partial x_j} + \mu \frac{\partial^2 u_j}{\partial x_k \partial x_k} + \rho_0 g_j + \tilde{\rho} g_j
	\end{equation}
 	The 2nd and 4th term in the LHS of (\ref{eq:raw}) can be neglected as $\tilde{\rho} << \rho_0$. Assuming $\frac{\mu}{\rho_0} \approxeq \frac{\mu}{\rho} = \nu$ yields
 	\begin{equation}\label{eq:rs}
 		\frac{\partial u_j}{\partial t} + u_k \frac{\partial u_j}{\partial x_k} = - \frac{1}{\rho_0} \frac{\partial p}{\partial x_j} + \nu \frac{\partial^2 u_j}{\partial x_k \partial x_k} + g_j + g_j \frac{\tilde{\rho}}{\rho_0} 
 	\end{equation}
 	When the EOS for ideal gas($p = \rho R T$) is adopted, $\rho T$ can be assumed to be constant when the change of $p$ is negligible and velocity is small. Hence
 	\begin{equation}
 		(\rho_0 + \tilde{\rho})(\bar{T} + \tilde{T}) = \rho_0 \bar{T}
 	\end{equation}
 	Thus
 	\begin{equation}
 		\frac{\tilde{\rho}}{\rho_0} + \frac{\tilde{T}}{\bar{T}} = 0
 	\end{equation}
 	This is achieved by neglecting the 2nd-order small quantities.
 	\newpage
 	Substitute into (\ref{eq:rs}) yields
 	\begin{equation}\label{eq:boussineq}
 		\frac{\partial u_j}{\partial t} + u_k \frac{\partial u_j}{\partial x_k} = - \frac{1}{\rho_0} \frac{\partial p}{\partial x_j} + \nu \frac{\partial^2 u_j}{\partial x_k \partial x_k} + g_j - g_j \frac{\tilde{T}}{\bar{T}}
 	\end{equation}
 	Decompose the velocity and pressure into mean and fluctuation as
 	\begin{equation}
 		\begin{aligned}
 			u_j & = U_j + u_j'\\
 			p & = P + p'
 		\end{aligned}
 	\end{equation}
 	Substitute into (\ref{eq:boussineq})
 	\begin{equation}
 		\frac{\partial (U_j + u_j')}{\partial t} + (U_k + u_k') \frac{\partial (U_j + u_j')}{\partial x_k} = - \frac{1}{\rho_0} \frac{\partial (P + p')}{\partial x_j} + \nu \frac{\partial^2 (U_j + u_j')}{\partial x_k \partial x_k} + g_j - g_j \frac{\tilde{T}}{\bar{T}}
 	\end{equation}
 	Multiply $u_j'$ and take ensemble average yields
 	\begin{equation}\label{eq:ea}
 		LHS \triangleq \overline{u_j' \frac{\partial u_j'}{\partial t}} + U_k \overline{u_j' \frac{\partial u_j'}{\partial x_k}} + \overline{u_j' u_k'}\frac{\partial U_j}{\partial x_k} + \overline{u_j' u_k' \frac{\partial u_j'}{\partial x_k}} = -\frac{1}{\rho_0} \overline{u_j' \frac{\partial p'}{\partial x_j}} + \nu \overline{u_j'\frac{\partial^2 u_j'}{\partial x_k \partial x_k}} + \frac{g_j}{\bar{T}}\overline{u_j' \tilde{T}} \triangleq RHS
 	\end{equation}
 	Denote $k_T = \frac{1}{2} \overline{u_j' u_j'}$ and follow from the continuity equation
 	\begin{equation}\label{eq:bl}
 		LHS = \frac{\bar{D}k_T}{\bar{D}t} + \overline{u_j' u_k'}\frac{\partial U_j}{\partial x_k} + \frac{1}{2}\frac{\partial}{\partial x_k}\overline{u_k' u_j' u_j'}
 	\end{equation}
 	Since
 	\begin{equation}
 		\overline{u_j'\frac{\partial^2 u_j'}{\partial x_k \partial x_k}} = \overline{\frac{\partial}{\partial x_k} \big(u_j'\frac{\partial u_j'}{\partial x_k}\big)} - \overline{\frac{\partial u_j'}{\partial x_k} \frac{\partial u_j'}{\partial x_k}} = \frac{\partial^2 k_T}{\partial x_k \partial x_k} - \overline{\frac{\partial u_j'}{\partial x_k} \frac{\partial u_j'}{\partial x_k}}
 	\end{equation}
 	then, also follows from the continuity equation
 	\begin{equation}\label{eq:br}
 		RHS = -\frac{1}{\rho_0} \frac{\partial \overline{u_j' p'}}{\partial x_j} + \nu \Big(\frac{\partial^2 k_T}{\partial x_k \partial x_k} - \overline{\frac{\partial u_j'}{\partial x_k} \frac{\partial u_j'}{\partial x_k}}\Big) + \frac{g_j}{\bar{T}}\overline{u_j' \tilde{T}}
 	\end{equation}
 	Combining (\ref{eq:bl}) and (\ref{eq:br}) yields the turbulent kinetic energy equation for the buoyancy case
 	\begin{equation}
 		\frac{\bar{D}k_T}{\bar{D}t} = -\overline{u_j' u_k'}\frac{\partial U_j}{\partial x_k} - \frac{1}{2}\frac{\partial}{\partial x_k}\overline{u_k' u_j' u_j'} -\frac{1}{\rho_0} \frac{\partial \overline{u_j' p'}}{\partial x_j} + \nu \Big(\frac{\partial^2 k_T}{\partial x_k \partial x_k} - \overline{\frac{\partial u_j'}{\partial x_k} \frac{\partial u_j'}{\partial x_k}}\Big) + \frac{g_j}{\bar{T}}\overline{u_j' \tilde{T}}
 	\end{equation}

\section{Exercise 2}

\end{document}

### 2018-11-06 VM524/HW3/submission.tex
Q2 done

@@
  	\end{equation}
+	where
+ 	\begin{equation}
+ 	\frac{\bar{D}}{\bar{D}t} = \frac{\partial}{\partial t} + U_k \frac{\partial}{\partial x_k}
+ 	\end{equation}
  	Since
@@
  	\end{equation}
+ 	\newpage
 
 \section{Exercise 2}
-
+	The governing equation for the passive scalar $\phi$ is
+	\begin{equation}\label{eq:passive}
+		\frac{D \phi}{D t} = \Gamma \triangledown^2 \phi
+	\end{equation}
+	The gradient of (\ref{eq:passive}) is
+	\begin{equation}
+		\frac{\partial \triangledown \phi}{\partial t} + \triangledown(\vec{U}\cdot\triangledown\phi) = \Gamma \triangledown^2(\triangledown\phi)
+	\end{equation}
+	An vector operation identity is used
+	\begin{equation}
+		\triangledown(\vec{f}\cdot\vec{g}) = (\vec{g}\cdot\triangledown)\vec{f} + \vec{g} \times (\triangledown \times \vec{f}) + (\vec{f} \cdot \triangledown)\vec{g} + \vec{f} \times (\triangledown \times \vec{g})
+	\end{equation}
+	Thus
+	\begin{equation}
+		\begin{aligned}
+			\triangledown(\vec{U} \cdot \triangledown\phi) 
+			& = (\triangledown\phi \cdot \vec{U})\vec{U} + \triangledown\phi \times (\triangledown \times \vec{U}) + (\vec{U} \cdot \triangledown) \triangledown \phi + \vec{U} \times (\triangledown \times \triangledown\phi)\\
+			& = (\triangledown\phi \cdot \vec{U})\vec{U} + \triangledown\phi \times (\triangledown \times \vec{U}) + (\vec{U} \cdot \triangledown) \triangledown \phi
+		\end{aligned}
+	\end{equation}
+	Hence, the governing equation for $\triangledown\phi$ is
+	\begin{equation}\label{eq:gp}
+		\frac{D}{Dt}\triangledown\phi = -(\vec{U} \cdot \triangledown\phi)\vec{U} - \triangledown\phi \times (\triangledown \times \vec{U}) + \Gamma \triangledown^2(\triangledown\phi)  
+	\end{equation}
+	Denote $\vec{W} = \triangledown \phi$, then (\ref{eq:gp}) can be re-written as
+	\begin{equation}
+		\frac{D}{Dt} \vec{W} = -(\vec{U} \cdot \vec{W})\vec{U} - \vec{W} \times (\triangledown \times \vec{U}) + \Gamma \triangledown^2 \vec{W} \triangleq RHS
+	\end{equation}
+	Inner product with $\vec{W}$, the 2nd term in $RHS$ vanishes, remaining parts yields
+	\begin{equation}
+		\frac{D}{Dt} \big(\frac{1}{2}|\vec{W}|^2\big) = -(\vec{U} \cdot \vec{W})^2  + \Gamma \vec{W} \triangledown^2 \vec{W}
+	\end{equation}
+	since
+	\begin{equation}
+			\vec{W} \triangledown^2 \vec{W} = \triangledown^2 \big(\frac{1}{2}|\vec{W}|^2\big) - \triangledown \vec{W} : \triangledown \vec{W}
+	\end{equation}
+	then, the governing equation for the scalar gradient energy $\triangledown\phi \cdot \triangledown\phi$ is
+	\begin{equation}
+		\frac{D}{Dt} \big(\frac{1}{2}|\vec{W}|^2\big) = -(\vec{U} \cdot \vec{W})^2  + \Gamma \Bigg(\triangledown^2 \big(\frac{1}{2}|\vec{W}|^2\big) - \triangledown \vec{W} : \triangledown \vec{W}\Bigg)
+	\end{equation}
+	Characteristic scales of dissipation term is estimated as
+	\begin{equation}
+		\Gamma \triangledown^2(\frac{1}{2} |\vec{W}|^2) \sim \Gamma \frac{\phi^2}{L^4}
+	\end{equation}
 \end{document}

### 2018-11-09 VV556/HW7/submission.tex
start...

--- 2018-10-24 VV556/HW5/submission.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Methods of Applied Mathematics I\\ HW5 \\ % The assignment title
+\huge Methods of Applied Mathematics I\\ HW7 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\author{Yu Cang \\ 018370210001} % Your name
+\author{Yu Cang \quad 018370210001\\ Zhiming Cui \quad 017370910006} % Your name
 
@@
 
-\section{Exercise5.1}
+\section{Exercise7.1}
+	\begin{enumerate}
+		\item 
 			\begin{proof}
-		Suppose $\dim(U) = N$ and $\dim(V)=M$. Since all the norm are equivalent in finite-dimension spaces, the linear operator $L$ can be represented in matrix form as $\{l_{ji}\}$. Then
+				Since $|\lambda|=1$, then
 				\begin{equation}
-			\begin{aligned}
-				||Lu|| & = \sqrt{\sum_{j=1}^{M}\Big|\sum_{i=1}^{N}l_{ji} u_i\Big|^2}\\
-					   & \leq \sqrt{\sum_{j=1}^{M} \Big[\sum_{i=1}^{N} l_{ji}^2 \sum_{i=1}^{N} u_{i}^2\Big]} \quad \text{(Cauchy-Schwartz)}\\
-					   & = \sqrt{\sum_{j=1}^{M} ||u||^2\sum_{i=1}^{N} l_{ji}^2}
-					    = ||u||\sqrt{\sum_{j=1}^{M}\sum_{i=1}^{N} l_{ji}^2}
-			\end{aligned}
-		\end{equation}
-		Hence, $L$ is bounded.
-	\end{proof}
-
-\section{Exercise5.2}
-	\begin{proof}
-		Denote $w = \alpha u + \beta v$, then
-		\begin{equation}
-			(Tw)(x) = xw(x) = x(\alpha u(x) + \beta v(x)) = \alpha xu(x) + \beta xv(x) = \alpha (Tu)(x) + \beta (Tv)(x)
-		\end{equation}
-		Hence, $T$ is linear.\\ Further
-		\begin{equation}
-			||T|| = \sup_{u\in\mathbb{C}[0, 1]}\frac{||Tu||}{||u||} = \sup_{u\in\mathbb{C}[0, 1]} \frac{\sup_{x\in[0, 1]}|xu(x)|}{\sup_{x\in[0, 1]}|u(x)|} = \sup_{u\in\mathbb{C}[0, 1]} \frac{\sup_{x\in[0, 1]}|u(x)|}{\sup_{x\in[0, 1]}|u(x)|} = 1
+					||e_\lambda^{(N)}||_2 = \frac{1}{\sqrt{N+1}} \sqrt{\sum_{i=0}^{N} \lambda^{2i}} =  \frac{1}{\sqrt{N+1}} \sqrt{N+1} = 1
 				\end{equation}
 			\end{proof}
+		\item
 
-\section{Exercise5.3}
+		\item
+
+		\item
+
+	\end{enumerate}
+
+\section{Exercise7.2}
+
+\section{Exercise7.3}
+
+\section{Exercise7.4}
 

### 2018-11-10 VV556/HW7/submission.tex
add ex3&4

@@
 \section{Exercise7.2}
+	\begin{enumerate}
+		\item
+
+		\item
+
+		\item
+
+		\item
+
+		\item
+
+	\end{enumerate}
 
 \section{Exercise7.3}
+	\begin{enumerate}
+		\item 
+			\begin{proof}
+				It's clear that $L^{-1}$ is the differentiate operator, and $L^{-1}$ is unbounded. So $L$ has unbounded inverse.\\
+				Since the domain of $L$ is composed of square-integrable functions over $[0,1]$, say
+				\begin{equation}
+					\int_{0}^{1} f^2(x) dx < \infty
+				\end{equation}
+				An element within the range of $L$ is
+				\begin{equation}
+					g(x) = \int_{0}^{x} f(t) dt
+				\end{equation}
+				Then, if $f(x)$ is a polynomial in $L^2$ , it must be bounded over $[0, 1]$ as it is continous.
+Denote the supreme of $f(x)$ as $M$, then $g(x) \leq Mx$.
+Hence $g(x)$ is square-integrable over $[0,1]$, say
+				\begin{equation}
+					\int_{0}^{1} g^2(x) dx \leq M^2 \int_{0}^{1} x^2 dx < \infty
+				\end{equation}
+				Clearly, the domain of $L$ doesn't contain all the polynomials and therefore the range of $L$ is open and incomplete.
+The boundary of the range of $L$ are the limits of squences like $f_n(x) = nx$ when $n\rightarrow \infty$.\\
+				Hence, the state of $L$ is $(III, 1_n)$.
+			\end{proof}
+		\item 
+			\begin{equation}
+				L^* = L
+			\end{equation}
+
+	\end{enumerate}
 
 \section{Exercise7.4}
+	\begin{proof}
+		For $p = 1$
+		\begin{equation}
+			\begin{aligned}
+				RHS & \triangleq ||(a_n)||_1 \cdot ||(b_n)||_1 = \sum_{i=0}^{\infty} |a_i| \cdot \sum_{j=0}^{\infty} |b_j| = \sum_{n=0}^{\infty} \sum_{i+j=n} |a_i||b_j|\\
+				 & \geq \sum_{n=0}^{\infty} |\sum_{i+j=n} a_i b_j| = \sum_{n=0}^{\infty} |c_n| = ||(c_n)||_1 \triangleq LHS
+			\end{aligned}
+		\end{equation} 
+		For $p>1$, take $q > 0$ s.t. $\frac{1}{p} + \frac{1}{q} = 1$\\
+		Then, using the Holder's inequality
+		\begin{equation}
+			\begin{aligned}
+				LHS & \triangleq ||(c_n)||_p = \Big(\sum_{n=0}^{\infty} |c_n|^p\Big)^{\frac{1}{p}} = \Big(\sum_{n=0}^{\infty} \Big|\sum_{i+j=n}a_i b_j\Big|^p\Big)^{\frac{1}{p}}\\
+				& = \Big(\sum_{n=0}^{\infty} \Big|\sum_{i+j=n}a_i b_j^\frac{1}{p} b_j^{\frac{1}{q}}\Big|^p\Big)^{\frac{1}{p}} \leq  \Big(\sum_{n=0}^{\infty} \Big|\sum_{i+j=n}\Big(|a_i| |b_j|^\frac{1}{p}\Big) |b_j|^{\frac{1}{q}}\Big|^p\Big)^{\frac{1}{p}}\\
+				& \leq \Big(\sum_{n=0}^{\infty} \Big[\Big(\sum_{i+j=n}|a_i|^p |b_j|\Big)^\frac{1}{p} \Big(\sum_{j=0}^{n}|b_j|\Big)^\frac{1}{q}\Big]^p\Big)^{\frac{1}{p}} \\ 
+				& = \Bigg[\sum_{n=0}^{\infty} \Big(\sum_{i+j=n}|a_i|^p |b_j|\Big) \Big(\sum_{j=0}^{n}|b_j|\Big)^\frac{p}{q}\Bigg]^\frac{1}{p} \\
+				& \leq \Big(\sum_{i=0}^{\infty}|a_i|^p\Big)^\frac{1}{p}\cdot\Big(\sum_{j=0}^{\infty}|b_j|\Big)^\frac{1}{p}\cdot\Big(\sum_{j=0}^{\infty}|b_j|\Big)^\frac{1}{q}\\
+				& = ||(a_n)||_p \cdot ||(b_n)||_1 \triangleq RHS
+			\end{aligned}
+		\end{equation}
+	\end{proof}
 

### 2018-11-10 VV556/HW7/submission.tex
add ex2

@@
 		\item 
-
+			Not figured out...
 		\item
-
+			\begin{equation}
+				Ru = \lambda u
+			\end{equation} 
+			Denote $u = (a_0, a_1, ..., a_n, ...)$, then
+			\begin{equation}
+				\begin{aligned}
+					0 &= \lambda a_0\\
+					a_0 &= \lambda a_1\\
+					...\\
+				\end{aligned}
+			\end{equation}
 	\end{enumerate}
@@
 		\item 
-
+			\begin{proof}
+				Take a subset of the domain of $L^{-1}$, which is denoted as $M$ and is defined as
+				\begin{equation}
+					M = \Big\{u \in L^2\big([0, 1]\big) \Big| \exists \xi >0 \  \forall x \in [0, \xi] \ u(x) = 0\Big\}
+				\end{equation}
+				Given any $u(x) \in L^2$, then
+				\begin{equation}
+					\int_{0}^{1} u^2(x) dx < \infty
+				\end{equation}
+				Hence $u(x)$ is bounded over $[0, 1]$. \\
+				Let 
+				\begin{equation}
+					T \triangleq \sup \limits_{x\in [0, 1]} |u(x)|
+				\end{equation}
+				then, $\forall \epsilon > 0$, $\exists v \in M $ s.t.
+				\begin{equation}
+					v(x) = \Bigg\{\begin{aligned}
+					0, &\quad x \in [0, \delta]\\
+					u(x), &\quad x \in (\delta, 1]
+					\end{aligned}
+				\end{equation}
+				where $\delta = \frac{\epsilon}{T^2}$. Therefore
+				\begin{equation}
+					d(u, v) \triangleq ||u-v||_2 = \int_{0}^{1} [u(x) - v(x)]^2 dx = \int_{0}^{\delta} u^2(x) dx \leq T^2 \delta = \epsilon
+				\end{equation}
+				which indicates that $M$ is dense in $L^2$, so do the domain of $L^{-1}$.
+			\end{proof}
 		\item 
-
+			\begin{proof}
+				\begin{equation}
+					||L|| = \sup_{u\in L^2}\frac{||Lu||_2}{||u||_2} = \sup_{u\in L^2}\frac{||xu(x)||_2}{||u(x)||_2} = \sup_{u\in L^2}\frac{|x| ||u||_2}{||u||_2} = \sup_{x\in [0, 1]} |x| = 1
+				\end{equation}
+				and
+				\begin{equation}
+					||L^{-1}|| = \sup_{u\in L^2}\frac{||L^{-1}u||_2}{||u||_2} = \sup_{x\in [0, 1]} \frac{1}{|x|} = \infty
+				\end{equation}
+				hence $L^{-1}$ is unbounded.
+			\end{proof}
 		\item 
-
+			The state of $L$ is $(I, 1_n)$.\\
+			The state of $L^{-1}$ is $(I, 2_c)$.
 		\item 
-
+			Yes
 		\item 
-
+			Since
+			\begin{equation}
+				[(L - \lambda I)u] (x) = (Lu)(x) - \lambda u(x) = (x-\lambda) u(x)
+			\end{equation}
+			The inverse of $(L - \lambda I)$ always exists, therefore $\sigma(L) = \emptyset$.
 	\end{enumerate}

### 2018-11-15 VM532/HW1/submission.tex
fix choice of thermal conductivity and specific heat, integral of source term still not correct

@@
 \section{PROBLEM 2}
+When it comes to constant property
+\begin{equation}
+	\frac{\partial}{\partial y}(k\frac{\partial T}{\partial y}) = k \frac{\partial T^2}{\partial^2 y}
+\end{equation}
+Since $i=C_p T$ when considering ideal gas
+\begin{equation}
+	\rho u \frac{\partial i}{\partial x} + \rho v \frac{\partial i}{\partial y} = \rho C_p (u\frac{\partial T}{\partial x} + v \frac{\partial T}{\partial y})
+\end{equation}
+As $(\frac{\partial u}{\partial y})^2$ is a small term compared to other terms, it can be seen as 0.\\
+(Sorry, haven't figured out how to eliminate $\frac{\partial p}{\partial x}$...)
 

### 2018-11-15 VV556/HW6/submission.tex
fix choice of thermal conductivity and specific heat, integral of source term still not correct

--- 2018-11-09 VV556/HW7/submission.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Methods of Applied Mathematics I\\ HW7 \\ % The assignment title
+\huge Methods of Applied Mathematics I\\ HW6 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\section{Exercise7.1}
+\section{Exercise6.1}
 	\begin{enumerate}
@@
 			\begin{proof}
-				Since $|\lambda|=1$, then
+				With the Cauchy-Schwartz inequality
 				\begin{equation}
-					||e_\lambda^{(N)}||_2 = \frac{1}{\sqrt{N+1}} \sqrt{\sum_{i=0}^{N} \lambda^{2i}} =  \frac{1}{\sqrt{N+1}} \sqrt{N+1} = 1
+					\sum_{n=1}^{\infty} |y_n|^2 = \sum_{n=1}^{\infty} (\sum_{m=1}^{\infty} a_{nm}x_m)^2 \leq \sum_{n=1}^{\infty} \Big[\sum_{m=1}^{\infty}x_m^2 \sum_{m=1}^{\infty} a_{nm}^2\Big] = \Big(\sum_{m=1}^{\infty}x_m^2\Big) \Big(\sum_{n=1}^{\infty} \sum_{m=1}^{\infty} a_{nm}^2\Big) < \infty
+				\end{equation}
+				The last setp is valid as $x$ is a square-summable sequence and $\sum_{m,n=1}^{\infty} a_{nm}^2 = M^2 < \infty$.\\
+				Hence $y\in l^2$.
+			\end{proof}
+		\item 
+			According to the definition of $L$
+			\begin{equation}
+				L e_j = (a_{1j}, a_{2j}, ... , a_{nj})
+			\end{equation}
+			Thus
+			\begin{equation}
+				L_{ij} = <e_i, L e_j> = a_{ij}
+			\end{equation}
+		\item 
+			\begin{proof}
+				Follow from the first part
+				\begin{equation}
+					||y||_2 \leq ||x||_2 \cdot M
+				\end{equation}
+				Thus
+				\begin{equation}
+					||L|| = \sup_{x \in l^2} \frac{||Lx||_2}{||x||_2} \leq \frac{||x||_2 M}{||x||_2} = M
 				\end{equation}
@@
 		\item 
-
-		\item
-
-		\item
+			\begin{proof}
+				Denote $(e_j)$ being the standard basis, then
+				\begin{equation}
+					L e_j = (0, 0, ..., \frac{1}{j}, 0, ... , 0)
+				\end{equation}
+				Thus
+				\begin{equation}
+					a_{ij} \triangleq L_{ij} = \delta_{ij}\frac{1}{j}
+				\end{equation}
+				Hence
+				\begin{equation}
+					\sum_{n, m = 1}^{\infty} |a_{nm}|^2 = \sum_{n=1}^{\infty} \frac{1}{n^2} = \frac{\pi^2}{6}
+				\end{equation}
+				which indicates that $L$ is a Hilbert-Schmidt operator.\\
+				Let $x_0 = (1, 0, 0, ... , 0)$, then
+				\begin{equation}
+					||L|| = \sup_{x \in l^2} \frac{||Lx||_2}{||x||_2} \geq \frac{||Lx_0||_2}{||x_0||_2} = \frac{||(1, 0, ...)||_2}{||(1, 0, ...)||_2} = 1
+				\end{equation}
+				Also, with the Cauchy-Schwartz inequality
+				\begin{equation}
+					||L|| = \sup_{x \in l^2} \frac{||Lx||_2}{||x||_2} = \sup_{x \in l^2} \frac{\sqrt{\sum_{n=1}^{\infty} (\frac{x_n}{n})^2}}{||x||_2} \leq \sup_{x \in l^2} \frac{\sqrt{\sum_{n=1}^{\infty} x_n^2}}{||x||_2} = \sup_{x \in l^2} \frac{||x||_2}{||x||_2} = 1
+				\end{equation}
+				Therefore $||L|| = 1$.\\
+				It can be seen that $M$ is the upper bound of $||L||$.
+			\end{proof}
 
@@
 
-\section{Exercise7.2}
-
-\section{Exercise7.3}
-
-\section{Exercise7.4}
-
 \end{document}

### 2018-11-15 VV570/HW6/submission.tex
fix choice of thermal conductivity and specific heat, integral of source term still not correct

@@
 \section{Integration}
+\begin{enumerate}
+	\item 
+		The number of nodes is too small s.t. the order of error is too large.
+	\item 
+		Denote
+		\begin{equation}
+			E(f) = \int_{a}^{b} f(x)dx - (b-a)f(\frac{a+b}{2})
+		\end{equation}
+		Thus
+		\begin{equation}
+			E(1) = (b-a) - (b-a) = 0
+		\end{equation}
+		\begin{equation}
+			E(x) = \frac{b^2-a^2}{2} - (b-a)\frac{b+a}{2} = 0
+		\end{equation}
+		and
+		\begin{equation}
+			E(x^2) = \frac{b^3-a^3}{3} - (b-a)(\frac{a+b}{2})^2 \neq 0
+		\end{equation}
+		Hence, the degree of this quadrature formula is $1$.\\
+		The kernel is determined as
+		\begin{equation}
+			\begin{aligned}
+				K_N(t) & = E(x\in [a, b] \rightarrow [(x-t)_+])\\
+					   & = \int_{a}^{b} f(x)dx - (b-a)f(\frac{a+b}{2})\\
+					   & = \int_{a}^{b} (x-t)_+dx - (b-a)(\frac{a+b}{2}-t)_+\\
+					   & = \frac{(b-t)_+^2 + (a-t)_+^2}{2} - (b-a)(\frac{a+b}{2}-t)_+
+			\end{aligned}
+		\end{equation} 
+		Divide the whole range into 4 sub-gap as $(-\infty, a]$,$(a, \frac{a+b}{2}]$,$(\frac{a+b}{2}, b]$,$(b, +\infty)$.
+		The non-negative property is seen when examine each gap.
+	\item 
+		\begin{proof}
+			As has been proved above, $k_N(t)$ is non-negative over $[a, b]$, so the first mean value theorem can be applied
+			\begin{equation}
+				\begin{aligned}
+					E(f) & = \frac{1}{N!} \int_{a}^{b}k_N(t)f''(t)dt\\
+					     & = f''(\xi) \int_{a}^{b}k_N(t)dt\\
+					     & = \frac{(b-a)^3}{24} f''(\xi)
+				\end{aligned}
+			\end{equation}
+		\end{proof}
+\end{enumerate}
 

### 2018-11-15 VV570/HW8/tex/submission.tex
fix choice of thermal conductivity and specific heat, integral of source term still not correct

--- 2018-07-19 VV570/HW8/submission.tex
@@
 \usepackage{enumerate}
+\usepackage{graphicx}
 
@@
 
-%----------------------------------------------------------------------------------------
-%	PROBLEM 1
-%----------------------------------------------------------------------------------------
 \section{Question 1}
@@
 		\item 
+			Let
+			\begin{equation}
+				RHS \triangleq t f(x) + (1-t)f(y)
+			\end{equation}
+			\begin{equation}
+				LHS \triangleq - f(tx+(1-t)y)
+			\end{equation}
 			It's concave as
@@
 				\begin{aligned}
-				  RHS-LHS & = t f(x) + (1-t)f(y) - f(tx+(1-t)y)\\
-						  & = [t x_1 x_2 + (1-t)y_1 y_2] -[t x_1 + (1-t)y_1][t x_2 + (1-t)y_2]\\
-						  & = -t(1-t)(x_1 y_2 + x_2 y_1) < 0
+				  & RHS-LHS\\
+						   = &[t x_1 x_2 + (1-t)y_1 y_2] -[t x_1 + (1-t)y_1][t x_2 + (1-t)y_2]\\
+						   = &-t(1-t)(x_1 y_2 + x_2 y_1) < 0
 				\end{aligned}
 			\end{equation}
+		\item 
+			Convex.
+
+		\item 
+			Convex.
+
+		\item 
+			Convex.
+
+		\item 
+			Concave.
 
@@
 
-%----------------------------------------------------------------------------------------
-%	PROBLEM 2
-%----------------------------------------------------------------------------------------
 \section{Question 2}
-	\begin{enumerate}
+	\begin{enumerate}[(a)]
 		\item 
+			\begin{proof}
+				Suppose $x = (x_1, x_2, ... , x_m)$, then it's left to prove that
+				\begin{equation}
+					\frac{\partial f}{\partial x_i} = 0
+				\end{equation}
+				for $i=1,2, ... , m$ at $x=x^*$.
+			\end{proof}
+			The partial derivative of $f$ at $x=x^*$ is defined as
+			\begin{equation}
+				\frac{\partial f}{\partial x_i}\Big|_{x=x^*} = 
+				\lim\limits_{\Delta x_i \rightarrow 0}\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i}
+			\end{equation}
+			Since $f(x^*)$ is the local minimum, $f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) \geq f(x_1, x_2, ... ,x_i^*, ... , x_m)$ however $\Delta x_i$ changes.\\
+			Thus
+			\begin{equation}
+				\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i} \leq 0
+			\end{equation} 
+			if $\Delta x_i < 0$.\\
+			And
+			\begin{equation}
+				\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i} \geq 0
+			\end{equation}  
+			if $\Delta x_i > 0$.\\
+			Hence, $\frac{\partial f}{\partial x_i}\Big|_{x=x^*} = 0$ as $f$ is continuously differentiable.
+			Therefore, $\triangledown f(x^*) =0$.
+		\item 
+			\begin{proof}
+				With taylor expansion of $f(x)$ at $x=x^*$
+				\begin{equation}
+					\begin{aligned}
+						  &f(x) - f(x^*) \geq 0 \quad \quad (\text{$f(x^*)$ is the local minimum})\\
+		  \Leftrightarrow &\triangledown f(x^*) \Delta x + \frac{1}{2} \Delta \xi H(x^*) \Delta \xi ^T \geq 0\\
+		  \Leftrightarrow &\frac{1}{2} \Delta \xi H(x^*) \Delta \xi ^T \geq 0 \quad \quad (\text{gradient be 0})
+					\end{aligned}
+				\end{equation}
+				where $d(\Delta \xi, x^*) \leq d(x, x^*)$, and the gradient is $0$ as been proved above.
+				Thus, $ \Delta \xi H(x^*) \Delta \xi ^T \geq 0$ for any $\Delta \xi$ within the local neighbourhood of $x=x^*$.\\
+				Hence $H(x^*)$ is semi-positive finite.
 
-	\end{enumerate}
-%----------------------------------------------------------------------------------------
-%	PROBLEM 3
-%----------------------------------------------------------------------------------------
-\section{Question 3}
-\begin{enumerate}
+			\end{proof}
 		\item 
+			\begin{proof}
+				($\Leftarrow$)The global minimum must be a local minimum, and the gradient is therefore 0 as $f$ is differentiable.
 
-\end{enumerate}
-%----------------------------------------------------------------------------------------
-%	PROBLEM 6
-%----------------------------------------------------------------------------------------
-\section{Question 6}
-	\begin{enumerate}
+				($\Rightarrow$)As has been proved above, $\triangledown f(x^*)=0$ indicates that $f(x^*)$ is the local minimum. It's left to prove that local minimum is also global minimum for a convex function.
+				Suppose there exist $x'$ s.t. 
+				\begin{equation}
+					f(x') < f(x^*)
+				\end{equation}
+				Then, by convexity
+				\begin{equation}
+					f(t x' + (1-t)x^*) \leq t f(x') + (1-t) f(x^*) < \leq t f(x^*) + (1-t) f(x^*) = f(x^*)
+				\end{equation}
+				When $t\rightarrow1$, the inequality above contradicts local optimality of $x^*$.\\
+				Thus, the assumption fails, which indicates that $f(x^*)$ is the global minimum for $f$.
+
+			\end{proof}
 		\item
+			\begin{proof}
+				($\Rightarrow$)By Taylor expansion
+				\begin{equation}
+					f(x+ d) = f(x) + \triangledown f(x) d + \frac{1}{2} d^T H(x) d + O(||d||^2)
+				\end{equation}
+				If the Hessian matrix $H$ is semi-definite positive, then
+				\begin{equation}
+					d^T H(x) d \geq 0
+				\end{equation}
+				Thus
+				\begin{equation}
+					f(x+ d) \geq f(x) + \triangledown f(x) d
+				\end{equation}
+				which is the so called 1-st order condition, and it implies that the function $f$ is convex.
+
+				($\Leftarrow$)By Taylor expansion
+				\begin{equation}
+					f(x+ t d) = f(x) + t \triangledown f(x) d + \frac{t^2}{2} d^T H(x) d + O(||d||^2)
+				\end{equation}
+				With the 1-st order condition
+				\begin{equation}
+					f(x+ t d) \geq f(x) + t \triangledown f(x) d
+				\end{equation}
+				Thus
+				\begin{equation}
+					\frac{t^2}{2} d^T H(x) d + O(t||d||^2) \geq 0
+				\end{equation}
+				Dividing it by $\frac{t^2}{2}$ and set $t \rightarrow 0$, it gives out that for any $d\in \mathbb{R}^n$, $d^T H(x) d \geq 0$.
+
+			\end{proof}
 
@@
 
+\section{Question 4}
+	The genetic algorithm is adopted as there exists intensive oscillation when $x$ approaches $0$, and optimization algorithms dependent on the gradient info are easy to fall into local minimum.\\
+	The global minimum found is $x_0=0.217, f(x_0)=-0.0249$.
+
+\section{Question 6}
+	The plot of $g(y)$ is given as follows
+	\begin{figure}[!htbp]
+		\centering
+		\includegraphics[width=15cm]{../pic/Task6.eps}
+	\end{figure}
+
+\section{Question 7}
+	According to the geometric relations, the allowable length of the ladder is given as
+	\begin{equation}
+		L(\alpha) = \min\limits_{\beta} (\frac{1}{sin(\beta)} + \frac{1}{sin(\alpha + \beta)})
+	\end{equation}
+	By solving the minimisation problem, the plot of $L$ versus $\alpha$ is given as follows
+	\begin{figure}[!htbp]
+		\centering
+		\includegraphics[width=15cm]{../pic/Task7.eps}	
+	\end{figure}
+
 \end{document}

### 2018-11-15 VV570/HW9/tex/submission.tex
question2 ok
fix choice of thermal conductivity and specific heat, integral of source term still not correct

--- 2018-07-30 VV570/HW9/submission.tex
@@
 		\item 
+			As $\Phi(t, y) = arctan(y)$, then
+			\begin{equation}
+				\Bigg| \frac{\partial \Phi}{\partial y} \Bigg| = \frac{1}{|1+y^2|} < 1 \triangleq c
+			\end{equation}
+		\item 
+			As $\dot{y} = \Phi(t, y) = arctan(y)$, then
+			\begin{equation}
+				|\ddot{y}| = \Bigg| \frac{\dot{y}}{1+y^2} \Bigg| = \frac{|arctan(y)|}{1+y^2} < \frac{\pi}{2(1+y^2)} \leq \frac{\pi}{2} 
+			\end{equation}
+		\item 
+			As the global error is bounded by
+			\begin{equation}
+				|e_k| \leq \frac{\tau^*}{hc}[e^{c(t_k - t_0)} - 1]
+			\end{equation}
+			where $\tau^* = \max\limits_{k}|\tau_k|$, $c$ is the Lipschitz constant and is taken as $1$ as has been illustrated above.\\
+			Since 
+			\begin{equation}
+				\begin{aligned}
+					\frac{\tau^*}{h} & = \max\limits_{k}\Bigg|\frac{y(t_k) - y(t_{k-1}) - h\Phi(t_{k-1}, y(t_{k-1}))}{h}\Bigg|\\
+									 & \leq \max\limits_{k}\Bigg| \frac{y(t_k) - y(t_{k-1})}{h}\Bigg| + |\Phi(t_{k-1}, y(t_{k-1}))|\\
+									 & = 2 \max\limits_{k} |\Phi(t_{k-1}, y(t_{k-1}))| < \pi
+				\end{aligned}
+			\end{equation}
+			Thus, $|e_k| < \pi[e^{(t_k - t_0)}-1]$.
+	\end{enumerate}
+
+\section{Question 3}
+	\begin{enumerate}[(a)]
+		\item 
+			With $y_0 = 4$, $y_k$ are calculated using Euler's method as follows
+			\begin{equation}
+				y_k = y_{k-1} + h \Phi(t_{k-1}, y_{k-1})
+			\end{equation}
+			The calculation is carried out with matlab, and the results are given as below
+			\begin{figure}[!htbp]
+				\centering
+				\includegraphics[width=8cm]{../pic/Q3_a.eps}
+			\end{figure}
+		\item 
+			The initial value of $y_k^{(0)}$ is calculated using Euler's method.\\
+			Then $y_k^{(i)}$ are calculated in $i-th$ iteration, and the back-ward Euler's method is adopted.
+			\begin{equation}
+				y_k^{(i)} = y_{k-1}^{(i)} + h \Phi(t_{k}, y_k^{(i-1)})
+			\end{equation} 
+			The calculation is carried out with matlab, and the results are given as below
+			\begin{figure}[!htbp]
+				\centering
+				\includegraphics[width=8cm]{../pic/Q3_b.eps}
+			\end{figure}
+		\item 
+			Iteration formula is given as 
+			\begin{equation}
+				y_k = y_{k-1} + h \Phi(t_{k-1}, y_{k-1}) + \frac{h^2}{2}[\Phi_t(t_{k-1}, y_{k-1}) + \Phi_y(t_{k-1}, y_{k-1}) \Phi(t_{k-1}, y_{k-1})]
+			\end{equation}
+			The calculation is carried out with matlab, and the results are given as below
+			\begin{figure}[!htbp]
+				\centering
+				\includegraphics[width=8cm]{../pic/Q3_c.eps}
+			\end{figure}
+		\item 
+			The calculation is carried out with the prediction-correction method. Iteration formulas are given as
+			\begin{equation}
+				y^* = y_{k-1} + h \Phi(t_{k-1}, y_{k-1})
+			\end{equation}
+			\begin{equation}
+				y_k = y_{k-1} + \frac{h}{2} [\Phi(t_{k-1}, y_{k-1}) + \Phi(t_k, y^*)] 
+			\end{equation}
+			The calculation is carried out with matlab, and the results are given as below
+			\begin{figure}[!htbp]
+				\centering
+				\includegraphics[width=8cm]{../pic/Q3_d.eps}
+			\end{figure}
+		\item 
+			Here, an extra initial point($y_1$) is required, and it is calculated using the Euler's method as
+			\begin{equation}
+				y_1 = y_0 + h \Phi(t_0, y_0)
+			\end{equation}
+			Then, the iteration steps are taken as
+			\begin{equation}
+				y_k = y_{k-1} + \frac{h}{2}[3\Phi(t_{k-1}, y_{k-1}) - \Phi(t_{k-2}, y_{k-2})]
+			\end{equation}
+			The calculation is carried out with matlab, and the results are given as below
+			\begin{figure}[!htbp]
+				\centering
+				\includegraphics[width=8cm]{../pic/Q3_e.eps}
+			\end{figure}
 

### 2018-11-15 VV570/PROJ1/article/article.tex
fix choice of thermal conductivity and specific heat, integral of source term still not correct

@@
 
+\usepackage{cite}
+
 %% if you use PostScript figures in your article
@@
 %% or use the graphicx package for more complicated commands
-%% \usepackage{graphicx}
+\usepackage{graphicx}
 %% or use the epsfig package if you prefer to use the old commands
 %% \usepackage{epsfig}
+\usepackage{epstopdf}
 
@@
 \usepackage{lineno}
-
-%use graph format
-\usepackage{graphicx} 
-\usepackage{epstopdf}
 
@@
 Two strategies are developed to determine the coefficients.
-One is windowing the error and the Cholesky decomposition is applied.
-The other is windowing the signal and the Topelitz equations are solved iteratively.
-The two strategies are compared using a sample speech finally.
+One is windowing the signal and the Topelitz equations are solved iteratively.
+The other is windowing the error and the Cholesky decomposition is applied.
+Both the two strategies are compared with a sample speech finally.
 \end{abstract}
@@
 \begin{keyword}
-Speech \sep Prediction \sep Cholesky \sep Topelitz
+Speech Prediction \sep Correlation \sep Covariance \sep Cholesky \sep Topelitz
 %% keywords here, in the form: keyword \sep keyword
@@
 \subsection{Relation between the error and $p$}
+Here, the covariance method is choosen for further investigating the relation between the error and the prediction order $p$.
+
+Again, the total number of samples is fixed($len = 120$).
+The error vector $e$ is measured with $\lVert e \rVert_2$.
+$p$ is equidistantly choosen ranging from $2$ to $50$.
+Plot indicating the relation between the order of error and $p$ is given as below.
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[height=5.5cm,width=9cm]{../pic/err_vs_p.eps}
+\end{figure}
+
+It can be seen from the plot that the error is reduced immediately when $p$ is increased from $5$ to $15$, but the error decreases slowly when $p$ continues to grow.
+
+\section{Conclusion}
+Two different methods were introduced to calculate the linear prediction coefficients.
+Numerical experiments were carried out to compare the performence of these two methods, and the results show that the covariance method
+does better than the correlation method.
+Possible reasons were suggested and a further study on the relation between the error and $p$ indicates that the error decreases intensively at the begining but tends to be converged later on.
 
@@
 
-%% References
-%%
-%% Following citation commands can be used in the body text:
-%% Usage of \cite is as follows:
-%%   \cite{key}          ==>>  [#]
-%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
-%%   \citet{key}         ==>>  Author [#]
-
-%% References with bibTeX database:
-
-\bibliographystyle{model1-num-names}
-\bibliography{sample.bib}
-
-%% Authors are advised to submit their bibtex database files. They are
-%% requested to list a bibtex style file in the manuscript if they do
-%% not want to use model1-num-names.bst.
-
-%% References without bibTeX database:
-
-% \begin{thebibliography}{00}
-
-%% \bibitem must have the following form:
-%%   \bibitem{key}...
-%%
-
-% \bibitem{}
-
-% \end{thebibliography}
+\bibliographystyle{plain}
+\bibliography{article.bib}
 
 \end{document}
-
-%%
-%% End of file `elsarticle-template-1-num.tex'.

### 2018-11-15 VV570/PROJ2/tex/report.tex
fix choice of thermal conductivity and specific heat, integral of source term still not correct

@@
 \section{Task 2}
-	With trival inequality analysis, the exact solution is given as $x=[0.5, 0, -\frac{\pi}{6}]$, which can be used for varification.
+	With trival inequality analysis, the exact solution is given as $x=[0.5, 0, -\frac{\pi}{6}]$, which can be used for verification.
 	\subsection{Solve directly}
-		Applying the fixed-point iteration, newton's method and the broyden's method to this non-linear system respectively, ...(TODO)
+		Applying the fixed-point iteration, newton's method and the broyden's method to this non-linear system respectively, with initial guess given as $x_0 = [0.1 0.1 0.1]^T$, and tolerance set to $10^{-10}$, the iteration process all converge to the exact solution as
+		\begin{equation}
+			\begin{aligned}
+				x_1 & = 0.5\\
+				x_2 & = 3.5440\times 10^{-11}\\
+				x_3 & = -0.5236\\
+			\end{aligned}
+		\end{equation}
+		The iteration function for fixed-point iteration is given as
+		\begin{equation}
+			G =
+			\begin{bmatrix}
+				\frac{0.5+cos(x_2 x_3)}{3}\\
+				\frac{\sqrt(0.25-x_1^2)}{25}\\
+				\frac{\frac{3-10 \pi}{3}-e^{-x_1 x_2}}{20}
+			\end{bmatrix}
+			= x
+		\end{equation}
+
 	\subsection{Downhill simplex algorithm}
-	In general, the initial value for such a non-linear system is hard to know, even the range for each component is hard to estimate.
-In this case, the downhill simplex method can be applied to produce a fine inital guess for further calculation like newton or quasi-newton.
+		In general, the initial value for such a non-linear system is hard to know, even the range of each component is hard to estimate.
+In this case, the downhill simplex method can be applied to produce a initial guess for further calculation.
+
+		The downhill simplex algorithm was implemented in my code. The kernel idea of this algorithm is to minimize the performance of the worst vertex gradually.
+
+		Inside the iteration loop, serval operations guide the simplex to move towards the minimum:
+		\begin{enumerate}
+			\item reflection
+			\item expansion
+			\item contraction
+			\item shrink
+		\end{enumerate}
+
+		 These operations are designed for different ranges respectively. The whole range of the function is divided by 3 points: 
+		 \begin{enumerate}
+		 	\item  the best
+		 	\item  the last-but-one
+		 	\item  the worst
+		 \end{enumerate}
+ 		 Details of the implement will not be discussed here and can be referenced clearly from the code.
+
 	\subsection{Solve with initialization}
-
+		Before using the downhill simplex to find a fine initial guess, a targeting function $f: \mathbb{R^n} \rightarrow \mathbb{R}$ is taken as
+		\begin{equation}
+			f(X) = ||F(x)||_2
+		\end{equation}
+		inside the matlab code as the evaluating function for the algorithm.\\
 		Numerical experiments were done to identify the difference in terms of time cost.
@@
 			Numerical experiments were done for 200 times to illustrate the initial guess(Fig\ref{coarse_ag}) and the variance(Fig\ref{err_ag}) of $\hat{\alpha}$ and $\hat{\gamma}$.
-			\begin{figure}[!htbp]\centering
-				\includegraphics[height=10cm]{../pic/coarse_estimation.eps}
+			\begin{figure}\centering
+				\includegraphics[height=8cm]{../pic/coarse_estimation.eps}
 				\caption{Coarse estimation} 
@@
 			\end{figure}
-			\begin{figure}[!htbp]\centering
-				\includegraphics[height=10cm]{../pic/coarse_estimation_err.eps}
+			\begin{figure}\centering
+				\includegraphics[height=8cm]{../pic/coarse_estimation_err.eps}
 				\caption{Error of estimation}

### 2018-11-15 VM432/HW3/Q2.m

@@ -1,7 +1,7 @@
 clear all; close all; clc;
 
 T0 = 300;
-Ti = 2000;
+Ti = 2200;
 Tf = 2300;
 P = oneatm;
 
@@ -10,9 +10,17 @@ gascomp = 'CH4:0.5, O2:1, N2:3.6';
 
 set(gas,'T', T0, 'P', P, 'X', gascomp);
 rho_u = density(gas);
-lambda = thermalConductivity(gas);
-cp = cp_mass(gas);
-SL = sqrt(2*lambda*summation(gas, Ti, Tf, 10000))/(rho_u * cp * (Ti - T0));
+lambda1 = thermalConductivity(gas);
+cp1 = cp_mass(gas);
+
+set(gas,'T', Tf, 'P', P, 'X', gascomp);
+lambda2 = thermalConductivity(gas);
+cp2 = cp_mass(gas);
+
+lambda = (lambda1 + lambda2)/2;
+cp = (cp1 + cp2)/2;
+
+SL = sqrt(2*lambda*summation(gas, Ti, Tf))/(rho_u * cp * (Ti - T0));
 
 fprintf('\tDensity: %f Kg/m^3\n', rho_u);
 fprintf('\tThermal Conductivity: %f W/(m K)\n', lambda);
@@ -26,13 +34,14 @@ function ret = s(tp, temp)
     ret = dot(w, h) * temp * gasconstant;
 end
 
-function ret = summation(tp, Ta, Tb, N)
+function ret = summation(tp, Ta, Tb)
+    N = 10000;
     step = (Tb-Ta)/N;
-    cT = Ta - step/2;
+    cur_T = Ta - step/2;
     ret = 0;
     for i = 1:N
-        cT = cT + step;
-        ret = ret + s(tp, cT);
+        cur_T = cur_T + step;
+        ret = ret + s(tp, cur_T);
     end
     ret = ret * step;    
 end

### 2018-11-15 VM432/HW3/Q2.m
Revert "fix choice of thermal conductivity and specific heat, integral of source term still not correct"
This reverts commit 67851a8b928fa960a2710cabc3cae4052839a7c5.

@@ -1,7 +1,7 @@
 clear all; close all; clc;
 
 T0 = 300;
-Ti = 2200;
+Ti = 2000;
 Tf = 2300;
 P = oneatm;
 
@@ -10,17 +10,9 @@ gascomp = 'CH4:0.5, O2:1, N2:3.6';
 
 set(gas,'T', T0, 'P', P, 'X', gascomp);
 rho_u = density(gas);
-lambda1 = thermalConductivity(gas);
-cp1 = cp_mass(gas);
-
-set(gas,'T', Tf, 'P', P, 'X', gascomp);
-lambda2 = thermalConductivity(gas);
-cp2 = cp_mass(gas);
-
-lambda = (lambda1 + lambda2)/2;
-cp = (cp1 + cp2)/2;
-
-SL = sqrt(2*lambda*summation(gas, Ti, Tf))/(rho_u * cp * (Ti - T0));
+lambda = thermalConductivity(gas);
+cp = cp_mass(gas);
+SL = sqrt(2*lambda*summation(gas, Ti, Tf, 10000))/(rho_u * cp * (Ti - T0));
 
 fprintf('\tDensity: %f Kg/m^3\n', rho_u);
 fprintf('\tThermal Conductivity: %f W/(m K)\n', lambda);
@@ -34,14 +26,13 @@ function ret = s(tp, temp)
     ret = dot(w, h) * temp * gasconstant;
 end
 
-function ret = summation(tp, Ta, Tb)
-    N = 10000;
+function ret = summation(tp, Ta, Tb, N)
     step = (Tb-Ta)/N;
-    cur_T = Ta - step/2;
+    cT = Ta - step/2;
     ret = 0;
     for i = 1:N
-        cur_T = cur_T + step;
-        ret = ret + s(tp, cur_T);
+        cT = cT + step;
+        ret = ret + s(tp, cT);
     end
     ret = ret * step;    
 end

### 2018-11-15 VM432/HW3/Q2.m
fix lambda and cp, integral of source term still not correct

@@ -10,8 +10,16 @@ gascomp = 'CH4:0.5, O2:1, N2:3.6';
 
 set(gas,'T', T0, 'P', P, 'X', gascomp);
 rho_u = density(gas);
-lambda = thermalConductivity(gas);
-cp = cp_mass(gas);
+lambda1 = thermalConductivity(gas);
+cp1 = cp_mass(gas);
+
+set(gas,'T', Tf, 'P', P, 'X', gascomp);
+lambda2 = thermalConductivity(gas);
+cp2 = cp_mass(gas);
+
+lambda = (lambda1 + lambda2)/2;
+cp = (cp1 + cp2)/2;
+
 SL = sqrt(2*lambda*summation(gas, Ti, Tf, 10000))/(rho_u * cp * (Ti - T0));
 
 fprintf('\tDensity: %f Kg/m^3\n', rho_u);

### 2018-11-20 VV556/HW8/submission.tex
HW8

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages

\usepackage{algorithm, algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}} %Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm

\usepackage{graphicx}

\usepackage{listings}
\lstset{language=Matlab}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Methods of Applied Mathematics I\\ HW8 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yu Cang \quad 018370210001\\ Zhiming Cui \quad 017370910006} % Your name

\date{\normalsize \today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title

\section{Exercise8.1}
	\begin{enumerate}
		\item 
			\begin{proof}
				Since
				\begin{equation}
					\sum_{i=1}^{\infty}\sum_{j=1}^{\infty}|a_{ij}|^2 = \sum_{k=1}^{\infty} \frac{1}{k} \rightarrow \infty
				\end{equation}
				Thus, $L$ is not a Hilbert-Schmidt operator.
			\end{proof}
		\item 
			\begin{proof}
				$\forall x, y \in l^2$, the inner product can be expressed as
				\begin{equation}
					\begin{aligned}
						<x, Ly> & =  <(x_1, x_2, ... , x_n, ...), (y_1, \frac{y_2}{\sqrt{2}}, ... , \frac{y_n}{\sqrt{n}}, ...)>\\
								& = \sum_{i=1}^{\infty} \frac{x_i y_i}{\sqrt{i}}\\
								& = <(x_1, \frac{x_2}{\sqrt{2}}, ... , \frac{x_n}{\sqrt{n}}, ...), (y_1, y_2, ... , y_n, ...)>\\
								& = <Lx, y>
					\end{aligned}
				\end{equation}
				Thus, $L$ is self adjoint.
			\end{proof}
		\item 
			\begin{proof}
				Denote $L_n : l^2 \rightarrow l^2$ by
				\begin{equation}
					L_n(x_n) = (x_1, \frac{x_2}{\sqrt{2}}, \frac{x_3}{\sqrt{3}}, ... , \frac{x_n}{\sqrt{n}}, 0, 0, ...)
				\end{equation}
				$L_n$ is a Hilbert-Schmidt operator as 
				\begin{equation}
					\sum_{i=1}^{\infty}\sum_{j=1}^{\infty}|a_{ij}|^2 = \sum_{k=1}^{n} \frac{1}{k} < \infty
				\end{equation}
				Thus, $L_n$ is compact. Then, $L$ is compact if $(L_n)$ converges to $L$ in norm, i.e.
				\begin{equation}
					\lim\limits_{n \rightarrow \infty} ||L_n - L|| = 0
				\end{equation}
				To show this, expand the operator norm as
				\begin{equation}
					\begin{aligned}
						||L_n - L||& = \sup\limits_{x\in l^2}\frac{||(L_n - L)x||}{||x||}\\
						& = \sup\limits_{x\in l^2}\frac{||(0, ... , 0, \frac{x_{n+1}}{\sqrt{n+1}}, \frac{x_{n+2}}{\sqrt{n+2}},...)||}{||x||}\\
						& \leq \frac{1}{\sqrt{n+1}} \frac{||(0, ... , 0, x_{n+1}, x_{n+2}, ...)||}{||x||}\\
						& \leq  \frac{1}{\sqrt{n+1}}
					\end{aligned}
				\end{equation}
				So, $\lim\limits_{n \rightarrow \infty} ||L_n - L|| \leq  \lim\limits_{n \rightarrow \infty} \frac{1}{\sqrt{n+1}} = 0$.\\
				According to the positivity of norm,  $\lim\limits_{n \rightarrow \infty} ||L_n - L||\geq 0$.\\
				Hence  $\lim\limits_{n \rightarrow \infty} ||L_n - L|| = 0$.
			\end{proof}
		\item
			Since
			\begin{equation}
				||L|| = \sup\limits_{x\in l^2} \frac{||Lx||}{||x||} \geq \frac{||Le_1||}{||e_1||} = 1
			\end{equation}
			and
			\begin{equation}
				||L|| = \sup\limits_{x\in l^2} \frac{||Lx||}{||x||} \leq \frac{||x||}{||x||} = 1
			\end{equation}
			Thus $||L|| = 1$.\\
			As the norm of operator is a bound for all its eigenvalues, then $|\lambda| \leq 1$. Thus the upper bound for the spcetrum is found.\\
			For the lower bound, Rayleigh Quotient is used. For $x\neq 0$, 
			\begin{equation}
				\lambda \geq L_T \triangleq \inf\limits_{x\in dom(L)} R(x) = \inf\limits_{x\in dom(L)} \frac{<x, Lx>}{||x||^2} = \lim\limits_{n \rightarrow \infty} \frac{<e_n, Le_n>}{||e_n||^2} = \lim\limits_{n \rightarrow \infty} \frac{1}{\sqrt{n}} = 0
			\end{equation}
			Thus the lower bound for the spcetrum is found.
		\item 
			Clearly, $\{1, \frac{1}{\sqrt{2}}, \frac{1}{\sqrt{3}}, ...\}$ is the point specturm as they are eigenvalues of $L$.

	\end{enumerate}

\section{Exercise8.2}
	\begin{enumerate}
		\item 
			\begin{proof}
				$\forall u \in M$, with the B.C. of $u$, the transform by operator $KL$ yields
				\begin{equation}
					\begin{aligned}
						(KL)u(x) & = \int_{0}^{1} g(x, \xi) (Lu)(\xi) d\xi\\
					 			 & = \int_{0}^{x} g(x, \xi) (Lu)(\xi) d\xi + \int_{x}^{1} g(x, \xi) (Lu)(\xi) d\xi\\
					 			 & = \int_{0}^{x} \xi(x-1) u^{\prime\prime}(\xi) d\xi + \int_{x}^{1} x(\xi - 1) u^{\prime\prime}(\xi) d\xi\\
					 			 & = \int_{0}^{x} \xi(x-1) du^{\prime}(\xi) + \int_{x}^{1} x(\xi - 1) du^{\prime}(\xi)\\
					 			 & = (\xi(x-1)u')\Big|_0^x - \int_{0}^{x} u' (x-1) d\xi + (x(\xi-1)u')\Big|_x^1 - \int_{x}^{1} u' x d\xi\\
					 			 & = x(x-1)u'(x) - (x-1) (u(x) - u(0)) - x(x-1)u'(x) - x (u(1)-u(x))\\
					 			 & = u(x)
					\end{aligned}
				\end{equation}
				Thus, $KL = I$ on $M$.
			\end{proof}
		\item 
			\begin{proof}
				For example, take $u(x) = \sqrt{x}$, then
				\begin{equation}
					||L|| \geq \frac{||Lu||}{||u||} = \frac{||x^{-\frac{3}{2}}||}{4||x^\frac{1}{2}||} \rightarrow \infty
				\end{equation}
				Thus, $L$ is unbounded.
			\end{proof}
		\item

		\item 
			\begin{proof}
				Swap $\xi$ and $x$, then
				\begin{equation}
					g(\xi, x) = 
					\left\{
						\begin{aligned}
							\xi(1-x) & \quad \xi<x\\
							x(1-\xi) & \quad \xi\geq x
						\end{aligned}
					\right.
					=
					\left\{
						\begin{aligned}
							x(1-\xi) & \quad x < \xi\\
							\xi(1-x) & \quad x \geq \xi
						\end{aligned}
					\right.
					=g(x,\xi)
				\end{equation}
				Thus, $\forall u, v\in M$,
				\begin{equation}
					\begin{aligned}
						<u, Kv> & = \int_{0}^{1} u(x) \Bigg(\int_{0}^{1} g(x, \xi) v(\xi) d\xi\Bigg) dx\\
								& = \int_{0}^{1} \int_{0}^{1} u(x) g(\xi, x) v(\xi) d\xi dx\\
								& = \int_{0}^{1} \Bigg(\int_{0}^{1} g(\xi, x) u(x) dx\Bigg) v(\xi) d\xi\\
								& = <Ku, v>
					\end{aligned}
				\end{equation}
				Hence, $K$ is self-adjoint.
			\end{proof}
		\item 
			\begin{equation}
				L_T = \inf\limits_{u\in M} \frac{<u, Ku>}{<u, u>} = \inf\limits_{u\in M} \frac{<Ku, u>}{<u, u>}
			\end{equation}
			and
			\begin{equation}
				U_T = \sup\limits_{u\in M} \frac{<u, Ku>}{<u, u>} = \sup\limits_{u\in M} \frac{<Ku, u>}{<u, u>}
			\end{equation}

	\end{enumerate}

\end{document}

### 2018-11-28 VV556/HW9/submission.tex
part of hw9 sol

--- 2018-11-20 VV556/HW8/submission.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Methods of Applied Mathematics I\\ HW8 \\ % The assignment title
+\huge Methods of Applied Mathematics I\\ HW9 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\section{Exercise8.1}
+\section{Exercise9.1}
 	\begin{enumerate}
@@
 				\begin{equation}
-					\sum_{i=1}^{\infty}\sum_{j=1}^{\infty}|a_{ij}|^2 = \sum_{k=1}^{\infty} \frac{1}{k} \rightarrow \infty
+					\begin{aligned}
+						(LKu)(x) & = -\frac{d^2}{d x^2} \int_{0}^{1} g(x, \xi) u(\xi) d\xi\\
+								 & = -\frac{d^2}{d x^2} \Bigg(\int_{0}^{x} g(x, \xi) u(\xi) d\xi + \int_{x}^{1} g(x, \xi) u(\xi) d\xi \Bigg)\\
+								 & = -\frac{d^2}{d x^2} \Bigg(\int_{0}^{x} \xi(1-x) u(\xi) d\xi + \int_{x}^{1} x(1-\xi) u(\xi) d\xi \Bigg)\\
+								 & = -\frac{d^2}{d x^2} \Bigg((1-x)\int_{0}^{x} \xi u(\xi) d\xi + x\int_{x}^{1} (1-\xi) u(\xi) d\xi \Bigg)\\
+								 & = -\frac{d}{d x} \Bigg(-\int_{0}^{x} \xi u(\xi) d\xi + \int_{x}^{1} (1-\xi) u(\xi) d\xi \Bigg)\\
+								 & = xu(x) + (1-x) u(x) = u(x)
+ 					\end{aligned}
 				\end{equation}
-				Thus, $L$ is not a Hilbert-Schmidt operator.
+				Thus, $LK=I$, which means $L = K^{-1}$.
 			\end{proof}
@@
 			\begin{proof}
-				$\forall x, y \in l^2$, the inner product can be expressed as
+				($\Rightarrow$) Suppose $\frac{1}{\lambda}$ is an eigenvalue for $K$, then
 				\begin{equation}
-					\begin{aligned}
-						<x, Ly> & =  <(x_1, x_2, ... , x_n, ...), (y_1, \frac{y_2}{\sqrt{2}}, ... , \frac{y_n}{\sqrt{n}}, ...)>\\
-								& = \sum_{i=1}^{\infty} \frac{x_i y_i}{\sqrt{i}}\\
-								& = <(x_1, \frac{x_2}{\sqrt{2}}, ... , \frac{x_n}{\sqrt{n}}, ...), (y_1, y_2, ... , y_n, ...)>\\
-								& = <Lx, y>
-					\end{aligned}
+					ku = \frac{1}{\lambda}u
 				\end{equation} 
-				Thus, $L$ is self adjoint.
+				Thus
+				\begin{equation}
+					u = \lambda K u
+				\end{equation}
+				Take the operator $L$ on it
+				\begin{equation}
+					Lu = \lambda LKu = \lambda Iu = \lambda u
+				\end{equation}
+				which indicates that $\lambda$ is an eigenvalue of $L$.\\
+				($\Leftarrow$) Suppose $\lambda \neq 0$ is an eigenvalue of $L$, then
+				\begin{equation}
+					Lu = \lambda u
+				\end{equation}
+				Thus
+				\begin{equation}
+					u = \frac{1}{\lambda} Lu
+				\end{equation}
+				As $K = L^{-1}$ is known, take the operator $K$ onto it yields
+				\begin{equation}
+					Ku = \frac{1}{\lambda}KLu = \frac{1}{\lambda} Iu = \frac{1}{\lambda} u
+				\end{equation}
+				which indicates that $\frac{1}{\lambda}$ is an eigenvalue of $K$.\\
+				It's clear that for the given $\lambda$, $K$ and $L$ share the same eigenfunction $u(x)$.
 			\end{proof}
@@
 			\begin{proof}
-				Denote $L_n : l^2 \rightarrow l^2$ by
-				\begin{equation}
-					L_n(x_n) = (x_1, \frac{x_2}{\sqrt{2}}, \frac{x_3}{\sqrt{3}}, ... , \frac{x_n}{\sqrt{n}}, 0, 0, ...)
-				\end{equation}
-				$L_n$ is a Hilbert-Schmidt operator as 
-				\begin{equation}
-					\sum_{i=1}^{\infty}\sum_{j=1}^{\infty}|a_{ij}|^2 = \sum_{k=1}^{n} \frac{1}{k} < \infty
-				\end{equation}
-				Thus, $L_n$ is compact. Then, $L$ is compact if $(L_n)$ converges to $L$ in norm, i.e.
-				\begin{equation}
-					\lim\limits_{n \rightarrow \infty} ||L_n - L|| = 0
-				\end{equation}
-				To show this, expand the operator norm as
+				It's obvious that $L$ is bounded over $M$.\\
+				Since
 				\begin{equation}
 					\begin{aligned}
-						||L_n - L||& = \sup\limits_{x\in l^2}\frac{||(L_n - L)x||}{||x||}\\
-						& = \sup\limits_{x\in l^2}\frac{||(0, ... , 0, \frac{x_{n+1}}{\sqrt{n+1}}, \frac{x_{n+2}}{\sqrt{n+2}},...)||}{||x||}\\
-						& \leq \frac{1}{\sqrt{n+1}} \frac{||(0, ... , 0, x_{n+1}, x_{n+2}, ...)||}{||x||}\\
-						& \leq  \frac{1}{\sqrt{n+1}}
+						<u, Lv> &= -\int_{0}^{1} u(x)v''(x) dx = -\Bigg(u(x)v'(x)\Big|_0^1 - \int_{0}^{1}u'(x)v'(x)dx\Bigg)\\
+								&= \int_{0}^{1}u'(x)v'(x)dx = \int_{0}^{1}u'(x)dv(x) = u'(x)v(x)\Big|_0^1 - \int_{0}^{1} v(x)u''(x)dx\\
+								& = -\int_{0}^{1} u''(x)v(x)dx = <Lu, v>
 					\end{aligned}
 				\end{equation}
-				So, $\lim\limits_{n \rightarrow \infty} ||L_n - L|| \leq  \lim\limits_{n \rightarrow \infty} \frac{1}{\sqrt{n+1}} = 0$.\\
-				According to the positivity of norm,  $\lim\limits_{n \rightarrow \infty} ||L_n - L||\geq 0$.\\
-				Hence  $\lim\limits_{n \rightarrow \infty} ||L_n - L|| = 0$.
-			\end{proof}
-		\item
-			Since
+				which indicates that $L$ is self-adjoint. Thus the eigenvalues of $L$ are real numbers.\\
+		 		The eigenfunction $\psi_n(x)$ of $L$ together with $\lambda_n$ satisfy 
 		 		\begin{equation}
-				||L|| = \sup\limits_{x\in l^2} \frac{||Lx||}{||x||} \geq \frac{||Le_1||}{||e_1||} = 1
+		 			\psi_n''(x) + \lambda_n \psi_n(x) = 0
 		 		\end{equation}
@@
 		 		\begin{equation}
-				||L|| = \sup\limits_{x\in l^2} \frac{||Lx||}{||x||} \leq \frac{||x||}{||x||} = 1
+		 			\psi_n(0) = \psi_n(1) = 0
 		 		\end{equation}
-			Thus $||L|| = 1$.\\
-			As the norm of operator is a bound for all its eigenvalues, then $|\lambda| \leq 1$. Thus the upper bound for the spcetrum is found.\\
-			For the lower bound, Rayleigh Quotient is used. For $x\neq 0$, 
-			\begin{equation}
-				\lambda \geq L_T \triangleq \inf\limits_{x\in dom(L)} R(x) = \inf\limits_{x\in dom(L)} \frac{<x, Lx>}{||x||^2} = \lim\limits_{n \rightarrow \infty} \frac{<e_n, Le_n>}{||e_n||^2} = \lim\limits_{n \rightarrow \infty} \frac{1}{\sqrt{n}} = 0
-			\end{equation}
-			Thus the lower bound for the spcetrum is found.
-		\item 
-			Clearly, $\{1, \frac{1}{\sqrt{2}}, \frac{1}{\sqrt{3}}, ...\}$ is the point specturm as they are eigenvalues of $L$.
-
-	\end{enumerate}
-
-\section{Exercise8.2}
+		 		Solution of this ODE depends on the sign of $\lambda_n$.\\
 		 		\begin{enumerate}
 		 			\item 
-			\begin{proof}
-				$\forall u \in M$, with the B.C. of $u$, the transform by operator $KL$ yields
+		 				If $\lambda_n > 0$, then
 		 				\begin{equation}
-					\begin{aligned}
-						(KL)u(x) & = \int_{0}^{1} g(x, \xi) (Lu)(\xi) d\xi\\
-					 			 & = \int_{0}^{x} g(x, \xi) (Lu)(\xi) d\xi + \int_{x}^{1} g(x, \xi) (Lu)(\xi) d\xi\\
-					 			 & = \int_{0}^{x} \xi(x-1) u^{\prime\prime}(\xi) d\xi + \int_{x}^{1} x(\xi - 1) u^{\prime\prime}(\xi) d\xi\\
-					 			 & = \int_{0}^{x} \xi(x-1) du^{\prime}(\xi) + \int_{x}^{1} x(\xi - 1) du^{\prime}(\xi)\\
-					 			 & = (\xi(x-1)u')\Big|_0^x - \int_{0}^{x} u' (x-1) d\xi + (x(\xi-1)u')\Big|_x^1 - \int_{x}^{1} u' x d\xi\\
-					 			 & = x(x-1)u'(x) - (x-1) (u(x) - u(0)) - x(x-1)u'(x) - x (u(1)-u(x))\\
-					 			 & = u(x)
-					\end{aligned}
+		 					\psi_n(x) = C_1 sin(\sqrt{\lambda_n}x) + C_2 cos(\sqrt{\lambda_n}x)
 		 				\end{equation}
-				Thus, $KL = I$ on $M$.
-			\end{proof}
+		 				apply the boundary condition yields
+		 				\begin{equation}
+		 					C_2 = 0
+		 				\end{equation}
+		 				and
+		 				\begin{equation}
+		 					C_1 sin(\sqrt{\lambda_n}) = 0
+		 				\end{equation}
+		 				Thus
+		 				\begin{equation}
+		 					\lambda_n = (n\pi)^2
+		 				\end{equation}
+		 				and
+		 				\begin{equation}
+		 					\psi_n(x) = C_2 sin(n\pi x) \quad (C_2 \neq 0)
+		 				\end{equation}
 		 			\item 
-			\begin{proof}
-				For example, take $u(x) = \sqrt{x}$, then
+		 				If $\lambda_n = 0$, then
 		 				\begin{equation}
-					||L|| \geq \frac{||Lu||}{||u||} = \frac{||x^{-\frac{3}{2}}||}{4||x^\frac{1}{2}||} \rightarrow \infty
+		 					\psi_n(x) = C_0 + C_1 x
 		 				\end{equation}
-				Thus, $L$ is unbounded.
+		 				Apply the B.C. yields $C_0 = C_1 = 0$, which indicates 0 is not an eigenvalue for $L$.
+		 			\item 
+		 				If $\lambda_n < 0$, then
+		 				\begin{equation}
+		 					\psi_n(x) = C_1 e^{\sqrt{-\lambda_n}x} + C_2 e^{-\sqrt{-\lambda_n}x}
+		 				\end{equation}
+		 				Apply the B.C. yields $C_0 = C_1 = 0$, which indicates  $\lambda_n < 0$ are not eigenvalues for $L$.
+		 		\end{enumerate}
 			\end{proof}
@@
 		\item
-			\begin{proof}
-				Swap $\xi$ and $x$, then
-				\begin{equation}
-					g(\xi, x) = 
-					\left\{
-						\begin{aligned}
-							\xi(1-x) & \quad \xi<x\\
-							x(1-\xi) & \quad \xi\geq x
-						\end{aligned}
-					\right.
-					=
-					\left\{
-						\begin{aligned}
-							x(1-\xi) & \quad x < \xi\\
-							\xi(1-x) & \quad x \geq \xi
-						\end{aligned}
-					\right.
-					=g(x,\xi)
-				\end{equation}
-				Thus, $\forall u, v\in M$,
-				\begin{equation}
-					\begin{aligned}
-						<u, Kv> & = \int_{0}^{1} u(x) \Bigg(\int_{0}^{1} g(x, \xi) v(\xi) d\xi\Bigg) dx\\
-								& = \int_{0}^{1} \int_{0}^{1} u(x) g(\xi, x) v(\xi) d\xi dx\\
-								& = \int_{0}^{1} \Bigg(\int_{0}^{1} g(\xi, x) u(x) dx\Bigg) v(\xi) d\xi\\
-								& = <Ku, v>
-					\end{aligned}
-				\end{equation}
-				Hence, $K$ is self-adjoint.
-			\end{proof}
-		\item 
-			\begin{equation}
-				L_T = \inf\limits_{u\in M} \frac{<u, Ku>}{<u, u>} = \inf\limits_{u\in M} \frac{<Ku, u>}{<u, u>}
-			\end{equation}
-			and
-			\begin{equation}
-				U_T = \sup\limits_{u\in M} \frac{<u, Ku>}{<u, u>} = \sup\limits_{u\in M} \frac{<Ku, u>}{<u, u>}
-			\end{equation}
 

### 2018-11-29 VV556/HW9/submission.tex
add Q3 and Q4 ans

@@
 		\item 
-
+			It's obvious that, from previous proof, the eigenvalues of $K$ are
+			\begin{equation}
+				\sigma_{point}(K) = \{\frac{1}{(n\pi)^2}, n=1,2,3, ....\}
+			\end{equation} 
+			As $K$ is compact and self-adjoint, it's obvious bounded and
+			\begin{equation}
+				\sigma_{compression}(K) = \sigma_{point}(K)
+			\end{equation} 
+			If $0$ is an eigenvalue of $K$, then
+			\begin{equation}
+				Ku = 0
+			\end{equation}
+			thus
+			\begin{equation}
+				LKu = 0 \quad \Rightarrow \quad u = 0
+			\end{equation}
+			which indicates that 0 is not an eigenvalue for $K$.\\
+			Hence, 
+			\begin{equation}
+				\sigma_{continous}(K) = {0}
+			\end{equation}
+			as $K^{-1} = L$ is unbounded.
 		\item 
-
+			It's obvious that, from previous proof, the eigenfunctions of $K$ are
+			\begin{equation}
+				u_n(x) = sin(n\pi x) \quad n = 1, 2, ...
+			\end{equation}
+			which form the Fouier basis.
 	\end{enumerate}

### 2018-12-06 VV556/HW10/submission.tex
done

--- 2018-11-28 VV556/HW9/submission.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Methods of Applied Mathematics I\\ HW9 \\ % The assignment title
+\huge Methods of Applied Mathematics I\\ HW10 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\section{Exercise9.1}
+\section{Exercise10.1}
 	\begin{enumerate}
@@
 					\begin{aligned}
-						(LKu)(x) & = -\frac{d^2}{d x^2} \int_{0}^{1} g(x, \xi) u(\xi) d\xi\\
-								 & = -\frac{d^2}{d x^2} \Bigg(\int_{0}^{x} g(x, \xi) u(\xi) d\xi + \int_{x}^{1} g(x, \xi) u(\xi) d\xi \Bigg)\\
-								 & = -\frac{d^2}{d x^2} \Bigg(\int_{0}^{x} \xi(1-x) u(\xi) d\xi + \int_{x}^{1} x(1-\xi) u(\xi) d\xi \Bigg)\\
-								 & = -\frac{d^2}{d x^2} \Bigg((1-x)\int_{0}^{x} \xi u(\xi) d\xi + x\int_{x}^{1} (1-\xi) u(\xi) d\xi \Bigg)\\
-								 & = -\frac{d}{d x} \Bigg(-\int_{0}^{x} \xi u(\xi) d\xi + \int_{x}^{1} (1-\xi) u(\xi) d\xi \Bigg)\\
-								 & = xu(x) + (1-x) u(x) = u(x)
+						<u, Lu> & = \int_{0}^{1} u(x) u''(x) dx\\
+								& = -\Big[uu'\big|_0^1 - \int_{0}^{1}(u'(x))^2 dx\Big]\\
+								& =  \int_{0}^{1}(u'(x))^2 dx \geq 0
 					\end{aligned}
 				\end{equation}
-				Thus, $LK=I$, which means $L = K^{-1}$.
+				Thus, the operator $L$ is positive definite.
 			\end{proof}
@@
 			\begin{proof}
-				($\Rightarrow$) Suppose $\frac{1}{\lambda}$ is an eigenvalue for $K$, then
+				Denote $\lambda$ as the eigenvalue, and $u$ being the corresponding eigenfunction, then
 				\begin{equation}
-					ku = \frac{1}{\lambda}u
+					Lu = \lambda u
+				\end{equation}
+				As has been proved before, the positive definite property of $L$ implies that
+				\begin{equation}
+					<u, Lu> = <u, \lambda u> = \lambda <u, u> = \lambda ||u||^2 \geq 0
 				\end{equation}
@@
 				\begin{equation}
-					u = \lambda K u
+					\lambda > 0
 				\end{equation}
-				Take the operator $L$ on it
+				as the case $\lambda = 0$ is trival.\\
+				Then, the solution of this ODE is 
 				\begin{equation}
-					Lu = \lambda LKu = \lambda Iu = \lambda u
+					u(x) = a sin(\sqrt{\lambda} x) + b cos(\sqrt{\lambda} x)
 				\end{equation}
-				which indicates that $\lambda$ is an eigenvalue of $L$.\\
-				($\Leftarrow$) Suppose $\lambda \neq 0$ is an eigenvalue of $L$, then
+				With the B.C. at endpoints, it follows that
 				\begin{equation}
-					Lu = \lambda u
+					b = 0
+				\end{equation}
+				and
+				\begin{equation}
+					a(sin(\sqrt{\lambda}) + \sqrt{\lambda}cos(\sqrt{\lambda})) = 0
 				\end{equation}
@@
 				\begin{equation}
-					u = \frac{1}{\lambda} Lu
+					sin(\sqrt{\lambda}) + \sqrt{\lambda}cos(\sqrt{\lambda}) = 0
 				\end{equation}
-				As $K = L^{-1}$ is known, take the operator $K$ onto it yields
+				which indicates that the eigenvalue $\lambda$ satisfies 
 				\begin{equation}
-					Ku = \frac{1}{\lambda}KLu = \frac{1}{\lambda} Iu = \frac{1}{\lambda} u
+					\sqrt{\lambda} = - tan(\sqrt{\lambda})
 				\end{equation}
-				which indicates that $\frac{1}{\lambda}$ is an eigenvalue of $K$.\\
-				It's clear that for the given $\lambda$, $K$ and $L$ share the same eigenfunction $u(x)$.
 			\end{proof}
 		\item 
-			\begin{proof}
-				It's obvious that $L$ is bounded over $M$.\\
-				Since
+			From the plot of $y_1(x) = -x$ and $y_2(x) = tan(x)$, the first 2 intersections in $x>0$ region lie in the gap $(\frac{1}{2}\pi, \pi)$ and $(\frac{3}{2}\pi, 2\pi)$.\\
+			With the aid of MATLAB, the 2 lowest eigenvalues $\lambda_1$ and $\lambda_2$ are found as
 			\begin{equation}
-					\begin{aligned}
-						<u, Lv> &= -\int_{0}^{1} u(x)v''(x) dx = -\Bigg(u(x)v'(x)\Big|_0^1 - \int_{0}^{1}u'(x)v'(x)dx\Bigg)\\
-								&= \int_{0}^{1}u'(x)v'(x)dx = \int_{0}^{1}u'(x)dv(x) = u'(x)v(x)\Big|_0^1 - \int_{0}^{1} v(x)u''(x)dx\\
-								& = -\int_{0}^{1} u''(x)v(x)dx = <Lu, v>
-					\end{aligned}
-				\end{equation}
-				which indicates that $L$ is self-adjoint. Thus the eigenvalues of $L$ are real numbers.\\
-		 		The eigenfunction $\psi_n(x)$ of $L$ together with $\lambda_n$ satisfy 
-		 		\begin{equation}
-		 			\psi_n''(x) + \lambda_n \psi_n(x) = 0
+				\lambda_1 = (2.0288)^2 = 4.1160
 			\end{equation}
@@
 			\begin{equation}
-		 			\psi_n(0) = \psi_n(1) = 0
+				\lambda_2 = (4.9132)^2 = 24.1395
 			\end{equation}
-		 		Solution of this ODE depends on the sign of $\lambda_n$.\\
-		 		\begin{enumerate}
 		\item 
-		 				If $\lambda_n > 0$, then
+			Denote $p(x) = a_0 + a_1 x + a_2 x^2$, the B.V. at endpoints implies that  
 			\begin{equation}
-		 					\psi_n(x) = C_1 sin(\sqrt{\lambda_n}x) + C_2 cos(\sqrt{\lambda_n}x)
+				V_1 = \Big\{ p(x) | p(x) =  a_2 (x^2 - \frac{3}{2}x)\Big\}
 			\end{equation}
-		 				apply the boundary condition yields
+			Thus, for any $v \in V_1$
 			\begin{equation}
-		 					C_2 = 0
+				\begin{aligned}
+					R(v) & = \frac{<v, Lv>}{<v, v>}\\
+					     & = \frac{\int_{0}^{1} a_2 (x^2 - \frac{3}{2}x) (-2a_2) dx }{\int_{0}^{1} a_2^2 (x^2 - \frac{3}{2}x)^2 dx}\\
+					     & = -2\frac{\int_{0}^{1} (x^2 - \frac{3}{2}x) dx }{\int_{0}^{1} (x^2 - \frac{3}{2}x)^2 dx}\\
+					     & = 4.167
+				\end{aligned}
+			\end{equation}
+		\item 
+			Denote $p(x) = a_0 + a_1 x + a_2 x^2 + a_3 x^3$, the B.V. at endpoints implies that  
+			\begin{equation}
+				V_2 = \Big\{ p(x) | p(x) =  a_2 (x^2 - \frac{3}{2}x) + a_3 (x^3 - 2x)\Big\}
+			\end{equation}
+			Thus, for any $v \in V_2$
+			\begin{equation}
+				\begin{aligned}
+					R(v) & = \frac{<v, Lv>}{<v, v>}\\
+						& = \frac{\int_{0}^{1} [a_2 (x^2 - \frac{3}{2}x) + a_3(x^2 - 2 x)][2a_2 + 6a_3 x] dx }{\int_{0}^{1} [a_2 (x^2 - \frac{3}{2}x) + a_3(x^2 - 2 x)]^2 dx}\\
+						& = \frac{175a_2^2 + 630a_2a_3 + 588a_3^2}{42a_2^2 + 154a_2a_3 + 142a_3^2}
+				\end{aligned}
+			\end{equation}
+			As the leading coefficient $a_3\neq 0$, then, denote $t \triangleq \frac{a_2}{a_3}$
+			\begin{equation}
+				R(v) = \frac{175t^2 + 630 t + 588}{42t^2 + 154t + 142}
+			\end{equation}
+			It's obvious that $R(v)$ goes to its minimal when $t \rightarrow \infty$, thus $\min R(v) = \frac{175}{42}=4.1667$.
+		\item 
+			Firstly, determine the general form of each element $v \in V_3$.\\
+			Denote $v(x) = a_2 (x^2 - \frac{3}{2}x) + a_3 (x^3 - 2x)$ as $v \in V_2$, then, as $v$ also lies in $V_1^\perp$, it means
+			\begin{equation}
+				\int_{0}^{1} (x^2 - \frac{3}{2}x) v(x) dx = 0
+			\end{equation}
+			namely
+			\begin{equation}
+				a_2 \int_{0}^{1} (x^2 - \frac{3}{2}x)^2 dx + a_3 \int_{0}^{1} (x^2 - \frac{3}{2}x)(x^3 - 2x) dx = 0
+			\end{equation}
+			Thus
+			\begin{equation}
+				a_2 = - \frac{16}{3} a_3
+			\end{equation}
+			Hence
+			\begin{equation}
+				v(x) = a_3(x^3 - \frac{16}{3}x^2 + 6x)
 			\end{equation}
@@
 			\begin{equation}
-		 					C_1 sin(\sqrt{\lambda_n}) = 0
+				v''(x) = a_3(6x - \frac{32}{3})
 			\end{equation}
-		 				Thus
+			Thus, for any $v \in V_3$, the second eigenvalue is estimated as
 			\begin{equation}
-		 					\lambda_n = (n\pi)^2
+				\begin{aligned}
+					R(v) & = \frac{<v, Lv>}{<v, v>}\\
+						& = -\frac{\int_{0}^{1} (x^3 - \frac{16}{3}x^2 + 6x)(6x - \frac{32}{3}) dx }{\int_{0}^{1} (x^3 - \frac{16}{3}x^2 + 6x)^2 dx}\\
+						& = 4.2803
+				\end{aligned}
 			\end{equation}
-		 				and
-		 				\begin{equation}
-		 					\psi_n(x) = C_2 sin(n\pi x) \quad (C_2 \neq 0)
-		 				\end{equation}
-		 			\item 
-		 				If $\lambda_n = 0$, then
-		 				\begin{equation}
-		 					\psi_n(x) = C_0 + C_1 x
-		 				\end{equation}
-		 				Apply the B.C. yields $C_0 = C_1 = 0$, which indicates 0 is not an eigenvalue for $L$.
-		 			\item 
-		 				If $\lambda_n < 0$, then
-		 				\begin{equation}
-		 					\psi_n(x) = C_1 e^{\sqrt{-\lambda_n}x} + C_2 e^{-\sqrt{-\lambda_n}x}
-		 				\end{equation}
-		 				Apply the B.C. yields $C_0 = C_1 = 0$, which indicates  $\lambda_n < 0$ are not eigenvalues for $L$.
-		 		\end{enumerate}
-			\end{proof}
-		\item
-
-		\item
-
 	\end{enumerate}

### 2018-12-06 VV556/HW10/Q1_5.m

@@ -1,0 +1,14 @@
+clear all; close all; clc;
+
+syms a2;
+syms a3;
+syms x;
+
+p = a2 .* (x.^2 - 1.5.*x) + a3 .*(x.^3 - 2.* x);
+ddp = 2.*a2 + 6.*a3.*x;
+
+t1 = -p .* ddp;
+t2 =p.^2;
+
+R = int(t1, x, 0, 1) / int(t2, x, 0, 1);
+simplify(R)

### 2018-12-06 VV556/HW10/Q1_6.m

@@ -1,0 +1,16 @@
+clear all; close all; clc;
+
+syms a2;
+syms a3;
+syms x;
+
+t1 = (x.^2 - 1.5.*x).^2;
+t2 = (x.^2 - 1.5.*x) .* (x.^3 - 2.* x);
+
+int(t1, 0, 1)
+int(t2, 0, 2)
+
+v1 = (x.^3 - 16/3 .*x.^2 + 6.*x) .* (6 .* x - 32/3);
+v2 = (x.^3 - 16/3 .*x.^2 + 6.*x) .^2;
+
+R = int(v1, 0, 1)/int(v2, 0, 1)

### 2019-03-03 VG500/WEEK1/summary.tex
week1 summary

\documentclass[paper=a4, fontsize=11pt]{scrartcl}

\usepackage{lipsum}
\usepackage{amsmath, amsfonts, amssymb}

\title{Summary of "PREMIX: A Program for Modeling Steady, Laminar, One-Dimensional Premixed Flames"}
\author{Yu Cang \ \ 018370210001}
\date{2019-03-01}

\begin{document}

\maketitle

Detailed numerical procedures on solving the 1-D steady laminar premixed flames are described in this report. Generally, this program combines the damped Newton method where second order convergence can be achived but may be unstable, and the explict time-stepping iteration which is very reliable but converge slowly.\\
At the beginning, this program tries to solve the steady equation set with the damped Newton method, once the newton iteration fails, it turns to solve the time-dependent equation set. In this way,  a new starting estimation can be provided for the next trial of the damped Newton method. \\
Controling parameters can be set inside each stage, which should be choose properly according to the properties of target physical problem.

\end{document}

### 2019-03-03 VG500/WEEK1/summary.tex
fix typo

@@
 Detailed numerical procedures on solving the 1-D steady laminar premixed flames are described in this report.
-Generally, this program combines the damped Newton method where second order convergence can be achived but may be unstable, and the explict time-stepping iteration which is very reliable but converge slowly.\\
+Generally, this program combines the damped Newton method where second order convergence can be achived but may be unstable, and the explict time-stepping iteration which is very reliable but converges slowly.\\
 At the beginning, this program tries to solve the steady equation set with the damped Newton method, once the newton iteration fails, it turns to solve the time-dependent equation set.
@@
 \\
-Controling parameters can be set inside each stage, which should be choose properly according to the properties of target physical problem.
+Controling parameters can be set inside each stage, which should be choosen properly according to the properties of target physical problem.
 

### 2019-03-06 VG500/HW0/submission.tex
HW0 done

--- 2018-11-28 VV556/HW9/submission.tex
@@
 
-%----------------------------------------------------------------------------------------
-%	TITLE SECTION
-%----------------------------------------------------------------------------------------
-
 \newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Methods of Applied Mathematics I\\ HW9 \\ % The assignment title
+\huge Technical Communication\\ HW0 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\author{Yu Cang \quad 018370210001\\ Zhiming Cui \quad 017370910006} % Your name
+\author{Author: Yu Cang \quad 018370210001\\ Partner: Guiwen Tan \quad 118370910014} % Your name
 
@@
 
-\section{Exercise9.1}
-	\begin{enumerate}
-		\item
-			\begin{proof}
-				Since
-				\begin{equation}
-					\begin{aligned}
-						(LKu)(x) & = -\frac{d^2}{d x^2} \int_{0}^{1} g(x, \xi) u(\xi) d\xi\\
-								 & = -\frac{d^2}{d x^2} \Bigg(\int_{0}^{x} g(x, \xi) u(\xi) d\xi + \int_{x}^{1} g(x, \xi) u(\xi) d\xi \Bigg)\\
-								 & = -\frac{d^2}{d x^2} \Bigg(\int_{0}^{x} \xi(1-x) u(\xi) d\xi + \int_{x}^{1} x(1-\xi) u(\xi) d\xi \Bigg)\\
-								 & = -\frac{d^2}{d x^2} \Bigg((1-x)\int_{0}^{x} \xi u(\xi) d\xi + x\int_{x}^{1} (1-\xi) u(\xi) d\xi \Bigg)\\
-								 & = -\frac{d}{d x} \Bigg(-\int_{0}^{x} \xi u(\xi) d\xi + \int_{x}^{1} (1-\xi) u(\xi) d\xi \Bigg)\\
-								 & = xu(x) + (1-x) u(x) = u(x)
- 					\end{aligned}
-				\end{equation}
-				Thus, $LK=I$, which means $L = K^{-1}$.
-			\end{proof}
-		\item 
-			\begin{proof}
-				($\Rightarrow$) Suppose $\frac{1}{\lambda}$ is an eigenvalue for $K$, then
-				\begin{equation}
-					ku = \frac{1}{\lambda}u
-				\end{equation} 
-				Thus
-				\begin{equation}
-					u = \lambda K u
-				\end{equation}
-				Take the operator $L$ on it
-				\begin{equation}
-					Lu = \lambda LKu = \lambda Iu = \lambda u
-				\end{equation}
-				which indicates that $\lambda$ is an eigenvalue of $L$.\\
-				($\Leftarrow$) Suppose $\lambda \neq 0$ is an eigenvalue of $L$, then
-				\begin{equation}
-					Lu = \lambda u
-				\end{equation}
-				Thus
-				\begin{equation}
-					u = \frac{1}{\lambda} Lu
-				\end{equation}
-				As $K = L^{-1}$ is known, take the operator $K$ onto it yields
-				\begin{equation}
-					Ku = \frac{1}{\lambda}KLu = \frac{1}{\lambda} Iu = \frac{1}{\lambda} u
-				\end{equation}
-				which indicates that $\frac{1}{\lambda}$ is an eigenvalue of $K$.\\
-				It's clear that for the given $\lambda$, $K$ and $L$ share the same eigenfunction $u(x)$.
-			\end{proof}
-		\item 
-			\begin{proof}
-				It's obvious that $L$ is bounded over $M$.\\
-				Since
-				\begin{equation}
-					\begin{aligned}
-						<u, Lv> &= -\int_{0}^{1} u(x)v''(x) dx = -\Bigg(u(x)v'(x)\Big|_0^1 - \int_{0}^{1}u'(x)v'(x)dx\Bigg)\\
-								&= \int_{0}^{1}u'(x)v'(x)dx = \int_{0}^{1}u'(x)dv(x) = u'(x)v(x)\Big|_0^1 - \int_{0}^{1} v(x)u''(x)dx\\
-								& = -\int_{0}^{1} u''(x)v(x)dx = <Lu, v>
-					\end{aligned}
-				\end{equation}
-				which indicates that $L$ is self-adjoint. Thus the eigenvalues of $L$ are real numbers.\\
-		 		The eigenfunction $\psi_n(x)$ of $L$ together with $\lambda_n$ satisfy 
-		 		\begin{equation}
-		 			\psi_n''(x) + \lambda_n \psi_n(x) = 0
-		 		\end{equation}
-		 		and
-		 		\begin{equation}
-		 			\psi_n(0) = \psi_n(1) = 0
-		 		\end{equation}
-		 		Solution of this ODE depends on the sign of $\lambda_n$.\\
-		 		\begin{enumerate}
-		 			\item 
-		 				If $\lambda_n > 0$, then
-		 				\begin{equation}
-		 					\psi_n(x) = C_1 sin(\sqrt{\lambda_n}x) + C_2 cos(\sqrt{\lambda_n}x)
-		 				\end{equation}
-		 				apply the boundary condition yields
-		 				\begin{equation}
-		 					C_2 = 0
-		 				\end{equation}
-		 				and
-		 				\begin{equation}
-		 					C_1 sin(\sqrt{\lambda_n}) = 0
-		 				\end{equation}
-		 				Thus
-		 				\begin{equation}
-		 					\lambda_n = (n\pi)^2
-		 				\end{equation}
-		 				and
-		 				\begin{equation}
-		 					\psi_n(x) = C_2 sin(n\pi x) \quad (C_2 \neq 0)
-		 				\end{equation}
-		 			\item 
-		 				If $\lambda_n = 0$, then
-		 				\begin{equation}
-		 					\psi_n(x) = C_0 + C_1 x
-		 				\end{equation}
-		 				Apply the B.C. yields $C_0 = C_1 = 0$, which indicates 0 is not an eigenvalue for $L$.
-		 			\item 
-		 				If $\lambda_n < 0$, then
-		 				\begin{equation}
-		 					\psi_n(x) = C_1 e^{\sqrt{-\lambda_n}x} + C_2 e^{-\sqrt{-\lambda_n}x}
-		 				\end{equation}
-		 				Apply the B.C. yields $C_0 = C_1 = 0$, which indicates  $\lambda_n < 0$ are not eigenvalues for $L$.
-		 		\end{enumerate}
-			\end{proof}
-		\item
+\section{Summary of Yu Cang's  research project}
+	Currently, my research focus on numerical simulation of the one-dimensional  counter-flow diffusion flame.\\
+	Numerical schemes play an important role in solving this problem as proper schemes have better convergence performance. \\
+	Generally speaking, a hybrid scheme consists of the damped Newton method and the semi-implicit time stepping scheme is used.\\
+	At the beginning, I try to solve the steady-state equation set with the damped Newton method, once the newton iteration fails, it turns to solve the time-dependent equation set.
+In this way,  a new starting estimation can be provided for the next trial of the newton method.
 
-		\item
+\section{Paraphrase of Guiwen Tan's work}
+	A wide range of spatial and temporal scales exist in a turbulence field and they interact with each other.\\
+	The spatial structure at different scales is the focus of his reseach. In order to show the spatial structures at different levels, the multi-level segment analysis(MSA) method is adopted.\\
+	At present, he uses the sinusoidal function, fractional Brownain motion, and DNS result of real turbulence field to verify the MSA method.
+The statistical characteristics of each testing case indicates if the MSA method is justified.
 
-	\end{enumerate}
+\section{Improved Version of Yu Cang's work}
+	The configuration of one-dimensional counter-fow diffusion flame involves a burning chamber and two opposing placed inlents, where fuel and oxdizer are pumped into the chamber.
+A flame front burning in between is sustained, and that is counter-flow diffusion flame.\\
+	My research mainly focus on the numerical simulation of the one-dimensional counter-flow diffusion flame.
+Numerical method should be choosen carefully as some of schemes may converge faster and better.
+\\
+	Usually, I use the damped Newton method and the semi-implicit time stepping scheme in numerical simulation.
+At first, I use the damped Newton method to deal with steady-state equation set.
+Once the damped Newton method fails or diverges, I switch to the time-dependent equation set with the semi-implicit time stepping scheme.
+In this way,  results from the time-dependent equation set can provide a new starting estimation for the newton method of next step.
 

### 2019-03-07 VG500/HW1/submission_ex2.tex
Hw1

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.1 distribution.
%   Version 4.1r of REVTeX, August 2010
%
%   Copyright (c) 2009, 2010 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\begin{document}

%\preprint{APS/123-QED}

\title{Summary of 2 paper related to turbulent combustion}% Force line breaks with \\
\thanks{VG500 course from JI SJTU}%

\author{Yu Cang}
\affiliation{Shanghai Jiaotong University}
\date{\today}

\begin{abstract}
	Summary of 2 papers published in PRL related to turbulent combustion are discussed.
\end{abstract}

\maketitle

%\tableofcontents

\section{Summary of "Spontaneous Transition of Turbulent Flames to Detonations in Unconfined Media"}

Deflagration-to-detonation transition (DDT) can occur in a wide range of environments, ranging from industrial systems to astrophysical thermonuclear supernovae explosions. \\
This paper talks mainly about the nature of DDT in confined systems with walls, internal obstacles, or pre-existing shocks, although it remains unclear if DDT can occur in unconfined media or not.\\
Direct numerical simulations (DNS) was used so that high enough turbulent intensities can be achived. Numerical results show that unconfined, subsonic, premixed, turbulent flames are inherently unstable to DDT. The associated mechanism, based on the nonsteady evolution of flames faster than the Chapman-Jouguet deflagrations, is qualitatively different from the traditionally suggested spontaneous reaction-wave model. Critical turbulent flame speeds, predicted by this mechanism for the onset of DDT, are in agreement with DNS results.

\section{Summary of "Facilitated Ignition in Turbulence through Differential Diffusion"}
In this paper, authors indicate that ignition in turbulence is much more likely to be done, compared with the case in quiescence. This is quite out of intuition and the reason behind is explained. \\
Experiments were carried out showing that it is thermal diffusivity that play an important role in spreading inside the mixture rather than the mass diffusivity. \\
In such cases, turbulence breaks the otherwise single spherical flame of positive curvature, and hence positive aerodynamics stretch, into a multitude of wrinkled flamelets subjected to either positive or negative stretch, such that the intensified burning of the latter constitutes local sources to facilitate ignition.

\end{document}
%
% ****** End of file apssamp.tex ******

### 2019-03-15 VG500/WEEK3/20190315.tex
weekly writting

\documentclass[paper=a4, fontsize=11pt]{scrartcl}

\usepackage{lipsum}
\usepackage{amsmath, amsfonts, amssymb}

\title{Summary of "Progress-variable approach for large-eddy simulation of non-premixed turbulent combustion"}
\author{Yu Cang \ \ 018370210001}
\date{2019-03-15}

\begin{document}

\maketitle

To simulate the combustion process, a set of partial differential equations needs to be solved, including the continuity equation, the momentum equation, the energy equation and the species equations. There exist quite strong non-linear source terms in the energy equation and the species equations, which pose difficulties to traditional solution methods.\newline
Instead of treating these non-linear terms directly, a new approach is introduced in this paper, where two mapping variables are introduced. In this way, all of the detailed chemical processes are mapped to a reduced system of tracking scalars. The governing equations of these mapped variables are much easier to handle, as the source terms do not exist any more.

\end{document}

### 2019-03-20 VG500/WEEK2/20190308.tex
re-paraphrase of week1 article

\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\usepackage{amsmath, amsfonts, amssymb}

\title{Paraphrase of  a paragraph in "PREMIX: A Program for Modeling Steady, Laminar, One-Dimensional Premixed Flames"}
\author{Yu Cang \ \ 018370210001}
\date{2019-03-08}

\begin{document}

\maketitle

\section{Original paragraph}
	The numerical solution procedure begins by making finite difference approximations to reducethe boundary value problem to a system of algebraic equations. The initial approximations are usually ona very coarse mesh that may have as few as five or six points. After obtaining a solution on the coarsemesh, new mesh points are added in regions where the solution or its gradients change rapidly.  Weobtain an initial guess for the solution on the finer mesh by interpolating the coarse mesh solution. Thisprocedure continues until no new mesh points are needed to resolve the solution to the degree specifiedby the user.  This continuation from coarse to fine meshes has several important benefits that areexplained later in this section.  We attempt to solve the system of algebraic equations by the dampedmodified Newton algorithm. However, if the Newton algorithm fails to converge, the solution estimate isconditioned by a time integration. This provides a new starting point for the Newton algorithm that iscloser to the solution, and thus more likely to be in the domain of convergence for Newton’s method. As the mesh becomes finer we normally find that the estimate interpolated from the previous mesh is withinthe domain of convergence of Newton’s method. This point is key to the solution strategy.

\section{My paraphrase}
	To solve the Boundary Value Problem(BVP), the governing equations are approximated by Finite Difference Method(FDM) and the a system of algebraic equations are to be solved.\newline
	The numerical procedure starts from a coarse mesh so that the converged solution is more likely to be achieved. Then it seeks better solution on a finer mesh and the corresponding initial values are calculated from interpolation of previous results.\newline
	A hybrid scheme is adopted to solve these algebraic equations. First, the solver tries the damped Newton method, which has faster convergence speed, but unstable. Once the damped Newton method fails, it switches to the time-stepping method which is stable but  slow to converge. As the mesh becomes finer and finer, it's normally expected that the converged solution will be achived.

\end{document}

### 2019-03-20 VG500/HW2/submission.tex
h2 draft

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages

\usepackage{algorithm, algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}} %Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm

\usepackage{graphicx}
\usepackage{blindtext}

\usepackage{listings}
\lstset{language=Matlab}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height
\newcommand*{\dif}{\mathop{}\!\mathrm{d}}

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Technical Communication\\ HW2 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yu Cang \quad 018370210001} % Your name

\date{\normalsize \today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title

\section{Writing Mathematics}
	As a final example, consider the triple compositions
	\begin{eqnarray}
		f(x)=\int_a^{\big(\int_a^{x^3} {\frac{1}{1+\sin^2{t}}} dt \big)} \frac{1}{1+\sin^2{t}} dt,
		\quad
		 g(x)=\int_a^{\left[\begin{matrix}(\int_a^x \frac{1}{1+\sin^2{t}} dt)\\\int_a \frac{1}{1+\sin^2{t}} dt\end{matrix}\right]} \frac{1}{1+\sin^2{t}} dt,\notag
	\end{eqnarray}
	which can be written
	\[
		f=F\circ F\circ C \quad \mbox{and}\quad g=F\circ F\circ F.
	\]
	Suppose $F(x)=\int_a^x \dfrac{1}{1+\sin^2{t}} dt$ and $C(x)=x^3$, we have
	\begin{align}
		f'(x) & = F'(F(C(x)))\cdot F'(C(x))\cdot C'(x) \notag\\
		       & = \dfrac{1}{1+\sin^2{\left( \int_a^{x^3} \dfrac{1}{1+\sin^2{t}} dt \right)}} \cdot \dfrac{1}{1+\sin^2{x^3}} \cdot 3x^2.\notag
	\end{align}
	Likewise, we have
	\begin{align}
		g'(x) & = F'(F(F(x)))\cdot F'(F(x))\cdot F'(x) \notag\\
			   & = \dfrac{1}{1+\sin^2{\left[ \int_a^{ \left( \int_a^x \dfrac{1}{1+\sin^2{t}} dt \right) } \dfrac{1}{1+\sin^2{t}} dt \right]}} \cdot \dfrac{1}{1+\sin^2{\left( \int_a^{x} \dfrac{1}{1+\sin^2{t}} dt \right)}} \cdot \dfrac{1}{1+\sin^2{x}}.\notag
	\end{align}

\section{\LaTeX}
	\subsection{Exercise on Slide 242}
		\begin{eqnarray}\notag
			x^{y+z}_{4t},\ \frac{y+\frac{3z}{2}}{b},\ \sqrt[n]{\Omega},\ \sum\limits_{n=0}^{\infty}n,\  \int_{0}^{1}\frac{1}{x} dx,\ \forall n \in \mathbb{N} \exists m\ \mbox{such that}\ n-m=0
		\end{eqnarray}
	\subsection{Exercise on Slide 246}
		\begin{enumerate}
			\item[1] \textbf{Using package blindtext} \newline
				\blindmathpaper

			\item[2] \textbf{Reproduce equations} \newline
				\begin{equation}\notag
					\bar{x}=\dfrac{1}{n}\sum_{i=1}^{i=n} x_i=\dfrac{x_1+x_2+\ldots+x_n}{n} 
				\end{equation}

				\begin{equation}\notag
					\int_0^\infty e^{-\alpha x^2} \dif{x}=\dfrac{1}{2} \sqrt{\int_{-\infty}^\infty e^{-\alpha x^2}}\dif{x} \int_{-\infty}^\infty e^{-\alpha y^2}\dif{y} =\dfrac{1}{2} \sqrt{\dfrac{\pi}{\alpha}}
				\end{equation}

				\begin{equation}\notag
					\sum_{k=0}^\infty a_0q^k=\lim_{n\rightarrow \infty}\sum_{k=0}^n a_0q^k=\lim_{n\rightarrow \infty}a_0 \dfrac{1-q^{n+1}}{1-q}=\dfrac{a_0}{1-q}
				\end{equation}

				\begin{equation}\notag
					x_{1,2}=\dfrac{-b\pm \sqrt{b^2-4ac}}{2a}=\dfrac{-p\pm \sqrt{p^2-4q}}{2}
				\end{equation}

				\begin{equation}\notag
					\dfrac{\partial^2 \Phi}{\partial x^2}+\dfrac{\partial^2 \Phi}{\partial y^2}+\dfrac{\partial^2 \Phi}{\partial z^2}=\dfrac{1}{c^2}\dfrac{\partial^2 \Phi}{\partial t^2}
				\end{equation}

			\item[3] \textbf{Vandermonde matrix}
				\begin{equation}\notag
					\left[\begin{matrix}
						1 & \alpha_1 & \alpha^2_1 &\ldots &\alpha^{n-1}_1 \\
						1 & \alpha_2 & \alpha^2_2 &\ldots &\alpha^{n-1}_2 \\
						1 & \alpha_3 & \alpha^2_3 &\ldots &\alpha^{n-1}_3 \\
						\vdots & \vdots & \vdots & \ddots & \vdots \\
						1 & \alpha_m & \alpha^2_m &\ldots &\alpha^{n-1}_m
					\end{matrix}\right]
				\end{equation}
		\end{enumerate}
	\subsection{Exercise on Slide 250}
		\begin{equation}\notag
			\begin{aligned}
				\tilde{E}(\omega)=& \int_{-\infty}^{\infty}E_0\sin(\omega_0t)e^{-2i\pi\omega t}dt \\
				\sin(x)= & \frac{e^{ix}-e^{-ix}}{2i} \\
				e^ae^b= & e^{a+b} \\
				\int_{-\infty}^{\infty}e^{it(x-x')}dt=&2\pi \delta(x-x')\\
				\tilde{E}(\omega)=& \frac{E_0}{2i}\int_{-\infty}^{\infty}e^{-2i\pi t(\omega-\frac{\omega_0}{2\pi})}-e^{-2i\pi t(\omega+\frac{\omega_0}{2\pi})}dt \\
				\tilde{E}(\omega)=&\frac{-2\pi^2}{i}E_0[\delta(\omega-\frac{\omega_0}{2\pi})-\delta(\omega+\frac{\omega_0}{2\pi})]
			\end{aligned}
		\end{equation}

\section{Group Exercise}
	I'm in Group 2, responsible for paragraph 4, 14 and 19.
	\subsection{Summary}
		In paragraph 4, the key idea author want to convey is, when writting something, we'd better have some target readers in mind. In this way, emphasis on will be paid at different levels and different aspects so that readers may have better understanding.\newline
		I paragraph 14, details about using correct words are explained. First of all, using words correctly does not mean to redundency. Instead, it means to express both clearly and precisely so that ambiguity does not exist, and readers will not be confused or mislead. Also, instead of using symbolic notations, which is quite cumbersome, it's better to use sentences expressing arguments or theorems.\newline
		In paragraph 19, the author tells us not to be disturbed by editorial related issues. Some of editorial work like spelling check are helpful, but they may apply some editorial rules mechanically, which change the original meaning of contents. If some intrinsic words have been used, we should pay attention to keep them unchanged.

\section{Grammar}
	\subsection{Plurals of given words}
		\begin{enumerate}
			\item[(a)] means: means
			\item[(b)] paralysis: paralyses
			\item[(c)] curriculum: curricula/curriculums
			\item[(d)] oasis: oases
			\item[(e)] offspring: offspring/offsprings
			\item[(f)] criterion: criteria/criterions
			\item[(g)] Chinese: Chinese
			\item[(h)] antenna: antennae/antennas
			\item[(i)] stimulus: stimuluses/stimuli
			\item[(j)] fungus: fung/funguses
			\item[(k)] alumnus: alumni
			\item[(l)] series: series
			\item[(m)] diagnosis: diagnoses
			\item[(n)] vita: vitae
			\item[(o)] American: American
			\item[(p)] synopsis: synopses
		\end{enumerate}

	\subsection{Filling the blanks}
		(a) \underline{\makebox[1cm]{The}} Decline and Fall of \underline{\makebox[1cm]{the}} Roman Empire\\
		(b) \underline{\makebox[1cm]{The}} complexity of \underline{\makebox[1cm]{the}} problem of \underline{\makebox[1cm]{the}} decline and fall of the Roman Empire is made evident by \underline{\makebox[1cm]{a}} wide variety of causes that are emphasized in varying degrees by \makebox[1cm]{\hrulefill}different authors.\\
		(c) Fortunately, \underline{\makebox[1cm]{a}} concise formulation of Edward Gibbon serves as \underline{\makebox[1cm]{a}} widely accepted basis for \makebox[1cm]{\hrulefill} modern discussion of \underline{\makebox[1cm]{the}} problem.\\
		(d) According to Gibbon,\underline{\makebox[1cm]{the}} empire reached its peak during \underline{\makebox[1cm]{the}} administration of \makebox[1cm]{\hrulefill} two Antonines.\\
		(e) After that, however, \underline{\makebox[1cm]{the}}extent of \makebox[1cm]{\hrulefill} Roman conquest became too great to be managed by \makebox[1cm]{\hrulefill} Roman government,\underline{\makebox[1cm]{the}} decline began.\\
		(f) \underline{\makebox[1cm]{The}} military government was weakened and finally dissolved as \makebox[1cm]{\hrulefill} barbarians were allowed to constitute \underline{\makebox[1cm]{an}} ever-growing percentage of \underline{\makebox[1cm]{the}} Roman legions.\\
		(g) \underline{\makebox[1cm]{The}} victorious legions began to dominate and corrupt \underline{\makebox[1cm]{the}} government, weakening it at \underline{\makebox[1cm]{the}} time when it most needed \underline{\makebox[1cm]{a}} strength to overcome \makebox[1cm]{\hrulefill} other problems.

\end{document}

### 2019-03-20 VG500/WEEK4/20190322.tex
weekly writting 4

--- 2019-03-20 VG500/WEEK2/20190308.tex
@@
 
-\title{Paraphrase of  a paragraph in "PREMIX: A Program for Modeling Steady, Laminar, One-Dimensional Premixed Flames"}
+\title{Paraphrase of  a paragraph in "Progress-variable approach for large-eddy simulation of non-premixed turbulent combustion"}
 \author{Yu Cang \ \ 018370210001}
-\date{2019-03-08}
+\date{2019-03-22}
 
@@
 \section{Original paragraph}
-	The numerical solution procedure begins by making finite difference approximations to reducethe boundary value problem to a system of algebraic equations.
-The initial approximations are usually ona very coarse mesh that may have as few as five or six points.
-After obtaining a solution on the coarsemesh, new mesh points are added in regions where the solution or its gradients change rapidly.
-Weobtain an initial guess for the solution on the finer mesh by interpolating the coarse mesh solution.
-Thisprocedure continues until no new mesh points are needed to resolve the solution to the degree specifiedby the user.
-This continuation from coarse to fine meshes has several important benefits that areexplained later in this section.
-We attempt to solve the system of algebraic equations by the dampedmodified Newton algorithm.
-However, if the Newton algorithm fails to converge, the solution estimate isconditioned by a time integration.
-This provides a new starting point for the Newton algorithm that iscloser to the solution, and thus more likely to be in the domain of convergence for Newton’s method.
-As the mesh becomes finer we normally find that the estimate interpolated from the previous mesh is withinthe domain of convergence of Newton’s method.
-This point is key to the solution strategy.
 
 \section{My paraphrase}
-	To solve the Boundary Value Problem(BVP), the governing equations are approximated by Finite Difference Method(FDM) and the a system of algebraic equations are to be solved.\newline
-	The numerical procedure starts from a coarse mesh so that the converged solution is more likely to be achieved.
-Then it seeks better solution on a finer mesh and the corresponding initial values are calculated from interpolation of previous results.\newline
-	A hybrid scheme is adopted to solve these algebraic equations.
-First, the solver tries the damped Newton method, which has faster convergence speed, but unstable.
-Once the damped Newton method fails, it switches to the time-stepping method which is stable but  slow to converge.
-As the mesh becomes finer and finer, it's normally expected that the converged solution will be achived.
 

### 2019-03-20 VG500/WEEK4/20190322.tex
paraphrase of a paragraph in week3 article

@@
 \title{Paraphrase of  a paragraph in "Progress-variable approach for large-eddy simulation of non-premixed turbulent combustion"}
-\author{Yu Cang \ \ 018370210001}
+\author{Yu Cang \quad 018370210001}
 \date{2019-03-22}
@@
 \section{Original paragraph}
-
+	A new approach to chemistry modelling for large-eddy simulation of turbulent reacting flows is developed.
+Instead of solving transport equations for all of the numerous species in a typical chemical mechanism and modelling the unclosed chemical source terms, the present study adopts an indirect mapping approach, whereby all of the detailed chemical processes are mapped to a reduced system of tracking scalars.
+Here, only two such scalars are considered: a mixture fraction variable, which tracks the mixing of fuel and oxidizer, and a progress variable, which tracks the global extent of reaction of the local mixture.
+The mapping functions, which describe all of the detailed chemical processes with respect to the tracking variables, are determined by solving quasi-steady diffusion-reaction equations with complex chemical kinetics and multicomponent mass diffusion.
+The performance of the new model is compared to fast-chemistry and steady-flamelet models for predicting velocity, species concentration, and temperature fields in a methane-fuelled coaxial jet combustor for which experimental data are available.
+The progress-variable approach is able to capture the unsteady, lifted flame dynamics observed in the experiment, and to obtain good agreement with the experimental data, while the fast-chemistry and steady-flamelet models both predict an attached flame.
 \section{My paraphrase}
+	Without the need to resolve all of the numerous species, in the simulation of chemical reacting flow, the author proposed a new method to ease the numerical efforts.\newline
+	A mapping technology is introduced such that only 2 scalar variables are to be considered.
+The mixture fraction has a linear relation with the numerous species and is used to track the mixing of fuel and oxidizer.
+The progress variable is used to track the global extend of local mixture reaction.\newline
+	Detailed chemical mechanism is used and the mapping function is determined by solving quasi-stead diffusion-reaction equations.
 

### 2019-03-20 VG500/HW2/submission.tex
fix section missing and import remark template

@@
 \usepackage{blindtext}
+\usepackage{enumerate}
 
@@
 	\subsection{Summary}
-		In paragraph 4, the key idea author want to convey is, when writting something, we'd better have some target readers in mind.
-In this way, emphasis on will be paid at different levels and different aspects so that readers may have better understanding.\newline
-		I paragraph 14, details about using correct words are explained.
-First of all, using words correctly does not mean to redundency.
-Instead, it means to express both clearly and precisely so that ambiguity does not exist, and readers will not be confused or mislead.
-Also, instead of using symbolic notations, which is quite cumbersome, it's better to use sentences expressing arguments or theorems.\newline
-		In paragraph 19, the author tells us not to be disturbed by editorial related issues.
-Some of editorial work like spelling check are helpful, but they may apply some editorial rules mechanically, which change the original meaning of contents.
-If some intrinsic words have been used, we should pay attention to keep them unchanged.
+		In paragraph 4, the author mainly talks about the necessity, the advantange and the way towards a well-organized structure.
+Organization is the core competence of a book.
+A clear structure helps readers follow the logic and understand easily.
+Writters need to prepare an outline at first, which may take a long period, and then decide what are around the kernel and put them in.\newline
+		In paragraph 14, the author indicated the importance of using technical terms correctly and gave 3 examples explaining it.
+It's better not to use newly created words, and use old ones instead.\newline
+		In paragraph 19, the author suggest writters to stop, without hesitation, after writting, not to worry about minor modifications. Some tips were provided for checking the manuscripts quickly.
+
+	\subsection{Remarks on peer's work}
+		\begin{enumerate}[(a)]
+			\item \textbf{Remarks on Shuixin Xiao's summary}\newline
+				All the key points in the article are listed, especially for section 4, of which the main ideas from the author are clearly summarized.
+It would be better if some conjunction words are used to connect points.
+This is a good summary without doubt.
+			\item \textbf{Remarks on Yijie Wang's summary}\newline
+				In this summary, the expression is clear and coherent. The core parts of the sections are extracted. It will be much better if the statement can be more concise.
+			\item \textbf{Remarks on Yaoxia Shao's summary}\newline
+				This groupmate makes a really good summary, of which the perspective is quite different and profound.
+Obviously, he has clearly understood the author’s ideas, and paraphrase them in his own words.
+		\end{enumerate}
+
+	\subsection{Discussion}
+		This part is submitted by Xiao Shuixin, whose student ID is 018370910023.
 

### 2019-03-20 VG500/HW2/submission.tex
add remarks

@@
 			\item \textbf{Remarks on Shuixin Xiao's summary}\newline
-				All the key points in the article are listed, especially for section 4, of which the main ideas from the author are clearly summarized.
-It would be better if some conjunction words are used to connect points.
-This is a good summary without doubt.
+				Statements are both clear and specific and core parts are described. No spelling mistakes nor grammar errors.
+
 			\item \textbf{Remarks on Yijie Wang's summary}\newline
-				In this summary, the expression is clear and coherent. The core parts of the sections are extracted. It will be much better if the statement can be more concise.
+				It'a a quite good summary as most aspects in the paragraphs are covered. Author's idea are exactly conveyed, no spelling mistakes nor grammar errors.
+
 			\item \textbf{Remarks on Yaoxia Shao's summary}\newline
-				This groupmate makes a really good summary, of which the perspective is quite different and profound.
-Obviously, he has clearly understood the author’s ideas, and paraphrase them in his own words.
+				This summary is quite pertinent, and main idea of original paragraphs are explained. No spelling mistakes nor grammar errors.
 		\end{enumerate}

### 2019-04-01 VG500/HW3/submission.tex
HW3 done

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages

\usepackage{algorithm, algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}} %Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm

\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{enumerate}
\usepackage{ulem} 
\usepackage{pdfpages}

\usepackage{listings}
\lstset{language=Matlab}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height
\newcommand*{\dif}{\mathop{}\!\mathrm{d}}

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Technical Communication\\ HW3 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yu Cang \quad 018370210001} % Your name

\date{\normalsize \today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title

\section{Mind Map}
	\begin{figure}[!h]
		\centering
		\includegraphics[scale=0.11]{pic/mind_map.png}
		\caption{How to write mathematics}
		\label{fig:htwm}
	\end{figure}

\section{Group Exercise}
	After discussion, we all think figures are generally properly used in this article, and comments from us are listed as below.

	\subsection{Comments from Yu Cang}
		From my point of view, most of the pictures used are of high quality and are both clear and concise. Most of the sketches are showed in 2D mode, which avoid 3D distortion and are easy to identify their meanings. Combination of colors are well arranged, where contrast is apparent and is suitable for printing and visualization. Line plots like Fig. 7 and Fig. 8 are simple and clear, without too many curves exhibited in one plot, distinctions and trends are well reflected. Besides, one remarkable point is that all the labels, if necessary, are accompanied with precisely stated units, which facilitates readers when making comparison and judgement. \newline

		However, some details in these figures need to be furnished. The arrows in Fig. 5 are too dense. The ending points of indicating lines in Fig. 9 seems randomly placed, without a consistent compliance. Further, the gray figure in Fig. 10 may not reveal the distinctions well enough, and may get blurred when printed in black and white.

	\subsection{Comments from Ronghan Chen}
		Generally, the figures in the article look clear at the first sight. The sketches are beautiful. But if we look carefully, we can find many flaws. First, the tips of the arrows are not consistent. For fig. 1, the gap between arrows and targets are different. For fig. 5, the arrows on the right lie on the edges of targets, while the arrow on the top sticks into the target. Second, some of the labels are bad. For fig. 6, fig. 7 and fig. 9, the labels of the axis are a bit vague compared to fig. 10. Third, some texts on the figures are hard to read. For fig. 4, the direction of the words should keep horizontal. For fig. 3, the serial numbers are hard to see. Fourth, the selection of thickness is bad. The arrows in fig. 9 are too thick, as well as the line in fig. 11. In my point of view, I think fig. 8 is the best one of all the figures.

	\subsection{Comments from Rui Gao}
		The figures in the paper by Johnson and Popil are of acceptable quality but not the best among what I have seen. The choice of color are well designed to facilitate reading. The size of words within the figures are designed to be slightly larger than the size of the text. The information within each figure is clearly conveyed. I could have a coarse idea of the whole topic after reading these figures only (i.e. they speak for themselves).\newline

		However, I could see that the figures blur slightly even at 100\% size, which means that when printed on A4 paper (equal to 120\% size) they would also blur. This also indicate that the figures are not vector plots, and the dpi is not high enough. In addition, while the arrows are large and clear enough, the endings are not unified (there are arrows that ends before, at, and after the object they are indicating, for example in figure 1). While the font size is well designed, the fonts in different figures seems to be different (switching between bold and normal). The colorbars in Fig. 10 are not aligned with each other in an unnecessary manner. A few figures seems to be stretched slightly, like Fig. 6.

\section{Writting skills}
	\begin{enumerate}
		\item 
			``\textbf{Just act naturally}'': `naturally' is not suitable to be adverb for `act'.\newline
			``\textbf{Please give your unbiased opinion}'': No objective in this sentence.\newline
			``\textbf{I need an exact estimate by Friday}'': The two words: `exact' and `estimate' contradict with each other.

		\item 
			Before the agent was \sout{completely} able to \sout{finish} explain\sout{ing} the \sout{various} differences between \sout{all of} the \sout{many} outdoor event packages her company was offering, the customer changed his \sout{future} plans.
	\end{enumerate}

\section{\LaTeX}
	Listed as follows
	\includepdf[pages=2]{assignment.pdf}

\end{document}

### 2019-04-01 VG500/WEEK5/20190329.tex
week5 summary

\documentclass[paper=a4, fontsize=11pt]{scrartcl}

\usepackage{lipsum}
\usepackage{amsmath, amsfonts, amssymb}

\title{Summary of "CFD modelling of combustion"}
\author{Yu Cang \ \ 018370210001}
\date{2019-03-29}

\begin{document}

\maketitle

Numerical simulation of gaseous combustions are brifely introduced in this article. Firstly, some basic concepts and definitions are reviewed. Then, classical models like infinitely fast chemistry, eddy break-up concept and laminar flamelet model are discussed. The most important model used nowadays is the laminar flamelet model, where flames are locally viewed as a steady flamelet as the timescale of chemical reaction is much smaller than that of flow. Finally, topics related to turbulent combustion are covered, where the difficulties faced currently are introduced. The lack of proper model to describe averaged chemical reaction source term poses difficulties in CFD practice.

\end{document}

### 2019-04-02 VG500/HW3/submission.tex
minor fix

@@
 		\centering
-		\includegraphics[scale=0.11]{pic/mind_map.png}
+		\includegraphics[width=13.5cm]{pic/mind_map.png}
 		\caption{How to write mathematics}
@@
 \section{Group Exercise}
-	After discussion, we all think figures are generally properly used in this article, and comments from us are listed as below.
-
-	\subsection{Comments from Yu Cang}
-		From my point of view, most of the pictures used are of high quality and are both clear and concise.
-Most of the sketches are showed in 2D mode, which avoid 3D distortion and are easy to identify their meanings.
-Combination of colors are well arranged, where contrast is apparent and is suitable for printing and visualization.
-Line plots like Fig.
-7 and Fig.
-8 are simple and clear, without too many curves exhibited in one plot, distinctions and trends are well reflected.
-Besides, one remarkable point is that all the labels, if necessary, are accompanied with precisely stated units, which facilitates readers when making comparison and judgement.
-\newline
-
-		However, some details in these figures need to be furnished.
-The arrows in Fig.
-5 are too dense.
-The ending points of indicating lines in Fig.
-9 seems randomly placed, without a consistent compliance.
-Further, the gray figure in Fig.
-10 may not reveal the distinctions well enough, and may get blurred when printed in black and white.
-
-	\subsection{Comments from Ronghan Chen}
-		Generally, the figures in the article look clear at the first sight.
-The sketches are beautiful.
-But if we look carefully, we can find many flaws.
-First, the tips of the arrows are not consistent.
-For fig.
-1, the gap between arrows and targets are different.
-For fig.
-5, the arrows on the right lie on the edges of targets, while the arrow on the top sticks into the target.
-Second, some of the labels are bad.
-For fig.
-6, fig.
-7 and fig.
-9, the labels of the axis are a bit vague compared to fig.
-10.
-Third, some texts on the figures are hard to read.
-For fig.
-4, the direction of the words should keep horizontal.
-For fig.
-3, the serial numbers are hard to see.
-Fourth, the selection of thickness is bad.
-The arrows in fig.
-9 are too thick, as well as the line in fig.
-11.
-In my point of view, I think fig.
-8 is the best one of all the figures.
-
-	\subsection{Comments from Rui Gao}
-		The figures in the paper by Johnson and Popil are of acceptable quality but not the best among what I have seen.
-The choice of color are well designed to facilitate reading.
-The size of words within the figures are designed to be slightly larger than the size of the text.
-The information within each figure is clearly conveyed.
-I could have a coarse idea of the whole topic after reading these figures only (i.e.
-they speak for themselves).\newline
-
-		However, I could see that the figures blur slightly even at 100\% size, which means that when printed on A4 paper (equal to 120\% size) they would also blur.
-This also indicate that the figures are not vector plots, and the dpi is not high enough.
-In addition, while the arrows are large and clear enough, the endings are not unified (there are arrows that ends before, at, and after the object they are indicating, for example in figure 1).
-While the font size is well designed, the fonts in different figures seems to be different (switching between bold and normal).
-The colorbars in Fig.
-10 are not aligned with each other in an unnecessary manner.
-A few figures seems to be stretched slightly, like Fig.
-6.
+	All the comments and discussions have been submitted to our team leader. Please see Rui Gao's work.
 
@@
 \section{\LaTeX}
-	Listed as follows
+	See next page.
 	\includepdf[pages=2]{assignment.pdf}

### 2019-04-08 VG500/WEEK6/20190406.tex
6th weekly writing

\documentclass[paper=a4, fontsize=11pt]{scrartcl}

\usepackage{lipsum}
\usepackage{amsmath, amsfonts, amssymb}

\title{Reparaphrase of "CFD modelling of combustion"}
\author{Yu Cang \ \ 018370210001}
\date{2019-04-06}

\begin{document}

\maketitle

\section{Original paragraph}
	The properties of laminar flamelets, e.g. the temperature, density and
species mass fractions as a function of the mixture fraction $\xi$, are evaluated
once and for all outside the flow field calculation to yield a so-called laminar
flamelet library. A library of such relationships used in a calculation is
shown later in an example (see Figure 12.16). The library comprises a set of
relationships $\phi(\xi)$ between scalar flow properties $\phi$ and the mixture fraction
$\xi$. Their form is similar to Figure 12.2, but turbulence causes the flames to
be stretched, which alters the details of the relationships $\phi(\xi)$. To accommodate
the effect of flame stretching due to the flow field in an actual turbulent
flame, it is common practice to incorporate as a parameter either the strain
rate or the scalar dissipation rate, both of which are flow properties, into
the laminar flamelet library calculations.

\section{Re-paraphrase}
	Temperature, density and species mass fractions are properties of laminar flamelets. They are related to the mixture fraction $\xi$, and these relations are called a laminar flamelet library. Such a library is needed to calculate the outside flow, and examples will be shown later (see Figure 12.16). The library is a collection of relations describing how the scalar flow properties $\phi$ changes when the mixtures fraction $\xi$ changes. They are similar to that in Figure 12.2, expect the stretching efffect caused by turbulence alters the details of the relationships $\phi(\xi)$. Usually, an extra parameter, either the strain rate or the scalar dissipation rate, is added into the laminar flamelet library to account for this stretching effect, as both of these two are flow properties.

\end{document}

### 2019-04-08 VG500/WEEK8/20190419.tex
8th weekly writing

\documentclass[paper=a4, fontsize=11pt]{scrartcl}

\usepackage{lipsum}
\usepackage{amsmath, amsfonts, amssymb}

\title{Reparaphrase of "Analysis of the filtered non-premixed turbulent flame"}
\author{Yu Cang \ \ 018370210001}
\date{2019-04-19}

\begin{document}

\maketitle

\section{Original paragraph}
	In reactive turbulence the interaction between the flame and
	flow is extremely complex. For problems with sufficiently high Reynolds numbers of practical interest, because of the large scale separation, both spatially and temporally, direction numerical simulations (DNS) are intractable. Thus models of the required relations need to be constructed. In non-premixed combustion simulation, the flamelet models originally developed by Williams and Peters play important roles. Physically if the flame scale is locally small compared with the turbulent dissipative scale, the flame structure remains to be laminar. Based on the flamelet equations, it is possible to largely reduce the dimensionality of the modeling parameters. The flamelet models have been widely applied because of the clear physical meaning and high numerical efficiency. In recent years successful examples have been extended to various cases such as unsteady processes and non-unity Lewis number effects. The detailed budget analyses suggest that typically the flamelet assumption remains to be reasonable.

\section{Re-paraphrase}
	In reactive turbulence, interaction between flame and flow is extremely complex.For problem with sufficiently high Reynolds number, Direct Numerical Simulation(DNS) is intractable as there exists large scale separation, both spatially and temporally. To describle inner relations, properly constructed models are needed.As originally developed by Williams and Peters, the flamelet model play an important role in the simulation of non-premixed combustion. Physically, the local flame structure remains to be laminar when flame scale is smaller than turbulent dissipative scale locally. With the help of flamelet model, the dimensionality of modeling parameters can be largely reduced. Because of its clear physical meaning and high numerical efficiency, flamelet model has been widely adopted. Recelently, various cases like unsteady process and non-unity Lewis number effects have been extened to successfully, and detailed budget analysis indicates that the flamelet assumption remains reasonable.

\end{document}

### 2019-04-08 VG500/HW4/submission.tex
hw4 draft

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages

\usepackage{algorithm, algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}} %Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm

\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{enumerate}
\usepackage{ulem} 
\usepackage{pdfpages}
\usepackage{multirow}

\usepackage{listings}
\lstset{language=Matlab}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height
\newcommand*{\dif}{\mathop{}\!\mathrm{d}}

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Technical Communication\\ HW4 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yu Cang \quad 018370210001} % Your name

\date{\normalsize \today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title

\section{Writting skills}
	\begin{enumerate}
		\item 
			As shown in Fig. 1, due to stencil aperture dimension variations and stencil cleanliness, variations across the die arise. Also, smaller variations would also show up, due to random defects, such as inclusions in the paste and contamination from the wafer or environment.
		\item 
			\begin{enumerate}[(a)]
				\item 
					While these systems are very sensitive, they are very reliable. As a result, many banks, shops, hotels and other businesses use them, because their components are of the highest quality.
				\item 
					 We are holding the above cheque, but there are insufficient funds in your account to clear it. Originally, our normal practice would be to charge you 150 RMB. However, we will waive the charge this time as this is your first time.
				\item 
					 For inspiring innovation and excellence in our customers and users within a secure and sustainable integrated community, we will create and manage distinctive spaces, and comprise mixed-use developments anchored by business space.
			\end{enumerate}
		\item 
			\begin{enumerate}[(a)]
				\item 
					We can deal with more problems of this kind in such a way, and bring about satisfactory solutions.
				\item 
					Some companies self-generating their own websites is a tendency in the industry, and Internet makes training for the skill of website development more accessible to everyone, so this activity can more and more be handled in-house.
				\item 
					 Harold recommended us to fire Mr. Harrison.
				\item 
					We will ask him to think about changing his work routine.
				\item 
					Their correspondence expired when he learned that they no longer supported his proposal.
				\item 
					This document is used to identify the recovered objects.
			\end{enumerate}
	\end{enumerate}

\section{Group Exercise}
	This section mainly talks about the general guidelines on graphics to be used in scientific writings. \newline
	Firstly, one should spare enough time to generate figures. Roughly, spend as much as that of writing text.\newline 
	Secondly, it is better to prepare an outline and decide what are the most important elements to conveyed before drawing pictures.\newline 
	Thirdly, either placed in stand-alone form or in inlined form, figures should be linked and referenced properly. Usually, one should provide a detailed caption, which illustrates the key point of the figure, and a complete reference that faciliates readers a lot. It's better not to use abbreviations like "Fig.", which may slow readers down. \newline
	Then, consistency between graphics and text should be maintained through out the whole article. For example, it is suggest to use figures of same sacles, take same line width, keep fonts in figures as same as that in text, and choose color coding according to that used in text etc. In practice, instead of using different graphics software, the best way to keep consistency is to use a single graphics program. \newline
	Also, labels play an important role in plots. Text in labels should be of the same font as that in the main text, and fonts between labels should also be consistent with each other. Notions should not be different, for example, $\frac{1}{2}$ vs $0.5$, $e^{-i\pi}$ vs $-1$. In addition, labels should be both clear and well placed, which provide a straight forward explanation.\newline
	Most importantly, issues concerning plots and charts should be carefully handled. 3D pie charts may introduce distortions and should be avoided whenever possible. Instead, table can be used to explain in detail numbers and percentages. It is recommended to use colors that can group things or direct readers' focus. As background patterns may distract and is likely to blur important messages, they should not be used as well. \newline
	Finally, "avoid distractions" and "steer attention" are useful concepts when designing figures. Distraction like strong contrast produced by sparse vs dense, white vs black should be avoided. As human eyes are much better at grouping things according to colors instead of line patterns, distraction originates from dashed or dot lines should also be avoided. Backgourd image is usually unnecessary as it convey little message.

\section{\LaTeX}
	\begin{table}[H]
		\begin{center}
			\begin{tabular}{c |c |c}
				\hline
				Component & Transition & Probability ($\lambda$)\\
				\hline
				\multirow{5}{*}{MDC$_{-}$A} & Limited Bandwidth &0.2\\
				& Memory Leak & 0.3\\
				&Bandwidth Upgrade & 0.5 \\
				& MDC$_{-}$A Reboot &0.4\\
				&MDC Exception & Fixed Rate = 0.8 \\
				\hline
				\multirow{5}{*}{MDC$_{-}$B}& Communication Delay & 0.6\\
				& No WIFI & 0.3\\
				&Protocol Adjustment & 0.2 \\
				& Router Reboot & 0.8  \\
				&MDC Exception & Fixed Rate = 0.8 \\
				\hline
				\multirow{5}{*}{MDC$_{-}$C} & Retrieval Exception &0.3\\
				& System No Response & 0.4 \\
				&Omit Retrieval & 0.8  \\
				& MDC$_{-}$C Reboot & 0.9\\
				&MDC Exception & Fixed Rate = 0.8 \\
				\hline
				\multirow{5}{*}{MSC} & Overload & 0.1\\
				& System Crashed & 0.2 \\
				& Load Adjustment& 0.7 \\
				& MSC  Reboot & 0.9\\
				&MSC Exception& Fixed Rate = 0.9 \\
				\hline
			\end{tabular}
		\end{center}
		\caption{ Transition and probability of MCAS}
	\end{table}

	\begin{table}
		\begin{center}
			\begin{tabular}{ c c}
				\hline
				Trapdoor Size Before Compression (bit) & 65536 \\
				Trapdoor Size After Compression (bit) &3260.32 \\
				Compression Rate (\%) & 4.97 \\
				\hline
			\end{tabular}
		\end{center}
		\caption{Compression Rate}
	\end{table}

	\begin{table}
		\begin{center}
			\begin{tabular}{c |c |c c |c c}
				\hline\multirow{3}{*}{} & \multirow{2}{*}{Native} & \multicolumn{2}{c}{SLA-aware} & \multicolumn{2}{c}{Proportional-share} \\
				& & \multicolumn{2}{c}{Scheduling} & \multicolumn{2}{c}{Scheduling}\\
				\cline{2-6}
				& FPS & FPS & Overhead(\%) & FPS &Overhead(\%)\\
				\hline
				GT1 & 43.023 & 42.044 & 2.28 & 42.221 & 1.86 \\
				GT2 & 48.686 & 45.996 & 5.53 & 48.284 & 0.83\\
				HDRT1 & 59.062 & 57.923 & 1.93 & 57.700 & 2.31 \\
				HDRT2 & 65.808 & 62.854 & 4.90 & 65.984 & -0.27 \\
				\hline
			\end{tabular}
		\end{center}
		\caption{Macrobenchmark Results.}
	\end{table}
\end{document}

### 2019-04-10 VG500/WEEK7/20190412.tex
7th weekly writting

\documentclass[paper=a4, fontsize=11pt]{scrartcl}

\usepackage{lipsum}
\usepackage{amsmath, amsfonts, amssymb}

\title{Summary of "Analysis of the filtered non-premixed turbulent flame"}
\author{Yu Cang \ \ 018370210001}
\date{2019-04-12}

\begin{document}

\maketitle
	In numerical simulation of non-premixed turbulent combustion using Large Eddy Simulation(LES), the author proposed a set of turbulent flamelet equations, which was based on the filtered governing equations. Then, database generated from Direct Numerical Simulation(DNS) was used to analyze the statistical relation between scalar dissipation and chemical reaction source term. Numerical results indicate that $P(\left|\frac{\partial Z}{\partial n}\right|)$ is strongly related to the filter scale, but $P(D_T)$ is almost invariant. Based on these observations, a scaling law was derived from the scalar structure function to describe the conditional mean of the difference between the filtered and original scalars, which is quite useful in estimating chemical source when sub-grid scale models were used.

\end{document}

### 2019-04-10 VG500/HW4/submission.tex
add part of group discussion

@@
 \section{Group Exercise}
+	I'm the group leader and members are Ning Kang and Reze Rouhi Ardeshiri.
+
+	\subsection{Yu Cang's summary}
 		This section mainly talks about the general guidelines on graphics to be used in scientific writings. \newline
@@
 Backgourd image is usually unnecessary as it convey little message.
+
+		\begin{itemize}
+			\item \textbf{Comment by Ning Kang} \newline
+				Yu's summary is very good, and his summary covers almost all the points of this section.
+In addition, he clearly described the precautions for figures.
+However, there are some grammatical problems in his summary.
+For example, the last sentence of the last paragraph is better written as "it conveys little information".
+
+			\item \textbf{Comment by Reze Rouhi Ardeshiri} \newline
+
+		\end{itemize}
+
+	\subsection{Reze Rouhi Ardeshiri's summary}
+		The author of “The TikZ and PGF Packages” book, in Section 7, describes the graphics, which points to good and useful tips.\newline
+		In the first step, to write a paper with a lot of figures, you need to spend a lot of time on each page to have high-quality work and for the design of a figure, at least we need to consider time as much as a text or even more so.\newline
+		In the next step, we must decide what kind of figure to put in the paper so that the reader reaches the goal of what we want that and the reader understands the issue.
+That is, the output of the figure you want to draw is clear to the reader.\newline
+		Also, placing the figure in the text and linking it to the text is one of the remarkable things that can be done in two ways: stand-alone and inline.\newline
+		Additionally, if you want to design the figure, we need to have the same sizes, fonts, and lines in all of the figures and not be different from the other figures and for the integrity of the figures, it's better to use the same software to design the figure.
+In general, there must be consistency between graphics and text to be nice.\newline
+		Label in graphics is one of the significant points in the paper.
+With a good label, you can summarize the description of a figure, also important for labeling should be important points to be readable.
+It’s implying that it should be legible.\newline
+		One of the most important and frequent issues in the papers are plots that can play an important role in understanding the problem and the reports.
+In this case, you should not use 3D pie or 3D bar charts because of the lack of realistic values and percentages.
+That’s why the table is proper replacing for providing the results.\newline
+		Specifying the paper format is one of the things considered in graphics.
+It should not be large headlines, bold text, large, and white areas.
+Also, some of the words that the author has to emphasize should be illustrated with Italic font.
+So the reader will not be confused by reading the paper.
+In a word, avoid distractions!
+
+		\begin{itemize}
+			\item \textbf{Comment by Ning Kang} \newline
+				Reza's summary is very good, and his summary contains the main content of this section.
+Here are two questions from his summary.
+First of all, his summary lacks a general description, and some paragraphs only mention the precautions.
+In addition, some paragraphs lack a description of specific considerations, such as his summary of the third part.
+
+			\item \textbf{Comment by Yu Cang} \newline
+				Obviously, Reze Rouhi Ardeshiri has read the paper thoroughly.
+Main ideas are conveyed with clear explanations.
+For each aspect, both reasons and understandings are well described.
+Examples are provided so that comparison can be imagined.
+In organizing all paragraphs, transitional words are used smoothly, which facilitate readers to grasp the structure quickly.
+But in terms of pronouns used, I think it is not good to use “you”, instead, “one” is much better.
+No spelling mistakes are found.
+In general, it is a wonderful summary.
+
+		\end{itemize}
+
+	\subsection{Ning Kang's summary}
+		This section focuses on the typical good practices and bad practices of the figures used in scientific papers and presents general guidelines. \newline
+		First, the authors should use enough time to generate figures.
+A typical mistake is to write text in a lot of time and to generate the figures in a very little time.
+In general, the cost of time in figures should be as much as writing text.\newline
+		Second, when creating a paper, the authors should firstly write a rough outline, then fill the text to create a draft and continually revise.  \newline
+		Third, whether you place figures in the stand-alone or inline form, you should make the correct links and references.
+In general, you should provide a title that explains the figures, as well as a complete reference.
+A bad practice is to use abbreviations, which may slow down the reader.\newline
+		Good articles need to ensure consistency between all figures and text.
+For example, all figures should be consistent in style, size, font, etc.
+In practice, the same drawing software can be used to meet the previous requirements.
+\newline
+		Almost all the figures contain labels.
+Good labels need to be the same font, consistent with each other and using the same notation.
+In addition, good labels need to help the reader, so the labels need to be close to the figures and let the reader put more focus on the figures.
+\newline
+		Be careful with plots and charts.
+3D pie charts may cause distortion, so try to avoid using them.
+Moreover, the irritating background should be avoided.
+Consider using a table instead of a pie chart.
+Also, avoid using colors arbitrarily, which will distract the reader.
+\newline
+		Finally, when authors design figures, they need to work hard to guide the reader's attention and avoid distractions.
+Good typography is something you do not notice.
+In addition, the strong contrast in the figures will distract the readers, which is something need to avoid.
+In terms of guiding the reader's attention, it is best to use colors instead of lines.
+
+		\begin{itemize}
+			\item \textbf{Comment by Yu Cang} \newline
+				Clearly, Ning Kang has noticed all the key points expressed by the author.
+He has listed all the aspects mentioned in the paper and explained them in detail.
+Both good and bad practices are highlighted and compared, which is convenient for readers to understand.
+Transitional words are properly used, making the summary reads quite smoothly.
+No spelling mistakes were found and, in my opinion, it is an excellent summary.
+
+			\item \textbf{Comment by Reze Rouhi Ardeshiri} \newline
+
+		\end{itemize}
+
+	\subsection{Final Version}
+		This section mainly talks about the general guidelines on graphics to be used in scientific writings. \newline
+		In the first step, to write a paper with a lot of figures, one need to spend a lot of time on each page to have high-quality work and for the design of a figure, at least we need to consider time as much as a text or even more so.\newline
+		Next, one should decide what kind of figure to put in the paper so that the reader reaches the goal of what we want that and the reader understands the issue.
+That is, the output of the figure you want to draw is clear to the reader.\newline
+		At the same time, either placed in stand-alone form or in inlined form, figures should be linked and referenced properly.
+Usually, one should provide a detailed caption, which illustrates the key point of the figure, and a complete reference that faciliates readers a lot.
+It's better not to use abbreviations like "Fig.", which may slow readers down.
+\newline
+		Then, consistency between graphics and text should be maintained through out the whole article.
+For example, it is suggest to use figures of same sacles, take same line width, keep fonts in figures as same as that in text, and choose color coding according to that used in text etc.
+In practice, instead of using different graphics software, the best way to keep consistency is to use a single graphics program.
+\newline
+		Also, labels play an important role in plots.
+Text in labels should be of the same font as that in the main text, and fonts between labels should also be consistent with each other.
+Notions should not be different, for example, $\frac{1}{2}$ vs $0.5$, $e^{-i\pi}$ vs $-1$.
+In addition, labels should be both clear and well placed, which provide a straight forward explanation.\newline
+		Most importantly, issues concerning plots and charts should be carefully handled.
+3D pie charts may introduce distortions and should be avoided whenever possible.
+Instead, table can be used to explain in detail numbers and percentages.
+It is recommended to use colors that can group things or direct readers' focus.
+As background patterns may distract and is likely to blur important messages, they should not be used as well.
+\newline
+		Finally, when authors design figures, they need to work hard to guide the reader's attention and avoid distractions.
+Good typography is something you do not notice.
+In addition, the strong contrast in the figures will distract the readers, which is something need to avoid.
+In terms of guiding the reader's attention, it is best to use colors instead of lines.
 

### 2019-04-11 VG500/HW4/submission.tex
add remaining comments, done

@@
 \section{Group Exercise}
-	I'm the group leader and members are Ning Kang and Reze Rouhi Ardeshiri.
+	I'm the group leader and members are Ning Kang(017370910016) and Reze Rouhi Ardeshiri(018370990002).
 
@@
 			\item \textbf{Comment by Reze Rouhi Ardeshiri} \newline
+				It is clear that Yu has fully studied the section 7 and has an accurate understanding of the content talked in this section.
+That's why he was able to make a good and understandable summary.
+It also used good descriptive words to describe the text so that the reader is not tired with reading the text.
+Although there are weaknesses in grammatically in the text, such as “suggested” instead of “suggest”, “same font like” instead of “same font as”, in general, I can say that it was great.
+Well done!
 
@@
 			\item \textbf{Comment by Reze Rouhi Ardeshiri} \newline
+				Ning had a good summarize for this section.
+He has played very well with words to describe the text, and this is one of the techniques in writing.
+I did not see grammatical errors in this text, except for one that in the second paragraph should use “first” instead of “firstly”.
+In a word, he has done a good job.
 

### 2019-04-14 VG500/HW5/submission.tex
add hw5 start

--- 2019-04-08 VG500/HW4/submission.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Technical Communication\\ HW4 \\ % The assignment title
+\huge Technical Communication\\ HW5 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\section{Writting skills}
+\section{Tense}
+	\begin{enumerate}
+		\item \textbf{past tense}\newline
+			By the time Tom noticed (notice) the doorbell, it had already rung (ring) three times.
+As usual, he was listening (listen) to loud music on his stereo.
+He turned (turn) the stereo down and stood up (stand up) to answer (answer) the door.
+An old man was standing (stand) on the steps.
+The man began (begin) to speak (speak) slowly, asking (ask) for directions.
+
+		\item \textbf{present tense}\newline
+			By the time Tom notices(notice) the doorbell, it has already rung(ring) three times.
+As usual, he is listening (listen) to loud music on his stereo.
+He turns (turn) the stereo down and stands up (stand up) to answer (answer) the door.
+An old man is standing (stand) on the steps.
+The man begins (begin) to speak (speak) slowly, asking (ask) for directions.
+	\end{enumerate}
+
+\section{Passive voice}
 	\begin{enumerate}
 		\item 
-			As shown in Fig.
-1, due to stencil aperture dimension variations and stencil cleanliness, variations across the die arise.
-Also, smaller variations would also show up, due to random defects, such as inclusions in the paste and contamination from the wafer or environment.
+			Your kindness should be thankful.(no passive voice)
 		\item 
-			\begin{enumerate}[(a)]
+			The decision has been delayed due to a lack of time.
 		\item 
-					While these systems are very sensitive, they are very reliable. As a result, many banks, shops, hotels and other businesses use them, because their components are of the highest quality.
+			Preparations for the project was begun in June.
 		\item 
-					 We are holding the above cheque, but there are insufficient funds in your account to clear it.
-Originally, our normal practice would be to charge you 150 RMB.
-However, we will waive the charge this time as this is your first time.
+			Several objections to the decision were raised by the customers.
 		\item 
-					 For inspiring innovation and excellence in our customers and users within a secure and sustainable integrated community, we will create and manage distinctive spaces, and comprise mixed-use developments anchored by business space.
-			\end{enumerate}
-		\item 
-			\begin{enumerate}[(a)]
-				\item 
-					We can deal with more problems of this kind in such a way, and bring about satisfactory solutions.
-				\item 
-					Some companies self-generating their own websites is a tendency in the industry, and Internet makes training for the skill of website development more accessible to everyone, so this activity can more and more be handled in-house.
-				\item 
-					 Harold recommended us to fire Mr. Harrison.
-				\item 
-					We will ask him to think about changing his work routine.
-				\item 
-					Their correspondence expired when he learned that they no longer supported his proposal.
-				\item 
-					This document is used to identify the recovered objects.
-			\end{enumerate}
+			Your application has been processed.
 	\end{enumerate}
 
-\section{Group Exercise}
-	This section mainly talks about the general guidelines on graphics to be used in scientific writings. \newline
-	Firstly, one should spare enough time to generate figures. Roughly, spend as much as that of writing text.\newline 
-	Secondly, it is better to prepare an outline and decide what are the most important elements to conveyed before drawing pictures.\newline 
-	Thirdly, either placed in stand-alone form or in inlined form, figures should be linked and referenced properly.
-Usually, one should provide a detailed caption, which illustrates the key point of the figure, and a complete reference that faciliates readers a lot.
-It's better not to use abbreviations like "Fig.", which may slow readers down.
-\newline
-	Then, consistency between graphics and text should be maintained through out the whole article.
-For example, it is suggest to use figures of same sacles, take same line width, keep fonts in figures as same as that in text, and choose color coding according to that used in text etc.
-In practice, instead of using different graphics software, the best way to keep consistency is to use a single graphics program.
-\newline
-	Also, labels play an important role in plots.
-Text in labels should be of the same font as that in the main text, and fonts between labels should also be consistent with each other.
-Notions should not be different, for example, $\frac{1}{2}$ vs $0.5$, $e^{-i\pi}$ vs $-1$.
-In addition, labels should be both clear and well placed, which provide a straight forward explanation.\newline
-	Most importantly, issues concerning plots and charts should be carefully handled.
-3D pie charts may introduce distortions and should be avoided whenever possible.
-Instead, table can be used to explain in detail numbers and percentages.
-It is recommended to use colors that can group things or direct readers' focus.
-As background patterns may distract and is likely to blur important messages, they should not be used as well.
-\newline
-	Finally, "avoid distractions" and "steer attention" are useful concepts when designing figures.
-Distraction like strong contrast produced by sparse vs dense, white vs black should be avoided.
-As human eyes are much better at grouping things according to colors instead of line patterns, distraction originates from dashed or dot lines should also be avoided.
-Backgourd image is usually unnecessary as it convey little message.
+\section{Positive tone}
+	\begin{enumerate}
+		\item 
+			You made this mistake due to your misunderstanding of our letter.
+		\item 
+			It indicates that you know absolutely nothing about our ﬁeld of research from your comment on the second paragraph of page four.
+		\item
+			 One-tenth of the results of the experiments are incoherent.
+		\item
+			 Since the experimental setup was not taken enough care for, the results cannot be as precise as they could have been.
+		\item
+			 We reached a 99.7\% purity level, failing to achieve a level of 100\% as many other authors [5, 12, 14, 15].
+	\end{enumerate}
 
 \section{\LaTeX}
-	\begin{table}[H]
-		\begin{center}
-			\begin{tabular}{c |c |c}
-				\hline
-				Component & Transition & Probability ($\lambda$)\\
-				\hline
-				\multirow{5}{*}{MDC$_{-}$A} & Limited Bandwidth &0.2\\
-				& Memory Leak & 0.3\\
-				&Bandwidth Upgrade & 0.5 \\
-				& MDC$_{-}$A Reboot &0.4\\
-				&MDC Exception & Fixed Rate = 0.8 \\
-				\hline
-				\multirow{5}{*}{MDC$_{-}$B}& Communication Delay & 0.6\\
-				& No WIFI & 0.3\\
-				&Protocol Adjustment & 0.2 \\
-				& Router Reboot & 0.8  \\
-				&MDC Exception & Fixed Rate = 0.8 \\
-				\hline
-				\multirow{5}{*}{MDC$_{-}$C} & Retrieval Exception &0.3\\
-				& System No Response & 0.4 \\
-				&Omit Retrieval & 0.8  \\
-				& MDC$_{-}$C Reboot & 0.9\\
-				&MDC Exception & Fixed Rate = 0.8 \\
-				\hline
-				\multirow{5}{*}{MSC} & Overload & 0.1\\
-				& System Crashed & 0.2 \\
-				& Load Adjustment& 0.7 \\
-				& MSC  Reboot & 0.9\\
-				&MSC Exception& Fixed Rate = 0.9 \\
-				\hline
-			\end{tabular}
-		\end{center}
-		\caption{ Transition and probability of MCAS}
-	\end{table}
 
-	\begin{table}
-		\begin{center}
-			\begin{tabular}{ c c}
-				\hline
-				Trapdoor Size Before Compression (bit) & 65536 \\
-				Trapdoor Size After Compression (bit) &3260.32 \\
-				Compression Rate (\%) & 4.97 \\
-				\hline
-			\end{tabular}
-		\end{center}
-		\caption{Compression Rate}
-	\end{table}
+\section{Group exercise}
 
-	\begin{table}
-		\begin{center}
-			\begin{tabular}{c |c |c c |c c}
-				\hline\multirow{3}{*}{} & \multirow{2}{*}{Native} & \multicolumn{2}{c}{SLA-aware} & \multicolumn{2}{c}{Proportional-share} \\
-				& & \multicolumn{2}{c}{Scheduling} & \multicolumn{2}{c}{Scheduling}\\
-				\cline{2-6}
-				& FPS & FPS & Overhead(\%) & FPS &Overhead(\%)\\
-				\hline
-				GT1 & 43.023 & 42.044 & 2.28 & 42.221 & 1.86 \\
-				GT2 & 48.686 & 45.996 & 5.53 & 48.284 & 0.83\\
-				HDRT1 & 59.062 & 57.923 & 1.93 & 57.700 & 2.31 \\
-				HDRT2 & 65.808 & 62.854 & 4.90 & 65.984 & -0.27 \\
-				\hline
-			\end{tabular}
-		\end{center}
-		\caption{Macrobenchmark Results.}
-	\end{table}
 \end{document}

### 2019-04-14 VG500/Slide/tex/main.tex
pdflatex beamer template

\input{preamble.tex}
\input{pdfinfo.tex}
\input{title.tex}

\begin{document}

\maketitle

\section{Themes}

\subsection{Background images}

\begin{xframe}{Themes for the Elegance}

    You need a \hl{style/images} directory
    with these files inside:

    \begin{itemize}
        \item style/background-section.pdf
        \item style/background-slide.pdf
        \item style/background-title.pdf
        \item style/logo.png
    \end{itemize}

\end{xframe}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../pic/theme-1.png}}
\begin{frame}[plain]
    .
\end{frame}
}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../pic/theme-2.png}}
\begin{frame}[plain]
    .
\end{frame}
}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../pic/theme-3.png}}
\begin{frame}[plain]
    .
\end{frame}
}

\section{Examples}

\subsection{Showing code}

\begin{xframe}{Code snippets}

    Do you have some code to show on the slide?

    And the same frame should also contain text?

    \begin{cxxcodebox}
        class example {
            // \codedots shows grayed-out dots
            @ \codedots @
        };
    \end{cxxcodebox}

    You can use \verb|cxxcodebox| environment.
    It has \verb|cxx| in the name,
    but no syntax highlighting is performed.

    For short code snippets,
    it is better just to highlight the important parts.

\end{xframe}

\subsection{Code slides and escapes}

\begin{xframe}{Second slide}

    \begin{cxxcode}
        class example {
            // There are a few useful escapes here
            @ \codedots @ // \codedots shows grayed-out dots

            // Invalid parts can be marked with \hlErr
            @\hlErr{operator;}@

            // Good parts can be marked with \hlOk
            @\hlOk{operator() ()}@

            // Other highlighting commands can be seen in
            // the preamble.tex file
        };
    \end{cxxcode}

\end{xframe}

\end{document}

### 2019-04-15 VG500/HW5/submission.tex
add bibtex

@@
 \usepackage{multirow}
-
+\usepackage[numbers,sort&compress]{natbib}
 \usepackage{listings}
@@
 \section{\LaTeX}
+	Lorem\citep{RN5}  ipsum  dolor\citep{RN11}  sit  amet,  consectetuer  adipiscing  elit.
+Ut  purus  elit,  vestibulum  ut,placerat  ac,  adipiscing  vitae,  felis.
+Curabitur  dictum  gravida  mauris.
+Nam  arcu  libero,nonummy eget, consectetuer id, vulputate a, magna.
+Donec vehicula augue eu neque.
+Pel-lentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.Mauris ut leo.
+Cras viverra metus rhoncus sem.
+Nulla et lectus vestibulum urna fringillaultrices.
+Phasellus\citep{RN14}  eu  tellus  sit  amet  tortor  gravida  placerat.
+Integer  sapien  est,  iaculisin,  pretium  quis,  viverra  ac,  nunc.
+Praesent  eget  sem  vel  leo  ultrices  bibendum.
+Aeneanfaucibus.
+Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla.
+Curabitur\citep{RN10} auctorsemper  nulla.
+Donec  varius  orci  eget  risus.
+Duis  nibh  mi,  congue  eu,  accumsan  eleifend,sagittis quis, diam.
+Duis eget orci sit amet orci dignissim rutrum.
 
@@
 
+\bibliographystyle{plainnat}
+\bibliography{reference}
+
 \end{document}

### 2019-04-15 VG500/HW5/submission.tex
add ex5

@@
 \lstset{language=Matlab}
-
+\usepackage{hyperref}
 \usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
@@
 \section{Group exercise}
+	In the traditional method of two round-trip secure search, the trapdoors of each keyword list are generated by the data owner or his agent, and then the user will search them.
+This will be a time-consuming job for mobile device and significantly degrade the user experience.
+In our method, each trapdoor can be generated by its own device.\newline
+	The user terminal stores the noise set and a frequently-used cache.
+The cache originally stores the keywords which are commonly used in the corpus and corresponding feature bits.
+If the user inputs a keyword, it will do the stemming process first, and then search the cache.
+If finding the keyword, it will return the intermediate trapdoor immediately, otherwise it will calculate the feature bits and add the keyword to the cache for next time use.
+The whole process is presented in Fig.
+4.
+By introducing cache, the time of generating trapdoors can be efficiently reduced.
 

### 2019-04-19 VG500/Slide/tex/main.tex
add intro

@@
 \input{preamble.tex}
-\input{pdfinfo.tex}
 \input{title.tex}
@@
 
-\section{Themes}
+\section{Introduction}
 
-\subsection{Background images}
+	\subsection{part1.1}
 
-\begin{xframe}{Themes for the Elegance}
-
-    You need a \hl{style/images} directory
-    with these files inside:
-
-    \begin{itemize}
-        \item style/background-section.pdf
-        \item style/background-slide.pdf
-        \item style/background-title.pdf
-        \item style/logo.png
-    \end{itemize}
-
+		\begin{xframe}{Backgound}
+			Turbulent combustion is encountered in most practical combustion system such as \textit{rocket}, \textit{ICE}, \textit{aircraft engien}, and \textit{industrial burner}.
+			\begin{figure}[htbp]\centering
+				\begin{minipage}{3.5cm}
+					\centering
+					\includegraphics[height=4.5cm, width=3cm]{../pic/rocket.jpg}
+				\end{minipage}%
+				\begin{minipage}{7.5cm}
+					\centering
+					\includegraphics[height=4.5cm, width=7cm]{../pic/engien.jpg}
+				\end{minipage}%
+			\end{figure}
 		\end{xframe}
 
-{
-\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../pic/theme-1.png}}
-\begin{frame}[plain]
-    .
-\end{frame}
-}
+		\begin{xframe}{Research aspects}
+			Meaningful to practical systems:
+			\begin{enumerate}[(a)]
+				\item 
+					Improve efficiency, meet demanding standards.
+				\item
+					Reduce pollution, environment friendly.
+			\end{enumerate}
+
+			Why is numerical simulation adopted?
+			\begin{enumerate}[(a)]
+				\item 
+				Analytical techniques are difficult to handle.
+				\item
+				Experiments are too expensive to be widely used.
+			\end{enumerate}
+		\end{xframe}
+
+		\begin{xframe}{Physical Configuration}
+			\includegraphics[width=7cm, height=8cm]{../pic/counterflow_configuration.png}	
+		\end{xframe}
 
@@
 \begin{frame}[plain]
-    .
+
 \end{frame}
@@
 
-\section{Examples}
+\section{Governing Equations}
 
@@
 
+\section{Numerical Solution}
+
 \end{document}

### 2019-04-21 VG500/Slide/tex/main.tex
basically done

--- 2019-04-14 VG500/Slide/tex/main.tex
@@
 
-\section{Themes}
+\section{Introduction}
+	\subsection{part1.1}
+		\begin{xframe}{Backgound}
+			Turbulent combustion is encountered in most practical combustion system such as rocket, ICE, and aircraft engien.
+			\begin{figure}
+				\begin{minipage}{3.5cm}
+					\centering
+					\includegraphics[height=3.5cm, width=3cm]{../pic/rocket.jpg}
+				\end{minipage}%
+				\begin{minipage}{7.5cm}
+					\centering
+					\includegraphics[height=3.5cm, width=7cm]{../pic/engien.jpg}
+				\end{minipage}%
+			\end{figure}
+			Meaningful to practical systems:
+			\begin{enumerate}[(a)]
+				\item 
+				Improve efficiency, meet demanding standards.
+				\item
+				Reduce pollution, environment friendly.
+			\end{enumerate}
+		\end{xframe}
+	\subsection{part1.2}
+		\begin{xframe}{Research aspects}
+			Why is numerical simulation adopted?
+			\begin{enumerate}[(a)]
+				\item 
+					Analytical techniques are difficult to handle.
+				\item
+					Experiments are too expensive to be widely used.
+			\end{enumerate}
+			What are the key points in numerical practice?
+			\begin{itemize}
+				\item Interaction between turbulence and combustion.
+				\item Proper flame model.
+			\end{itemize}
+		\end{xframe}
+	\subsection{part1.3}
+		\begin{xframe}{Numerical simulation of flowfield}
+			Based on CFD, there're 3 possible approaches:
+			\begin{enumerate}[(a)]
+				\item{Direct Numerical Simulation(DNS)}\newline
+					--Precise, but costly(Tremendous memory and CPU). \XSolid
+				\item Large Eddy Simulation(LES)\newline
+					--Compromise between accuracy and computational cost. \Checkmark
+				\item Reynolds Averaged Navier-Stokes(RANS)\newline
+					--Inaccurate for combustion phenomenon. \XSolid
+			\end{enumerate}
+			\includegraphics[width=11cm, height=3cm]{../pic/comparision.png}
+		\end{xframe}
+	\subsection{part1.4}
+		\begin{xframe}{Numerical simulation of flame}
+			Although based on LES, traditional flame models are inadequate:
+			\begin{itemize}
+				\item
+					Distribution of flame properties are mannually assumed.
+				\item
+					Parameter tuning may be unphysical.
+			\end{itemize}
+			These drawbacks are overcome by the turbulent flamelet model to be introduced:
+			\begin{itemize}
+				\item
+					Designed especially for LES, with tfewer approximation.
+				\item
+					Relations are provided through scaling law, which is based on DNS database.
+			\end{itemize}		
+		\end{xframe}
+\section{Turbulent Flamelet Model}
+	\subsection{part2.1}
+		\begin{xframe}{Theory}
+			Original G.E. in the context of LES:
+			\begin{equation}
+				\frac{\partial \bar{\rho}\tilde{Z}}{\partial t} + \nabla \cdot (\bar{\rho} \tilde{Z}\tilde{\vec{u}}) = \nabla \cdot [\bar{\rho}(D+D_T)\nabla\tilde{Z}]
+			\end{equation}
+			\begin{equation}
+				\frac{\partial \bar{\rho}\tilde{Y_i}}{\partial t} + \nabla \cdot (\bar{\rho} \tilde{Y_i}\tilde{\vec{u}}) = \nabla \cdot [\bar{\rho}(D+D_T)\nabla\tilde{Y_i}] + \overline{\omega_i}
+			\end{equation}
+			After coordinate transformation$(x_1,x_2,x_3,t)\rightarrow(Z,Z_2,Z_3,\tau)$:
+			\begin{equation}
+				\begin{split}
+					\bar{\rho}\frac{\partial \tilde{Y_i}}{\partial \tau} + \bar{\rho} \Big(\tilde{\vec{u}} \cdot \nabla_\perp \tilde{Y_i} + \frac{\partial \tilde{Y_i}}{\partial Z_2}\frac{\partial Z_2}{\partial t} + \frac{\partial \tilde{Y_i}}{\partial Z_3}\frac{\partial Z_3}{\partial t}\Big) = \frac{\bar{\rho}\chi}{2Le_T}\frac{\partial^2 \tilde{Y_i}}{\partial^2 \tilde{Z}}\\ + \frac{\partial \tilde{Y_i}}{\partial \tilde{Z}}\nabla\cdot\Bigg[\bar{\rho}(\mathcal{D}_{T,i}-\mathcal{D}_T)\vec{n}\cdot\frac{\partial \tilde{Z}}{\partial \vec{n}}\Bigg] + \nabla \cdot (\bar{\rho}\mathcal{D}_{T,i}\nabla_\perp\tilde{Y_i}) + \overline{\omega_i}
+				\end{split}	
+			\end{equation}
+		\end{xframe}
+	\subsection{part2.2}
+		\begin{xframe}{Laminar Flamelet assumption}
+			Locally, the characteristic timescale of chemical reaction is much smaller that that of flow$(t_c \ll t_f)$.\newline
+			Thus, local flame structure can be described by the difffusion flame under counterflow configuration.
+			\includegraphics[width=10cm, height=3cm]{../pic/flamelet.png}
 
-\subsection{Background images}
+			Each micro flamelet can be described by $Z$ and $\chi$:
+			\begin{itemize}
+				\item $Z$ describes chemical reaction.
+				\item $\chi$ indicates turbulence stretching effect.
+			\end{itemize}
+			Thus, a database can be pre-computed for later looking-up. 
+		\end{xframe}
+	\subsection{part2.3}
+		\begin{xframe}{Turbulent Flamelet}
+			\begin{multicols}{2}
+				\includegraphics[width=5.5cm, height=7cm]{../pic/counterflow.png}
 
-\begin{xframe}{Themes for the Elegance}
-
-    You need a \hl{style/images} directory
-    with these files inside:
-
+				Unlike the laminar flamelet introduced above,\\
+				G.E. of the counterflow flame is slightly modified by our turbulet flamelet model from
+				\begin{equation}
+					\rho \frac{D Y_i}{D t} = \mathcal{D}_i\frac{\partial^2 Y_i}{\partial^2 x} + \omega_i(T, \vec{Y})
+				\end{equation}
+				to
+				\begin{equation}
+					\bar{\rho} \frac{D \tilde{Y_i}}{D t} = \mathcal{D}_i\frac{\partial^2 \tilde{Y_i}}{\partial^2 x} + \tilde{\omega_i}(\tilde{T}, \tilde{\vec{Y}})
+				\end{equation}
+				The two equations share similar form, but have totally different meanings.
+			\end{multicols}
+		\end{xframe}
+	\subsection{part2.4}
+		\begin{xframe}{Solution procedure}
+			Based on the filtered turbulent flamelet database generated in the way descirbed above, the full solution procedure that incorporates a CFD solver can be described as follows:
+			\centering
+			\includegraphics[width=9cm, height=6.5cm]{../pic/solver.png}
+		\end{xframe}
+\section{Numerical Results}
+	\subsection{part3.1}
+		\begin{xframe}{Comparsion of ``S'' curve}
+			The $T_{max}$ plot:
 			\begin{itemize}
-        \item style/background-section.pdf
-        \item style/background-slide.pdf
-        \item style/background-title.pdf
-        \item style/logo.png
+				\item
+					One of the most convincing testing cases.
+				\item
+					Difference and transition position are clearly revealed! 
 			\end{itemize}			
-
+			\includegraphics[width=11cm, height=6cm]{../pic/Tmax.jpg}	
 		\end{xframe}
-
-{
-\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../pic/theme-1.png}}
-\begin{frame}[plain]
-    .
-\end{frame}
-}
-
-{
-\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../pic/theme-2.png}}
-\begin{frame}[plain]
-    .
-\end{frame}
-}
-
-{
-\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../pic/theme-3.png}}
-\begin{frame}[plain]
-    .
-\end{frame}
-}
-
-\section{Examples}
-
-\subsection{Showing code}
-
-\begin{xframe}{Code snippets}
-
-    Do you have some code to show on the slide?
-
-    And the same frame should also contain text?
-
-    \begin{cxxcodebox}
-        class example {
-            // \codedots shows grayed-out dots
-            @ \codedots @
-        };
-    \end{cxxcodebox}
-
-    You can use \verb|cxxcodebox| environment.
-    It has \verb|cxx| in the name,
-    but no syntax highlighting is performed.
-
-    For short code snippets,
-    it is better just to highlight the important parts.
-
-\end{xframe}
-
-\subsection{Code slides and escapes}
-
-\begin{xframe}{Second slide}
-
-    \begin{cxxcode}
-        class example {
-            // There are a few useful escapes here
-            @ \codedots @ // \codedots shows grayed-out dots
-
-            // Invalid parts can be marked with \hlErr
-            @\hlErr{operator;}@
-
-            // Good parts can be marked with \hlOk
-            @\hlOk{operator() ()}@
-
-            // Other highlighting commands can be seen in
-            // the preamble.tex file
-        };
-    \end{cxxcode}
-
+	\subsection{part3.2}
+		\begin{xframe}{Standard case}
+			Comparsion between experimental data, which is widely used as benchmark.
+			\begin{figure}
+				\begin{minipage}{3.5cm}
+					\centering
+					\includegraphics[height=3cm, width=5cm]{../pic/slice.png}
+				\end{minipage}%
+				\begin{minipage}{7.5cm}
+					\centering
+					\includegraphics[height=5.5cm, width=7cm]{../pic/line.png}
+				\end{minipage}%
+			\end{figure}
 		\end{xframe}

### 2019-04-22 VG500/Slide/tex/main.tex
fix citation
add some citation

@@
 				\item 
-				Improve efficiency, meet demanding standards.
+				Improve efficiency, meet demanding standards\cite{RN1}.
 				\item
@@
 				\item{Direct Numerical Simulation(DNS)}\newline
-					--Precise, but costly(Tremendous memory and CPU). \XSolid
+					--Precise, but costly(Tremendous memory and CPU). %\XSolid
 				\item Large Eddy Simulation(LES)\newline
-					--Compromise between accuracy and computational cost. \Checkmark
+					--Compromise between accuracy and computational cost. %\Checkmark
 				\item Reynolds Averaged Navier-Stokes(RANS)\newline
-					--Inaccurate for combustion phenomenon. \XSolid
+					--Inaccurate for combustion phenomenon. %\XSolid
 			\end{enumerate}
@@
 				\item
-					Relations are provided through scaling law, which is based on DNS database.
+					Relations are provided through scaling law, which is based on DNS database\cite{RN2}.
 			\end{itemize}		
@@
 				\item
-					Difference and transition position are clearly revealed! 
+					Difference and transition position are clearly revealed\cite{RN11}.
 			\end{itemize}			
@@
 		\begin{xframe}{Standard case}
-			Comparsion between experimental data, which is widely used as benchmark.
+			Comparsion between experimental data, which is widely used as benchmark\cite{RN14}.
 			\begin{figure}
@@
 
+	\begin{xframe}{Reference}
+		\printbibliography
+	\end{xframe}
 \end{document}

### 2019-04-22 VG500/Poster/poster.tex
poster done

\documentclass[a0,portrait]{a0poster}

\usepackage{setspace}
\usepackage{multicol} % This is so we can have multiple columns of text side-by-side
\columnsep=100pt % This is the amount of white space between the columns in the poster
\columnseprule=3pt % This is the thickness of the black line between the columns in the poster

\usepackage[svgnames]{xcolor} % Specify colors by their 'svgnames', for a full list of all colors available see here: http://www.latextemplates.com/svgnames-colors

\usepackage{times} % Use the times font
%\usepackage{palatino} % Uncomment to use the Palatino font

\usepackage{graphicx} % Required for including images
\graphicspath{{figures/}} % Location of the graphics files
\usepackage{booktabs} % Top and bottom rules for table
\usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures
\usepackage{amsfonts, amsmath, amsthm, amssymb} % For math fonts, symbols and environments
\usepackage{wrapfig} % Allows wrapping text around tables and figures
\usepackage{setspace}
\usepackage{subfigure}
\usepackage{commath}
\usepackage{enumerate}
\usepackage{multimedia}
\usepackage{biblatex}

\begin{document}

%----------------------------------------------------------------------------------------
%	POSTER HEADER
%----------------------------------------------------------------------------------------

% The header is divided into two boxes:
% The first is 75% wide and houses the title, subtitle, names, university/organization and contact information
% The second is 25% wide and houses a logo for your university/organization or a photo of you
% The widths of these boxes can be easily edited to accommodate your content as you see fit

\begin{minipage}[b]{\linewidth}

\Huge \color{NavyBlue} \textbf{Numerical simulation of turbulent combustion using turbulent flamelet model} \color{Black}\\ % Title
\vspace{0.5cm}
\Huge\textit{VG500 Poster}\\[-2cm] % Subtitle

\setlength\columnseprule{0pt}
\begin{multicols}{2}
	\huge \textbf{Yu Cang}\\[0.5cm] % Author(s)
	\LARGE UM-SJTU Joint Institute\\[0.4cm] % University/organization
	\Large \texttt{yu.cang@sjtu.edu.cn}\\

	\columnbreak

	\includegraphics[height=6cm]{pic/JI_logo}\\
\end{multicols}

\end{minipage}
%

\vspace{1cm} % A bit of extra whitespace between the header and poster content

%----------------------------------------------------------------------------------------

\begin{multicols}{2} % This is how many columns your poster will be broken into, a portrait poster is generally split into 2 columns

\color{Navy} % Navy color for the abstract

\begin{abstract}

\large Numerical simulation of turbulent combustion is carried out using the turbulent flamelet model. Numerical results, compared with traditional methods, suggest that this new model is well designed for Large Eddy Simulation(LES) and has better agreement with experimental data.

\end{abstract}

\color{SaddleBrown} % SaddleBrown color for the introduction
\section*{Combustor Model}
	\begin{center}
		\vspace{-0.5cm}
		\includegraphics[width=0.8\linewidth]{pic/burner.png}\\
		\vspace{-0.5cm}
		{\color{Green} Fig. 1 Channel Model with Sawtoothed Surface}
	\end{center}

\section*{Governing Equations}
	\color{DarkSlateGray}
    \begin{align}
      \mbox{(Continuity)}\qquad & \frac{\partial \bar{\rho}}{\partial t} + \frac{\partial (\bar{\rho}\tilde{u}_j)}{\partial x_j}=0\\
      \mbox{(Momentum)}\qquad & \dfrac{\partial(\bar{\rho}\tilde{u}_i)}{\partial t} + \dfrac{\partial (\bar{\rho}\tilde{u}_i\tilde{u}_j)}{\partial x_j} = -\dfrac{\partial \bar{p}}{\partial x_i} + 2\dfrac{\partial \bar{\mu}\tilde{S}_{ij}}{\partial x_j} + \dfrac{\partial t_{ij
      }}{\partial x_j}\label{NS}\\
      \mbox{(Scalar transport)}\qquad & \dfrac{\partial(\bar{\rho}\tilde{\phi}_i)}{\partial t} + \dfrac{\partial (\bar{\rho}\tilde{\phi}_i\tilde{u}_j)}{\partial x_j} = \dfrac{\partial \bar{\rho}\tilde{\alpha}_{i}\tilde{\phi}_{i, k}}{\partial x_k} + \bar{\rho}\tilde{\omega}_i + \dfrac{\partial q_{ik
      }}{\partial x_k}
    \end{align}
	where
	\[\tilde{S}_{ij} = \frac{1}{2}(\tilde{u}_{i,j} + \tilde{u}_{j, i}) - \frac{1}{3}\delta_{ij}\tilde{u}_{k,k}\]

\color{SaddleBrown}
\section*{Flamelet Assumption}
	\color{DarkSlateGray}
	Locally, the characteristic timescale of chemical reaction is much smaller that that of flow$(t_c \ll t_f)$.\newline
	Thus, local flame structure can be described by the difffusion flame under counterflow configuration.
	\vspace{0.5cm}
	\begin{center}
		\vspace{-0.5cm}
		\includegraphics[width=0.85\linewidth]{pic/flamelet.png}\\
		\vspace{-0.25cm}
		{\color{Green} Fig. 2 Local laminar flamelet}
	\end{center}

\color{SaddleBrown}
\section*{Solution Procedure}
	\vspace{-1.5cm}
	\setlength\columnseprule{0pt}
	\begin{multicols}{2}
		\color{DarkSlateGray}
		An iterative process:
		\begin{enumerate}[(1)]
			\item Prepare all properties at $t=n$.
			\item Update flow properties at $t=n+1$ from CFD solver.
			\item Calculate mix-fraction($Z$) and strain-rate($\chi$).
			\item From pre-computed table, lookup temperature($T$) and mass fraction($Y_i$) at $t=n+1$.
			\item Update density($\rho$) at $t=n+1$.
			\item Check convergence.
		\end{enumerate}

		\begin{center}
			\includegraphics[width=\linewidth]{pic/solver.png}\\
			{\color{Green} Fig. 3 Solution Flowchart}
		\end{center}

	\end{multicols}
	\setlength\columnseprule{3pt}

\color{SaddleBrown}
\section*{Grid Layout}
	\vspace{-0.5cm}
	\color{DarkSlateGray}
	Unstructured grid containing tetrahedral, hexahedron and pyramids. Refined locally.
	\vspace{0.5cm}
	\begin{center}
		\vspace{-0.5cm}
		\includegraphics[width=0.55\linewidth]{pic/grid.png}\\
		\vspace{-0.5cm}
		{\color{Green} Fig. 4 Computation grid}
	\end{center}

\color{SaddleBrown}
\section*{Numerical Schemes}
	\vspace{-0.5cm}
	\color{DarkSlateGray}
	Based on the Finite Volume Method(FVM), the intercell flux are computed from 2nd-order upwind schemes. Dynamic subgrid model is adopted in the context of Large Eddy Simulation(LES).

	\setlength\columnseprule{0pt}
	\begin{multicols}{2}
		\color{DarkSlateGray}
		\begin{center}
			\includegraphics[width=\linewidth]{pic/cell.jpg}\\
			\vspace{0.5cm}
			{\color{Green} Fig. 5 Cell-centered variable}
		\end{center}

		\begin{center}
			\includegraphics[width=\linewidth]{pic/vertex.jpg}\\
			\vspace{-0.5cm}
			{\color{Green} Fig. 6 Vertex-centered variable}
		\end{center}
	\end{multicols}
	\setlength\columnseprule{3pt}

\color{SaddleBrown}
\section*{Results}
	\color{DarkSlateGray}
	\begin{enumerate}[(1)]
		\item 
			\textbf{The $T_{max}$ plot}.
			\begin{itemize}
				\item 
					One of the most convincing testing cases.
				\item 
					Nice agreement in ignition range compared with reference data.
				\item 
					Difference and transition position are also revealed clearly.	
			\end{itemize}
			\begin{center}
				\includegraphics[width=\linewidth]{pic/Tmax.jpg}\\
				{\color{Green} Fig. 6 ``S''\ Curve}
			\end{center}
		\item 
			\textbf{Flame structure}.
			\begin{itemize}
				\item 
					Fine vortex structure is resolved.
				\item 
					Better prediction of minor species like NOx and COx.
			\end{itemize}
			\begin{center}
				\includegraphics[width=\linewidth]{pic/flame.png}\\
				{\color{Green} Fig. 7 Jet flame}
			\end{center}
	\end{enumerate}

\vspace{-2cm}
\color{SaddleBrown} % SaddleBrown color for the conclusions to make them stand out
\section*{Conclusions}
	\color{DarkSlateGray}
	\begin{itemize}
	    \item
	    	Turbulent flamelet model shows better performance that traditional flame models.
	    \item
	    	$T_{max}$ curve solved in physical space has lower temperature, which is desired in practice.
	    \item 
	    	Finer vortex structures can be well resolved.
	    \vspace{10pt}
	\end{itemize}%

\nocite{*} % Print all references regardless of whether they were cited in the poster or not
\printbibliography

\section*{Acknowledgements}
	Special Thanks to Prof. Lipo Wang and Dr. Manuel Charlemagne.

\end{multicols}
\end{document}

### 2019-04-22 VG500/Game/group_4.tex
folder rename

\documentclass[a4paper, twocolumn, 12pt, twoside, english]{article}
\usepackage{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
%\usepackage[utf8]{inputenc} % not used as we need ctex
%\usepackage[UTF8, scheme = plain]{ctex} %cjk is too old
%\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsfonts, commath}
%\usepackage{lipsum}
%\usepackage{setspace}
%\usepackage{blindtext}
\usepackage{ulem}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{stfloats}
\usepackage{wrapfig}
\usepackage{tcolorbox}

\author{Group 4\\Rui Gao\footnote{Corresponding author, garrygao@sjtu.edu.cn}\quad118370910003\\Guiwen Tan\quad118370910014\\ Muhammad Umer Siddique\quad118370990001\\Yu Cang\quad 018370210001}
\title{Wonder Builder: the first Skyscraper!}
\date{\today}

\begin{document}
\maketitle

\section{Introduction}
\begin{tcolorbox}[title = {Hello!}]
Welcome back to the time of inventions and rapid-development!

While the roars of steam whistle is still dominating the factories and rails, the second industrial revolution quietly started. With the invention of elevators, people start to look up for living space.

The time have come to conquer the sky!
\end{tcolorbox}

Welcome to {\it Wonder Builder: the first Skyscraper!}

You are the owner of a building company in the United States, the heart of the second industrial revolution. As a shrewd businessman, you are aware of the big chance hiding behind the invention of the elevators.

Construct a building that is higher than EVERY other building to draw the attention of the whole world. However, be aware that a lot of other businessmen are competing with you.

Fight through the difficulties and defeat other players, for the glory of building the first Skyscraper in the world!\bigskip

The goal of the game is to construct a skyscraper with toothpicks. To win, make sure that you are the first to build a 10-floor skyscraper. Both wisdom and luck are necessary to achieve final victory.

\section{Set Up the Game}

\subsection{Necessary Materials}
Some materials are needed before the game starts.

{\bf One table} with flat horizontal surface is needed to serve as the base for the buildings by the players.

{\bf Some toothpicks}\cite{ref:por} are needed as the construction material. A fair estimate for the total number of toothpicks needed is
\[
\text{Toothpicks Needed} \approx \text{No. Of Players} \times 50
\]

{\bf A dice} is needed to enable the game mechanics.

Figure~\ref{fig:stp} shows a typical setup.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{Diagram_game_setup_2.png}
\caption{Necessary materials}
\label{fig:stp}
\end{figure}

\subsection{Start the Building}
\begin{tcolorbox}
You heard that a rival company has started to hire engineers and workers for their skyscraper. You decided to start immediately, but you need to find a suitable place to lay down the foundations.
\end{tcolorbox}
The players sit around the table. A random player starts his turn first, and then the next one clockwise starts his turn.

At the first turn, you need to throw a dice to see whether the place you selected is suitable. Throw six to lay the foundations of your building. If not, you need to re-throw next turn.

After a player has laid down the foundation, he could work on building surface floors in this turn and also later turns. See section~\ref{sec:turn} for detailed turn mechanics.

\subsection{End-Game Rules}
\begin{tcolorbox}
The Dutch are also planning to build a skyscraper. Obviously they will not stop to wait for you.
\end{tcolorbox}
The game concludes after 10 rounds, when Dutch people finished the famous {\it Witte Huis} in Rotterdam. The first player that finishes a 10-floor building before that wins the game.

\subsection{Build Proper Floors}
\begin{tcolorbox}
There was one stupid man in your hometown who one day erected a rod that is 10 stories high and claimed to have constructed a skyscraper. Everyone laughed at him.
\end{tcolorbox}
Similar to any other normal buildings, the surface of a floor should be flat. Figure~\ref{fig:flr} shows one of the correct and incorrect way to construct a two-floor building. The right building is not a correct two-floor building because the surface is not flat.
\begin{figure}[!h]
\centering
\includegraphics[width=0.45\textwidth]{Diagram_floors_2.png}
\caption{Correct and wrong examples of a two floor building}
\label{fig:flr}
\end{figure}

\section{Turn Mechanics}
\label{sec:turn}
Each turn is basically composed of two phases: Construction and Sabotage. In the Construction phase, the player constructs his building. In the Sabotage phase, the player attacks the buildings by other players. Figure~\ref{fig:flc} in the last page shows the flowchart if the game.
\subsection{Construction Phase}
\begin{tcolorbox}
To ensure the supply of building materials and fund, you go to bargain with the supplier and the bank, which would have random outcomes depending on your luck. Interestingly, the closer you are to success, the more helpful they become.
\end{tcolorbox}
In this phase, the player throws a dice to determine his supply of building material this turn, and additional toothpicks based on the current number of floors of his building. For example, if one that have a building of three floors throws five, then he would get three plus five toothpicks as his building material. The player can use these toothpicks to expand his existing building (or start to build one) in this turn. Each floor of the building can compose of any number of toothpicks as long as it does not collapse, but the player could only build on the topmost floor of the building, i.e., after the player starts to build the third floor, he cannot add toothpicks to the second floor anymore. Unused materials cannot be saved to the next turn.
%
%Version hand-sticking
%In this phase, the player sticks his hands to the toothpick container once to determine his supply of building material this turn. For example, if five toothpicks stick on his hands when he take his hands out, then he would get five toothpicks as his building material. The player can then use these toothpicks to expand his existing building (or start to build one if there is no building yet). Each floor of the building can compose of any number of toothpicks as long as it does not collapse, but the player could only build on the top floor of the building, i.e., after the player starts to build the second floor, he cannot add toothpicks to the first floor anymore. Unused materials cannot be saved to the next turn.
\subsection{Sabotage Phase}
\begin{tcolorbox}
``Business is war without bullets'', says Phil Knight. Some tricks may be helpful to your cause.
\end{tcolorbox}
In this phase, the player throws a dice. If the player throws five or six, then he successfully bribes one of the engineers in another company, and thus can sabotage another player's building by choosing one toothpick in his building and force the target player to remove that specific toothpick from the building.

If player A's building collapsed in player B's Sabotage phase, he enters the ``revival'' phase. See section~\ref{sec:rev} for details.

\subsection{Revival Phase}
\label{sec:rev}
\begin{tcolorbox}
``Failure the mother of success.'' You learn from the failure, and restart with better ideas in mind.
\end{tcolorbox}
Once a player's building collapsed, he enters the Revival phase. Depending on the reason for the collapse, he could restart his building effort with different terms.

If the building collapsed when the player is trying to build it, he should start from the ruins, i.e., what is left over after the collapse. For this turn and next turn only, he could build on any floor to strengthen the building.

If a player's building collapsed during another player's Sabotage phase, he should move to build a new building, as other parts of the old building may also be sabotaged. The player gains extra number of Construction phases equal to the number of floors left over in the ruin after the collapse.

In either case, the revival phase lasts for two turns (the two active turns after the building collapsed), in which the player put all his focus on the rebuilding effort. The player could get construction materials using the same rule as the Construction phase, but he would not be able to sabotage other player's building during these two turns.

\begin{thebibliography}{}
\bibitem{ref:por}
Manuel Charlemagne, {\it Vg500 Technical Communication Project}. UM-SJTU JI canvas, available from https://umjicanvas.com/courses/962/ files/folder/project?

\end{thebibliography}
\newpage
\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{flowchart.pdf}
	\caption{Flowchart for the game}
	\label{fig:flc}	
\end{figure*}
\end{document}

### 2019-04-23 VG500/Slide/tex/main.tex
drop one

@@
 			\end{figure}
+			\pause
 			Meaningful to practical systems:
@@
 			\end{enumerate}
-		\end{xframe}
-	\subsection{part1.2}
-		\begin{xframe}{Research aspects}
-			Why is numerical simulation adopted?
-			\begin{enumerate}[(a)]
-				\item 
-					Analytical techniques are difficult to handle.
-				\item
-					Experiments are too expensive to be widely used.
-			\end{enumerate}
-			What are the key points in numerical practice?
-			\begin{itemize}
-				\item Interaction between turbulence and combustion.
-				\item Proper flame model.
-			\end{itemize}
 		\end{xframe}
@@
 			\end{itemize}
-			These drawbacks are overcome by the turbulent flamelet model to be introduced:
+			\pause
+			These drawbacks are overcame by the turbulent flamelet model to be introduced:
 			\begin{itemize}
 				\item
-					Designed especially for LES, with tfewer approximation.
+					Designed especially for LES, with fewer approximation.
 				\item
@@
 			\end{equation}
+			\pause
 			After coordinate transformation$(x_1,x_2,x_3,t)\rightarrow(Z,Z_2,Z_3,\tau)$:
@@
 		\end{xframe}
-
+\section{Conclusions}
+	\subsection{part4.1}
+		\begin{xframe}{Conclusions}
+			\begin{itemize}
+				\item
+					Turbulent flamelet model has good agreement with experimental data.
+				\pause
+				\item
+					Numerical simulation based on Large Eddy Simulation(LES) shows better resolution of flame structures.
+				\pause
+				\item
+					Flamelet modeling based on the filtered G.E. is physically effective for combustion problem.
+			\end{itemize}	
+		\end{xframe}
+	\subsection{part4.2}
 		\begin{xframe}{Reference}

### 2019-04-24 VG500/HW6/submission.tex
hw6 done

--- 2019-04-02 VG500/HW3/submission.tex
@@
 \usepackage{pdfpages}
+\usepackage{multirow}
 
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Technical Communication\\ HW3 \\ % The assignment title
+\huge Technical Communication\\ HW6 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\section{Mind Map}
-	\begin{figure}[!h]
+\section{Slides in \LaTeX}
+	Please refer to ``../ex1/slide.pdf'' and ``../ex1/slide.tex''.
+
+\section{Writting}
+	\subsection*{First version}
+		Turbulence combustion consists of complex flow and combustion phenomenon.
+Based on the model of flamelet, progress variable-flamelet model was developed for simulation of turbulence combustion.
+The progress variable was introduced to describe the complicated combustion phenomenon, such as local extinction and re-ignition.
+In my project, In order to exam the LES based on progress variable-flamelet model, I have been trying to apply this model to the simulation of diffusion jet flame, especially investigating the accuracy and availability of this model under the conditions of different Reynolds number, inflow profiles, and ignition approaches.
+	\subsection*{Modified version}
+		The research focuses on developing the progress variable flamelet model for simulating the turbulence combustion.
+There are some common phenomenon in turbulence combustion, e.g.
+local extinction and re-ignition, bringing great trouble to the simulation.
+And progress variable is very suitable to describe them.
+Large-eddy simulation(LES) is one of the most popular simulation methods in combustion field, and it is combined with variable-flamelet model for the simulation of diffusion jet flame in his project.
+The details include investigating the performance of this method under different combustion conditions.
+	\subsection*{Final version}
+		Focusing on developing the progress variable flamelet model for the simulation of turbulent combustion, the research is combining Large-eddy simulation(LES) with variable flamelet model, for diffusion jet flame simulation.
+Some complicated phenomenon in turbulence combustion, e.g.
+local extinction and re-ignition, bring great trouble to the simulation.
+And progress variable is developed to describe them.
+On the other hand, Large-eddy simulation is one of
+		the most popular simulation methods in combustion field. To exam the availability of this combined model, a lot of numerical experiments under different conditions are proposed.
+
+\section{Group Exercise}
+	Please refer to Xuqing Zhou's submission, whose student ID is 118370910023.
+
+\section{Leonardo da Vinci}
+	This letter is excellent in terms of both contents and expressing skills. Generally, it is full of passion and confidence, which helps to make a positive atmosphere. \newline
+	Introductions are split into 10 parts, with each focusing on a specific topic. This makes the general structure looks much clear. \newline
+	In each part, active verbs and simple tense are used in the beginning to make it reads more powerful and reliable.
+Then, effects are vividly described.
+This is exactly the selling strategy "Sell the hole" does.\newline
+	Besides, rhetoric words are used properly, which make it looks polite and suitable. All aspects like target readers, contends, time and conditions are well considered. I think it's a good job.
+
+\section{IDEA survey}
+	\begin{figure}[h]
 		\centering
-		\includegraphics[width=13.5cm]{pic/mind_map.png}
-		\caption{How to write mathematics}
-		\label{fig:htwm}
+		\includegraphics[width=\linewidth]{IDEA.jpg}
 	\end{figure}
 
-\section{Group Exercise}
-	All the comments and discussions have been submitted to our team leader. Please see Rui Gao's work.
-
-\section{Writting skills}
-	\begin{enumerate}
-		\item 
-			``\textbf{Just act naturally}'': `naturally' is not suitable to be adverb for `act'.\newline
-			``\textbf{Please give your unbiased opinion}'': No objective in this sentence.\newline
-			``\textbf{I need an exact estimate by Friday}'': The two words: `exact' and `estimate' contradict with each other.
-
-		\item 
-			Before the agent was \sout{completely} able to \sout{finish} explain\sout{ing} the \sout{various} differences between \sout{all of} the \sout{many} outdoor event packages her company was offering, the customer changed his \sout{future} plans.
-	\end{enumerate}
-
-\section{\LaTeX}
-	See next page.
-	\includepdf[pages=2]{assignment.pdf}
-
 \end{document}

### 2019-04-26 VG500/WEEK9/20190426.tex
week9 summary

\documentclass[paper=a4, fontsize=11pt]{scrartcl}

\usepackage{lipsum}
\usepackage{amsmath, amsfonts, amssymb}

\title{Summary of "A conservative, thermodynamically consistent numerical approach for
	low Mach number combustion. Part I: Single-level integration"}
\author{Yu Cang \ \ 018370210001}
\date{2019-04-26}

\begin{document}

\maketitle
	In this paper, a numerical scheme targeting at variable density Navier-Stokes equations was proposed. This equation set is common in the research of combustion phenomenon. Details of this scheme was introduced. In general, it is based on the projection method, where the advection-diffusion equation is firstly solved to obtain the prediction of intermediate velocities, and then these velocities are projected onto a space of approximately divergence-free vector field.This method is of 2nd-order accuracy and validations has been performed to demonstrate the algorithm maintains the EOS.

\end{document}

### 2019-05-20 VM552/HW1/submission.tex
Hw1 done

--- 2018-10-06 VV556/HW3/submission.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Methods of Applied Mathematics I\\ HW3 \\ % The assignment title
+\huge Mechatronic Systems Design\\ HW1 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\author{Yu Cang \\ 018370210001} % Your name
+\author{Yu Cang \quad 018370210001} % Your name
 
@@
 
-\section{Exercise3.1}
+The autonomous drone is a new type of mechatronic system gaining popularity nowadays. 
+\section{Hardware}
+	Generally, it is based on the traditional multi-rotor configuration like Fig(\ref{fig:drone}), where 4 or 6 rotors are placed symmetrically around the central body.
+The central body contains power supply packages, controling unit and sensing facilities, with carbon fiber shell protecting them away from external dust, moist, or possible damage.
 
-\section{Exercise3.2}
+	\begin{figure}[!h]
+		\centering
+		\includegraphics[width=5cm]{pic/drone.jpg}
+		\caption{Autonomous drone}
+		\label{fig:drone}
+	\end{figure}
 
-\section{Exercise3.3}
+	Usually, a camera is mounted at the bottom for taking pictures or performing vision-based guiding.
+	For professional use, both laser radar and milimeter-wave radar are equipped for advanced perception.
+
+\section{Components}
+	The most important 3 components are
+	\begin{enumerate}
+		\item \textbf{Sensing Unit}\\
+			Usually, it is composed of accelerometer, gyroscope, barometer, geomagnetic sensor and GPS.These sensors are usually in chip format called MEMS, and can be mounted on the surface of PCB precisely, see Fig(\ref{fig:imu_pcb}).\\
+
+			\begin{figure}[!h]
+				\centering
+				\includegraphics[width=5cm]{pic/imu.png}
+				\caption{Sensing Unit PCB}
+				\label{fig:imu_pcb}
+			\end{figure}
+
+			\begin{enumerate}
+				\item \textit{Accelerometer}\\
+					It provides the inertial force info, and 3-axis pose(Roll Yaw, Pitch) can be estimated from acceleration in each axis.
+				\item \textit{Gyroscope}\\
+					It provides the angular velocity info. It is based on the conservation of angular momentum.
+				\item \textit{Barometer}\\
+					It provide the pressure of atomosphere, and height can be estimated.
+				\item \textit{Geomagnetic sensor}\\
+					Guiding the \textbf{North} direction.
+				\item \textit{GPS}\\
+					Global position like longtitude and latitude are provided. Timing is also available.
+			\end{enumerate}
+
+			In general, sensing unit provides the state of drone.
+
+		\item \textbf{Perception Facility}\\
+			To provide the infomation of environment, Radar, optical flow and ultrasonic sensor are integrated.
+
+			\begin{enumerate}
+				\item \textit{Laser Radar}\\
+					Usually in shape like Fig(\ref{fig:lidar}), for sensing obstacles around. It can also be done using an RGB-D camera.
+				\item \textit{Milimeter-wave Radar}\\
+					Barometer may not accurate, Radar has better resolution on determining height.
+				\item \textit{Optical Flow}\\
+					Local positioning and velocity estimation.
+				\item \textit{Ultrasonic sensor}\\
+					Sensing in a specific direction, it has similar function as LiDAR but shorter range.
+			\end{enumerate}
+
+			\begin{figure}[!htbp]
+				\centering
+				\begin{minipage}[t]{0.48\textwidth}
+					\centering
+					\includegraphics[width=5cm]{pic/lidar.png}
+					\caption{LiDAR}
+					\label{fig:lidar}
+				\end{minipage}
+				\begin{minipage}[t]{0.48\textwidth}
+					\centering
+					\includegraphics[width=5cm]{pic/radar.jpg}
+					\caption{Milimeter-wave Radar}
+					\label{fig:mm-wave}
+				\end{minipage}
+			\end{figure}
+
+		\item \textbf{Control Unit}\\
+			It do realtime response under both internal and external constraints. Signals in PWM form are generated to the electrical speed regulator to drive the motors. Usually, serial PID algorithm is used.
+
+	\end{enumerate}
+
+\section{Specifications}
+	Usually, this kind of automous drones can be used for agricultural, topographic or transportation purpose. Typically, the diameter ranges from 0.5 to 2m, and weighs 2 to 20kg.\\
+	Due to the energy density limit of lithium battery, endurance is usually about 20 minutes.\\
+	For safety issues, flight speed is usually lower than 5m/s, and flight height is restricted to 10m.
+
+\section{Challenges in design and control}
+	\begin{enumerate}
+		\item 
+			Data fusion.
+		\item 
+			Proper placement to minimize vibration.
+		\item 
+			PID param tuning.
+		\item 
+			Obstacle detection.
+		\item 
+			Reliable wireless communication.
+	\end{enumerate}
+
+\section{Future trends of developments}
+	\begin{enumerate}
+		\item 
+			Communication for long range and high fidelity.
+		\item 
+			Advanced and robust control algorithm.
+		\item 
+			Optimized aerodynamic shape design(For agricultural spray).
+		\item 
+			Higher energy density batteries or use gasoline.
+		\item 
+			More mature environment perception.
+	\end{enumerate}
 

### 2019-05-21 VM552/HW2/submission.tex
Hw2 done:

--- 2018-10-06 VV556/HW3/submission.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Methods of Applied Mathematics I\\ HW3 \\ % The assignment title
+\huge Mechatronic Systems Design\\ HW2 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\section{Exercise3.1}
-	\begin{proof}
-		Let $\phi(x) = (x^2 - 1)^n$, then
-		\begin{equation}
-			\phi(\pm 1) = \phi^{(1)}(\pm 1) = \cdots = \phi^{(n-1)}(\pm 1) = 0
-		\end{equation}
-		The $L^2$ norm of $P_n(x)$ is
-		\begin{equation}
-			\begin{aligned}
-				||P_n||_2  & = \sqrt{\int_{-1}^{1} P_n^2(x) dx}\\
-						   & = \sqrt{(\frac{1}{2^n n!})^2 \int_{-1}^{1} [\phi^{(n)}(x)]^2 dx}\\
-						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n \int_{-1}^{1} \phi^{(2n)}(x) \phi(x) dx} \quad \text{(Integrate by parts)}\\
-						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n (2n)! \int_{-1}^{1} (x^2 - 1)^n dx}\\
-						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n (2n)! \cdot 2 \int_{0}^{\frac{\pi}{2}} (sin^2(x) - 1)^n cos(x) dx}\\
-						   & = \sqrt{(\frac{1}{2^n n!})^2 (2n)! \cdot 2 \int_{0}^{\frac{\pi}{2}} cos^{2n+1}(x) dx}\\
-			\end{aligned}
-		\end{equation}
-		Since
-		\begin{equation}
-			\int_{0}^{\frac{\pi}{2}} cos^{2n+1}(x) dx = \frac{2 \times 4 \times \cdots \times (2n)}{1\times3\times \cdots \times (2n+1)} 
-		\end{equation}
-		substitute it into the norm equation of $P_n$ yields
-		\begin{equation}
-			||P_n||_2 = \sqrt{(\frac{1}{2^n n!})^2 (2n)! \cdot 2 \cdot \frac{2 \times 4 \times \cdots \times (2n)}{1\times3\times \cdots \times(2n+1)}} = \sqrt{\frac{2}{2n+1}}
-		\end{equation}
-	\end{proof}
+\section*{Problem1}
+	The higher the primary excitation frequency is, the more precise resolution will be. If the frequency is not higher enough, it will be mixed with the core motion.\newline
 
-\section{Exercise3.2}
+	The cut-off frequency of the low-pass filter must be choosen carefully to preserve core motion info and discard frequency induced by rectified wave.
 
-\section{Exercise3.3}
+\section*{Problem2}
+	\begin{enumerate}
+		\item 
+			It usually consists of a rotating shaft(rotor) with a primary winding and a stationary housing(stator) with two secondary windings offset by $90^\circ$. \newline
+
+			When the primary is exited with an AC signal, AC voltages are induced in the secondary coils, which are proportional to the sine and cosine of the shaft angle.
+Thus, the real angle can be resolved using function like $\theta = atan(V_s, V_c)$.
+
+		\item 
+			Resolution, Excitation voltage, Excitation frequency, Input impedance, Output voltage, Phase shift, Maximum angular velocity.
+		\item 
+			Pros: Simple structure, Reliable, Robust, High precision.\newline
+			Cons: Analog output make it uneasy to resolve real angle.
+
+		\item 
+			High precision machine tool: monitor shaft angle.\\
+			Power plant: monitor rotor status.\\
+			Robot: detect ankle pose.\\
+			Aircraft: monitor flap deflection angle.
+
+	\end{enumerate}
 

### 2019-05-28 VM552/HW3/submission.tex
HW3 done

--- 2018-10-06 VV556/HW3/submission.tex
@@
 \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
-\huge Methods of Applied Mathematics I\\ HW3 \\ % The assignment title
+\huge Mechatronic Systems Design\\ HW3 \\ % The assignment title
 \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
@@
 
-\section{Exercise3.1}
-	\begin{proof}
-		Let $\phi(x) = (x^2 - 1)^n$, then
-		\begin{equation}
-			\phi(\pm 1) = \phi^{(1)}(\pm 1) = \cdots = \phi^{(n-1)}(\pm 1) = 0
-		\end{equation}
-		The $L^2$ norm of $P_n(x)$ is
-		\begin{equation}
-			\begin{aligned}
-				||P_n||_2  & = \sqrt{\int_{-1}^{1} P_n^2(x) dx}\\
-						   & = \sqrt{(\frac{1}{2^n n!})^2 \int_{-1}^{1} [\phi^{(n)}(x)]^2 dx}\\
-						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n \int_{-1}^{1} \phi^{(2n)}(x) \phi(x) dx} \quad \text{(Integrate by parts)}\\
-						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n (2n)! \int_{-1}^{1} (x^2 - 1)^n dx}\\
-						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n (2n)! \cdot 2 \int_{0}^{\frac{\pi}{2}} (sin^2(x) - 1)^n cos(x) dx}\\
-						   & = \sqrt{(\frac{1}{2^n n!})^2 (2n)! \cdot 2 \int_{0}^{\frac{\pi}{2}} cos^{2n+1}(x) dx}\\
-			\end{aligned}
-		\end{equation}
-		Since
-		\begin{equation}
-			\int_{0}^{\frac{\pi}{2}} cos^{2n+1}(x) dx = \frac{2 \times 4 \times \cdots \times (2n)}{1\times3\times \cdots \times (2n+1)} 
-		\end{equation}
-		substitute it into the norm equation of $P_n$ yields
-		\begin{equation}
-			||P_n||_2 = \sqrt{(\frac{1}{2^n n!})^2 (2n)! \cdot 2 \cdot \frac{2 \times 4 \times \cdots \times (2n)}{1\times3\times \cdots \times(2n+1)}} = \sqrt{\frac{2}{2n+1}}
-		\end{equation}
-	\end{proof}
+\section*{Problem1}
+	\begin{itemize}
+		\item Q: Investigate and explain the coding for the disk of an absolute encoder.
 
-\section{Exercise3.2}
+		\item A: Inside an absolute encoder, there're serval concentric tracks on the code disk.
+				 Each track represents a bit, combining these bits yields a digital word. 
+		Each digital word corresponds to a unique rotational position of the shaft. 
+		Thus, the absolute position of the shaft can be identified easily.\\
+		The most common types of numerical encoding used are gray and natural binary codes.
+Natural binary code is straight forward but may suffer from mutiple changes of bits in one transition.
+Usually, the gray code is preferred as only one bit changes state for each count transition.
 
-\section{Exercise3.3}
+	\end{itemize}
+
+\section*{Problem2}
+	\begin{itemize}
+		\item 
+			Q: Investigate and explain how does the hall sensors in the ABS work to measure the wheel velocity in a reasonable accuracy? Note that the sensor is essentially a low-resolution position sensor.
+
+		\item 
+			A: A typical configuration is shown as Fig(\ref{fig:hall}).
+Each time a gear teeth is opposed to the magnet, a peak voltage is generated.
+Thus the velocity can be measured from the gap between two pauses.
+
+			\begin{figure}[!htbp]
+				\centering
+				\includegraphics{hall.jpeg}
+				\caption{Hall sensor in ABS}
+				\label{fig:hall}
+			\end{figure}
+
+	\end{itemize}
 

### 2019-05-29 VM552/HW4/tex/submission.tex
HW4 done

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages

\usepackage{algorithm, algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}} %Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm

\usepackage{graphicx}

\usepackage{listings}
\lstset{language=Matlab}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Mechatronic Systems Design\\ HW4 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yu Cang \quad 018370210001} % Your name

\date{\normalsize \today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title

\section*{Problem1}
	\begin{itemize}
		\item
			 Q: A spring-mass-damper vibrometer is designed with a seismic mass of 1 kg, a coil spring of spring constant 2 N/m, and a dashpot with damping constant 2Ns/m. Determine an expression for the steady state displacement of the seismic mass $\textbf{x}_{out}(t)$ given an object input displacement of $\textbf{x}_{in}(t)=10sin(1.25t)$ mm.

		\item
			 A:  Let $\textbf{x}_r = \textbf{x}_{out} - \textbf{x}_{in}$, then the G.E. of $\textbf{x}_r$ is

			 \begin{equation}
			 	\ddot{\textbf{x}}_r + 2 \xi \omega_n \dot{\textbf{x}}_r + {\omega_n}^2\textbf{x}_r = -\ddot{\textbf{x}}_{in} 
			 \end{equation}

			 where the natural frequence is $\omega_n = \sqrt{\frac{k}{m}} = \sqrt{2}$ rad/s, and the damping ratio is $\xi = \frac{b}{2\sqrt{k\cdot m}} = \frac{\sqrt{2}}{2}$. With $\textbf{x}_{in}(t)=10sin(1.25t)$, denoting $X_{in}= 10$ mm and $\omega = 1.25$ rad/s, solution of $\textbf{x}_r$ can be expressed as:

			 \begin{equation}
			 	\textbf{x}_r(t) = X_rsin(\omega t + \phi)
			 \end{equation}

			 Since

			 \begin{equation}
			 	\frac{X_r}{X_{in}} = \frac{(\frac{\omega}{\omega_n})^2}{\sqrt{\Big(1-(\frac{\omega}{\omega_n})^2\Big)^2 + 4 \xi^2  (\frac{\omega}{\omega_n})^2}} \approxeq 0.616
			 \end{equation}

			 and

			 \begin{equation}
				\phi = -atan\Big(\frac{2\xi(\frac{\omega}{\omega_n})}{1-(\frac{\omega}{\omega_n})^2}\Big) \approxeq -1.398
			 \end{equation}

			 Thus, $\textbf{x}_r(t) = 6.16 sin(1.25t -1.398)$. \\
			 Hence $\textbf{x}_{out} = \textbf{x}_r + \textbf{x}_{in} = 6.16 sin(1.25t -1.398) + 10sin(1.25t)$

	\end{itemize}

\section*{Problem2}
	\begin{itemize}
		\item 
			Q: Investigate so-called ``impedance control'' for the applications involving multiple robots and the interaction between machine and human; use an example to explain principle of this control and why the feedback of force such as using load cells is important (one piece of A4 paper with proper references; IEEE journal paper template is preferred).

		\item 
			A: ``Impedance control'' is an approach to dynamically control relating force and position. It is often used in applications where a manipulator interacts with its environment and the force position relation is of concern.

			\begin{figure}[!ht]
				\centering
				\includegraphics[height=5cm]{../pic/door.png}
				\caption{Typical scene when openning a door}
				\label{fig:door}
			\end{figure}

			Take a simple case for illustration, where a robot arm is trying to open the door shown in Fig(\ref{fig:door}). In traditional control strategy, the robot arm will move along the circle precisely. However, the actual track programmed by robot may be different due to noises like sensing errors. This is illustrated in Fig(\ref{fig:track}). In this case, the door will be broken by the robot arm or the robot arm will be pulled apart as the track of door edge will not change.

			\begin{figure}[!ht]
				\centering
				\includegraphics[height=5cm]{../pic/track.png}
				\caption{Real track of the robot arm}
				\label{fig:track}
			\end{figure}

			A simple remedy is to add a spring in between like Fig(\ref{fig:spring}). In this way, errors are absorbed into the spring.

			\begin{figure}[!ht]
				\centering
				\includegraphics[height=5cm]{../pic/robot.png}
				\caption{Robot arm with spring}
				\label{fig:spring}
			\end{figure}

			Also, friction is need to prevent endless vibration of the spring, which results in the 2nd-order ``Mass-Spring-Damper'' system shown in Fig(\ref{fig:arm}).

			\begin{figure}[!ht]
				\centering
				\includegraphics[height=5cm]{../pic/msd.png}
				\caption{Mass-Spring-Damper system}
				\label{fig:arm}
			\end{figure}

			Thus, the behaviour of this system can be described as follows:

			\begin{equation}
				M\frac{d^2 \textbf{x}}{d t^2} + b\frac{d \textbf{x}}{d t} + k \textbf{x} = \textbf{F} + \textbf{F}_{ext}\label{eq:newton}
			\end{equation}

			Impededance control is to modify $\textbf{F}$ according to measured position and difference to target track\cite{ref1}. This is usually done by changing the torque at joints. In this way, Eq(\ref{eq:newton}) can be re-formulated as

			\begin{equation}
				\textbf{F} = M\frac{d^2 \textbf{x}}{d t^2} + b\frac{d \textbf{x}}{d t} + k \textbf{x} - \textbf{F}_{ext}\label{eq:impedence}
			\end{equation}

			In order to provide suitable experience when interacting with human beings, the magnitude of \textbf{F} needs to be controlled exactly. Thus, a sensor measuring \textbf{F} is needed to provide feedback to controller. This is usually done by using a load cell.

	\end{itemize}

\begin{thebibliography}{16}  
	\bibitem{ref1}C. Ott, R. Mukherjee and Y. Nakamura, "Unified Impedance and Admittance Control," 2010 IEEE International Conference on Robotics and Automation, Anchorage, AK, 2010, pp. 554-561.
	doi: 10.1109/ROBOT.2010.5509861
\end{thebibliography}

\end{document}
